### 2019-04-11 README.Rmd
readme updated

---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, echo = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "README-"
)
# Please put your title here to include it in the file below. 
Title <- "Title of your paper goes here"
```

# vmacfeaturesearch

This repository contains the data and code for our project investigating whether overt attention to reward-related distractors can be suppressed under feature search conditions in the same way as for physically salient distractors (see Gaspelin, Leonard, & Luck, 2017 - Attn Percept Psychophys).

<!-- Our pre-print is online here:

> Authors, (YYYY). _`r Title`_. Name of journal/book, Accessed `r format(Sys.Date(), "%d %b %Y")`. Online at <https://doi.org/xxx/xxx>

### How to cite

Please cite this compendium as:

> Authors, (`r format(Sys.Date(), "%Y")`). _Compendium of R code and data for `r Title`_. Accessed `r format(Sys.Date(), "%d %b %Y")`. Online at <https://doi.org/xxx/xxx>  -->

### How to download or install

You can download the compendium as a zip from from this URL: <https://github.com/danielpearson90/vmacfeaturesearch/archive/master.zip>

Or you can install this compendium as an R package, vmacfeaturesearch, from GitHub with:
```{r gh-installation, eval = FALSE}
# install.packages("devtools")
devtools::install_github("danielpearson90/vmacfeaturesearch")
```
### Licenses

**Text and figures :**  [CC-BY-4.0](http://creativecommons.org/licenses/by/4.0/), Copyright (c) 2019 Daniel Pearson.

**Code :** See the [DESCRIPTION](DESCRIPTION) file

**Data :** [CC-BY-4.0](http://creativecommons.org/licenses/by/4.0/), Copyright (c) 2019 Daniel Pearson.

### Contributions

We welcome contributions from everyone. Before you get started, please see our [contributor guidelines](CONTRIBUTING.md). Please note that this project is released with a [Contributor Code of Conduct](CONDUCT.md). By participating in this project you agree to abide by its terms.

### 2019-04-11 analysis/paper/paper.Rmd
raw data files added

---
title: "Title Goes Here"
author:
  - Author One
  - Author Two
date: "`r format(Sys.time(), '%d %B, %Y')`"
output: 
    bookdown::html_document2:
      fig_caption: yes
      reference_docx: "../templates/template.docx" # Insert path for the DOCX file
bibliography: references.bib
csl: "../templates/journal-of-archaeological-science.csl" # Insert path for the bib-style
abstract: |
  Text of abstract
keywords: |
  keyword 1; keyword 2; keyword 3
highlights: |
  These are the highlights. 
---

<!-- This is the format for text comments that will be ignored during renderings. Do not put R code in these comments because it will not be ignored. -->

```{r, setup, echo = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  warning = FALSE,
  message = FALSE,
  echo = FALSE,
  comment = "#>",
  fig.path = "../figures/"
)

library(vmacfeaturesearch) # Or use devtools::load_all('.', quiet = T) if your code is in script files, rather than as functions in the `/R` diretory
```

# Introduction

Here is a citation [@Marwick2017]

# Background

```{r demo, eval = FALSE}
1 + 1
```

# Methods

# Results

```{r get-data, eval = FALSE}
# Note the path that we need to use to access our data files when rendering this document
my_data <- readr::read_csv(here::here('analysis', 'data', 'raw_data', 'my_csv_file.csv'))
```

# Discussion

# Conclusion

# Acknowledgements

<!-- The following line inserts a page break when the output is MS Word. For page breaks in PDF, use \newpage on its own line.  -->
##### pagebreak

# References 
<!-- The following line ensures the references appear here for the MS Word or HTML output files, rather than right at the end of the document (this will not work for PDF files):  -->
<div id="refs"></div>

##### pagebreak

### Colophon

This report was generated on `r Sys.time()` using the following computational environment and dependencies:

```{r colophon, cache = FALSE}
# which R packages and versions?
devtools::session_info()
```

The current Git commit details are:

```{r}
# what commit is this file at? 
git2r::repository(here::here())
```

### 2019-04-11 analysis/analysis_report.rmd
added necessary functions and started report

---
title: "Analysis_Report"
author: "Daniel Pearson"
date: "11 April 2019"
output: html_document
editor_options: 
  chunk_output_type: console
---

```{r setup, include=FALSE, echo=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
library(R.matlab)
library(afex)
library(emmeans)
library(here)
library(patchwork)
library(cowplot)
library(BayesFactor)
```

### 2019-04-11 R/dp_pal.R

@@ -1,0 +1,7 @@
+#' Qualitative colour palette
+dp_pal <- function() {
+  pal <- c("#E69F00", "#56B4E9", "#009E73", "#F0E442", "#0072B2", "#D55E00",
+           "#CC79A7", "#000000", "#999999")
+
+  pal
+}

### 2019-04-11 R/ds_calculator.r

@@ -1,0 +1,24 @@
+#' Calculator for d<sub>s</sub> (between subjects effect size)
+#'
+#' Calculator for d<sub>s</sub> (between subjects effect size)
+#' @param x,y vectors of the DV for each group
+#' @export
+#' @examples ds_calculator()
+
+ds_calculator <- function(group1, group2) {
+
+  mean1 <- mean(group1)
+  sd1 <- sd(group1)
+  n1 <- length(group1)
+
+  mean2 <- mean(group2)
+  sd2 <- sd(group2)
+  n2 <- length(group2)
+
+  ds <- (mean1 - mean2)/
+    (sqrt(
+        ((n1-1)*sd1^2 + (n2-1)*sd2^2)/
+          (n1 + n2 - 2)))
+
+  return(abs(ds))
+}

### 2019-04-11 R/summarySEwithin2.r

@@ -1,0 +1,95 @@
+#' Calculate standard error
+summarySE2 <- function (data = NULL, measurevar, groupvars = NULL, na.rm = TRUE, conf.interval = 0.95) {
+  library(data.table)
+  data <- data.table(data)
+
+  length2 <- function(x, na.rm = FALSE) {
+    if (na.rm)
+      sum(!is.na(x))
+    else length(x)
+  }
+
+  datac <- data[, .(unlist(lapply(.SD, length2, na.rm = na.rm)),
+                    unlist(lapply(.SD, mean, na.rm = na.rm)),
+                    unlist(lapply(.SD, sd, na.rm = na.rm))),
+                by = groupvars, .SDcols = measurevar]
+  names(datac) <- c(groupvars, "N", measurevar, "sd")
+  setkeyv(datac, groupvars)
+
+  datac[, se := unlist(sd) / sqrt(unlist(N))] #compute standard error
+
+  ciMult <- qt(conf.interval / 2 + 0.5, unlist(datac$N) - 1)
+  datac[, ci := se * ciMult]
+  datac <- data.frame(datac)
+  return(datac)
+}
+#' Normalize for within subjects standard error calculation
+normDataWithin2 <- function (data = NULL, idvar, measurevar, betweenvars = NULL,
+                             na.rm = TRUE) {
+  library(data.table); library(dplyr)
+  data <- data.table(data)
+  setkeyv(data, idvar)
+
+  data.subjMean <- data[, .(unlist(lapply(.SD, mean, na.rm = na.rm))), by = idvar, .SDcols = measurevar]
+  names(data.subjMean) <- c(idvar, 'subjMean')
+  data <- merge(data, data.subjMean)
+  setkeyv(data, c(idvar, betweenvars))
+
+  measureNormedVar <- paste(measurevar, "Normed", sep = "")
+  data <- data.frame(data)
+
+  data[, measureNormedVar] <- data[, measurevar] - unlist(data[, "subjMean"]) + mean(data[, measurevar], na.rm = na.rm)
+  return(data)
+}
+
+
+#' Calculate within-subjects standard error
+summarySEwithin2 <- function (data = NULL, measurevar, betweenvars = NULL, withinvars = NULL,
+                              idvar = NULL, na.rm = TRUE, conf.interval = 0.95) {
+
+  # Ensure that the betweenvars and withinvars are factors
[…]

### 2019-04-11 R/theme_dp.R

@@ -1,0 +1,139 @@
+#' Personal Light Theme
+#'
+#' Personal [ggplot2] theme for manuscript figures, based heavily on the package: hrbrthemes (https://github.com/hrbrmstr/hrbrthemes)
+#' @param base_family,base_size base font family and size
+#' @param plot_title_family,plot_title_face,plot_title_size,plot_title_margin plot title family, face, size and margi
+#' @param subtitle_family,subtitle_face,subtitle_size plot subtitle family, face and size
+#' @param subtitle_margin plot subtitle margin bottom (single numeric value)
+#' @param strip_text_family,strip_text_face,strip_text_size facet label font family, face and size
+#' @param caption_family,caption_face,caption_size,caption_margin plot caption family, face, size and margin
+#' @param axis_title_family,axis_title_face,axis_title_size axis title font family, face and size
+#' @param axis_title_just axis title font justification, one of `[blmcrt]`
+#' @param plot_margin plot margin (specify with [ggplot2::margin()])
+#' @param grid_col,axis_col grid & axis colors; both default to `#cccccc`
+#' @param grid panel grid (`TRUE`, `FALSE`, or a combination of `X`, `x`, `Y`, `y`)
+#' @param axis_text_size font size of axis text
+#' @param axis add x or y axes? `TRUE`, `FALSE`, "`xy`"
+#' @param ticks ticks if `TRUE` add ticks
+#' @export
+#' @examples theme_dp()
+theme_dp <- function(base_family="Roboto Condensed",
+                     base_size = 12,
+                     plot_title_family = base_family,
+                     plot_title_size = 18,
+                     plot_title_face ="bold",
+                     plot_title_margin = 10,
+                     subtitle_family = base_family,
+                     subtitle_size = 12,
+                     subtitle_face = "plain",
+                     subtitle_margin = 15,
+                     strip_text_family = base_family,
+                     strip_text_size = 12,
+                     strip_text_face = "plain",
+                     caption_family = base_family,
+                     caption_size = 9,
+                     caption_face = "italic",
+                     caption_margin = 10,
+                     axis_text_size = base_size,
+                     axis_title_family = subtitle_family,
+                     axis_title_size = base_size,
[…]

### 2019-04-11 R/vmac_pal.R

@@ -1,0 +1,20 @@
+#' Qualitative colour palette for standard VMAC colours
+#'
+#' Qualitative colour palette for standard VMAC colours
+#' @param high,low,absent,other TRUE/FALSE to pull colour for each trial type
+#' @export
+#' @examples vmac_pal()
+
+vmac_pal <- function(high = TRUE, low = TRUE, absent = TRUE, other = FALSE) {
+  pal <- c("#E69F00", "#56B4E9", "#009E73", "#F0E442", "#0072B2", "#D55E00",
+           "#CC79A7", "#000000", "#999999")
+
+  if (high) {a = 1} else {a = NA}
+  if (low) {b = 2} else {b = NA}
+  if (absent) {c = 9} else {c = NA}
+  if (other) {d = 3} else {d = NA}
+
+  pal <- pal[c(a,b,d,c)]
+  pal <- pal[!is.na(pal)]
+  pal
+}

### 2019-04-11 analysis/analysis_report.rmd
up to omission trial reward analysis

@@
 library(BayesFactor)
+library(hrbrthemes)
+library(ggsignif)
+
+vmacCols <- vmac_pal()
+my_theme <- theme_ipsum_rc(grid = F, axis_title_just = "c", axis_title_size = 14, axis_text_size = 12, strip_text_size = 14, plot_title_size = 14, subtitle_size = 14, ticks = T) +
+  theme(legend.position = "none", 
+        plot.margin = margin(.5,1,.5,1,"cm"),
+        axis.line = element_line(colour = "black", size = .5),
+        axis.ticks.x = element_blank(),
+        axis.ticks.y = element_line(colour = "black", size = .5),
+        #aspect.ratio = 1.1,
+        plot.tag = element_text(size = 20, family = font_rc),
+        axis.title = element_text(margin = margin(12,1,1,1, unit = "cm")),
+        axis.text.x = element_text(margin = margin(t = 4, unit = 'pt'), colour = 'black'),
+        axis.text.y = element_text(margin = margin(r = 4, unit = 'pt'), colour = 'black'),
+        axis.title.x = element_text(margin = margin(t = 8, unit = 'pt')),
+        axis.title.y = element_text(margin = margin(r = 8, unit = 'pt')),
+        legend.text = element_text(size = 14),
+        legend.title = element_text(size = 14))
+
 ```
+
+# Behavioural Analysis
+
+```{r Load Behavioural Data, include=FALSE}
+files <- dir(path = here::here("analysis", "data", "raw_data", "BehavData"), pattern = "*.mat")
+
+filedata <- here::here("analysis", "data", "raw_data", "BehavData", files) %>%
+  map(readMat) %>%
+  map("DATA")
+```
+
+```{r Tidy Behavioural Data, include = FALSE}
+#This is some messy code that lets us tidy the exptTrialInfo data from the nested .mat struct files
+
+subNums <- filedata %>%
+  map(1) %>%
+  flatten() %>%
+  map_dbl(1)
+
+exptdata <- filedata %>%
+  map(24) %>%
+  map(2) %>%
+  modify(as.data.frame)
+
+counterbals <- filedata %>%
+  map(2) %>%
+  flatten() %>%
+  map_dbl(1)
+
+ages <- filedata %>%
+  map(10) %>%
+  flatten() %>%
+  map_dbl(1)
+
+ages_summ <- ages %>%
+  tibble() %>% 
+  rename("age" = ".")%>%
+  summarise(m = mean(age, na.rm = T), stdev = sd(age))
+
+bonuses <- filedata %>%
+  map(17) %>%
+  flatten() %>% 
+  map_dbl(1)
+
+bonuses_sum <- bonuses %>%
+  tibble() %>% 
+  rename("bonus" = ".") %>%
+  summarise(m = mean(bonus, na.rm = T), stdev = sd(bonus))
+
+genders <- filedata %>%
+  map(11) %>%
+  flatten()  %>%
+  map_chr(1) %>%
+  tolower()
+
+genders_summ <- genders %>%
+  as.factor() %>% 
+  tibble() %>% 
+  rename("gender" = ".") %>%
+  count(gender)
+
+exptdata <- Map(cbind, exptdata, sub = subNums, counterbal = counterbals, age = ages, gender = genders) %>%
+  bind_rows()
+
+colnames(exptdata)[1:24] <- c("block", "trial", "trialCounter", "trials_since_break", "targetLoc", "targetType", "distractLoc", "distractShape", "distractType", "fixationTime", "fixationPropGoodSamples", "fixationTimeout", "trialPropGoodSamples", "timeout", "softTimeoutTrial", "omissionTrial", "rt", "trialPay", "sessionPay", paste("timeOnLoc", c(1:5)))
+
+exptdata <- exptdata %>%
+  mutate(condition = if_else(counterbal %in% c(1,2), "Singleton Search", "Feature Search"))
+
+exptdata <- exptdata %>% 
+  mutate(gender = tolower(gender)) %>% 
+  mutate(dType = factor(distractType, levels = c(1,2,3), labels = c("High", "Low", "Absent")))
+```
+
+```{r Remove participants with poor gaze data}
+propCutoff <- .5
+allTracks <- exptdata %>%
+  group_by(sub) %>%
+  summarise(fixationProp = mean(fixationPropGoodSamples),
+            trialProp = mean(trialPropGoodSamples))
+
+poortracks <- allTracks %>%
+  filter(fixationProp < propCutoff | trialProp < propCutoff)
+
+allTracks <- allTracks %>%
+  filter(!sub %in% poortracks$sub)
+
+allTracks_summ <- allTracks %>%
+  summarise(mean_fixation_prop = round(mean(fixationProp)*100, 1), sd_fixation_prop = round(sd(fixationProp)*100, 1), mean_trial_prop = round(mean(trialProp)*100, 1), sd_trial_prop = round(sd(trialProp)*100,1))
+
+exptdata <- exptdata %>%
+ filter(!sub %in% poortracks$sub)
+```
+
+We removed data for any participants who did not have sufficient quality gaze data.
+If participants have an average of less than `r propCutoff*100`% valid gaze data during the fixation period or during a trial, they are removed from the data set.
+
+`r length(poortracks)` participants were removed due to having a poor track.
+
+```{r Remove participants for any other reasons}
+
+remove_p_numbers <- c(37)
+
+#  check to make sure that everyone has completed the full 480 trials
+didNotComplete <- exptdata %>%
+  group_by(sub) %>%
+  filter(block > 0) %>%
+  tally() %>%
+  filter(n < 480) %>%
+  select(sub)
+
+# remove those that did not complete the full expt
+remove_p_numbers <- c(remove_p_numbers, didNotComplete$sub)
+
+exptdata <- exptdata %>%
+  filter(!sub %in% remove_p_numbers)
+```
+
+`r length(remove_p_numbers)` participants were removed for other reasons (participant #37 they thought that they needed to look at the coloured circle in order to earn rewards, participant #26 and #85 did not complete the experiment due to difficulty tracking their eyes).
+
+Then we remove the first two trials of the experiment, the first two trials after breaks, and timeouts from the data (in line with previous VMAC analysis protocols):
+
+```{r Additional data exclusions}
+# first we determine the percentage of trials that were timeouts (for reporting in the MS)
+hardtimeouts <- exptdata %>%
+  group_by(timeout) %>%
+  summarise(n = n()) %>%
+  mutate(perc = round(n/sum(n)*100, 1))
+
+exptdata <- exptdata %>%
+  filter(trial > 2 & trials_since_break > 2) %>% #removing first two trials and trials after breaks
+  filter(timeout != 1) # removing timeouts
+```
+
+## Omission Trials
+```{r Omission Trial Means}
+exptdata_means_byparticipant <- exptdata %>%
+  ungroup() %>%
+  group_by(sub, condition, dType) %>%
+  summarise(m = mean(omissionTrial))
+
+exptdata_means_bycondition <- summarySEwithin2(data = exptdata_means_byparticipant, measurevar = "m", betweenvars = "condition", withinvars = "dType", idvar = "sub") %>%
+  select(-ends_with("Normed"))
+```
+
+```{r Omission Trial Graph}
+
+omissionPlot_singleton <- exptdata %>%
+  filter(condition == "Singleton Search") %>%
+  group_by(sub, dType) %>%
+  summarise(m = mean(omissionTrial)) %>%
+  ggplot(aes(x = dType, y = m, fill = dType, shape = dType)) +
+  geom_errorbar(data = filter(exptdata_means_bycondition, condition == "Singleton Search"), aes(x = dType, y = m, ymin = m-se, ymax = m+se), colour = "black", width = .15) +
+  geom_line(aes(group = sub), colour = "black", alpha = .1, linetype = "solid", size = .5) +
+  geom_line(data = filter(exptdata_means_bycondition, condition == "Singleton Search"), aes(x = dType, y = m, group = 1), colour = "black") + 
+  geom_point(data = filter(exptdata_means_bycondition, condition == "Singleton Search"), aes(x = dType, y = m), colour = "black", size = 3) +
+  geom_signif(comparisons = list(c("High", "Low"), c("Low", "Absent")), annotations = c("***","*"), y_position = c(.61,.57), colour = "black", tip_length = 0) +
+  scale_y_continuous(labels = scales::percent_format(accuracy = 1), expand = c(0,0), limits = c(0,.8)) +
+  scale_x_discrete(labels = c("High\nreward", "Low\nreward", "Distractor\nabsent")) +
+  scale_fill_manual(values = vmacCols) +
+  scale_colour_manual(values = vmacCols) +
+  scale_shape_manual(name = "Trial Type", guide = guide_legend(), values = c(21,22,23)) +
+  labs(y = "% Reward Omissions", x = "Trial Type", tag = "A", title = "Singleton Search") +
+  my_theme
+
+omissionPlot_feature <- 
+  exptdata %>%
+  filter(condition == "Feature Search") %>%
+  group_by(sub, dType) %>%
+  summarise(m = mean(omissionTrial)) %>%
+  ggplot(aes(x = dType, y = m, fill = dType, shape = dType)) +
+  geom_line(aes(group = sub), colour = "black", alpha = .1, linetype = "solid", size = .5) +
+  geom_errorbar(data = filter(exptdata_means_bycondition, condition == "Feature Search"), aes(x = dType, y = m, ymin = m-se, ymax = m+se), colour = "black", width = .15) +
+  geom_line(data = filter(exptdata_means_bycondition, condition == "Feature Search"), aes(x = dType, y = m, group = 1), colour = "black") + 
+  geom_point(data = filter(exptdata_means_bycondition, condition == "Feature Search"), aes(x = dType, y = m), colour = "black", size = 3) +
+  geom_signif(comparisons = list(c("High", "Low"), c("Low", "Absent")), annotations = c("***","***"), y_position = c(.61,.57), colour = "black", tip_length = 0) +
+  scale_y_continuous(labels = scales::percent_format(accuracy = 1), expand = c(0,0), limits = c(0,.8)) +
+  scale_x_discrete(labels = c("High\nreward", "Low\nreward", "Distractor\nabsent")) +
+  scale_fill_manual(values = vmacCols) +
+  scale_shape_manual(name = "Distractor Type", guide = guide_legend(), values = c(21,22,23)) +
+  labs(y = "% Reward Omissions", x = "Trial Type", tag = "B", title = "Feature Search") +
+  my_theme
+
+omissionPlot_ms <- omissionPlot_singleton / omissionPlot_feature
+
+save_plot(here::here("analysis", "figures", "omission_plot.png"), omissionPlot_ms, ncol = 1, nrow = 2, type = "cairo", base_aspect_ratio = 1.1, dpi = 300)
+
+omissionPlot_ms
+
+```
+
+### Effect of Reward
+Effect of reward ANOVA:
+```{r Effect of Reward - Omissions}
+omissions_vmac.ANOVA <- aov_car(m ~ condition*dType + Error(sub/dType), data = filter(exptdata_means_byparticipant, dType != "Absent"), anova_table = list(es="pes"))
+```
+Significant main effect of reward (indicating VMAC effect), but no interaction with or main effect of search condition.
+
+Planned t-tests:
+```{r Effect of Reward - Omissions - Planned t-tests}
+singleton_high_omissions <- exptdata_means_byparticipant %>%
+  ungroup() %>%
+  filter(condition == "Singleton Search") %>%
+  filter(dType == "High") %>%
+  select(m) %>%
+  pull()
+
+singleton_low_omissions <-  exptdata_means_byparticipant %>%
+  ungroup() %>%
+  filter(condition == "Singleton Search") %>%
+  filter(dType == "Low") %>%
+  select(m) %>%
+  pull()
+
+feature_high_omissions <- exptdata_means_byparticipant %>%
+  ungroup() %>%
+  filter(condition == "Feature Search") %>%
+  filter(dType == "High") %>%
+  select(m) %>%
+  pull()
+
+feature_low_omissions <-  exptdata_means_byparticipant %>%
+  ungroup() %>%
+  filter(condition == "Feature Search") %>%
+  filter(dType == "Low") %>%
+  select(m) %>%
+  pull()
+
+singleton_VMAC_omissions.ttest <- t.test(singleton_high_omissions, singleton_low_omissions, paired = T)
+singleton_VMAC_omissions.es <- dz_calculator(singleton_high_omissions, singleton_low_omissions)
+feature_VMAC_omissions.ttest <- t.test(feature_high_omissions, feature_low_omissions, paired = T)
+feature_VMAC_omissions.es <- dz_calculator(feature_high_omissions, feature_low_omissions)
+
+vmac_singleton <- exptdata_means_byparticipant %>%
+  filter(dType != "Absent", condition == "Singleton Search") %>%
+  spread(dType, m) %>%
+  mutate(vmac = High - Low) %>%
+  pull(vmac)
+
+vmac_feature <- exptdata_means_byparticipant %>%
+  filter(dType != "Absent", condition == "Feature Search") %>%
+  spread(dType, m) %>%
+  mutate(vmac = High - Low) %>%
+  pull
+
+vmac_condition_bayes <- ttestBF(x = vmac_singleton, y = vmac_feature)
+```

### 2019-04-11 analysis/analysis_report.rmd
first saccade direction analysis

@@
 
+singleton_absent_omissions <- exptdata_means_byparticipant %>%
+  ungroup() %>%
+  filter(condition == "Singleton Search") %>%
+  filter(dType == "Absent") %>%
+  select(m) %>%
+  pull()
+
 feature_high_omissions <- exptdata_means_byparticipant %>%
@@
   filter(dType == "Low") %>%
+  select(m) %>%
+  pull()
+
+feature_absent_omissions <- exptdata_means_byparticipant %>%
+  ungroup() %>%
+  filter(condition == "Feature Search") %>%
+  filter(dType == "Absent") %>%
   select(m) %>%
@@
 ```
+
+### Effect of Physical Salience
+Effect of physical salience ANOVA:
+```{r Effect of Physical Salience - Omissions}
+omissions_salience.ANOVA <- aov_car(m ~ condition*dType + Error(sub/dType), data = filter(exptdata_means_byparticipant, dType != "High"), anova_table = list(es="pes"))
+
+omissions_salience.ANOVA
+```
+
+Planned t-tests:
+```{r Effect of Physical Salience - Omissions - Planned t-tests}
+singleton_physicalsalience_omissions.ttest <- t.test(singleton_low_omissions, singleton_absent_omissions, paired = T)
+
+singleton_physicalsalience_omissions.es <- dz_calculator(singleton_low_omissions, singleton_absent_omissions)
+
+feature_physicalsalience_omissions.ttest <- t.test(feature_absent_omissions, feature_low_omissions, paired = T) # reverse the order here so can get positive t value
+
+feature_physicalsalience_omissions.es <- dz_calculator(feature_low_omissions, feature_absent_omissions)
+```
+
+# Gaze Data Analyses
+
+```{r Load Gaze Data, include=FALSE}
+saccade_files <- dir(path = here::here("analysis", "data", "derived_data","ProcessedSaccadeData"), pattern = "^S")
+
+saccade_filedata <- here::here("analysis", "data", "derived_data","ProcessedSaccadeData", saccade_files) %>%
+  map(readMat) %>%
+  map("saccadeSessionData") %>%
+  map(1) %>%
+  map(2) %>%
+  modify(as.data.frame)
+```
+
+```{r Tidy Gaze Data, include = FALSE}
+# collapse the data into a dataframe format
+saccade_filedata <- saccade_filedata %>%
+  map_df(bind_rows)
+
+# give the columns appropriate headers
+colnames(saccade_filedata)[1:13] <- c("subj", "trial", "latency", paste("loc", c(1:5), sep = "_"), "discardTrial", "anticipatorySaccade", "outsideFixation", "noSaccades", "noValidData")
+
+discardSaccadeCounter <- saccade_filedata %>%
+  mutate(bad_data_discard = case_when(noSaccades == 1 ~ 1,
+                                      noValidData == 1 ~ 1,
+                                      TRUE ~ 0)) %>%
+  group_by(subj) %>%
+  summarise(prop_discarded = mean(discardTrial)*100, prop_anticipatory = mean(anticipatorySaccade)*100, prop_outside_fix = mean(outsideFixation)*100, prop_bad_data = mean(bad_data_discard)*100)
+
+totalSaccadeTrialsDiscarded <- discardSaccadeCounter %>%
+  summarise_all(mean) %>%
+  summarise_all(round, 1)
+
+saccade_filedata <- saccade_filedata %>%
+  filter(discardTrial != 1) %>% # discard trials marked to be discarded
+  mutate(first_saccade_loc = loc_1*1+loc_2*2+loc_3*3+loc_4*4+loc_5*5)
+
+saccadedata <- left_join(exptdata, saccade_filedata, by = c("sub" = "subj", "trial" = "trial")) %>% #join saccade data up with behavioural data
+  mutate(saccade_to_target = if_else(targetLoc == first_saccade_loc, 1, 0)) %>% # create variables indicating whether first saccade went towards the target...
+  mutate(saccade_to_singleton = if_else(dType == "Absent", 2, 
+                                        if_else(distractLoc == first_saccade_loc, 1, 0))) %>% # singleton (for all except distractor absent trials)
+  mutate(saccade_to_singleton = replace(saccade_to_singleton, saccade_to_singleton == 2, NA)) %>%
+  mutate(saccade_to_nonsingleton = if_else((dType != "Absent" & targetLoc != first_saccade_loc & distractLoc != first_saccade_loc & first_saccade_loc < 5) | (dType == "Absent" & targetLoc != first_saccade_loc & first_saccade_loc < 5), 1, 0)) %>% # or non-singleton
+  mutate(num_nonsingletons = if_else(dType == "Absent", 3, 2)) # add the number of nonsingletons for each trial type
+```
+
+## First saccade direction
+```{r First saccade direction - means}
+# calculate summary statistics for each participant
+saccadeData_means_byparticipant <- saccadedata %>%
+  ungroup() %>%
+  mutate(sub = as.factor(sub)) %>%
+  group_by(sub, condition, dType) %>%
+  summarise(saccade_to_target = mean(saccade_to_target, na.rm = T),
+            saccade_to_singleton = mean(saccade_to_singleton, na.rm = T),
+            saccade_to_nonsingleton = mean(saccade_to_nonsingleton, na.rm = T)/mean(num_nonsingletons, na.rm = T),
+            num_nonsingletons = mean(num_nonsingletons, na.rm = T))
+
+targetmeans <- summarySEwithin2(data = saccadeData_means_byparticipant, measurevar = "saccade_to_target", betweenvars = "condition", withinvars = c("dType"), idvar = "sub", na.rm = T) %>%
+  rename(proportionSaccades = saccade_to_target) %>%
+  mutate(stimType = "Target") %>%
+  select(-ends_with("Normed"))
+
+singletonmeans <- summarySEwithin2(data = saccadeData_means_byparticipant, measurevar = "saccade_to_singleton", betweenvars = "condition", withinvars = c("dType"), idvar = "sub", na.rm = T) %>%
+  rename(proportionSaccades = saccade_to_singleton) %>%
+  mutate(stimType = "Singleton")%>%
+  select(-ends_with("Normed"))
+
+nonsingletonmeans <- summarySEwithin2(data = saccadeData_means_byparticipant, measurevar = "saccade_to_nonsingleton", betweenvars = "condition", withinvars = c("dType"), idvar = "sub", na.rm = T) %>%
+  rename(proportionSaccades = saccade_to_nonsingleton) %>%
+  mutate(stimType = "Nonsingleton")%>%
+  select(-ends_with("Normed"))
+
+# collapse together
+saccadeData_means_bycondition <- bind_rows(targetmeans, singletonmeans, nonsingletonmeans) %>%
+  mutate(stimType = factor(stimType, levels = c("Target","Nonsingleton","Singleton")))
+
+saccadePlotDataParticipants <- gather(saccadeData_means_byparticipant, key = "stimType", value = "proportionSaccades", starts_with("saccade_to")) %>%
+  mutate(stimType = case_when(stimType == "saccade_to_target" ~ "Target",
+                              stimType == "saccade_to_nonsingleton" ~ "Nonsingleton",
+                              stimType == "saccade_to_singleton" ~ "Singleton",
+                              TRUE ~ ""))
+
+captureData_means_byparticipant <- saccadeData_means_byparticipant %>%
+  filter(dType != "Absent") %>%
+  mutate(Capture = saccade_to_singleton - saccade_to_nonsingleton)
+
+captureMeans <- summarySEwithin2(captureData_means_byparticipant, measurevar = "Capture", betweenvars = "condition", withinvars = "dType", idvar = "sub") %>%
+  select(-ends_with("Normed"))
+```
+
+```{r First Saccade Direction - Plot, echo = FALSE}
+saccadePlot_singleton <- saccadeData_means_bycondition %>%
+  filter(condition == "Singleton Search", dType != "Absent") %>%
+  ggplot(aes(group = dType, y = proportionSaccades, fill = dType, x = stimType, shape = dType, colour = dType)) +
+  geom_line(aes(linetype = dType, colour = dType), na.rm = T, size = .5, position = position_dodge(width = .6)) +
+  geom_point(aes(group = dType, y = proportionSaccades, x = stimType), na.rm = T, size = 1.5, alpha = .3, stroke = F, data = filter(saccadePlotDataParticipants, condition == "Singleton Search", dType != "Absent"), position = position_jitterdodge(dodge.width = .6, jitter.width = .2)) +
+  geom_errorbar(aes(ymin = proportionSaccades-se, ymax = proportionSaccades+se), na.rm = T, linetype = "solid", position = position_dodge(width = .6, preserve = "total"), show.legend = FALSE, colour = "black", width = .3) +
+  geom_point(na.rm = T, size = 3, position = position_dodge(width = .6), colour = "black") +
+  scale_y_continuous(labels = scales::percent_format(accuracy = 1), expand = c(0,0), limits = c(0,.8)) +
+  scale_linetype_manual(name = "Trial Type", values = c("solid", "longdash", "dotdash"), guide = guide_legend(), labels = c("High-reward", "Low-reward")) +
+  scale_fill_manual(name = "Trial Type", values = vmacCols, labels = c("High-reward", "Low-reward")) +
+  scale_colour_manual(name = "Trial Type", values = vmacCols, labels = c("High-reward", "Low-reward")) +
+  scale_shape_manual(name = "Trial Type", guide = guide_legend(), values = c(21,22,23), labels = c("High-reward", "Low-reward")) +
+  ylab("% First Saccades") + xlab("Stimulus Type") + labs(tag = "A", title = "Singleton Search") +
+  my_theme
+
+saccadePlot_feature <- saccadeData_means_bycondition %>%
+  filter(condition == "Feature Search", dType != "Absent") %>%
+  ggplot(aes(group = dType, y = proportionSaccades, fill = dType, x = stimType, shape = dType, colour = dType)) +
+  geom_line(aes(linetype = dType, colour = dType), na.rm = T, size = .5, position = position_dodge(width = .6)) +
+  geom_point(aes(group = dType, y = proportionSaccades, x = stimType), na.rm = T, size = 1.5, alpha = .3, stroke = F, data = filter(saccadePlotDataParticipants, condition == "Feature Search", dType != "Absent"), position = position_jitterdodge(dodge.width = .6, jitter.width = .2)) +
+  geom_errorbar(aes(ymin = proportionSaccades-se, ymax = proportionSaccades+se), na.rm = T, linetype = "solid", position = position_dodge(width = .6, preserve = "total"), show.legend = FALSE, colour = "black", width = .3) +
+  geom_point(na.rm = T, size = 3, position = position_dodge(width = .6), colour = "black") +
+  scale_y_continuous(labels = scales::percent_format(accuracy = 1), expand = c(0,0), limits = c(0,.8)) +
+  scale_linetype_manual(name = "Distractor Type", values = c("solid", "longdash", "dotdash"), guide = guide_legend()) +
+  scale_fill_manual(name = "Distractor Type", values = vmacCols) +
+  scale_colour_manual(name = "Distractor Type", values = vmacCols) +
+  scale_shape_manual(name = "Distractor Type", guide = guide_legend(), values = c(21,22,23)) +
+  ylab("% First Saccades") + xlab("Stimulus Type") + labs(tag = "C", title = "Feature Search") +
+  my_theme
+
+legend_saccade <- get_legend(saccadePlot_singleton + theme(legend.position = "bottom",
+                                                           legend.title = element_text(size = 14),
+                                                           legend.text = element_text(size = 14),
+                                                           legend.key.width = unit(24, 'pt')))
+
+## Capture Bar Plots
+captureBarPlot_singleton <- captureMeans %>%
+  filter(condition == "Singleton Search") %>%
+  mutate(annotation = c("***", " ")) %>%
+  ggplot(aes(x = dType, y = Capture, fill = dType)) +
+  annotate(geom = "text", label = "Capture", x = 2.85, y = .15, angle = 90, vjust = 1, hjust = .5, family = font_rc) +
+  annotate(geom = "text", label = "Suppression", x = 2.85, y = -.15, angle = 90, vjust = 1, hjust = .5, family = font_rc) +
+  annotate(geom = "segment", x = 2.65, xend = 2.65, y = -.03, yend = -.27, arrow = arrow(type = 'closed', length = unit(6, 'pt'))) +
+  annotate(geom = "segment", x = 2.65, xend = 2.65, y = .03, yend = .27, arrow = arrow(type = 'closed', length = unit(6, 'pt'))) +
+  geom_col(position = position_dodge(.9), size = .3) +
+  geom_hline(yintercept = 0, color = "black", size = .5) +
+  geom_errorbar(aes(ymax = Capture + se, ymin = Capture - se), position = position_dodge(.9), width = .1) +
+  geom_text(aes(label = annotation), nudge_y = .05) +
+  scale_y_continuous(labels = scales::percent_format(accuracy = 1), expand = c(0,0), limits = c(-.3001, .3001)) +
+  scale_x_discrete(labels = c("High\nreward", "Low\nreward")) +
+  coord_cartesian(xlim = c(1,2),
+                  clip = 'off') +
+  scale_fill_manual(name = "Distractor Type", values = vmacCols, guide = guide_legend()) +
+  ylab("Capture Score") + xlab("Trial Type") + labs(tag = "B") +
+  my_theme
+
+captureBarPlot_feature <- 
+  captureMeans %>%
+  filter(condition == "Feature Search") %>%
+  mutate(annotation = c("***", "*")) %>%
+  ggplot(aes(x = dType, y = Capture, fill = dType)) +
+  annotate(geom = "text", label = "Capture", x = 2.85, y = .15, angle = 90, vjust = 1, hjust = .5, family = font_rc) +
+  annotate(geom = "text", label = "Suppression", x = 2.85, y = -.15, angle = 90, vjust = 1, hjust = .5, family = font_rc) +
+  annotate(geom = "segment", x = 2.65, xend = 2.65, y = -.03, yend = -.27, arrow = arrow(type = 'closed', length = unit(6, 'pt'))) +
+  annotate(geom = "segment", x = 2.65, xend = 2.65, y = .03, yend = .27, arrow = arrow(type = 'closed', length = unit(6, 'pt'))) +
+  geom_col(position = position_dodge(.9), size = .3) + 
+  geom_hline(yintercept = 0, size = .5) +
+  geom_errorbar(aes(ymax = Capture + se, ymin = Capture - se), position = position_dodge(.9), width = .1) +
+  geom_text(aes(label = annotation), nudge_y = c(.05, .07)) +
+  scale_y_continuous(labels = scales::percent_format(accuracy = 1), expand = c(0,0), limits = c(-.3001, .3001)) +
+  scale_x_discrete(labels = c("High\nreward", "Low\nreward")) +
+  coord_cartesian(xlim = c(1,2),
+                  clip = 'off') +
+  scale_fill_manual(name = "Distractor Type", values = vmacCols, guide = guide_legend()) +
+  ylab("Capture Score") + xlab("Trial Type") + labs(tag = "D") +
+  my_theme
+
+saccadePlot_ms_row1 <- saccadePlot_singleton + captureBarPlot_singleton + plot_spacer() + plot_layout(nrow = 1, widths = c(2,1,.1))
+
+saccadePlot_ms_row2 <- saccadePlot_feature + captureBarPlot_feature + plot_spacer() + plot_layout(nrow = 1, widths = c(2,1,.1))
+
+saccadePlot_ms <- saccadePlot_ms_row1 / legend_saccade / saccadePlot_ms_row2 + plot_layout(heights = c(1,.1,1))
+
+save_plot(here("analysis", "figures", "saccade_plot.png"), saccadePlot_ms, ncol = 2, nrow = 2, type = "cairo", base_aspect_ratio = .9, dpi = 300)
+
+saccadePlot_ms
+```
+
+```{r First Saccade Direction - Capture ANOVA}
+capture.ANOVA <- aov_car(Capture ~ condition*dType + Error(sub/dType), data = captureData_means_byparticipant,  anova_table = list(es="pes"))
+
+capture.ANOVA
+
+# Bayes Factor for interaction contrast
+captureData_wide <- captureData_means_byparticipant %>%
+  select(sub, condition, dType, Capture) %>%
+  spread(dType, Capture) %>%
+  mutate(vmac = High - Low)
+
+capture_bayes <- ttestBF(x = captureData_wide$vmac[captureData_wide$condition == "Singleton Search"], 
+                         y = captureData_wide$vmac[captureData_wide$condition == "Feature Search"])
+
+1/capture_bayes
+
+```
+
+```{r First Saccade Direction - Planned t-tests}
+Singleton_high.ttest <- captureData_means_byparticipant %>%
+  ungroup() %>%
+  filter(condition == "Singleton Search") %>%
+  filter(dType == "High") %>%
+  select(Capture) %>%
+  pull() %>%
+  t.test()
+
+Singleton_high.es <- captureData_means_byparticipant %>%
+  ungroup() %>%
+  filter(condition == "Singleton Search") %>%
+  filter(dType == "High") %>%
+  select(Capture) %>%
+  summarise(mean_capture = mean(Capture), sd_capture = sd(Capture), d_z = mean_capture/sd_capture) %>%
+  pull(d_z)
+
+Singleton_low.ttest <- captureData_means_byparticipant %>%
+  ungroup() %>%
+  filter(condition == "Singleton Search") %>%
+  filter(dType == "Low") %>%
+  select(Capture) %>%
+  pull() %>%
+  t.test()
+
+Singleton_low.es <- captureData_means_byparticipant %>%
+  ungroup() %>%
+  filter(condition == "Singleton Search") %>%
+  filter(dType == "Low") %>%
+  select(Capture) %>%
+  summarise(mean_capture = mean(Capture), sd_capture = sd(Capture), d_z = mean_capture/sd_capture) %>%
+  pull(d_z)
+
+Feature_high.ttest <- captureData_means_byparticipant %>%
+  ungroup() %>%
+  filter(condition == "Feature Search") %>%
+  filter(dType == "High") %>%
+  select(Capture) %>%
+  pull() %>%
+  t.test()
+
+Feature_high.es <- captureData_means_byparticipant %>%
+  ungroup() %>%
+  filter(condition == "Feature Search") %>%
+  filter(dType == "High") %>%
+  select(Capture) %>%
+  summarise(mean_capture = mean(Capture), sd_capture = sd(Capture), d_z = mean_capture/sd_capture) %>%
+  pull(d_z)
+
+Feature_low.ttest <- captureData_means_byparticipant %>%
+  ungroup() %>%
+  filter(condition == "Feature Search") %>%
+  filter(dType == "Low") %>%
+  select(Capture) %>%
+  pull() %>%
+  t.test()
+
+Feature_low.ttest$statistic <- Feature_low.ttest$statistic*-1 # just making the t value positive for reporting in the manuscript
+
+Feature_low.es <- captureData_means_byparticipant %>%
+  ungroup() %>%
+  filter(condition == "Feature Search") %>%
+  filter(dType == "Low") %>%
+  select(Capture) %>%
+  summarise(mean_capture = mean(Capture), sd_capture = sd(Capture), d_z = abs(mean_capture/sd_capture)) %>%
+  pull(d_z)
+```

### 2019-04-12 analysis/analysis_report.rmd
block analysis added

@@
 ```
+
+## Development of suppression/capture effect across blocks
+
+```{r Block Analysis Data Tidying}
+saccadeData_means_byparticipant_byblock <- 
+  saccadedata %>%
+  mutate(sub = as.factor(sub), newblock = ceiling(as.numeric(block)/2)) %>%
+  group_by(sub, condition, dType, newblock) %>%
+  summarise(saccade_to_target = mean(saccade_to_target, na.rm = T),
+            saccade_to_singleton = mean(saccade_to_singleton, na.rm = T),
+            saccade_to_nonsingleton = mean(saccade_to_nonsingleton, na.rm = T)/mean(num_nonsingletons, na.rm = T),
+            num_nonsingletons = mean(num_nonsingletons, na.rm = T),
+            capture = saccade_to_singleton - saccade_to_nonsingleton) %>%
+  filter(dType != "Absent")
+
+capturemeans_byblock <- summarySEwithin2(data = saccadeData_means_byparticipant_byblock, measurevar = "capture", betweenvars = "condition", withinvars = c("dType", "newblock"), idvar = "sub", na.rm = T) %>%
+  select(-ends_with("Normed"))
+```
+
+```{r Block Analysis Graph}
+capturePlot_byblock_singleton <- 
+  capturemeans_byblock %>%
+  filter(condition == "Singleton Search") %>%
+  ggplot(aes(x = newblock, y = capture, group = dType, shape = dType, colour = dType)) +
+  #geom_rect(fill = "#D3D3D3", xmin = -Inf, xmax = Inf, ymin = -Inf, ymax = 0, alpha = .3, inherit.aes = F) +
+  geom_hline(yintercept = 0, colour = "black", size = .5, linetype = "dotted") +
+  annotate(geom = "text", label = "Capture", x = 4.7, y = .15, angle = 90, vjust = 1, hjust = .5, family = font_rc) +
+  annotate(geom = "text", label = "Suppression", x = 4.7, y = -.15, angle = 90, vjust = 1, hjust = .5, family = font_rc) +
+  annotate(geom = "segment", x = 4.5, xend = 4.5, y = -.03, yend = -.27, arrow = arrow(type = 'closed', length = unit(6, 'pt'))) +
+  annotate(geom = "segment", x = 4.5, xend = 4.5, y = .03, yend = .27, arrow = arrow(type = 'closed', length = unit(6, 'pt'))) +
+  geom_line(aes(linetype = dType), size = .5) +
+  geom_errorbar(aes(ymin = capture - se, ymax = capture + se), width = .1, colour = "black") +
+  geom_point(aes(shape = dType, fill = dType), size = 3, colour = "black") +
+  scale_shape_manual(name = "Distractor Type", guide = guide_legend(), values = c(21,22)) +
+  scale_fill_manual(name = "Distractor Type", values = vmacCols, guide = guide_legend()) +
+  scale_colour_manual(name = "Distractor Type", values = vmacCols, guide = guide_legend()) +
+  scale_y_continuous(expand = c(0,0), limits = c(-.3,.301), breaks = seq(-.3, .3, .1), labels = scales::percent_format(accuracy = 1)) +
+  scale_x_discrete() +
+  coord_cartesian(xlim = c(1,4),
+                  clip = 'off') +
+  scale_linetype_manual(name = "Distractor Type", values = c("solid", "longdash"), guide = guide_legend()) +
+  ylab("Capture Score") + xlab("Epoch (96 trials)") + labs(tag = "A", title = 'Singleton Search') +
+  my_theme
+
+capturePlot_byblock_feature <- 
+  capturemeans_byblock %>%
+  filter(condition == "Feature Search") %>%
+  ggplot(aes(x = newblock, y = capture, group = dType, shape = dType, colour = dType)) +
+  geom_hline(yintercept = 0, colour = "black", size = .5, linetype = "dotted") +
+  annotate(geom = "text", label = "Capture", x = 4.7, y = .15, angle = 90, vjust = 1, hjust = .5, family = font_rc) +
+  annotate(geom = "text", label = "Suppression", x = 4.7, y = -.15, angle = 90, vjust = 1, hjust = .5, family = font_rc) +
+  annotate(geom = "segment", x = 4.5, xend = 4.5, y = -.03, yend = -.27, arrow = arrow(type = 'closed', length = unit(6, 'pt'))) +
+  annotate(geom = "segment", x = 4.5, xend = 4.5, y = .03, yend = .27, arrow = arrow(type = 'closed', length = unit(6, 'pt'))) +
+  geom_line(aes(linetype = dType), size = .5) +
+  geom_errorbar(aes(ymin = capture - se, ymax = capture + se), width = .1, colour = "black") +
+  geom_point(aes(shape = dType, fill = dType), size = 3, colour = "black") +
+  scale_shape_manual(name = "Distractor Type", guide = guide_legend(), values = c(21,22)) +
+  scale_fill_manual(name = "Distractor Type", values = vmacCols, guide = guide_legend()) +
+  scale_colour_manual(name = "Distractor Type", values = vmacCols, guide = guide_legend()) +
+  scale_y_continuous(expand = c(0,0), limits = c(-.3,.301), breaks = seq(-.3, .3, .1), labels = scales::percent_format(accuracy = 1)) +
+  scale_x_discrete() +
+  coord_cartesian(xlim = c(1,4),
+                  clip = 'off') +
+  scale_linetype_manual(name = "Distractor Type", values = c("solid", "longdash"), guide = guide_legend()) +
+  ylab("Capture Score") + xlab("Epoch (96 trials)") + labs(tag = "B", title = 'Feature Search') +
+  my_theme
+
+capturePlot_byblock_vert <- (capturePlot_byblock_singleton + plot_spacer() + plot_layout(widths = c(1,.1))) / legend_saccade / (capturePlot_byblock_feature + plot_spacer() + plot_layout(widths = c(1,.1))) + plot_layout(heights = c(1,.1,1))
+
+capturePlot_byblock_vert
+
+save_plot(here("analysis", "figures","capture_plot_by_block.png"), capturePlot_byblock_vert, ncol = 1, nrow = 2, type = "cairo", base_aspect_ratio = 1.1, dpi = 300)
+
+```
+
+```{r Block Analysis Statistics}
+capture_byblock.ANOVA <- aov_car(capture ~ newblock*dType*condition + Error(sub/newblock*dType), data = saccadeData_means_byparticipant_byblock, anova_table = list(es="pes"))
+
+capture_byblock.ANOVA
+
+ref_all <- lsmeans(capture_byblock.ANOVA, ~newblock | dType)
+
+capture_byblock.polys <- summary(contrast(ref_all, method = "poly")) %>%
+  mutate(t.ratio = abs(t.ratio),
+         df = round(df, digits = 0))
+
+capture_byblock.polys
+```

### 2019-04-18 analysis/analysis_report.rmd
basic analysis report done

@@
 ---
-title: "Analysis_Report"
+title: "Analysis Report"
 author: "Daniel Pearson"
@@
 library(ggsignif)
+library(summarytools)
+
+st_options(bootstrap.css     = FALSE,       # Already part of the theme so no need for it
+           plain.ascii       = FALSE,       # One of the essential settings
+           style             = "rmarkdown", # Idem.
+           dfSummary.silent  = TRUE,        # Suppresses messages about temporary files
+           footnote          = NA,          # Keeping the results minimalistic
+           subtitle.emphasis = FALSE)       # For the vignette theme, this gives
+                                            # much better results. Your mileage may vary.
+
+st_css()
+
+library(knitr)
+opts_chunk$set(comment=NA, prompt=FALSE, cache=FALSE, echo=TRUE, results='asis')
+
+source(here::here("R", "dz_calculator.r"))
+source(here::here("R", "vmac_pal.R"))
+source(here::here("R", "summarySEwithin2.r"))
 
@@
 
-# Behavioural Analysis
+# Omission Trial Analysis
 
@@
 
+We first removed participants who had poor gaze data (mean proportion of valid gaze samples during the fixation or trial period < .5).
 ```{r Remove participants with poor gaze data}
@@
 
-We removed data for any participants who did not have sufficient quality gaze data.
-If participants have an average of less than `r propCutoff*100`% valid gaze data during the fixation period or during a trial, they are removed from the data set.
-
-`r length(poortracks)` participants were removed due to having a poor track.
+`r length(poortracks)` participants were removed due to having a poor quality eye gaze data.
 
@@
 
-#  check to make sure that everyone has completed the full 480 trials
+#  check to make sure that everyone has completed the full 480 trials (e.g., if the experiment crashed/was abandoned due to poor gaze data)
 didNotComplete <- exptdata %>%
@@
 
-`r length(remove_p_numbers)` participants were removed for other reasons (participant #37 they thought that they needed to look at the coloured circle in order to earn rewards, participant #26 and #85 did not complete the experiment due to difficulty tracking their eyes).
+During a post-experiment debrief, participant #37 reported that they thought that they needed to look at the coloured circle in order to earn rewards, and so they were removed from the data set.
 
-Then we remove the first two trials of the experiment, the first two trials after breaks, and timeouts from the data (in line with previous VMAC analysis protocols):
+Then we removed the first two trials of the experiment, the first two trials after breaks, and timeouts from the data (in line with previous VMAC analysis protocols, e.g.
+Le Pelley et al, 2015 - __JEP:General__).
 
@@
 
+This is the data set that we are left with:
+
+```{r Glimpse exptdata after exclusions}
+print(dfSummary(exptdata, style = "grid", graph.magnif = 0.75, tmp.img.dir = "/tmp"),  max.tbl.height = 300, method = "render")
+```
+
+Key for each of the variables in the table:
+
+```{r table2, echo=FALSE, message=FALSE, warnings=FALSE, results='asis'}
+tabl <- "
+| Variable name | Explanation                                  |
+|---------------|--------------------------------------------|
+| block         | Experiment block (1--8; 60 trials per block) |
+| trial         | Experiment trial (1--480)      |
+| trialCounter  | Trial counter within a block (1--60)      |
+| trials_since_break         | Trial counter since last break (same as trialCounter for this experiment) |
+| targetLoc         | Location of the target stimulus of 4 possible locations     |
+| targetType  | Whether the target was a diamond or a circle (1 - diamond, 2 - circle)    |
+| distractLoc         | Location of the singleton distractor (or random non-singleton on distractor absent trials) |
+| distractShape         | The shape that defined the singleton distractor (1 - diamond, 2 - circle, 3 - hexagon, 4 - square)      |
+| distractType  | Whether it was a high (1), low (2), or absent (3) trial     |
+| fixationTime         | Length of fixation period in seconds |
+| fixationPropGoodSamples         | The proportion of valid samples within the fixation period     |
+| fixationTimeout  | Whether the fixation timeout period (4 seconds) was reached before a valid fixation was recorded  |
+| trialPropGoodSamples         | The proportion of valid samples within the trial period |
+| timeout         | Whether a hard-timeout (2 seconds) was reached before the target was fixated      |
+| softTimeoutTrial  | Whether a soft-timeout (1 second) was reached, meaning that no reward was awarded   |
+| omissionTrial         | Whether an omission trial was recorded  |
+| rt         | Response time in seconds     |
+| trialPay  | The reward for the current trial (in points)    |
+| sessionPay         | Total reward accumulated during the experiment (in points) |
+| timeOnLoc 1--5         | Amount of time (in seconds) that gaze was recorded on each stimulus location (1--4), and anywhere else (5)     |
+| sub  | Participant identifier     |
+| counterbal         | Code assigning participants to each condition (singleton vs feature) and colour--reward mapping |
+| age         | Age in years     |
+| gender  | Self-reported gender (m/f/o)  |
+| condition         | Search condition (1 - feature search, 2 - singleton search)    |
+| dType  | Distractor type (1 - high, 2 - low, 3 - absent)  |
+"
+cat(tabl) # output the table in a format good for HTML/PDF/docx conversion
+```
+
 ## Omission Trials
-```{r Omission Trial Means}
+```{r Omission Trial Means, message=FALSE, warning=FALSE}
+# Calculate mean proportion of omission trials for each trial type, by participant
 exptdata_means_byparticipant <- exptdata %>%
@@
 
+# Calculate mean proportion of omission trials for each trial type, by condition
 exptdata_means_bycondition <- summarySEwithin2(data = exptdata_means_byparticipant, measurevar = "m", betweenvars = "condition", withinvars = "dType", idvar = "sub") %>%
@@
 
-```{r Omission Trial Graph}
+Draw a graph of omission trials for each condition:
 
+```{r Omission Trial Graph, fig.height=10, fig.width=5.5, message=FALSE, warning=FALSE, echo=FALSE}
 omissionPlot_singleton <- exptdata %>%
@@
 omissions_vmac.ANOVA <- aov_car(m ~ condition*dType + Error(sub/dType), data = filter(exptdata_means_byparticipant, dType != "Absent"), anova_table = list(es="pes"))
+
+knitr::kable(nice(omissions_vmac.ANOVA))
 ```
-Significant main effect of reward (indicating VMAC effect), but no interaction with or main effect of search condition.
 
 Planned t-tests:
-```{r Effect of Reward - Omissions - Planned t-tests}
+```{r Effect of Reward - Omissions - Planned t-tests, results="markup"}
 singleton_high_omissions <- exptdata_means_byparticipant %>%
@@
 singleton_VMAC_omissions.ttest <- t.test(singleton_high_omissions, singleton_low_omissions, paired = T)
+singleton_VMAC_omissions.ttest
 singleton_VMAC_omissions.es <- dz_calculator(singleton_high_omissions, singleton_low_omissions)
+singleton_VMAC_omissions.es
 feature_VMAC_omissions.ttest <- t.test(feature_high_omissions, feature_low_omissions, paired = T)
+feature_VMAC_omissions.ttest
 feature_VMAC_omissions.es <- dz_calculator(feature_high_omissions, feature_low_omissions)
+feature_VMAC_omissions.es
 
@@
 vmac_condition_bayes <- ttestBF(x = vmac_singleton, y = vmac_feature)
+vmac_condition_bayes
 ```
@@
 
-omissions_salience.ANOVA
+knitr::kable(nice(omissions_salience.ANOVA))
 ```
@@
 Planned t-tests:
-```{r Effect of Physical Salience - Omissions - Planned t-tests}
+```{r Effect of Physical Salience - Omissions - Planned t-tests, results="markup"}
 singleton_physicalsalience_omissions.ttest <- t.test(singleton_low_omissions, singleton_absent_omissions, paired = T)
-
+singleton_physicalsalience_omissions.ttest
 singleton_physicalsalience_omissions.es <- dz_calculator(singleton_low_omissions, singleton_absent_omissions)
+singleton_physicalsalience_omissions.es
 
 feature_physicalsalience_omissions.ttest <- t.test(feature_absent_omissions, feature_low_omissions, paired = T) # reverse the order here so can get positive t value
-
+feature_physicalsalience_omissions.ttest
 feature_physicalsalience_omissions.es <- dz_calculator(feature_low_omissions, feature_absent_omissions)
+feature_physicalsalience_omissions.es
 ```
@@
 
+```{r Glimpse saccadedata}
+print(dfSummary(saccadedata, style = "grid", graph.magnif = 0.75, tmp.img.dir = "/tmp"),  max.tbl.height = 300, method = "render")
+```
+
+Key for each of the new variables in saccadedata data frame:
+
+```{r table3, echo=FALSE, message=FALSE, warnings=FALSE, results='asis'}
+tabl2 <- "
+| Variable name | Explanation                                  |
+|---------------|--------------------------------------------|
+| latency         | Saccade latency in milliseconds |
+| loc 1--5         | Whether the first saccade was directed towards location 1--4, or somewhere else (loc 5)      |
+| discardTrial  | Whether the trial should be excluded from saccade analyses due to exclusion criteria      |
+| anticipatorySaccade         | Whether saccade latency was <80ms |
+| outsideFixation         | Trials in which no gaze was reocrded within 100 pixels of fixation in the first 80 ms    |
+| noSaccades  | Trials in which the saccade identification algorithm did not detect a saccade   |
+| noValidData         | Trials in which there was insufficient valid gaze data to detect a saccade |
+| first_saccade_loc         | The direction of the first saccade (locations 1--4, or elsewhere [loc 5])     |
+| saccade_to_target  | Whether the first saccade was directed towards the target    |
+| saccade_to_nonsingleton         | Whether the first saccade was directed towards one of the non-singleton distractors |
+| num_nonsingletons         | The number of non-singleton distractors in the display (2 on high and low trials, 3 on distractor absent trials)     |
+"
+cat(tabl2) # output the table in a format good for HTML/PDF/docx conversion
+```
+
 ## First saccade direction
-```{r First saccade direction - means}
+```{r First saccade direction - means, warning=FALSE, message=FALSE}
 # calculate summary statistics for each participant
@@
 
-```{r First Saccade Direction - Plot, echo = FALSE}
+Graph of the first saccade data and capture scores:
+
+```{r First Saccade Direction - Plot, echo=FALSE, fig.height=10, fig.width=10, message=FALSE, warning=FALSE}
 saccadePlot_singleton <- saccadeData_means_bycondition %>%
@@
 
-```{r First Saccade Direction - Capture ANOVA}
+```{r First Saccade Direction - Capture ANOVA, results="markup", message = FALSE}
 capture.ANOVA <- aov_car(Capture ~ condition*dType + Error(sub/dType), data = captureData_means_byparticipant,  anova_table = list(es="pes"))
 
-capture.ANOVA
+knitr::kable(nice(capture.ANOVA))
 
@@
 
-1/capture_bayes
+capture_bayes
 
@@
 
-```{r First Saccade Direction - Planned t-tests}
+```{r First Saccade Direction - Planned t-tests, results = "markup"}
 Singleton_high.ttest <- captureData_means_byparticipant %>%
@@
   t.test()
+
+Singleton_high.ttest
 
@@
 
+Singleton_high.es
+
 Singleton_low.ttest <- captureData_means_byparticipant %>%
@@
   t.test()
+
+Singleton_low.ttest
 
@@
 
+Singleton_low.es
+
 Feature_high.ttest <- captureData_means_byparticipant %>%
@@
   t.test()
+
+Feature_high.ttest
 
@@
 
+Feature_high.es
+
 Feature_low.ttest <- captureData_means_byparticipant %>%
@@
   t.test()
+
+Feature_low.ttest
 
@@
   pull(d_z)
+
+Feature_low.es
 ```
@@
 
-```{r Block Analysis Graph}
+```{r Block Analysis Graph, echo=FALSE, fig.height=10, fig.width=5, message=FALSE, warning=FALSE}
 capturePlot_byblock_singleton <- 
@@
 
-capture_byblock.ANOVA
+knitr::kable(nice(capture_byblock.ANOVA))
 
@@
 
-capture_byblock.polys
+knitr::kable(capture_byblock.polys)
 ```
+
+## Vincentized Analysis
+
+This analysis looks at the percentage of trials captured/suppressed by each distractor as a function of saccade latency.
+
+```{r Vincentized Analysis - Data Tidying}
+quartiles_cutoffs <- saccadedata %>%
+  group_by(sub, dType, condition) %>%
+  summarise(q1 = quantile(latency, probs = .25, na.rm = T), q2 = quantile(latency, probs = .5, na.rm = T), q3 = quantile(latency, probs = .75, na.rm = T), q4 = quantile(latency, probs = 1, na.rm = T))
+
+quartiles_cutoffs_figures <- saccadedata %>% 
+  group_by(sub, dType, condition) %>%
+  summarise(qs = list(enframe(quantile(latency, probs=seq(.25,.75,.25), na.rm = T)))) %>% 
+  unnest
+
+saccadedata <- full_join(saccadedata, quartiles_cutoffs, by = c("sub","dType", "condition"))
+
+saccadedata <- saccadedata %>% 
+  mutate(quartile = case_when(latency <= q1 ~ 1,
+                              latency <= q2 ~ 2,
+                              latency <= q3 ~ 3,
+                              latency <= q4 ~ 4))
+
+saccade_latency_quartiles_means_byparticipant <- saccadedata %>%
+  ungroup() %>%
+  drop_na(quartile) %>% 
+  group_by(sub, condition, dType, quartile) %>%
+  summarise(mean_latency = mean(latency, na.rm = T))
+
+saccade_latency_quartiles_means_bycondition <- summarySEwithin2(saccade_latency_quartiles_means_byparticipant, measurevar = "mean_latency", betweenvars = "condition", withinvars = c("dType", "quartile"), idvar = "sub") %>%
+  select(-ends_with("Normed"))
+
+saccade_direction_quartiles_means_byparticipant <- saccadedata %>%
+  ungroup() %>%
+  drop_na(quartile) %>% 
+  group_by(sub, condition, dType, quartile) %>%
+  summarise(saccade_to_target = mean(saccade_to_target, na.rm = T),
+            saccade_to_singleton = mean(saccade_to_singleton, na.rm = T),
+            saccade_to_nonsingleton = mean(saccade_to_nonsingleton, na.rm = T)/mean(num_nonsingletons, na.rm = T),
+            num_nonsingletons = mean(num_nonsingletons, na.rm = T),
+            capture = saccade_to_singleton - saccade_to_nonsingleton) %>%
+  filter(dType != "Absent")
+
+saccade_direction_quartiles_means_bycondition <- summarySEwithin2(saccade_direction_quartiles_means_byparticipant, measurevar = "capture", betweenvars = "condition", withinvars = c("dType", "quartile"), idvar = "sub") %>%
+  select(-ends_with("Normed")) %>%
+  left_join(., saccade_latency_quartiles_means_bycondition, by = c("dType", "condition", "quartile"), suffix = c(".prop", ".latency"))
+```
+
+```{r Vincentized Analysis - Graph, echo=FALSE, warning=FALSE, fig.height=10, fig.width=5, message=FALSE}
+
+vincentized_annotations <- c("***"," "," "," ","**"," "," "," ","***"," "," "," ","***"," "," ","")
+
+vincentizedPlot_singleton <- saccade_direction_quartiles_means_bycondition %>%
+  mutate(annotations = vincentized_annotations) %>%
+  filter(condition == "Singleton Search") %>%
+  ggplot(aes(x = mean_latency, y = capture, fill = dType, linetype = dType, colour = dType)) +
+  annotate(geom = "text", label = "Capture", x = 370, y = .3, angle = 90, vjust = 1, hjust = .5, family = font_rc) +
+  annotate(geom = "text", label = "Suppression", x = 370, y = -.2, angle = 90, vjust = 1, hjust = .5, family = font_rc) +
+  annotate(geom = "segment", x = 365, xend = 365, y = -.03, yend = -.37, arrow = arrow(type = 'closed', length = unit(6, 'pt'))) +
+  annotate(geom = "segment", x = 365, xend = 365, y = .03, yend = .57, arrow = arrow(type = 'closed', length = unit(6, 'pt'))) +
+  geom_linerange(aes(ymin = capture-se.prop, ymax = capture + se.prop), colour = "black", linetype = "solid", size = .5) +
+  geom_errorbarh(aes(xmin = mean_latency-se.latency, xmax = mean_latency+se.latency, height = 0), linetype = "solid", size = .5, colour = "black") +
+  geom_line(size = .5) +
+  geom_point(aes(shape = dType, fill = dType), size = 3, colour = "black") +
+  geom_hline(yintercept = 0, colour = "black", size = .5, linetype = "dotted") +
+  geom_text(aes(label = annotations), nudge_y = .07, colour = "black") +
+  scale_fill_manual(name = "Trial Type", values = vmacCols, guide = guide_legend(), labels = c("High-reward", "Low-reward")) +
+  scale_colour_manual(name = "Trial Type", values = vmacCols, guide = guide_legend(), labels = c("High-reward", "Low-reward")) +
+  scale_y_continuous(labels = scales::percent_format(accuracy = 1), expand = c(0,0), limits = c(-.4,.621)) +
+  scale_x_continuous(expand = c(0,0), limits = c(165, 380), breaks = seq(125,375,50)) +
+  scale_shape_manual(name = "Trial Type", guide = guide_legend(), values = c(21,22), labels = c("High-reward", "Low-reward")) +
+  scale_linetype_manual(name = "Trial Type", values = c("solid", "longdash"), guide = guide_legend(), labels = c("High-reward", "Low-reward")) +
+  coord_cartesian(xlim = c(165,360),
+                  clip = 'off') +
+  ylab("Capture Score") + xlab("Saccade latency (ms)") + labs(tag = "A", title = 'Singleton Search') +
+  my_theme + theme(axis.ticks.x = element_line(colour = "black", size = .5))
+
+vincentizedPlot_feature <- 
+  saccade_direction_quartiles_means_bycondition %>%
+  mutate(annotations = vincentized_annotations) %>%
+  filter(condition == "Feature Search") %>%
+  mutate(nudge_y = c(rep(.07, 7), -.07), nudge_x = c(0,0,0,-5,0,0,0,5)) %>%
+  ggplot(aes(x = mean_latency, y = capture, fill = dType, linetype = dType, colour = dType)) +
+  annotate(geom = "text", label = "Capture", x = 370, y = .3, angle = 90, vjust = 1, hjust = .5, family = font_rc) +
+  annotate(geom = "text", label = "Suppression", x = 370, y = -.2, angle = 90, vjust = 1, hjust = .5, family = font_rc) +
+  annotate(geom = "segment", x = 365, xend = 365, y = -.03, yend = -.37, arrow = arrow(type = 'closed', length = unit(6, 'pt'))) +
+  annotate(geom = "segment", x = 365, xend = 365, y = .03, yend = .57, arrow = arrow(type = 'closed', length = unit(6, 'pt'))) +
+  geom_linerange(aes(ymin = capture-se.prop, ymax = capture + se.prop), colour = "black", linetype = "solid", size = .5) +
+  geom_errorbarh(aes(xmin = mean_latency-se.latency, xmax = mean_latency+se.latency, height = 0), linetype = "solid", size = .5, colour = "black") +
+  geom_line(size = .5) +
+  geom_point(aes(shape = dType, fill = dType), size = 3, colour = "black") +
+  geom_hline(yintercept = 0, colour = "black", size = .5, linetype = "dotted") +
+  geom_text(aes(label = annotations, y = capture + nudge_y, x = mean_latency), colour = "black") +
+  scale_fill_manual(name = "Trial Type", values = vmacCols, guide = guide_legend()) +
+  scale_colour_manual(name = "Trial Type", values = vmacCols, guide = guide_legend()) +
+  scale_y_continuous(labels = scales::percent_format(accuracy = 1), expand = c(0,0), limits = c(-.4,.621)) +
+  scale_x_continuous(expand = c(0,0), limits = c(165, 380), breaks = seq(125,375,50)) +
+  scale_linetype_manual(name = "Trial Type", values = c("solid", "longdash"), guide = guide_legend()) +
+  scale_shape_manual(name = "Trial Type", guide = guide_legend(), values = c(21,22)) +
+  coord_cartesian(xlim = c(165,360),
+                  clip = 'off') +
+  ylab("Capture Score") + xlab("Saccade latency (ms)") + labs(tag = "B", title = 'Feature Search') +
+  my_theme + theme(axis.ticks.x = element_line(colour = "black", size = .5))
+
+legend_vincentizedPlot <- get_legend(vincentizedPlot_singleton + theme(legend.position = "bottom",
+                                                                       legend.title = element_text(size = 12),
+                                                                       legend.text = element_text(size = 12),
+                                                                       legend.key.width = unit(24, 'pt')))
+
+vincentizedPlot_ms <- vincentizedPlot_singleton + plot_spacer() + legend_saccade + plot_spacer() + vincentizedPlot_feature + plot_spacer() + plot_layout(nrow = 3, ncol = 2, heights = c(1,.2,1), widths = c(1,.05))
+
+save_plot(here("analysis","figures","vincentized_plot.png"), vincentizedPlot_ms, ncol = 1, nrow = 2, type = "cairo", base_aspect_ratio = 1.1, dpi = 300)
+
+vincentizedPlot_ms
+```
+
+```{r Vincentized Analysis - Statistics, results="markup"}
+vincentized_singleton_high_q1.ttest <- saccade_direction_quartiles_means_byparticipant%>%
+  ungroup() %>%
+  filter(condition == "Singleton Search", dType == "High", quartile == 1) %>%
+  select(capture) %>%
+  pull() %>%
+  t.test()
+
+vincentized_singleton_high_q1.ttest
+
+vincentized_singleton_high_q1.es <- saccade_direction_quartiles_means_byparticipant %>%
+  ungroup() %>%
+  filter(condition == "Singleton Search") %>%
+  filter(dType == "High", quartile == 1) %>%
+  select(capture) %>%
+  summarise(mean_capture = mean(capture), sd_capture = sd(capture), d_z = abs(mean_capture/sd_capture)) %>%
+  pull(d_z)
+
+vincentized_singleton_high_q1.es
+
+vincentized_singleton_low_q1.ttest <- saccade_direction_quartiles_means_byparticipant%>%
+  ungroup() %>%
+  filter(condition == "Singleton Search", dType == "Low", quartile == 1) %>%
+  select(capture) %>%
+  pull() %>%
+  t.test()
+
+vincentized_singleton_low_q1.ttest
+
+vincentized_singleton_low_q1.es <- saccade_direction_quartiles_means_byparticipant %>%
+  ungroup() %>%
+  filter(condition == "Singleton Search") %>%
+  filter(dType == "Low", quartile == 1) %>%
+  select(capture) %>%
+  summarise(mean_capture = mean(capture), sd_capture = sd(capture), d_z = abs(mean_capture/sd_capture)) %>%
+  pull(d_z)
+
+vincentized_singleton_low_q1.es
+
+vincentized_feature_high_q1.ttest <- saccade_direction_quartiles_means_byparticipant%>%
+  ungroup() %>%
+  filter(condition == "Feature Search", dType == "High", quartile == 1) %>%
+  select(capture) %>%
+  pull() %>%
+  t.test()
+
+vincentized_feature_high_q1.ttest
+
+vincentized_feature_high_q1.es <- saccade_direction_quartiles_means_byparticipant %>%
+  ungroup() %>%
+  filter(condition == "Feature Search") %>%
+  filter(dType == "High", quartile == 1) %>%
+  select(capture) %>%
+  summarise(mean_capture = mean(capture), sd_capture = sd(capture), d_z = abs(mean_capture/sd_capture)) %>%
+  pull(d_z)
+
+vincentized_feature_high_q1.es
+
+vincentized_feature_low_q1.ttest <- saccade_direction_quartiles_means_byparticipant%>%
+  ungroup() %>%
+  filter(condition == "Feature Search", dType == "Low", quartile == 1) %>%
+  select(capture) %>%
+  pull() %>%
+  t.test()
+
+vincentized_feature_low_q1.ttest
+
+vincentized_feature_low_q1.es <- saccade_direction_quartiles_means_byparticipant %>%
+  ungroup() %>%
+  filter(condition == "Feature Search") %>%
+  filter(dType == "Low", quartile == 1) %>%
+  select(capture) %>%
+  summarise(mean_capture = mean(capture), sd_capture = sd(capture), d_z = abs(mean_capture/sd_capture)) %>%
+  pull(d_z)
+
+vincentized_feature_low_q1.es
+```

### 2019-04-18 analysis/paper/paper.Rmd
testing circleci

@@
 ---
-title: "Title Goes Here"
+title             : "Overt attentional capture by reward-related stimuli overcomes top-down suppression"
+shorttitle        : "Reward overcomes attentional suppression"
+
 author: 
-  - Author One
-  - Author Two
-date: "`r format(Sys.time(), '%d %B, %Y')`"
-output: 
-    bookdown::html_document2:
-      fig_caption: yes
-      reference_docx: "../templates/template.docx" # Insert path for the DOCX file
-bibliography: references.bib
-csl: "../templates/journal-of-archaeological-science.csl" # Insert path for the bib-style
+  - name          : "Daniel Pearson"
+    affiliation   : "1"
+    corresponding : yes    # Define only one corresponding author
+    address       : "School of Psychology, University of New South Wales, UNSW Sydney NSW 2052, Australia"
+    email         : "d.pearson@unsw.edu.au"
+  - name          : "Poppy Watson"
+    affiliation   : "1"
+  - name          : "Phillip Cheng"
+    affiliation   : "2"
+  - name          : "Mike E. Le Pelley"
+    affiliation   : "1"
+
+affiliation:
+  - id            : "1"
+    institution   : "School of Psychology, UNSW Sydney"
+  - id            : "2"
+    institution   : "Department of Psychology, Macquarie University"
+
+authornote: |
+  **Conflict of interest:** The authors declare no conflict of interest.
+
+  **Funding:** This research was supported by Australian Research Council grant DP170101715. Daniel Pearson was supported by an Australian Government Research Training Program Scholarship.
+
 abstract: |
-  Text of abstract
-keywords: |
-  keyword 1; keyword 2; keyword 3
-highlights: |
-  These are the highlights. 
+  Salient-but-irrelevant distractors can automatically capture attention and eye-gaze in visual search.
+However, recent findings have suggested that attention to salient-but-irrelevant stimuli can be suppressed when observers use a specific target template to guide their search (i.e., feature search).
+Increasingly, evidence suggests that attentional selection is influenced by factors other than the physical salience of a stimulus and the observer’s goals.
+For instance, pairing a stimulus with reward has been shown to increase the extent to which it captures attention and gaze (as though it has become more physically salient), even when such capture has negative consequences for the observer.
+We investigated whether capture by reward can be suppressed in the same way as capture by physical salience using eye-tracking with a rewarded visual search task.
+When participants were encouraged to use feature search, attention to a distractor paired with relatively small reward was suppressed.
+By contrast, attention was captured by a distractor paired with large reward, even when such capture resulted in the loss of large reward.
+These findings suggest that reward-related stimuli are given special priority to the visual attention system and have implications for our understanding of real-world biases to reward-related stimuli, such as those seen in addiction.
+
+keywords          : "attentional capture, reward, suppression, cognitive control"
+wordcount         : "6656"
+
+bibliography      : ["r-references.bib", "mendeley.bib"]
+
+floatsintext      : yes
+figurelist        : no
+tablelist         : no
+footnotelist      : no
+linenumbers       : no
+mask              : no
+draft             : no
+
+header-includes:
+  - \raggedbottom
+
+documentclass     : "apa6"
+classoption       : "jou, a4paper, noextraspace"
+output            : papaja::apa6_pdf
+nocite: |
+
 ---
 
-<!-- This is the format for text comments that will be ignored during renderings. Do not put R code in these comments because it will not be ignored. -->
+```{r setup, include = FALSE}
+library("papaja")
+library(here)
+load(here::here("analysis", "data", "completed_analysis.rda"))
+# source(here("Analysis Programs", "Figures", "manuscript_figs.r"))
+# use this to allow custom decimal places later on
+op = function(x, d=2) sprintf(paste0("%1.",d,"f"), x) 
+```
 
-```{r, setup, echo = FALSE}
-knitr::opts_chunk$set(
-  collapse = TRUE,
-  warning = FALSE,
-  message = FALSE,
-  echo = FALSE,
-  comment = "#>",
-  fig.path = "../figures/"
-)
-
-library(vmacfeaturesearch) # Or use devtools::load_all('.', quiet = T) if your code is in script files, rather than as functions in the `/R` diretory
+```{r analysis-preferences}
+# Seed for random number generation
+set.seed(42)
+knitr::opts_chunk$set(cache.extra = knitr::rand_seed)
 ```
@@
 # Introduction
+When we interact with the world, our visual attention system can prioritise important information.
+For example, when driving towards an intersection, we can selectively attend to a stop sign on a busy street.
+Sometimes, however, we may find that stimuli that are irrelevant to our current task may nevertheless capture our attention in a seemingly automatic and involuntary way (e.g., a flashing alert, or colourful billboard).
+Consistent with this framework, an influential view of attentional selection has drawn a distinction between two forms of attentional control: one that is volitional and goal directed (top-down control) and another that is automatic and stimulus driven [@Yantis2000].
+However, exactly how these two processes interact has been the subject of extensive debate.
 
-Here is a citation [@Marwick2017]
+Most models of attentional selection can be categorised into one of two opposing theoretical positions.
+*Stimulus-driven* accounts argue that attention is initially captured by the most salient stimulus presented to an observer, regardless of their current goals [@Theeuwes2010; @Theeuwes1992].
+That is, individuals have no voluntary control over the initial allocation of their attention, which is automatically drawn to the most salient stimulus in a scene.
+By contrast, *goal-directed* accounts posit that attention is allocated only to stimuli that are in some way related to the observer's current goals [@Folk1992; @Leber2006].
+These theories predict that physically salient stimuli will be completely ignored by the visual attention system, unless they share some feature(s) with the observer's template of expected targets.
 
-# Background
+Recently, a hybrid model of attentional selection has been proposed---the *signal suppression hypothesis* [@Gaspelin2018; @Sawaki2010]---which attempts to integrate these two competing accounts.
+According to this model, salient stimuli automatically generate an attentional priority signal (or "attend-to-me" signal) that will go on to capture attention unless it is suppressed by a top-down control process, which builds over repeated experience with the salient stimulus [@Gaspelin2018b].
+This account is consistent with stimulus-driven theories, in that it proposes that physically salient stimuli have the potential to involuntarily capture attention; however it is also consistent with goal-directed theories in that it proposes that there is some top-down control of the allocation of attention.
+Evidence supporting the signal suppression hypothesis has largely come from the event-related potential (ERP) literature [for review, see @Gaspelin2018a], however recent studies have demonstrated behavioural evidence of suppression in the context of overt attention [i.e., eye-movements: see @Gaspelin2016; @Gaspelin2018b; @Ipata2006] and covert attention [i.e., shifts of attention that are not accompanied by eye-movements: see @Gaspelin2015].
 
-```{r demo, eval = FALSE}
-1 + 1
-```
+For example, across two experiments @Gaspelin2016 had participants perform variants of a commonly used  procedure for examining attentional capture---the *additional singleton task* [@Theeuwes1991a; @Theeuwes1992]---while recording eye movements.
+Eye movements provide a useful index of attention since an eye movement to a location (a saccade) is necessarily preceded by a shift of spatial attention to that location [@Deubel1996].
+In this task, participants were required to locate and respond to a shape-singleton target that was presented in an array of non-target shapes.
+On half of the trials, one of the non-target shapes was rendered in a different colour from the rest of the array so as to be a physically salient colour-singleton distractor.
+If participants were *more* likely to make a saccade towards the singleton distractor than one of the nonsingleton non-targets, this would indicate that the singleton distractor had captured attention.
+By contrast, if participants were *less* likely to make a saccade to the singleton distractor than one of the nonsingleton non-targets, this would suggest that attention to the singleton distractor had been suppressed.
+In @Gaspelin2016\'s Experiment 1, participants were encouraged to adopt a strategy of searching for the "odd-one-out" in the display [i.e, *singleton-search mode*; @Bacon1994], by having the target be randomly either a circle amongst diamonds or a diamond amongst circles on each trial (see Figure \@ref(fig:methodFig)A for an example from the current study).
+Under these conditions, both stimulus-driven [@Theeuwes1992] and goal-directed [@Bacon1994] accounts of attentional selection would predict capture, as the template that participants use to locate the target (i.e., any singleton) is broad enough to include the singleton distractor.
+As expected, under these singleton-search conditions Gaspelin et al.
+found that participants' overt attention was captured by the salient singleton.
+In Experiment 2, participants were instead encouraged to adopt a more specific target template [i.e., *feature-search mode*; @Bacon1994], by consistently mapping the target identity to one shape (e.g., search for a circle on every trial), and having a heterogeneous set of shapes act as the non-targets (see Figure \@ref(fig:methodFig)B).
+This manipulation makes searching for any singleton a highly inefficient strategy, as there are multiple singleton nontargets in the display (e.g., a circle, a square, a triangle, and a red shape).
+Thus, participants should be encouraged to search for the specific features that define the target (i.e., the "circleness" of the circle).
+Under these conditions, attention to the salient colour-singleton distractor was suppressed relative to the other non-targets, suggesting that it was treated differently from the other non-targets (inconsistent with goal-directed accounts), yet did not capture gaze (inconsistent with stimulus-driven accounts).
+By contrast, the signal suppression hypothesis can account for these findings by suggesting that the singleton generated an attentional priority signal as a consequence of its physical salience, but this signal could be suppressed by top-down control under conditions that promote a more specific search strategy (i.e., feature search).
+Importantly, this suppression effect was observed even for the most rapidly generated eye movements, which was taken as evidence that the suppression effect operates early in processing, before attention is initially allocated.
+
+## The role of selection history in guiding attention
+Up to this point we have discussed the set of influences on attentional control as a dichotomy: goal-directed versus stimulus-driven.
+However, a growing literature has questioned this framework, pointing to demonstrations of attentional selection biases that fall outside this dichotomy [@Awh2012; @LePelleya; @Failing2018].
+@Awh2012 suggested a third category of influences on attentional selection, labelled *selection history*.
+This category describes attentional biases that are formed through learned relationships between stimulus features and motivationally significant outcomes---such as reward [@Anderson2015a; @Failing2018; @LePelleya] or punishment [@Watson2019]---as well as other biases related to the history of attentional deployment that cannot be easily explained in terms of goal-directed or stimulus-driven control, such as biases for selecting stimulus features that have previously acted as targets [e.g., @Maljkovic1994].
+
+The influence of learned stimulus-reward associations on attentional capture is demonstrated in a study by Le Pelley et al.
+[-@LePelley2015b; see also @Pearson2015].
+In a variant of the additional singleton task, participants were more likely to make a saccade towards a colour-singleton distractor signalling the availability of high reward (e.g., 10$\text{\textcent{}}$) than a singleton distractor signalling low reward (1$\text{\textcent{}}$), even though looking at the reward-signalling singletons was counterproductive, as it resulted in the omission of the reward that would otherwise have been delivered.
+That is, participants were more likely to have their attention and gaze captured by a distractor signalling high reward, even though this led to the omission of more high rewards.
+This result cannot be explained in terms of stimulus-driven influences, as the colour-reward associations were counterbalanced across participants to avoid any influence of differential physical salience on capture.
+Similarly, the effect cannot be explained by goal-directed influences, as capture by the reward associated distractor was directly counterproductive to participants' goal of maximizing reward.
+Thus, this study demonstrates that experiencing the relationship between a stimulus feature and reward influences the likelihood that that feature will capture attention and gaze, a finding termed *value-modulated attentional capture* (VMAC).
+
+Pairing a stimulus with reward is thought to increase its attentional priority in a way that mimics or otherwise interacts with its physical salience.
+For example, eye-tracking studies have demonstrated that VMAC is largest for the most rapidly generated saccades, and diminishes with increasing saccade latency [@Pearson2016; @Failing2015], a pattern similar to that observed in capture by physical salience [e.g., @VanZoest2004].
+Similarly, electrophysiological studies have shown that reward affects ERP components thought to index low-level perceptual activity [@Hickey2010].
+This is consistent with the idea of *incentive salience* [@Berridge1998], wherein a reward-related stimulus becomes more salient and attention grabbing to the observer through a change in its perceptual representation.
+This begs the question, if associating a stimulus with reward increases its perceptual priority as though it has become more physically salient, can this priority signal be suppressed by the top-down control process proposed by the signal suppression hypothesis?
+That is, can incentive salience be suppressed in the same way as physical salience?
+Aside from the theoretical importance of this question, it may also have important clinical implications.
+Recent evidence suggests that the processes underlying VMAC are closely related to the attentional biases towards drug-related stimuli observed in addiction [@Albertella2017a; @Anderson2013; for review see @Field2008], which can promote relapse in recovering addicts [@Marissen2006; @Waters2012; @Marhe2013].
+Thus it is important to know whether top-down cognitive control processes can be used to overcome the influence of reward on attention when such capture is counterproductive and contrary to our goals.
+We addressed this question by combining Le Pelley et al.'s VMAC procedure with Gaspelin et al.'s (2017) overt attentional suppression procedure to investigate whether reward-related attentional biases can be suppressed by top-down control processes under conditions promoting feature search.
 
@@
 
+## Participants
+This study was approved by the UNSW Sydney Human Research Ethics Advisory Panel (Psychology).
+Previous studies of VMAC using gaze measures [@LePelley2015b; @Pearson2015; @Pearson2016] have demonstrated medium to large effect sizes ($d_z$ = 0.41--1.4, mean = 0.73), and previous studies of overt attentional suppression of physical salience [@Gaspelin2016] have demonstrated a large effect size ($d_z$ = 1.6).
+Based on an anticipated effect size of $d$ = 0.73, a power analysis conducted with G\*Power [@Faul2007] indicated that 32 participants per group would provide adequate power (power ~.98 to detect within-subjects effects and power of ~.82 for between-subjects effects).
+We therefore tested 64 UNSW Sydney students ($n =$ 32 per group, `r genders_summ$n[genders_summ$gender == 'f']` females, age $M=$ `r ages_summ$m`, $SD=$ `r ages_summ$stdev`) who participated in exchange for course credit or payment of 20 AUD.
+All participants also received a monetary bonus that was dependent on their performance ($M =$ `r bonuses_sum$m` AUD, $SD =$ `r bonuses_sum$stdev` AUD).
+
+## Apparatus
+Participants were tested using a Tobii TX-300 eye-tracker (sampling frequency 300 Hz), mounted on a 23-inch monitor (1920 $\times$ 1080 resolution, 60 Hz refresh rate).
+Participants' heads were positioned in a chin rest 60 cm from the screen.
+Gaze data were down-sampled to 100 Hz for gaze contingent calculations during stimulus presentation, with gaze position in each sample defined as the average position during the preceding 10 ms window.
+Stimulus presentation was controlled by MATLAB using the Psychophysics Toolbox extensions [@Brainard1997; @Kleiner2007; @Pelli1997].
+Experiment scripts, analysis scripts, and raw data are available at (**OSF**).
+
+## Stimuli
+The task was based on that used by @Gaspelin2016 and Pearson et al.
+[-@Pearson2015; -@Pearson2016].
+Each trial consisted of a fixation display, a search display, and a feedback display (see Figure \@ref(fig:methodFig)C).
+All stimuli were presented on a black background.
+The fixation display consisted of a white cross (0.5$^\circ$ visual angle), presented in the centre of the screen and surrounded by a white circle (diameter 3.0$^\circ$).
+The search display consisted of four filled shapes (size 1.6$^\circ$ $\times$ 1.6$^\circ$) presented above, below, left and right of screen centre (eccentricity 4.5$^\circ$).
+One of the shapes was designated as the target, and the other three shapes were designated non-targets.
+For all participants, the target was randomly determined to be either a circle or a diamond on each trial [^1].
+The identity of the non-target shapes varied by search condition.
+For the *singleton search* condition, the non-target stimuli were all rendered as the alternative target shape (i.e., if the target was a diamond, all of the non-targets were circles; Figure \@ref(fig:methodFig)B).
+For the *feature search* condition, the non-target stimuli were randomly selected without replacement from a set of two squares and two hexagons, and were never rendered as the alternative target shape (Figure \@ref(fig:methodFig)C).
+The target and two of the non-targets were always rendered in grey (CIE $x$,$y$ chromaticity coordinates of .327/.400).
+On the majority of trials, one of the non-target shapes (the *singleton distractor*) was rendered in either orange or blue (CIE $x$,$y$ coordinates .492/.445 and .192/.216, respectively).
+On the remaining trials, all shapes were rendered in grey such that there was no singleton distractor.
+The values of blue and orange had similar luminance (~24.5 cd/m^2^), which was higher than that of grey (~8.3 cd/m^2^).
+The feedback display showed the points earned on the current trial.
+If the response time (RT) exceeded the soft-timeout threshold (see below), the message "Too slow" appeared below the reward feedback.
+
+[^1]: This aspect of our design differs from that of @Gaspelin2016.
+In their study, for half of participants in the feature search condition the target was always a circle, and for other participants the target was always a diamond.
+By contrast, for the singleton search condition, for all participants the target was a circle among diamonds on some trials, and a diamond among circles on others.
+That is, target identity (circle/diamond) was manipulated between-subjects for the feature search condition, and within-subjects for the singleton search condition.
+In the current study, we equated the two conditions by varying target identity within-subjects for all participants.
+This ensured that any difference between the two search conditions was driven by a difference in the specificity of participants’ target template and not by a difference in participants’ history of selecting the target shape [e.g., @Maljkovic1994].
+
+```{r methodFig, fig.align='center', fig.cap = '(ref:methodFig)', out.width='100%'}
+knitr::include_graphics(here("analysis", "figures", "Methods_fig.png"), dpi = 300)
+
+```
+
+## Design
+Participants were randomly assigned to either the singleton search or feature search conditions.
+For half of the participants in each condition, orange was the high-reward colour and blue was the low-reward colour; these colour-reward relationships were reversed for the remaining participants.
+There were three types of trial: (1) *high-reward trials*, in which the singleton distractor was rendered in the high-reward colour and 500 points were available for a rapid respnse (see below); (2) *low-reward trials*, in which the singleton distractor was rendered in the low-reward colour and 10 points were available; and (3) *distractor-absent trials*, in which all non-targets were rendered in grey and 10 points were available.
+The experiment comprised 8 blocks of 60 trials each, for a total of 480 experimental trials.
+Each block consisted of 20 high-reward trials, 20 low-reward trials, and 20 distractor-absent trials, in random order.
+Participants took a short break between blocks.
+
+On each trial, the location of the target was determined randomly.
+On high-reward and low-reward trials, the location of the singleton distractor was randomly selected from the three remaining locations.
+A small, circular region of interest (ROI) with diameter 1.7$^\circ$ visual angle was defined around the centre of the target, with a larger ROI (diameter 2.6$^\circ$) defined around the singleton distractor.
+A response was registered when the participant had accumulated 100 ms of gaze dwell time within the target ROI.
+If any gaze was detected within the singleton ROI, the reward for the trial was not awarded (henceforth referred to as *reward omissions*).
+On distractor-absent trials, one of the non-target shapes was selected at random to act as the "singleton distractor" location.
+Any gaze falling within the ROI around this (non-salient) stimulus triggered a reward omission in the same way as on trials with a singleton distractor.
+Responses with RTs that were slower than the soft-timeout threshold (1000 ms) were also not rewarded.
+
+## Procedure
+Participants were told that their task was to move their eyes to the target "as quickly and directly as possible" on each trial.
+Those in the singleton search condition were instructed to move their eyes to the "unique shape" on each trial, whereas those in the feature search condition were instructed to move their eyes to the "circle or diamond".
+Participants were also informed about the relationships between distractor colour and reward availability (e.g., that if an orange shape was present in the display they could 500 points, and if a blue shape was present they could win 10 points); they were not informed that looking at the reward-associated distractor would cancel the reward for the current trial.
+The instructions stated that they would earn 0 points if their RT was slower than the soft-timeout threshold, and that their reward also depended on how accurately they moved their eyes to the target.
+Participants were told that they could earn between 7 and 15 AUD for good performance, but no specific information about the conversion rate from points to AUD was provided.
+
+Each trial began with the presentation of the fixation display.
+Participants' gaze location was superimposed over the display as a small yellow dot.
+Once 700 ms of gaze time had accumulated within the circle surrounding the fixation cross, or after 5000 ms, the cross and the circle turned yellow and the dot marking the participants' gaze location disappeared.
+After 300 ms the screen blanked, and after a 150 ms delay the search display was presented until a response was recorded, or until 2000 ms (hard-timeout threshold) had passed.
+The feedback display then appeared for 2500 ms during the first block, and 1500 ms in all subsequent blocks.
+The inter-trial interval was 700 ms.
+
+## Data analysis
+In line with previous VMAC protocols [e.g., @LePelley2015b; @Pearson2016], data from the first two experimental trials, and the first two trials after each break were discarded.
+Hard timeouts (`r op(hardtimeouts$perc[hardtimeouts$timeout == 1], 1)`\% of all trials) were also discarded.
+One participant was replaced because their mean proportion of valid gaze samples during each trial was less than 50\%.
+One other participant was replaced after reporting that they had misunderstood the task instructions.
+For the remaining participants, valid gaze data were registered on an average of `r op(allTracks_summ$mean_trial_prop, 1)`\% ($SD=$ `r op(allTracks_summ$sd_trial_prop, 1)`\%) of samples, suggesting high fidelity of gaze data.
+
+Saccades were detected in the raw gaze data (sampled at 300 Hz) using a velocity-threshold identification algorithm [@Salvucci2000].
+Saccade latency was measured as the duration from onset of the search display to the point at which eye-movement velocity exceeded 40$^\circ$/s.
+Following previous protocols [@Pearson2016], we excluded trials with anticipatory saccades (saccade latency <80 ms; `r op(totalSaccadeTrialsDiscarded$prop_anticipatory,1)`\% of all trials), trials in which no gaze was recorded within 100 pixels (5.1$^\circ$) of the fixation point within the first 80 ms (`r op(totalSaccadeTrialsDiscarded$prop_outside_fix, 1)`\% of trials), and trials in which there was insufficient gaze data to detect a saccade (`r op(totalSaccadeTrialsDiscarded$prop_bad_data, 1)`\% of trials).
+To classify the direction of the first saccade on each trial, the angular deviation between the endpoint of the saccade and each stimulus location was calculated.
+The saccade was defined as going in the direction of a stimulus if the angular deviation was less than $30^\circ$ to the left or right of that stimulus.
+
+There were two primary dependent measures: (1) the percentage of reward omissions---that is, trials on which participants looked at the singleton distractor (or nonsingleton distractor randomly assigned to act as the "singleton distractor" location: see Design) and hence reward was cancelled---for high-reward, low-reward, and distractor-absent trials, and (2) the percentage of first saccades directed towards the singleton distractor versus the average nonsingleton distractor (that is, the mean across the two nonsingleton distractors present in each search display; see Figure \@ref(fig:methodFig)), on high-reward and low-reward trials.
+
+For the analysis of reward omissions, we were particularly interested in two contrasts.
+First, the comparison between the high-reward and low-reward trials allowed us to examine the effect of reward on attention, since both displays contained a physically salient colour-singleton distractor, with the only difference being the magnitude of reward that the distractor signalled.
+Second, the comparison between the low-reward and distractor-absent trials allowed us to examine the effect of physical salience on attention, since these different trial types differed in whether the display contained a colour-singleton distractor, but had the same reward magnitude available (10 points).
+These contrasts were compared for the singleton search and feature search conditions using 2 $\times$ 2 mixed ANOVAs.
+
+For the analysis of saccade direction, we were primarily interested in the difference between the percentage of trials on which first saccades were directed towards the singleton distractor and the mean of both nonsingleton distractors across high- and low-reward trials.
+These data were converted into a *capture score* by subtracting the percentage of trials where the first saccade was directed towards the average nonsingleton from the percentage of trials where the first saccade was directed towards the singleton.
+A positive capture score indicated that gaze was more likely to have been directed towards the singleton than the average nonsingleton (i.e., the singleton had captured overt attention), whereas a negative capture score indicated that gaze was more likely to be directed toward the average nonsingleton than the singleton (overt attention to the singleton was suppressed).
+A 2 $\times$ 2 mixed ANOVA was used to compare capture scores for high- and low-reward trials across search conditions.
+In addition to any group differences in the patterns of attentional capture and/or suppression across trial type, we were also interested in directly investigating whether attention was captured by the singleton distractor (capture score $>0$), or whether attention to the singleton was suppressed (capture score $<0$) for each trial type $\times$ search condition combination.
+We therefore tested the capture score for each trial type and search condition with planned one-sample *t*-tests against zero.
+
+Statistical analyses were conducted in `r cite_r()` with the afex package  [@R-afex] used to calculate ANOVAs and the emmeans package [@R-emmeans] for follow-up contrasts.
+Greenhouse-Geisser corrections are reported where appropriate.
+In cases where a conclusion is drawn on the basis of a null effect, we report the Bayes factor that corresponds to a Bayesian *t*-test using the default Cauchy prior, conducted using the BayesFactor package [@R-BayesFactor].
+
 # Results
 
-```{r get-data, eval = FALSE}
-# Note the path that we need to use to access our data files when rendering this document
-my_data <- readr::read_csv(here::here('analysis', 'data', 'raw_data', 'my_csv_file.csv'))
+## Reward Omissions
+Figure \@ref(fig:OmissionPlot) displays the percentage of trials on which a reward omission was triggered by the participant looking at the singleton distractor, across search conditions and trial types, averaged across all trial-blocks.
+
+```{r OmissionPlot, fig.align='center', fig.cap = '(ref:omissions)', out.width='100%'}
+knitr::include_graphics(here("analysis", "figures", "omission_plot.png"), dpi = 300)
+
 ```
 
+### Effect of reward.
+ANOVA analysis of the percentage of reward omissions with factors of trial type (high-reward vs low-reward) and search condition (singleton search vs feature search) revealed a main effect of trial type `r apa_print.afex_aov(omissions_vmac.ANOVA, mse = F, es = "pes")$full_result$dType`.
+Planned paired-samples *t*-tests confirmed that participants triggered more reward omissions (i.e., were more likely to look at the colour-singleton distractor) on high-reward trials than low-reward trials in both the singleton search condition, `r apa_print(singleton_VMAC_omissions.ttest)$statistic`, $d_z=$ `r singleton_VMAC_omissions.es` (Figure \@ref(fig:OmissionPlot)A) and feature search condition, `r apa_print(feature_VMAC_omissions.ttest)$statistic`, $d_z=$ `r feature_VMAC_omissions.es` (Figure \@ref(fig:OmissionPlot)B), demonstrating an effect of reward on overt attentional capture (i.e., a VMAC effect) regardless of whether participants were encouraged to adopt a more specific target template.
+Importantly, search condition did not exert a significant main effect, `r apa_print.afex_aov(omissions_vmac.ANOVA, mse = F, es = "pes")$full_result$condition`, or significantly interact with the effect of trial type, $F(1,62) < 0.01$, $p=.985$, $\hat{\eta}^2_p < .0001$.
+In order to quantify support for the null hypothesis that the influence of reward on attentional capture did not vary depending on participants' target template, we conducted a Bayesian *t*-test to compare the magnitude of the VMAC effect across the two search conditions.
+This revealed a Bayes Factor of `r apa_print(vmac_condition_bayes)$statistic`, indicating moderate support for the null hypothesis of no difference in the size of the VMAC effect under singleton search and fearure search conditions.
+
+### Effect of physical salience.
+ANOVA analysis of the percentage of reward omissions revealed a non-significant main effect of trial type (low-reward vs distractor-absent), `r apa_print.afex_aov(omissions_salience.ANOVA, mse = F, es = "pes")$full_result$dType`, and a significant main effect of search condition (singleton search vs feature search), `r apa_print.afex_aov(omissions_salience.ANOVA, mse = F, es = "pes")$full_result$condition`.
+Critically, this main effect was qualified by a significant trial type $\times$ search condition interaction, `r apa_print.afex_aov(omissions_salience.ANOVA, mse = F, es = "pes")$full_result$condition_dType`, indicating that the effect of physical salience on overt attentional capture differed across search conditions.
+Paired-samples *t*-tests revealed that participants in the singleton search condition triggered significantly more reward omissions on trials that contained a colour-singleton distractor than those that did not, `r apa_print(singleton_physicalsalience_omissions.ttest)$statistic`, $d_z=$ `r singleton_physicalsalience_omissions.es`, suggesting that overt attention was captured by the physically salient singleton.
+In contrast, participants in the feature search condition triggered fewer reward omissions on trials containing a colour-singleton distractor than trials with no coloured singleton, `r apa_print(feature_physicalsalience_omissions.ttest)$statistic`, $d_z=$ `r feature_physicalsalience_omissions.es`, suggesting that overt attention to the singleton distractor was suppressed under conditions promoting feature search, consistent with previous findings [@Gaspelin2016].
+
+```{r SaccadePlot, fig.align='center', fig.cap = '(ref:saccadeFig)', out.width='100%'}
+knitr::include_graphics(here("analysis", "figures", "saccade_plot.png"), dpi = 300)
+
+```
+
+## First Saccade Direction
+Figure \@ref(fig:SaccadePlot) shows the percentage of first saccades directed towards each stimulus type (i.e., the target[^2], average nonsingleton distractor, and singleton distractor) on high- and low-reward trials for the singleton search (Figure \@ref(fig:SaccadePlot)A) and feature search (Figure \@ref(fig:SaccadePlot)C) conditions; Figures \@ref(fig:SaccadePlot)B and \@ref(fig:SaccadePlot)D show capture scores (difference in percentage of first saccades directed towards singleton versus average nonsingleton distractor) for the singleton search and feature search conditions, respectively.
+ANOVA analysis of capture scores revealed a significant main effect of trial type (high-reward vs low-reward), `r apa_print.afex_aov(capture.ANOVA, mse = F, es = "pes")$full_result$dType`, with the singleton capturing attention more often on high-reward trials than low-reward trials; once again demonstrating a VMAC effect.
+A main effect of search condition (singleton search vs feature search), `r apa_print.afex_aov(capture.ANOVA, mse = F, es = "pes")$full_result$condition`, indicated that both the high-reward and low-reward singleton captured attention more often, on average, in the singleton search condition than the feature search condition.
+Importantly, the trial type $\times$ search condition interaction was non-significant, `r apa_print.afex_aov(capture.ANOVA, mse = F, es = "pes")$full_result$condition_dType`, with a corresponding Bayes factor of `r apa_print(capture_bayes)$statistic` indicating moderate support for the null hypothesis that search condition had no effect on the magnitude of the VMAC effect on first saccade direction.
+
+[^2]: Note that the comparison of interest in determining whether a stimulus captured attention, or was otherwise suppressed, is the percentage of first saccades to the singleton vs.
+the average nonsingleton distractor.
+Thus, while we have included the percentage of first saccades to the target in Figure \@ref(fig:SaccadePlot) for the sake of completeness, we have not included these data in our analyses.
+
+Next we tested whether overt attention to each distractor type was captured or suppressed in each search condition.
+Planned one-sample *t*-tests showed that capture scores were significantly greater than zero (indicating that overt attention was captured by the high-reward singleton) under conditions promoting singleton search, `r apa_print(Singleton_high.ttest)$statistic`, $d_z=$ `r Singleton_high.es`, as well as feature search, `r apa_print(Feature_high.ttest)$statistic`, $d_z=$ `r Feature_high.es`.
+For the low-reward distractor, there was a non-significant numerical trend towards capture in the singleton search condition, `r apa_print(Singleton_low.ttest)$statistic`, $d_z=$ `r Singleton_low.es`.
+In contrast, for the feature search condition, capture score was significantly below zero, `r apa_print(Feature_low.ttest)$statistic`, $d_z=$ `r Feature_low.es`, indicating that overt attention to the low-reward singleton was suppressed.
+Thus, in line with previous findings [@Gaspelin2016], our data suggest that overt attention to physically salient singletons can be suppressed when participants are encouraged to adopt a specific target template.
+However, singletons that have been associated with high-reward reward capture overt attention, regardless of participants' target template and despite such capture being directly counterproductive to earning reward.
+
+```{r blockPlot, fig.align='center', fig.cap = '(ref:blockFig)', out.width='100%'}
+knitr::include_graphics(here("analysis", "figures", "capture_plot_by_block.png"), dpi = 300)
+
+```
+
+## Development of attentional capture/suppression across training
+Recent research suggests that attentional suppression develops over the course of repeated experience with the to-be-ignored stimulus feature [@Gaspelin2018b; @Vatterott2012].
+In order to investigate this in the current study, we divided the experiment into four epochs (96 trials/epoch) and calculated capture scores (as described earlier) for each trial type (see Figure \@ref(fig:blockPlot)).
+These data were analysed using an ANOVA with factors of search condition (singleton search, feature search), trial type (high, low), and epoch (1--4).
+This once again revealed a main effect of search condition, `r apa_print.afex_aov(capture_byblock.ANOVA, mse = F, es = "pes")$full_result$condition`, and trial type, `r apa_print.afex_aov(capture_byblock.ANOVA, mse = F, es = "pes")$full_result$dType`.
+Critically, there was also a significant interaction between trial type and epoch, `r apa_print.afex_aov(capture_byblock.ANOVA, mse = F, es = "pes")$full_result$newblock_dType`.
+There were no other significant main or interaction effects (all *p*'s $>.25$).
+Follow-up contrasts revealed a significant negative linear trend for low-reward trials, $t(369)=$ `r printnum(capture_byblock.polys$t.ratio[[4]])`, $p$ `r printp(capture_byblock.polys$p.value[[4]])`, with capture by the low-reward distractor decreasing as the experiment progressed and experience with the physically salient feature increased (notably, in the feature search condition scores become increasingly negative, indicating increasing \emph{suppression} of the low-reward distractor).
+In contrast, for high-reward trials there was a significant positive linear trend, $t(369)=$ `r printnum(capture_byblock.polys$t.ratio[[1]])`, $p=$ `r printp(capture_byblock.polys$p.value[[1]])`, with capture by the high-reward distractor increasing as the experiment progressed and experience with the reward associated feature increased.
+
+```{r VincentizedPlot, fig.align='center', fig.cap = '(ref:vincentizedFig)', out.width='100%'}
+knitr::include_graphics(here("analysis", "figures", "vincentized_plot.png"), dpi = 300)
+
+```
+
+## Attentional capture/suppression effects for the fastest quartile of saccadic latencies
+To investigate the time course of the overt attentional capture and suppression effects, we analysed capture scores (proportion of first saccades towards the singleton distractor minus the average nonsingleton distractor) on high-reward and low-reward trials as a function of saccade latency using the Vincentizing procedure [@Ratcliff1979].
+We calculated mean saccade latency and capture score separately for each trial type and quartile of the individual saccade latency distributions.
+We then analysed the capture scores for the most rapidly generated saccades.
+According to the signal suppression hypothesis, the top-down suppression effect is activated early in processing, prior to the initial allocation of attention [@Gaspelin2018a].
+Therefore the speed with which a saccade is initiated should have no effect on the extent to which overt attention can be suppressed.
+As illustrated in Figure \@ref(fig:VincentizedPlot), the most rapidly generated saccades were captured by the high-reward singleton (capture scores $>0$) in both the singleton search, `r apa_print(vincentized_singleton_high_q1.ttest)$statistic`, $d_z=$ `r vincentized_singleton_high_q1.es`, and feature search conditions, `r apa_print(vincentized_feature_high_q1.ttest)$statistic`, $d_z=$ `r vincentized_feature_high_q1.es`.
+Similarly, the the most rapidly generated saccades were captured by the low-reward singleton in both the singleton search, `r apa_print(vincentized_singleton_low_q1.ttest)$statistic`, $d_z=$ `r vincentized_singleton_low_q1.es`, and feature search conditions, `r apa_print(vincentized_feature_low_q1.ttest)$statistic`, $d_z=$ `r vincentized_feature_low_q1.es`.
+It is notable that we observed capture (rather than suppression) for the fastest saccades for both trial-types in the feature search condition.
+This finding is inconsistent with Gaspelin et al.’s [-@Gaspelin2016] previous report of attentional suppression of physically salient singleton distractors in the fastest eye-movements.
+
 # Discussion
+In this experiment, we investigated the role of top-down control processes in actively suppressing overt attention to physically salient and reward-associated distractor stimuli.
+In line with the signal suppression hypothesis [@Gaspelin2016; @Gaspelin2015], we found that overt attention to physically salient colour singleton distractors can be actively suppressed under conditions that promote top-down guidance of attention.
+Consistent with recent findings [@Gaspelin2018b; @Vatterott2012], this attentional suppression effect gradually emerged over the course of the experiment, as participants gained experience with the physically salient distractor feature.
+Furthermore, we found an effect of reward association on overt attention [i.e., VMAC; @LePelley2015b; @Pearson2015], with participants' gaze more likely to be captured by distractor stimuli that signalled high reward than low reward, even though looking at reward-signalling distractors caused omission of rewards that otherwise would have been delivered.
+Similar to the attentional suppression effect, attentional capture by reward-associated distractors also emerged over the course of the experiment, as participants experienced more pairings of stimulus features with reward.
+Critically, this study was the first to demonstrate that---unlike the influence of physical salience---the influence of reward association on attention cannot be suppressed under conditions that promote top-down guidance of attention.
+Regardless of whether participants were encouraged to search for specific target defining features (i.e., feature search mode) or to search for the odd-one-out (singleton search mode), stimuli associated with high reward captured overt attention.
+Notably, this attentional bias was counterproductive, in that it led to the omission of more high rewards than low rewards, and so participants should have been highly motivated to suppress their attention to the high-reward distractor if possible.
+Nevertheless, the high-reward distractor captured attention, even under conditions that allowed participants to suppress their attention to physically salient distractors that were associated with low reward.
+Our key finding, then, is that reward-related stimuli constitute especially potent attentional priority signals that are relatively immune to suppression by top-down control processes that can act to prevent distraction by physical salience.
 
-# Conclusion
+Most influential models of attentional selection assume that stimulus-driven and goal-directed influences are integrated onto a common priority map in the brain, with attention directed towards the spatial location with the highest peak of activation [e.g., @Itti2001; @Theeuwes2010; @Wolfe2007].
+The priority map concept has also been used to explain how selection history influences attentional allocation [@Awh2012; @Failing2018], with the attentional priority signal of reward-related stimulus features increasing with repeated stimulus-reward pairings through a process of associative learning [@Pearson2016; @LePelleya].
+Recent formulations of the signal suppression hypothesis have suggested that the top-down suppression mechanism may operate in a similar way, with the attentional priority of to-be-ignored stimulus features being proactively downweighted with repeated experience [@Gaspelin2018a].
+At first glance, the results of the current study may seem inconsistent with the idea that reward and top-down suppression engage in competition on a common priority map, as the magnitude of the VMAC effect did not differ between search conditions, even though the feature search condition should have encouraged top-down guidance of attention.
+However, there was an overall decrease in the amount of capture by both the high- and low-reward distractor in the feature search condition This raises the possibility that repeated experience of the physically salient stimulus features (i.e., orange and blue colour) allows the attentional priority of those features to be uniformly downweighted by the top-down suppression mechanism.
+In addition, our findings are consistent with the idea that repeated experience of the stimulus feature-reward pairings selectively upweights the attentional priority of the high-reward distractor, such that it overpowers the influence of top-down suppression and thus captures attention.
 
-# Acknowledgements
+An inconsistency between the results of the current study and that of @Gaspelin2016 comes from the time-course of the attentional capture and suppression effects that were observed.
+According to the signal suppression hypothesis, top-down suppression operates prior to the initial allocation of attention, and so suppression should be observed even for the most rapidly generated saccades.
+Consistent with this idea, @Gaspelin2016 observed an overt attentional suppression effect to physically salient singleton distractors amongst the fastest quartile of saccade latencies.
+In contrast, in the current experiment we observed overt attentional capture in the fastest quartile of saccade latencies, with the suppression effect emerging on trials with slower saccades.
+Methodological differences between Gaspelin et al.'s  [-@Gaspelin2016] experiment and the current study may be responsible for this discrepancy.
+For example, the availability of reward on low-reward trials may have influenced capture, either by somewhat increasing the attentional priority of the stimulus feature associated with low-reward reward, or by otherwise influencing participants' motivation to respond quickly.
+Alternatively, the discrepancy in findings may reflect our use of two potential targets (circle and diamond) in the feature search condition, as opposed to the same target on all trials in Gaseplin et al.'s procedure.
+Having two possible targets could reduce the influence of trial-by-trial upweighting of target features [@Maljkovic1994], but may also result in less effective feature search [e.g., @Houtkamp2009; but see @Grubert2015].
+How these methodological differences might influence the time-course of overt attentional capture and suppression remains a question for future research.
+Nonetheless, the finding does raise questions about whether the attentional suppression effect that we have observed is truly the result of proactive top-down suppression of salient stimuli, as suggested by the signal suppression hypothesis, or potentially the result of rapid covert disengagement from the salient stimuli [see @Theeuwes2010; @VanZoest2004 for similar arguments].
 
-<!-- The following line inserts a page break when the output is MS Word. For page breaks in PDF, use \newpage on its own line.  -->
-##### pagebreak
+As mentioned previously, attentional capture by stimuli associated with monetary rewards can be mapped on to the attentional biases to drug-related stimuli seen in addiction.
+Indeed, recent findings suggest that these biases may be the result of a common mechanism [@Anderson2013; @Albertella2017a].
+This is consistent with the idea of incentive salience [@Berridge1998], where the perceptual representation of an otherwise neutral stimulus is modified so as to become more salient and attention grabbing to the observer, as a result of its association with a desired outcome (e.g., drugs, money).
+The current study suggests that incentive salience has a particularly powerful influence on the attentional system, overcoming top-down control mechanisms that can effectively prevent capture by physically salient stimuli.
+This may have implications for the development of treatments for substance use disorders that target these attentional biases.
+
+(ref:methodFig) Trial structure of the current task.
+(A) Participants in the singleton search condition experienced search displays where the target was a unique shape (either a circle amongst diamonds or diamond amongst circles).
+(B) Participants in the feature search condition experienced search displays where the target was either a circle or diamond shape presented amongst a set of heterogenous shapes.
+On most trials, one of the non-target shapes was rendered in either orange or blue so as to be a colour singleton distractor, leaving two other nonsingleton non-targets in the display.
+(C) Participants began by fixating on a centrally presented fixation cross.
+A search display then appeared, and participants were required to make a rapid saccade to the target.
+The colour of the singleton distractor indicated the available reward (10 or 500 points), but looking at the distractor led to reward omission.
+
+(ref:omissions) Filled points show the mean percentage of reward omissions on each trial type for the (A) singleton search condition, and (B) feature search condition.
+A reward omission was triggered when the participant looked at the singleton distractor (or the nonsingleton distractor assigned as the "singleton" location on distractor absent trials; see Design) prior to looking at the target.
+Individual participant performance is shown by faint grey lines.
+Error bars in all figures represent within-subjects SEM [@Cousineau2005] with Morey [-@Morey2008] correction.
+*** $p<.005$, * $p<.05$.
+
+(ref:saccadeFig) First saccade direction data.
+(A) Filled points show the mean percentage of first saccades directed towards the target, average nonsingleton distractor and singleton distractor, on high- and low-reward trials, for participants in the singleton search condition.
+Individual participant performance shown by faint underlying points.
+(B) These data are converted into capture scores (calculated as the percentage saccades to the singleton distractor minus percentage saccades to the average nonsingleton distractor) for high-reward and low-reward trials.
+Positive capture scores indicate that the singleton distractor captured overt attention, and negative capture scores indicate that the overt attention to the singleton distractor was suppressed.
+(C) Mean percentage of first saccades to each stimulus type, and (D) capture scores for participants in the feature search condition.
+Error bars represent within-subjects SEM.
+*** $p<.001$, * $p<.05$.
+
+(ref:blockFig) Capture scores across five 96-trial epochs of the experiment for participants in the (A) singleton search condition and (B) feature search condition.
+Positive capture scores indicate that the singleton distractor captured attention, whereas negative capture scores indicate that attention to the singleton distractor was suppressed.
+Error bars represent within-subjects SEM.
+
+(ref:vincentizedFig) Capture scores as a function of saccade latency quartile for participants in the (A) singleton search condition and (B) feature search condition.
+Mean first saccade latencies and the proportion of first saccades directed towards each stimulus type were calculated separately for each quintile of individual participant saccade latency distributions using the Vincentizing procedure [@Ratcliff1979].
+Positive capture scores indicate that the singleton distractor captured attention, whereas negative capture scores indicate that attention to the singleton distractor was suppressed.
+Error bars represent within-subjects SEM.
+*** $p<.001$, ** $p<.01$.
+
+\newpage
 
 # References
-<!-- The following line ensures the references appear here for the MS Word or HTML output files, rather than right at the end of the document (this will not work for PDF files):  -->
-<div id="refs"></div>
-
-##### pagebreak
-
-### Colophon
-
-This report was generated on `r Sys.time()` using the following computational environment and dependencies:
-
-```{r colophon, cache = FALSE}
-# which R packages and versions?
-devtools::session_info()
+```{r create_r-references}
+r_refs(file = "r-references.bib")
 ```
 
-The current Git commit details are:
+\begingroup
+\setlength{\parindent}{-0.5in}
+\setlength{\leftskip}{0.5in}
 
-```{r}
-# what commit is this file at? 
-git2r::repository(here::here())
-```
+<div id = "refs"></div>
+\endgroup

### 2019-04-18 analysis/paper/paper.tex
testing circleci

\documentclass[jou, a4paper, noextraspace,floatsintext]{apa6}
\usepackage{lmodern}
\usepackage{amssymb,amsmath}
\usepackage{ifxetex,ifluatex}
\usepackage{fixltx2e} % provides \textsubscript
\ifnum 0\ifxetex 1\fi\ifluatex 1\fi=0 % if pdftex
  \usepackage[T1]{fontenc}
  \usepackage[utf8]{inputenc}
\else % if luatex or xelatex
  \ifxetex
    \usepackage{mathspec}
  \else
    \usepackage{fontspec}
  \fi
  \defaultfontfeatures{Ligatures=TeX,Scale=MatchLowercase}
\fi
% use upquote if available, for straight quotes in verbatim environments
\IfFileExists{upquote.sty}{\usepackage{upquote}}{}
% use microtype if available
\IfFileExists{microtype.sty}{%
\usepackage{microtype}
\UseMicrotypeSet[protrusion]{basicmath} % disable protrusion for tt fonts
}{}
\usepackage{hyperref}
\hypersetup{unicode=true,
            pdftitle={Overt attentional capture by reward-related stimuli overcomes top-down suppression},
            pdfauthor={Daniel Pearson, Poppy Watson, Phillip Cheng, \& Mike E. Le Pelley},
            pdfkeywords={attentional capture, reward, suppression, cognitive control},
            pdfborder={0 0 0},
            breaklinks=true}
\urlstyle{same}  % don't use monospace font for urls
\usepackage{graphicx,grffile}
\makeatletter
\def\maxwidth{\ifdim\Gin@nat@width>\linewidth\linewidth\else\Gin@nat@width\fi}
\def\maxheight{\ifdim\Gin@nat@height>\textheight\textheight\else\Gin@nat@height\fi}
\makeatother
% Scale images if necessary, so that they will not overflow the page
% margins by default, and it is still possible to overwrite the defaults
% using explicit options in \includegraphics[width, height, ...]{}
\setkeys{Gin}{width=\maxwidth,height=\maxheight,keepaspectratio}
\IfFileExists{parskip.sty}{%
\usepackage{parskip}
}{% else
\setlength{\parindent}{0pt}
\setlength{\parskip}{6pt plus 2pt minus 1pt}
}
\setlength{\emergencystretch}{3em}  % prevent overfull lines
\providecommand{\tightlist}{%
  \setlength{\itemsep}{0pt}\setlength{\parskip}{0pt}}
\setcounter{secnumdepth}{0}
% Redefines (sub)paragraphs to behave more like sections
\ifx\paragraph\undefined\else
\let\oldparagraph\paragraph
\renewcommand{\paragraph}[1]{\oldparagraph{#1}\mbox{}}
\fi
\ifx\subparagraph\undefined\else
\let\oldsubparagraph\subparagraph
\renewcommand{\subparagraph}[1]{\oldsubparagraph{#1}\mbox{}}
\fi

%%% Use protect on footnotes to avoid problems with footnotes in titles
\let\rmarkdownfootnote\footnote%
\def\footnote{\protect\rmarkdownfootnote}

  \title{Overt attentional capture by reward-related stimuli overcomes top-down
suppression}
    \author{Daniel Pearson\textsuperscript{1}, Poppy Watson\textsuperscript{1},
Phillip Cheng\textsuperscript{2}, \& Mike E. Le
Pelley\textsuperscript{1}}
    \date{}

\shorttitle{Reward overcomes attentional suppression}
\affiliation{
\vspace{0.5cm}
\textsuperscript{1} School of Psychology, UNSW Sydney\\\textsuperscript{2} Department of Psychology, Macquarie University}
\keywords{attentional capture, reward, suppression, cognitive control\newline\indent Word count: 6656}
\usepackage{csquotes}
\usepackage{upgreek}
\captionsetup{font=singlespacing,justification=justified}

\usepackage{longtable}
\usepackage{lscape}
\usepackage{multirow}
\usepackage{tabularx}
\usepackage[flushleft]{threeparttable}
\usepackage{threeparttablex}

\newenvironment{lltable}{\begin{landscape}\begin{center}\begin{ThreePartTable}}{\end{ThreePartTable}\end{center}\end{landscape}}

\makeatletter
\newcommand\LastLTentrywidth{1em}
\newlength\longtablewidth
\setlength{\longtablewidth}{1in}
\newcommand{\getlongtablewidth}{\begingroup \ifcsname LT@\roman{LT@tables}\endcsname \global\longtablewidth=0pt \renewcommand{\LT@entry}[2]{\global\advance\longtablewidth by ##2\relax\gdef\LastLTentrywidth{##2}}\@nameuse{LT@\roman{LT@tables}} \fi \endgroup}

\raggedbottom

\authornote{\textbf{Conflict of interest:} The authors declare
no conflict of interest.

\textbf{Funding:} This research was supported by Australian Research
Council grant DP170101715. Daniel Pearson was supported by an Australian
Government Research Training Program Scholarship.

Correspondence concerning this article should be addressed to Daniel
Pearson, School of Psychology, University of New South Wales, UNSW
Sydney NSW 2052, Australia. E-mail:
\href{mailto:d.pearson@unsw.edu.au}{\nolinkurl{d.pearson@unsw.edu.au}}}

\abstract{
Salient-but-irrelevant distractors can automatically capture attention
and eye-gaze in visual search. However, recent findings have suggested
that attention to salient-but-irrelevant stimuli can be suppressed when
observers use a specific target template to guide their search (i.e.,
feature search). Increasingly, evidence suggests that attentional
selection is influenced by factors other than the physical salience of a
stimulus and the observer's goals. For instance, pairing a stimulus with
reward has been shown to increase the extent to which it captures
attention and gaze (as though it has become more physically salient),
even when such capture has negative consequences for the observer. We
investigated whether capture by reward can be suppressed in the same way
as capture by physical salience using eye-tracking with a rewarded
visual search task. When participants were encouraged to use feature
search, attention to a distractor paired with relatively small reward
was suppressed. By contrast, attention was captured by a distractor
paired with large reward, even when such capture resulted in the loss of
large reward. These findings suggest that reward-related stimuli are
given special priority to the visual attention system and have
implications for our understanding of real-world biases to
reward-related stimuli, such as those seen in addiction.

}

\usepackage{amsthm}
\newtheorem{theorem}{Theorem}[section]
\newtheorem{lemma}{Lemma}[section]
\theoremstyle{definition}
\newtheorem{definition}{Definition}[section]
\newtheorem{corollary}{Corollary}[section]
\newtheorem{proposition}{Proposition}[section]
\theoremstyle{definition}
\newtheorem{example}{Example}[section]
\theoremstyle{definition}
\newtheorem{exercise}{Exercise}[section]
\theoremstyle{remark}
\newtheorem*{remark}{Remark}
\newtheorem*{solution}{Solution}
\begin{document}
\maketitle

\section{Introduction}\label{introduction}

When we interact with the world, our visual attention system can
prioritise important information. For example, when driving towards an
intersection, we can selectively attend to a stop sign on a busy street.
Sometimes, however, we may find that stimuli that are irrelevant to our
current task may nevertheless capture our attention in a seemingly
automatic and involuntary way (e.g., a flashing alert, or colourful
billboard). Consistent with this framework, an influential view of
attentional selection has drawn a distinction between two forms of
attentional control: one that is volitional and goal directed (top-down
control) and another that is automatic and stimulus driven (S. Yantis,
2000). However, exactly how these two processes interact has been the
subject of extensive debate.

Most models of attentional selection can be categorised into one of two
opposing theoretical positions. \emph{Stimulus-driven} accounts argue
that attention is initially captured by the most salient stimulus
presented to an observer, regardless of their current goals (J.
Theeuwes, 1992, 2010). That is, individuals have no voluntary control
over the initial allocation of their attention, which is automatically
drawn to the most salient stimulus in a scene. By contrast,
\emph{goal-directed} accounts posit that attention is allocated only to
stimuli that are in some way related to the observer's current goals
(Folk, Remington, \& Johnston, 1992; Leber \& Egeth, 2006). These
theories predict that physically salient stimuli will be completely
ignored by the visual attention system, unless they share some
feature(s) with the observer's template of expected targets.

Recently, a hybrid model of attentional selection has been
proposed---the \emph{signal suppression hypothesis} (Gaspelin \& Luck,
2018b; Sawaki \& Luck, 2010)---which attempts to integrate these two
competing accounts. According to this model, salient stimuli
automatically generate an attentional priority signal (or
\enquote{attend-to-me} signal) that will go on to capture attention
unless it is suppressed by a top-down control process, which builds over
repeated experience with the salient stimulus (Gaspelin \& Luck, 2018a).
This account is consistent with stimulus-driven theories, in that it
proposes that physically salient stimuli have the potential to
involuntarily capture attention; however it is also consistent with
goal-directed theories in that it proposes that there is some top-down
control of the allocation of attention. Evidence supporting the signal
suppression hypothesis has largely come from the event-related potential
(ERP) literature (for review, see Gaspelin \& Luck, 2019), however
recent studies have demonstrated behavioural evidence of suppression in
the context of overt attention (Gaspelin \& Luck, 2018a; i.e.,
eye-movements: see Gaspelin, Leonard, \& Luck, 2017; Ipata, Gee,
Gottlieb, Bisley, \& Goldberg, 2006) and covert attention (i.e., shifts
of attention that are not accompanied by eye-movements: see Gaspelin,
Leonard, \& Luck, 2015).

For example, across two experiments Gaspelin et al. (2017) had
participants perform variants of a commonly used procedure for examining
attentional capture---the \emph{additional singleton task} (J. Theeuwes,
1991, 1992)---while recording eye movements. Eye movements provide a
useful index of attention since an eye movement to a location (a
saccade) is necessarily preceded by a shift of spatial attention to that
location (Deubel \& Schneider, 1996). In this task, participants were
required to locate and respond to a shape-singleton target that was
presented in an array of non-target shapes. On half of the trials, one
of the non-target shapes was rendered in a different colour from the
rest of the array so as to be a physically salient colour-singleton
distractor. If participants were \emph{more} likely to make a saccade
towards the singleton distractor than one of the nonsingleton
non-targets, this would indicate that the singleton distractor had
captured attention. By contrast, if participants were \emph{less} likely
to make a saccade to the singleton distractor than one of the
nonsingleton non-targets, this would suggest that attention to the
singleton distractor had been suppressed. In Gaspelin et al. (2017)'s
Experiment 1, participants were encouraged to adopt a strategy of
searching for the \enquote{odd-one-out} in the display (i.e,
\emph{singleton-search mode}; Bacon \& Egeth, 1994), by having the
target be randomly either a circle amongst diamonds or a diamond amongst
circles on each trial (see Figure \ref{fig:methodFig}A for an example
from the current study). Under these conditions, both stimulus-driven
(J. Theeuwes, 1992) and goal-directed (Bacon \& Egeth, 1994) accounts of
attentional selection would predict capture, as the template that
participants use to locate the target (i.e., any singleton) is broad
enough to include the singleton distractor. As expected, under these
singleton-search conditions Gaspelin et al. found that participants'
overt attention was captured by the salient singleton. In Experiment 2,
participants were instead encouraged to adopt a more specific target
template (i.e., \emph{feature-search mode}; Bacon \& Egeth, 1994), by
consistently mapping the target identity to one shape (e.g., search for
a circle on every trial), and having a heterogeneous set of shapes act
as the non-targets (see Figure \ref{fig:methodFig}B). This manipulation
makes searching for any singleton a highly inefficient strategy, as
there are multiple singleton nontargets in the display (e.g., a circle,
a square, a triangle, and a red shape). Thus, participants should be
encouraged to search for the specific features that define the target
(i.e., the \enquote{circleness} of the circle). Under these conditions,
attention to the salient colour-singleton distractor was suppressed
relative to the other non-targets, suggesting that it was treated
differently from the other non-targets (inconsistent with goal-directed
accounts), yet did not capture gaze (inconsistent with stimulus-driven
accounts). By contrast, the signal suppression hypothesis can account
for these findings by suggesting that the singleton generated an
attentional priority signal as a consequence of its physical salience,
but this signal could be suppressed by top-down control under conditions
that promote a more specific search strategy (i.e., feature search).
Importantly, this suppression effect was observed even for the most
rapidly generated eye movements, which was taken as evidence that the
suppression effect operates early in processing, before attention is
initially allocated.

\subsection{The role of selection history in guiding
attention}\label{the-role-of-selection-history-in-guiding-attention}

Up to this point we have discussed the set of influences on attentional
control as a dichotomy: goal-directed versus stimulus-driven. However, a
growing literature has questioned this framework, pointing to
demonstrations of attentional selection biases that fall outside this
dichotomy (Awh, Belopolsky, \& Theeuwes, 2012; Failing \& Theeuwes,
2018; M. E. Le Pelley, Mitchell, Beesley, George, \& Wills, 2016). Awh
et al. (2012) suggested a third category of influences on attentional
selection, labelled \emph{selection history}. This category describes
attentional biases that are formed through learned relationships between
stimulus features and motivationally significant outcomes---such as
reward (Brian A. Anderson, 2016; Failing \& Theeuwes, 2018; M. E. Le
Pelley et al., 2016) or punishment (Watson, Pearson, Wiers, \& Le
Pelley, 2019)---as well as other biases related to the history of
attentional deployment that cannot be easily explained in terms of
goal-directed or stimulus-driven control, such as biases for selecting
stimulus features that have previously acted as targets (e.g., Maljkovic
\& Nakayama, 1994).

The influence of learned stimulus-reward associations on attentional
capture is demonstrated in a study by Le Pelley et al. (2015; see also
Pearson, Donkin, Tran, Most, \& Le Pelley, 2015). In a variant of the
additional singleton task, participants were more likely to make a
saccade towards a colour-singleton distractor signalling the
availability of high reward (e.g., 10\(\text{\textcent{}}\)) than a
singleton distractor signalling low reward (1\(\text{\textcent{}}\)),
even though looking at the reward-signalling singletons was
counterproductive, as it resulted in the omission of the reward that
would otherwise have been delivered. That is, participants were more
likely to have their attention and gaze captured by a distractor
signalling high reward, even though this led to the omission of more
high rewards. This result cannot be explained in terms of
stimulus-driven influences, as the colour-reward associations were
counterbalanced across participants to avoid any influence of
differential physical salience on capture. Similarly, the effect cannot
be explained by goal-directed influences, as capture by the reward
associated distractor was directly counterproductive to participants'
goal of maximizing reward. Thus, this study demonstrates that
experiencing the relationship between a stimulus feature and reward
influences the likelihood that that feature will capture attention and
gaze, a finding termed \emph{value-modulated attentional capture}
(VMAC).

Pairing a stimulus with reward is thought to increase its attentional
priority in a way that mimics or otherwise interacts with its physical
salience. For example, eye-tracking studies have demonstrated that VMAC
is largest for the most rapidly generated saccades, and diminishes with
increasing saccade latency (Failing, Nissens, Pearson, Le Pelley, \&
Theeuwes, 2015; Pearson et al., 2016), a pattern similar to that
observed in capture by physical salience (e.g., Zoest, Donk, \&
Theeuwes, 2004). Similarly, electrophysiological studies have shown that
reward affects ERP components thought to index low-level perceptual
activity (Hickey, Chelazzi, \& Theeuwes, 2010). This is consistent with
the idea of \emph{incentive salience} (Berridge \& Robinson, 1998),
wherein a reward-related stimulus becomes more salient and attention
grabbing to the observer through a change in its perceptual
representation. This begs the question, if associating a stimulus with
reward increases its perceptual priority as though it has become more
physically salient, can this priority signal be suppressed by the
top-down control process proposed by the signal suppression hypothesis?
That is, can incentive salience be suppressed in the same way as
physical salience? Aside from the theoretical importance of this
question, it may also have important clinical implications. Recent
evidence suggests that the processes underlying VMAC are closely related
to the attentional biases towards drug-related stimuli observed in
addiction (Albertella et al., 2017; Brian A Anderson, Faulkner, Rilee,
Yantis, \& Marvel, 2013; for review see Field \& Cox, 2008), which can
promote relapse in recovering addicts (Marhe, Waters, Wetering, \&
Franken, 2013; Marissen et al., 2006; A. J. Waters, Marhe, \& Franken,
2012). Thus it is important to know whether top-down cognitive control
processes can be used to overcome the influence of reward on attention
when such capture is counterproductive and contrary to our goals. We
addressed this question by combining Le Pelley et al.'s VMAC procedure
with Gaspelin et al.'s (2017) overt attentional suppression procedure to
investigate whether reward-related attentional biases can be suppressed
by top-down control processes under conditions promoting feature search.

\section{Methods}\label{methods}

\subsection{Participants}\label{participants}

This study was approved by the UNSW Sydney Human Research Ethics
Advisory Panel (Psychology). Previous studies of VMAC using gaze
measures (M. E. Le Pelley et al., 2015; Pearson et al., 2015, 2016) have
demonstrated medium to large effect sizes (\(d_z\) = 0.41--1.4, mean =
0.73), and previous studies of overt attentional suppression of physical
salience (Gaspelin et al., 2017) have demonstrated a large effect size
(\(d_z\) = 1.6). Based on an anticipated effect size of \(d\) = 0.73, a
power analysis conducted with G*Power (Faul, Erdfelder, Lang, \&
Buchner, 2007) indicated that 32 participants per group would provide
adequate power (power \textasciitilde{}.98 to detect within-subjects
effects and power of \textasciitilde{}.82 for between-subjects effects).
We therefore tested 64 UNSW Sydney students (\(n =\) 32 per group, 44
females, age \(M=\) 20.15, \(SD=\) 4.74) who participated in exchange
for course credit or payment of 20 AUD. All participants also received a
monetary bonus that was dependent on their performance (\(M =\) 8.88
AUD, \(SD =\) 2.68 AUD).

\subsection{Apparatus}\label{apparatus}

Participants were tested using a Tobii TX-300 eye-tracker (sampling
frequency 300 Hz), mounted on a 23-inch monitor (1920 \(\times\) 1080
resolution, 60 Hz refresh rate). Participants' heads were positioned in
a chin rest 60 cm from the screen. Gaze data were down-sampled to 100 Hz
for gaze contingent calculations during stimulus presentation, with gaze
position in each sample defined as the average position during the
preceding 10 ms window. Stimulus presentation was controlled by MATLAB
using the Psychophysics Toolbox extensions (D. H. Brainard, 1997;
Kleiner et al., 2007; Pelli, 1997). Experiment scripts, analysis
scripts, and raw data are available at (\textbf{OSF}).

\subsection{Stimuli}\label{stimuli}

The task was based on that used by Gaspelin et al. (2017) and Pearson et
al. (2015, 2016). Each trial consisted of a fixation display, a search
display, and a feedback display (see Figure \ref{fig:methodFig}C). All
stimuli were presented on a black background. The fixation display
consisted of a white cross (0.5\(^\circ\) visual angle), presented in
the centre of the screen and surrounded by a white circle (diameter
3.0\(^\circ\)). The search display consisted of four filled shapes (size
1.6\(^\circ\) \(\times\) 1.6\(^\circ\)) presented above, below, left and
right of screen centre (eccentricity 4.5\(^\circ\)). One of the shapes
was designated as the target, and the other three shapes were designated
non-targets. For all participants, the target was randomly determined to
be either a circle or a diamond on each trial.\footnote{This aspect of
  our design differs from that of Gaspelin et al. (2017). In their
  study, for half of participants in the feature search condition the
  target was always a circle, and for other participants the target was
  always a diamond. By contrast, for the singleton search condition, for
  all participants the target was a circle among diamonds on some
  trials, and a diamond among circles on others. That is, target
  identity (circle/diamond) was manipulated between-subjects for the
  feature search condition, and within-subjects for the singleton search
  condition. In the current study, we equated the two conditions by
  varying target identity within-subjects for all participants. This
  ensured that any difference between the two search conditions was
  driven by a difference in the specificity of participants' target
  template and not by a difference in participants' history of selecting
  the target shape (e.g., Maljkovic \& Nakayama, 1994).} The identity of
the non-target shapes varied by search condition. For the
\emph{singleton search} condition, the non-target stimuli were all
rendered as the alternative target shape (i.e., if the target was a
diamond, all of the non-targets were circles; Figure
\ref{fig:methodFig}B). For the \emph{feature search} condition, the
non-target stimuli were randomly selected without replacement from a set
of two squares and two hexagons, and were never rendered as the
alternative target shape (Figure \ref{fig:methodFig}C). The target and
two of the non-targets were always rendered in grey (CIE \(x\),\(y\)
chromaticity coordinates of .327/.400). On the majority of trials, one
of the non-target shapes (the \emph{singleton distractor}) was rendered
in either orange or blue (CIE \(x\),\(y\) coordinates .492/.445 and
.192/.216, respectively). On the remaining trials, all shapes were
rendered in grey such that there was no singleton distractor. The values
of blue and orange had similar luminance (\textasciitilde{}24.5
cd/m\textsuperscript{2}), which was higher than that of grey
(\textasciitilde{}8.3 cd/m\textsuperscript{2}). The feedback display
showed the points earned on the current trial. If the response time (RT)
exceeded the soft-timeout threshold (see below), the message
\enquote{Too slow} appeared below the reward feedback.

\begin{figure}

{\centering \includegraphics[width=1\linewidth]{C:/Users/Daniel/Google Drive/Research/vmacfeaturesearch/analysis/figures/Methods_fig}

}

\caption{Trial structure of the current task. (A) Participants in
the singleton search condition experienced search displays where the
target was a unique shape (either a circle amongst diamonds or diamond
amongst circles). (B) Participants in the feature search condition
experienced search displays where the target was either a circle or
diamond shape presented amongst a set of heterogenous shapes. On most
trials, one of the non-target shapes was rendered in either orange or
blue so as to be a colour singleton distractor, leaving two other
nonsingleton non-targets in the display. (C) Participants began by
fixating on a centrally presented fixation cross. A search display then
appeared, and participants were required to make a rapid saccade to the
target. The colour of the singleton distractor indicated the available
reward (10 or 500 points), but looking at the distractor led to reward
omission.}\label{fig:methodFig}
\end{figure}

\subsection{Design}\label{design}

Participants were randomly assigned to either the singleton search or
feature search conditions. For half of the participants in each
condition, orange was the high-reward colour and blue was the low-reward
colour; these colour-reward relationships were reversed for the
remaining participants. There were three types of trial: (1)
\emph{high-reward trials}, in which the singleton distractor was
rendered in the high-reward colour and 500 points were available for a
rapid respnse (see below); (2) \emph{low-reward trials}, in which the
singleton distractor was rendered in the low-reward colour and 10 points
were available; and (3) \emph{distractor-absent trials}, in which all
non-targets were rendered in grey and 10 points were available. The
experiment comprised 8 blocks of 60 trials each, for a total of 480
experimental trials. Each block consisted of 20 high-reward trials, 20
low-reward trials, and 20 distractor-absent trials, in random order.
Participants took a short break between blocks.

On each trial, the location of the target was determined randomly. On
high-reward and low-reward trials, the location of the singleton
distractor was randomly selected from the three remaining locations. A
small, circular region of interest (ROI) with diameter 1.7\(^\circ\)
visual angle was defined around the centre of the target, with a larger
ROI (diameter 2.6\(^\circ\)) defined around the singleton distractor. A
response was registered when the participant had accumulated 100 ms of
gaze dwell time within the target ROI. If any gaze was detected within
the singleton ROI, the reward for the trial was not awarded (henceforth
referred to as \emph{reward omissions}). On distractor-absent trials,
one of the non-target shapes was selected at random to act as the
\enquote{singleton distractor} location. Any gaze falling within the ROI
around this (non-salient) stimulus triggered a reward omission in the
same way as on trials with a singleton distractor. Responses with RTs
that were slower than the soft-timeout threshold (1000 ms) were also not
rewarded.

\subsection{Procedure}\label{procedure}

Participants were told that their task was to move their eyes to the
target \enquote{as quickly and directly as possible} on each trial.
Those in the singleton search condition were instructed to move their
eyes to the \enquote{unique shape} on each trial, whereas those in the
feature search condition were instructed to move their eyes to the
\enquote{circle or diamond}. Participants were also informed about the
relationships between distractor colour and reward availability (e.g.,
that if an orange shape was present in the display they could 500
points, and if a blue shape was present they could win 10 points); they
were not informed that looking at the reward-associated distractor would
cancel the reward for the current trial. The instructions stated that
they would earn 0 points if their RT was slower than the soft-timeout
threshold, and that their reward also depended on how accurately they
moved their eyes to the target. Participants were told that they could
earn between 7 and 15 AUD for good performance, but no specific
information about the conversion rate from points to AUD was provided.

Each trial began with the presentation of the fixation display.
Participants' gaze location was superimposed over the display as a small
yellow dot. Once 700 ms of gaze time had accumulated within the circle
surrounding the fixation cross, or after 5000 ms, the cross and the
circle turned yellow and the dot marking the participants' gaze location
disappeared. After 300 ms the screen blanked, and after a 150 ms delay
the search display was presented until a response was recorded, or until
2000 ms (hard-timeout threshold) had passed. The feedback display then
appeared for 2500 ms during the first block, and 1500 ms in all
subsequent blocks. The inter-trial interval was 700 ms.

\subsection{Data analysis}\label{data-analysis}

In line with previous VMAC protocols (e.g., M. E. Le Pelley et al.,
2015; Pearson et al., 2016), data from the first two experimental
trials, and the first two trials after each break were discarded. Hard
timeouts (2.5\% of all trials) were also discarded. One participant was
replaced because their mean proportion of valid gaze samples during each
trial was less than 50\%. One other participant was replaced after
reporting that they had misunderstood the task instructions. For the
remaining participants, valid gaze data were registered on an average of
97.5\% (\(SD=\) 3.7\%) of samples, suggesting high fidelity of gaze
data.

Saccades were detected in the raw gaze data (sampled at 300 Hz) using a
velocity-threshold identification algorithm (Salvucci \& Goldberg,
2000). Saccade latency was measured as the duration from onset of the
search display to the point at which eye-movement velocity exceeded
40\(^\circ\)/s. Following previous protocols (Pearson et al., 2016), we
excluded trials with anticipatory saccades (saccade latency
\textless{}80 ms; 7.4\% of all trials), trials in which no gaze was
recorded within 100 pixels (5.1\(^\circ\)) of the fixation point within
the first 80 ms (4.8\% of trials), and trials in which there was
insufficient gaze data to detect a saccade (2.2\% of trials). To
classify the direction of the first saccade on each trial, the angular
deviation between the endpoint of the saccade and each stimulus location
was calculated. The saccade was defined as going in the direction of a
stimulus if the angular deviation was less than \(30^\circ\) to the left
or right of that stimulus.

There were two primary dependent measures: (1) the percentage of reward
omissions---that is, trials on which participants looked at the
singleton distractor (or nonsingleton distractor randomly assigned to
act as the \enquote{singleton distractor} location: see Design) and
hence reward was cancelled---for high-reward, low-reward, and
distractor-absent trials, and (2) the percentage of first saccades
directed towards the singleton distractor versus the average
nonsingleton distractor (that is, the mean across the two nonsingleton
distractors present in each search display; see Figure
\ref{fig:methodFig}), on high-reward and low-reward trials.

For the analysis of reward omissions, we were particularly interested in
two contrasts. First, the comparison between the high-reward and
low-reward trials allowed us to examine the effect of reward on
attention, since both displays contained a physically salient
colour-singleton distractor, with the only difference being the
magnitude of reward that the distractor signalled. Second, the
comparison between the low-reward and distractor-absent trials allowed
us to examine the effect of physical salience on attention, since these
different trial types differed in whether the display contained a
colour-singleton distractor, but had the same reward magnitude available
(10 points). These contrasts were compared for the singleton search and
feature search conditions using 2 \(\times\) 2 mixed ANOVAs.

For the analysis of saccade direction, we were primarily interested in
the difference between the percentage of trials on which first saccades
were directed towards the singleton distractor and the mean of both
nonsingleton distractors across high- and low-reward trials. These data
were converted into a \emph{capture score} by subtracting the percentage
of trials where the first saccade was directed towards the average
nonsingleton from the percentage of trials where the first saccade was
directed towards the singleton. A positive capture score indicated that
gaze was more likely to have been directed towards the singleton than
the average nonsingleton (i.e., the singleton had captured overt
attention), whereas a negative capture score indicated that gaze was
more likely to be directed toward the average nonsingleton than the
singleton (overt attention to the singleton was suppressed). A 2
\(\times\) 2 mixed ANOVA was used to compare capture scores for high-
and low-reward trials across search conditions. In addition to any group
differences in the patterns of attentional capture and/or suppression
across trial type, we were also interested in directly investigating
whether attention was captured by the singleton distractor (capture
score \(>0\)), or whether attention to the singleton was suppressed
(capture score \(<0\)) for each trial type \(\times\) search condition
combination. We therefore tested the capture score for each trial type
and search condition with planned one-sample \emph{t}-tests against
zero.

Statistical analyses were conducted in R (Version 3.5.1; R Core Team,
2018) with the afex package (Singmann, Bolker, Westfall, \& Aust, 2018)
used to calculate ANOVAs and the emmeans package (Lenth, 2018) for
follow-up contrasts. Greenhouse-Geisser corrections are reported where
appropriate. In cases where a conclusion is drawn on the basis of a null
effect, we report the Bayes factor that corresponds to a Bayesian
\emph{t}-test using the default Cauchy prior, conducted using the
BayesFactor package (Morey \& Rouder, 2018).

\section{Results}\label{results}

\subsection{Reward Omissions}\label{reward-omissions}

Figure \ref{fig:OmissionPlot} displays the percentage of trials on which
a reward omission was triggered by the participant looking at the
singleton distractor, across search conditions and trial types, averaged
across all trial-blocks.

\begin{figure}

{\centering \includegraphics[width=1\linewidth]{C:/Users/Daniel/Google Drive/Research/vmacfeaturesearch/analysis/figures/omission_plot}

}

\caption{Filled points show the mean percentage of reward
omissions on each trial type for the (A) singleton search condition, and
(B) feature search condition. A reward omission was triggered when the
participant looked at the singleton distractor (or the nonsingleton
distractor assigned as the \enquote{singleton} location on distractor
absent trials; see Design) prior to looking at the target. Individual
participant performance is shown by faint grey lines. Error bars in all
figures represent within-subjects SEM (Cousineau, 2005) with Morey
(2008) correction. *** \(p<.005\), * \(p<.05\).}\label{fig:OmissionPlot}
\end{figure}

\subsubsection{Effect of reward.}\label{effect-of-reward.}

ANOVA analysis of the percentage of reward omissions with factors of
trial type (high-reward vs low-reward) and search condition (singleton
search vs feature search) revealed a main effect of trial type
\(F(1, 62) = 43.11\), \(p < .001\), \(\hat{\eta}^2_p = .410\). Planned
paired-samples \emph{t}-tests confirmed that participants triggered more
reward omissions (i.e., were more likely to look at the colour-singleton
distractor) on high-reward trials than low-reward trials in both the
singleton search condition, \(t(31) = 5.87\), \(p < .001\), \(d_z=\)
1.04 (Figure \ref{fig:OmissionPlot}A) and feature search condition,
\(t(31) = 3.96\), \(p < .001\), \(d_z=\) 0.70 (Figure
\ref{fig:OmissionPlot}B), demonstrating an effect of reward on overt
attentional capture (i.e., a VMAC effect) regardless of whether
participants were encouraged to adopt a more specific target template.
Importantly, search condition did not exert a significant main effect,
\(F(1, 62) = 0.21\), \(p = .647\), \(\hat{\eta}^2_p = .003\), or
significantly interact with the effect of trial type,
\(F(1,62) < 0.01\), \(p=.985\), \(\hat{\eta}^2_p < .0001\). In order to
quantify support for the null hypothesis that the influence of reward on
attentional capture did not vary depending on participants' target
template, we conducted a Bayesian \emph{t}-test to compare the magnitude
of the VMAC effect across the two search conditions. This revealed a
Bayes Factor of \(\mathrm{BF}_{\textrm{01}} = 3.91\), indicating
moderate support for the null hypothesis of no difference in the size of
the VMAC effect under singleton search and fearure search conditions.

\subsubsection{Effect of physical
salience.}\label{effect-of-physical-salience.}

ANOVA analysis of the percentage of reward omissions revealed a
non-significant main effect of trial type (low-reward vs
distractor-absent), \(F(1, 62) = 1.83\), \(p = .181\),
\(\hat{\eta}^2_p = .029\), and a significant main effect of search
condition (singleton search vs feature search), \(F(1, 62) = 7.26\),
\(p = .009\), \(\hat{\eta}^2_p = .105\). Critically, this main effect
was qualified by a significant trial type \(\times\) search condition
interaction, \(F(1, 62) = 20.61\), \(p < .001\),
\(\hat{\eta}^2_p = .249\), indicating that the effect of physical
salience on overt attentional capture differed across search conditions.
Paired-samples \emph{t}-tests revealed that participants in the
singleton search condition triggered significantly more reward omissions
on trials that contained a colour-singleton distractor than those that
did not, \(t(31) = 2.32\), \(p = .027\), \(d_z=\) 0.41, suggesting that
overt attention was captured by the physically salient singleton. In
contrast, participants in the feature search condition triggered fewer
reward omissions on trials containing a colour-singleton distractor than
trials with no coloured singleton, \(t(31) = 4.05\), \(p < .001\),
\(d_z=\) 0.72, suggesting that overt attention to the singleton
distractor was suppressed under conditions promoting feature search,
consistent with previous findings (Gaspelin et al., 2017).

\begin{figure}

{\centering \includegraphics[width=1\linewidth]{C:/Users/Daniel/Google Drive/Research/vmacfeaturesearch/analysis/figures/saccade_plot}

}

\caption{First saccade direction data. (A) Filled points show
the mean percentage of first saccades directed towards the target,
average nonsingleton distractor and singleton distractor, on high- and
low-reward trials, for participants in the singleton search condition.
Individual participant performance shown by faint underlying points. (B)
These data are converted into capture scores (calculated as the
percentage saccades to the singleton distractor minus percentage
saccades to the average nonsingleton distractor) for high-reward and
low-reward trials. Positive capture scores indicate that the singleton
distractor captured overt attention, and negative capture scores
indicate that the overt attention to the singleton distractor was
suppressed. (C) Mean percentage of first saccades to each stimulus type,
and (D) capture scores for participants in the feature search condition.
Error bars represent within-subjects SEM. *** \(p<.001\), * \(p<.05\).}\label{fig:SaccadePlot}
\end{figure}

\subsection{First Saccade Direction}\label{first-saccade-direction}

Figure \ref{fig:SaccadePlot} shows the percentage of first saccades
directed towards each stimulus type (i.e., the target\footnote{Note that
  the comparison of interest in determining whether a stimulus captured
  attention, or was otherwise suppressed, is the percentage of first
  saccades to the singleton vs.~the average nonsingleton distractor.
  Thus, while we have included the percentage of first saccades to the
  target in Figure \ref{fig:SaccadePlot} for the sake of completeness,
  we have not included these data in our analyses.}, average
nonsingleton distractor, and singleton distractor) on high- and
low-reward trials for the singleton search (Figure
\ref{fig:SaccadePlot}A) and feature search (Figure
\ref{fig:SaccadePlot}C) conditions; Figures \ref{fig:SaccadePlot}B and
\ref{fig:SaccadePlot}D show capture scores (difference in percentage of
first saccades directed towards singleton versus average nonsingleton
distractor) for the singleton search and feature search conditions,
respectively. ANOVA analysis of capture scores revealed a significant
main effect of trial type (high-reward vs low-reward),
\(F(1, 62) = 45.55\), \(p < .001\), \(\hat{\eta}^2_p = .424\), with the
singleton capturing attention more often on high-reward trials than
low-reward trials; once again demonstrating a VMAC effect. A main effect
of search condition (singleton search vs feature search),
\(F(1, 62) = 4.89\), \(p = .031\), \(\hat{\eta}^2_p = .073\), indicated
that both the high-reward and low-reward singleton captured attention
more often, on average, in the singleton search condition than the
feature search condition. Importantly, the trial type \(\times\) search
condition interaction was non-significant, \(F(1, 62) = 0.12\),
\(p = .735\), \(\hat{\eta}^2_p = .002\), with a corresponding Bayes
factor of \(\mathrm{BF}_{\textrm{01}} = 3.73\) indicating moderate
support for the null hypothesis that search condition had no effect on
the magnitude of the VMAC effect on first saccade direction.

Next we tested whether overt attention to each distractor type was
captured or suppressed in each search condition. Planned one-sample
\emph{t}-tests showed that capture scores were significantly greater
than zero (indicating that overt attention was captured by the
high-reward singleton) under conditions promoting singleton search,
\(t(31) = 9.03\), \(p < .001\), \(d_z=\) 1.60, as well as feature
search, \(t(31) = 3.98\), \(p < .001\), \(d_z=\) 0.70. For the
low-reward distractor, there was a non-significant numerical trend
towards capture in the singleton search condition, \(t(31) = 1.02\),
\(p = .313\), \(d_z=\) 0.18. In contrast, for the feature search
condition, capture score was significantly below zero, \(t(31) = 2.30\),
\(p = .028\), \(d_z=\) 0.41, indicating that overt attention to the
low-reward singleton was suppressed. Thus, in line with previous
findings (Gaspelin et al., 2017), our data suggest that overt attention
to physically salient singletons can be suppressed when participants are
encouraged to adopt a specific target template. However, singletons that
have been associated with high-reward reward capture overt attention,
regardless of participants' target template and despite such capture
being directly counterproductive to earning reward.

\begin{figure}

{\centering \includegraphics[width=1\linewidth]{C:/Users/Daniel/Google Drive/Research/vmacfeaturesearch/analysis/figures/capture_plot_by_block}

}

\caption{Capture scores across five 96-trial epochs of the
experiment for participants in the (A) singleton search condition and
(B) feature search condition. Positive capture scores indicate that the
singleton distractor captured attention, whereas negative capture scores
indicate that attention to the singleton distractor was suppressed.
Error bars represent within-subjects SEM.}\label{fig:blockPlot}
\end{figure}

\subsection{Development of attentional capture/suppression across
training}\label{development-of-attentional-capturesuppression-across-training}

Recent research suggests that attentional suppression develops over the
course of repeated experience with the to-be-ignored stimulus feature
(Gaspelin \& Luck, 2018a; Vatterott \& Vecera, 2012). In order to
investigate this in the current study, we divided the experiment into
four epochs (96 trials/epoch) and calculated capture scores (as
described earlier) for each trial type (see Figure \ref{fig:blockPlot}).
These data were analysed using an ANOVA with factors of search condition
(singleton search, feature search), trial type (high, low), and epoch
(1--4). This once again revealed a main effect of search condition,
\(F(1, 62) = 4.97\), \(p = .029\), \(\hat{\eta}^2_p = .074\), and trial
type, \(F(1, 62) = 46.60\), \(p < .001\), \(\hat{\eta}^2_p = .429\).
Critically, there was also a significant interaction between trial type
and epoch, \(F(2.73, 169.44) = 9.77\), \(p < .001\),
\(\hat{\eta}^2_p = .136\). There were no other significant main or
interaction effects (all \emph{p}'s \(>.25\)). Follow-up contrasts
revealed a significant negative linear trend for low-reward trials,
\(t(369)=\) 4.07, \(p\) \textless{} .001, with capture by the low-reward
distractor decreasing as the experiment progressed and experience with
the physically salient feature increased (notably, in the feature search
condition scores become increasingly negative, indicating increasing
\emph{suppression} of the low-reward distractor). In contrast, for
high-reward trials there was a significant positive linear trend,
\(t(369)=\) 2.97, \(p=\) .003, with capture by the high-reward
distractor increasing as the experiment progressed and experience with
the reward associated feature increased.

\begin{figure}

{\centering \includegraphics[width=1\linewidth]{C:/Users/Daniel/Google Drive/Research/vmacfeaturesearch/analysis/figures/vincentized_plot}

}

\caption{Capture scores as a function of saccade latency
quartile for participants in the (A) singleton search condition and (B)
feature search condition. Mean first saccade latencies and the
proportion of first saccades directed towards each stimulus type were
calculated separately for each quintile of individual participant
saccade latency distributions using the Vincentizing procedure
(Ratcliff, 1979). Positive capture scores indicate that the singleton
distractor captured attention, whereas negative capture scores indicate
that attention to the singleton distractor was suppressed. Error bars
represent within-subjects SEM. *** \(p<.001\), ** \(p<.01\).}\label{fig:VincentizedPlot}
\end{figure}

\subsection{Attentional capture/suppression effects for the fastest
quartile of saccadic
latencies}\label{attentional-capturesuppression-effects-for-the-fastest-quartile-of-saccadic-latencies}

To investigate the time course of the overt attentional capture and
suppression effects, we analysed capture scores (proportion of first
saccades towards the singleton distractor minus the average nonsingleton
distractor) on high-reward and low-reward trials as a function of
saccade latency using the Vincentizing procedure (Ratcliff, 1979). We
calculated mean saccade latency and capture score separately for each
trial type and quartile of the individual saccade latency distributions.
We then analysed the capture scores for the most rapidly generated
saccades. According to the signal suppression hypothesis, the top-down
suppression effect is activated early in processing, prior to the
initial allocation of attention (Gaspelin \& Luck, 2019). Therefore the
speed with which a saccade is initiated should have no effect on the
extent to which overt attention can be suppressed. As illustrated in
Figure \ref{fig:VincentizedPlot}, the most rapidly generated saccades
were captured by the high-reward singleton (capture scores \(>0\)) in
both the singleton search, \(t(31) = 13.02\), \(p < .001\), \(d_z=\)
2.30, and feature search conditions, \(t(31) = 6.45\), \(p < .001\),
\(d_z=\) 1.14. Similarly, the the most rapidly generated saccades were
captured by the low-reward singleton in both the singleton search,
\(t(31) = 4.10\), \(p < .001\), \(d_z=\) 0.72, and feature search
conditions, \(t(31) = 3.34\), \(p = .002\), \(d_z=\) 0.59. It is notable
that we observed capture (rather than suppression) for the fastest
saccades for both trial-types in the feature search condition. This
finding is inconsistent with Gaspelin et al.'s (2017) previous report of
attentional suppression of physically salient singleton distractors in
the fastest eye-movements.

\section{Discussion}\label{discussion}

In this experiment, we investigated the role of top-down control
processes in actively suppressing overt attention to physically salient
and reward-associated distractor stimuli. In line with the signal
suppression hypothesis (Gaspelin et al., 2015, 2017), we found that
overt attention to physically salient colour singleton distractors can
be actively suppressed under conditions that promote top-down guidance
of attention. Consistent with recent findings (Gaspelin \& Luck, 2018a;
Vatterott \& Vecera, 2012), this attentional suppression effect
gradually emerged over the course of the experiment, as participants
gained experience with the physically salient distractor feature.
Furthermore, we found an effect of reward association on overt attention
(i.e., VMAC; M. E. Le Pelley et al., 2015; Pearson et al., 2015), with
participants' gaze more likely to be captured by distractor stimuli that
signalled high reward than low reward, even though looking at
reward-signalling distractors caused omission of rewards that otherwise
would have been delivered. Similar to the attentional suppression
effect, attentional capture by reward-associated distractors also
emerged over the course of the experiment, as participants experienced
more pairings of stimulus features with reward. Critically, this study
was the first to demonstrate that---unlike the influence of physical
salience---the influence of reward association on attention cannot be
suppressed under conditions that promote top-down guidance of attention.
Regardless of whether participants were encouraged to search for
specific target defining features (i.e., feature search mode) or to
search for the odd-one-out (singleton search mode), stimuli associated
with high reward captured overt attention. Notably, this attentional
bias was counterproductive, in that it led to the omission of more high
rewards than low rewards, and so participants should have been highly
motivated to suppress their attention to the high-reward distractor if
possible. Nevertheless, the high-reward distractor captured attention,
even under conditions that allowed participants to suppress their
attention to physically salient distractors that were associated with
low reward. Our key finding, then, is that reward-related stimuli
constitute especially potent attentional priority signals that are
relatively immune to suppression by top-down control processes that can
act to prevent distraction by physical salience.

Most influential models of attentional selection assume that
stimulus-driven and goal-directed influences are integrated onto a
common priority map in the brain, with attention directed towards the
spatial location with the highest peak of activation (e.g., Itti \&
Koch, 2001; J. Theeuwes, 2010; Wolfe, 2007). The priority map concept
has also been used to explain how selection history influences
attentional allocation (Awh et al., 2012; Failing \& Theeuwes, 2018),
with the attentional priority signal of reward-related stimulus features
increasing with repeated stimulus-reward pairings through a process of
associative learning (M. E. Le Pelley et al., 2016; Pearson et al.,
2016). Recent formulations of the signal suppression hypothesis have
suggested that the top-down suppression mechanism may operate in a
similar way, with the attentional priority of to-be-ignored stimulus
features being proactively downweighted with repeated experience
(Gaspelin \& Luck, 2019). At first glance, the results of the current
study may seem inconsistent with the idea that reward and top-down
suppression engage in competition on a common priority map, as the
magnitude of the VMAC effect did not differ between search conditions,
even though the feature search condition should have encouraged top-down
guidance of attention. However, there was an overall decrease in the
amount of capture by both the high- and low-reward distractor in the
feature search condition This raises the possibility that repeated
experience of the physically salient stimulus features (i.e., orange and
blue colour) allows the attentional priority of those features to be
uniformly downweighted by the top-down suppression mechanism. In
addition, our findings are consistent with the idea that repeated
experience of the stimulus feature-reward pairings selectively upweights
the attentional priority of the high-reward distractor, such that it
overpowers the influence of top-down suppression and thus captures
attention.

An inconsistency between the results of the current study and that of
Gaspelin et al. (2017) comes from the time-course of the attentional
capture and suppression effects that were observed. According to the
signal suppression hypothesis, top-down suppression operates prior to
the initial allocation of attention, and so suppression should be
observed even for the most rapidly generated saccades. Consistent with
this idea, Gaspelin et al. (2017) observed an overt attentional
suppression effect to physically salient singleton distractors amongst
the fastest quartile of saccade latencies. In contrast, in the current
experiment we observed overt attentional capture in the fastest quartile
of saccade latencies, with the suppression effect emerging on trials
with slower saccades. Methodological differences between Gaspelin et
al.\enquote{s (2017) experiment and the current study may be responsible
for this discrepancy. For example, the availability of reward on
low-reward trials may have influenced capture, either by somewhat
increasing the attentional priority of the stimulus feature associated
with low-reward reward, or by otherwise influencing participants}
motivation to respond quickly. Alternatively, the discrepancy in
findings may reflect our use of two potential targets (circle and
diamond) in the feature search condition, as opposed to the same target
on all trials in Gaseplin et al.'s procedure. Having two possible
targets could reduce the influence of trial-by-trial upweighting of
target features (Maljkovic \& Nakayama, 1994), but may also result in
less effective feature search (but see Grubert \& Eimer, 2015; e.g.,
Houtkamp \& Roelfsema, 2009). How these methodological differences might
influence the time-course of overt attentional capture and suppression
remains a question for future research. Nonetheless, the finding does
raise questions about whether the attentional suppression effect that we
have observed is truly the result of proactive top-down suppression of
salient stimuli, as suggested by the signal suppression hypothesis, or
potentially the result of rapid covert disengagement from the salient
stimuli (see J. Theeuwes, 2010; Zoest et al., 2004 for similar
arguments).

As mentioned previously, attentional capture by stimuli associated with
monetary rewards can be mapped on to the attentional biases to
drug-related stimuli seen in addiction. Indeed, recent findings suggest
that these biases may be the result of a common mechanism (Albertella et
al., 2017; Brian A Anderson et al., 2013). This is consistent with the
idea of incentive salience (Berridge \& Robinson, 1998), where the
perceptual representation of an otherwise neutral stimulus is modified
so as to become more salient and attention grabbing to the observer, as
a result of its association with a desired outcome (e.g., drugs, money).
The current study suggests that incentive salience has a particularly
powerful influence on the attentional system, overcoming top-down
control mechanisms that can effectively prevent capture by physically
salient stimuli. This may have implications for the development of
treatments for substance use disorders that target these attentional
biases.

\newpage

\section{References}\label{references}

\begingroup
\setlength{\parindent}{-0.5in} \setlength{\leftskip}{0.5in}

\hypertarget{refs}{}
\hypertarget{ref-Albertella2017a}{}
Albertella, L., Copeland, J., Pearson, D., Watson, P., Wiers, R. W., \&
Le Pelley, M. E. (2017). Selective attention moderates the relationship
between attentional capture by signals of nondrug reward and illicit
drug use. \emph{Drug and Alcohol Dependence}, \emph{175}, 99--105.
doi:\href{https://doi.org/10.1016/j.drugalcdep.2017.01.041}{10.1016/j.drugalcdep.2017.01.041}

\hypertarget{ref-Anderson2015a}{}
Anderson, B. A. (2016). The attention habit: How reward learning shapes
attentional selection. \emph{Annals of the New York Academy of
Sciences}, \emph{1369}, 24--39.
doi:\href{https://doi.org/10.1111/nyas.12957}{10.1111/nyas.12957}

\hypertarget{ref-Anderson2013}{}
Anderson, B. A., Faulkner, M. L., Rilee, J. J., Yantis, S., \& Marvel,
C. L. (2013). Attentional bias for nondrug reward is magnified in
addiction. \emph{Experimental and Clinical Psychopharmacology},
\emph{21}, 499--506.
doi:\href{https://doi.org/10.1037/a0034575}{10.1037/a0034575}

\hypertarget{ref-Awh2012}{}
Awh, E., Belopolsky, A. V., \& Theeuwes, J. (2012). Top-down versus
bottom-up attentional control: A failed theoretical dichotomy.
\emph{Trends in Cognitive Sciences}, \emph{16}, 437--443.
doi:\href{https://doi.org/10.1016/j.tics.2012.06.010}{10.1016/j.tics.2012.06.010}

\hypertarget{ref-Bacon1994}{}
Bacon, W. F., \& Egeth, H. E. (1994). Overriding stimulus-driven
attentional capture. \emph{Perception \& Psychophysics}, \emph{55},
485--496.
doi:\href{https://doi.org/10.3758/BF03205306}{10.3758/BF03205306}

\hypertarget{ref-Berridge1998}{}
Berridge, K. C., \& Robinson, T. E. (1998). What is the role of dopamine
in reward: Hedonic impact, reward learning, or incentive salience?
\emph{Brain Research Reviews}, \emph{28}, 309--369.
doi:\href{https://doi.org/10.1016/S0165-0173(98)00019-8}{10.1016/S0165-0173(98)00019-8}

\hypertarget{ref-Brainard1997}{}
Brainard, D. H. (1997). The Psychophysics Toolbox. \emph{Spatial
Vision}, \emph{10}, 433--436.
doi:\href{https://doi.org/10.1163/156856897X00357}{10.1163/156856897X00357}

\hypertarget{ref-Cousineau2005}{}
Cousineau, D. (2005). Confidence intervals in within-subject designs: A
simpler solution to Loftus and Masson's method. \emph{Tutorials in
Quantitative Methods for Psychology}, \emph{1}, 42--45.

\hypertarget{ref-Deubel1996}{}
Deubel, H., \& Schneider, W. X. (1996). Saccade target selection and
object recognition: Evidence for a common attentional mechanism.
\emph{Vision Research}, \emph{36}, 1827--1837.
doi:\href{https://doi.org/10.1016/0042-6989(95)00294-4}{10.1016/0042-6989(95)00294-4}

\hypertarget{ref-Failing2018}{}
Failing, M., \& Theeuwes, J. (2018). Selection history: How reward
modulates selectivity of visual attention. \emph{Psychonomic Bulletin \&
Review}, \emph{25}, 514--538.
doi:\href{https://doi.org/10.3758/s13423-017-1380-y}{10.3758/s13423-017-1380-y}

\hypertarget{ref-Failing2015}{}
Failing, M., Nissens, T., Pearson, D., Le Pelley, M., \& Theeuwes, J.
(2015). Oculomotor capture by stimuli that signal the availability of
reward. \emph{Journal of Neurophysiology}, \emph{114}, 2316--2327.
doi:\href{https://doi.org/10.1152/jn.00441.2015}{10.1152/jn.00441.2015}

\hypertarget{ref-Faul2007}{}
Faul, F., Erdfelder, E., Lang, A.-G., \& Buchner, A. (2007). G*Power 3:
A flexible statistical power analysis program for the social,
behavioral, and biomedical sciences. \emph{Behavior Research Methods},
\emph{39}, 175--191.
doi:\href{https://doi.org/10.3758/BF03193146}{10.3758/BF03193146}

\hypertarget{ref-Field2008}{}
Field, M., \& Cox, W. M. (2008). Attentional bias in addictive
behaviors: A review of its development, causes, and consequences.
\emph{Drug and Alcohol Dependence}, \emph{97}, 1--20.
doi:\href{https://doi.org/10.1016/j.drugalcdep.2008.03.030}{10.1016/j.drugalcdep.2008.03.030}

\hypertarget{ref-Folk1992}{}
Folk, C. L., Remington, R. W., \& Johnston, J. C. (1992). Involuntary
covert orienting is contingent on attentional control settings.
\emph{Journal of Experimental Psychology. Human Perception and
Performance}, \emph{18}, 1030--1044.
doi:\href{https://doi.org/10.1037/0096-1523.18.4.1030}{10.1037/0096-1523.18.4.1030}

\hypertarget{ref-Gaspelin2018b}{}
Gaspelin, N., \& Luck, S. J. (2018a). Distinguishing among potential
mechanisms of singleton suppression. \emph{Journal of Experimental
Psychology: Human Perception and Performance}, \emph{44}, 626--644.
doi:\href{https://doi.org/10.1037/xhp0000484}{10.1037/xhp0000484}

\hypertarget{ref-Gaspelin2018}{}
Gaspelin, N., \& Luck, S. J. (2018b). The role of inhibition in avoiding
distraction by salient stimuli. \emph{Trends in Cognitive Sciences},
\emph{22}, 79--92.
doi:\href{https://doi.org/10.1016/j.tics.2017.11.001}{10.1016/j.tics.2017.11.001}

\hypertarget{ref-Gaspelin2018a}{}
Gaspelin, N., \& Luck, S. J. (2019). Inhibition as a potential
resolution to the attentional capture debate. \emph{Current Opinion in
Psychology}, \emph{29}, 12--18.
doi:\href{https://doi.org/10.1016/j.copsyc.2018.10.013}{10.1016/j.copsyc.2018.10.013}

\hypertarget{ref-Gaspelin2015}{}
Gaspelin, N., Leonard, C. J., \& Luck, S. J. (2015). Direct evidence for
active suppression of salient-but-irrelevant sensory inputs.
\emph{Psychological Science}, \emph{26}, 1740--1750.
doi:\href{https://doi.org/10.1177/0956797615597913}{10.1177/0956797615597913}

\hypertarget{ref-Gaspelin2016}{}
Gaspelin, N., Leonard, C. J., \& Luck, S. J. (2017). Suppression of
overt attentional capture by salient-but-irrelevant color singletons.
\emph{Attention, Perception, \& Psychophysics}, \emph{79}, 45--62.
doi:\href{https://doi.org/10.3758/s13414-016-1209-1}{10.3758/s13414-016-1209-1}

\hypertarget{ref-Grubert2015}{}
Grubert, A., \& Eimer, M. (2015). Rapid parallel attentional target
selection in single-color and multiple-color visual search.
\emph{Journal of Experimental Psychology: Human Perception and
Performance}, \emph{41}, 86--101.
doi:\href{https://doi.org/10.1037/xhp0000019}{10.1037/xhp0000019}

\hypertarget{ref-Hickey2010}{}
Hickey, C., Chelazzi, L., \& Theeuwes, J. (2010). Reward changes
salience in human vision via the anterior cingulate. \emph{Journal of
Neuroscience}, \emph{30}, 11096--11103.
doi:\href{https://doi.org/10.1523/JNEUROSCI.1026-10.2010}{10.1523/JNEUROSCI.1026-10.2010}

\hypertarget{ref-Houtkamp2009}{}
Houtkamp, R., \& Roelfsema, P. R. (2009). Matching of visual input to
only one item at any one time. \emph{Psychological Research}, \emph{73},
317--326.
doi:\href{https://doi.org/10.1007/s00426-008-0157-3}{10.1007/s00426-008-0157-3}

\hypertarget{ref-Ipata2006}{}
Ipata, A. E., Gee, A. L., Gottlieb, J., Bisley, J. W., \& Goldberg, M.
E. (2006). LIP responses to a popout stimulus are reduced if it is
overtly ignored. \emph{Nature Neuroscience}, \emph{9}, 1071--1076.
doi:\href{https://doi.org/10.1038/nn1734}{10.1038/nn1734}

\hypertarget{ref-Itti2001}{}
Itti, L., \& Koch, C. (2001). Computational modelling of visual
attention. \emph{Nature Reviews Neuroscience}, \emph{2}, 194--203.
doi:\href{https://doi.org/10.1038/35058500}{10.1038/35058500}

\hypertarget{ref-Kleiner2007}{}
Kleiner, M., Brainard, D. H., Pelli, D. G., Broussard, C., Wolf, T., \&
Niehorster, D. (2007). What's new in Psychtoolbox-3? \emph{Perception},
\emph{36}, S14.
doi:\href{https://doi.org/10.1068/v070821}{10.1068/v070821}

\hypertarget{ref-LePelleya}{}
Le Pelley, M. E., Mitchell, C. J., Beesley, T., George, D. N., \& Wills,
A. J. (2016). Attention and associative learning in humans: An
integrative review. \emph{Psychological Bulletin}, \emph{142},
1111--1140.
doi:\href{https://doi.org/10.1037/bul0000064}{10.1037/bul0000064}

\hypertarget{ref-LePelley2015b}{}
Le Pelley, M. E., Pearson, D., Griffiths, O., \& Beesley, T. (2015).
When goals conflict with values: Counterproductive attentional and
oculomotor capture by reward-related stimuli. \emph{Journal of
Experimental Psychology: General}, \emph{144}, 158--171.
doi:\href{https://doi.org/10.1037/xge0000037}{10.1037/xge0000037}

\hypertarget{ref-Leber2006}{}
Leber, A. B., \& Egeth, H. E. (2006). It's under control: Top-down
search strategies can override attentional capture. \emph{Psychonomic
Bulletin \& Review}, \emph{13}, 132--138.
doi:\href{https://doi.org/10.3758/BF03193824}{10.3758/BF03193824}

\hypertarget{ref-R-emmeans}{}
Lenth, R. (2018). \emph{Emmeans: Estimated marginal means, aka
least-squares means}. Retrieved from
\url{https://CRAN.R-project.org/package=emmeans}

\hypertarget{ref-Maljkovic1994}{}
Maljkovic, V., \& Nakayama, K. (1994). Priming of pop-out: I. Role of
features. \emph{Memory \& Cognition}, \emph{22}, 657--672.
doi:\href{https://doi.org/10.3758/BF03209251}{10.3758/BF03209251}

\hypertarget{ref-Marhe2013}{}
Marhe, R., Waters, A. J., Wetering, B. J. M. van de, \& Franken, I. H.
A. (2013). Implicit and explicit drug-related cognitions during
detoxification treatment are associated with drug relapse: An ecological
momentary assessment study. \emph{Journal of Consulting and Clinical
Psychology}, \emph{81}, 1--12.
doi:\href{https://doi.org/10.1037/a0030754}{10.1037/a0030754}

\hypertarget{ref-Marissen2006}{}
Marissen, M. A. E., Franken, I. H. A., Waters, A. J., Blanken, P., Van
Den Brink, W., \& Hendriks, V. M. (2006). Attentional bias predicts
heroin relapse following treatment. \emph{Addiction}, \emph{101},
1306--1312.
doi:\href{https://doi.org/10.1111/j.1360-0443.2006.01498.x}{10.1111/j.1360-0443.2006.01498.x}

\hypertarget{ref-Morey2008}{}
Morey, R. D. (2008). Confidence intervals from normalized data: A
correction to Cousineau (2005). \emph{Tutorials in Quantitative Methods
for Psychology}, \emph{4}, 61--64.
doi:\href{https://doi.org/10.3758/s13414-012-0291-2}{10.3758/s13414-012-0291-2}

\hypertarget{ref-R-BayesFactor}{}
Morey, R. D., \& Rouder, J. N. (2018). \emph{BayesFactor: Computation of
bayes factors for common designs}. Retrieved from
\url{https://CRAN.R-project.org/package=BayesFactor}

\hypertarget{ref-Pearson2015}{}
Pearson, D., Donkin, C., Tran, S. C., Most, S. B., \& Le Pelley, M. E.
(2015). Cognitive control and counterproductive oculomotor capture by
reward-related stimuli. \emph{Visual Cognition}, \emph{23}, 41--66.
doi:\href{https://doi.org/10.1080/13506285.2014.994252}{10.1080/13506285.2014.994252}

\hypertarget{ref-Pearson2016}{}
Pearson, D., Osborn, R., Whitford, T. J., Failing, M., Theeuwes, J., \&
Le Pelley, M. E. (2016). Value-modulated oculomotor capture by
task-irrelevant stimuli is a consequence of early competition on the
saccade map. \emph{Attention, Perception, \& Psychophysics}, \emph{78},
2226--2240.
doi:\href{https://doi.org/10.3758/s13414-016-1135-2}{10.3758/s13414-016-1135-2}

\hypertarget{ref-Pelli1997}{}
Pelli, D. G. (1997). The VideoToolbox software for visual psychophysics:
Transforming numbers into movies. \emph{Spatial Vision}, \emph{10},
437--442.
doi:\href{https://doi.org/10.1163/156856897X00366}{10.1163/156856897X00366}

\hypertarget{ref-R-base}{}
R Core Team. (2018). \emph{R: A language and environment for statistical
computing}. Vienna, Austria: R Foundation for Statistical Computing.
Retrieved from \url{https://www.R-project.org/}

\hypertarget{ref-Ratcliff1979}{}
Ratcliff, R. (1979). Group reaction time distributions and an analysis
of distribution statistics. \emph{Psychological Bulletin}, \emph{86},
446--461.
doi:\href{https://doi.org/10.1037/0033-2909.86.3.446}{10.1037/0033-2909.86.3.446}

\hypertarget{ref-Salvucci2000}{}
Salvucci, D. D., \& Goldberg, J. H. (2000). Identifying fixations and
saccades in eye-tracking protocols. In \emph{Proceedings of the
symposium on eye tracking research \& applications - etra '00} (pp.
71--78). New York, NY: ACM Press.
doi:\href{https://doi.org/10.1145/355017.355028}{10.1145/355017.355028}

\hypertarget{ref-Sawaki2010}{}
Sawaki, R., \& Luck, S. J. (2010). Capture versus suppression of
attention by salient singletons: Electrophysiological evidence for an
automatic attend-to-me signal. \emph{Attention, Perception, \&
Psychophysics}, \emph{72}, 1455--1470.

\hypertarget{ref-R-afex}{}
Singmann, H., Bolker, B., Westfall, J., \& Aust, F. (2018). \emph{Afex:
Analysis of factorial experiments}. Retrieved from
\url{https://CRAN.R-project.org/package=afex}

\hypertarget{ref-Theeuwes1991a}{}
Theeuwes, J. (1991). Cross-dimensional perceptual selectivity.
\emph{Perception \& Psychophysics}, \emph{50}, 184--193.
doi:\href{https://doi.org/10.3758/BF03212219}{10.3758/BF03212219}

\hypertarget{ref-Theeuwes1992}{}
Theeuwes, J. (1992). Perceptual selectivity for color and form.
\emph{Perception \& Psychophysics}, \emph{51}, 599--606.
doi:\href{https://doi.org/10.3758/BF03211656}{10.3758/BF03211656}

\hypertarget{ref-Theeuwes2010}{}
Theeuwes, J. (2010). Top-down and bottom-up control of visual selection.
\emph{Acta Psychologica}, \emph{135}, 77--99.
doi:\href{https://doi.org/10.1016/j.actpsy.2010.02.006}{10.1016/j.actpsy.2010.02.006}

\hypertarget{ref-Vatterott2012}{}
Vatterott, D. B., \& Vecera, S. P. (2012). Experience-dependent
attentional tuning of distractor rejection. \emph{Psychonomic Bulletin
\& Review}, \emph{19}, 871--878.
doi:\href{https://doi.org/10.3758/s13423-012-0280-4}{10.3758/s13423-012-0280-4}

\hypertarget{ref-Waters2012}{}
Waters, A. J., Marhe, R., \& Franken, I. H. A. (2012). Attentional bias
to drug cues is elevated before and during temptations to use heroin and
cocaine. \emph{Psychopharmacology}, \emph{219}, 909--921.
doi:\href{https://doi.org/10.1007/s00213-011-2424-z}{10.1007/s00213-011-2424-z}

\hypertarget{ref-Watson2019}{}
Watson, P., Pearson, D., Wiers, R. W., \& Le Pelley, M. E. (2019).
Prioritizing pleasure and pain: Attentional capture by reward-related
and punishment-related stimuli. \emph{Current Opinion in Behavioral
Sciences}, \emph{26}, 107--113.
doi:\href{https://doi.org/10.1016/j.cobeha.2018.12.002}{10.1016/j.cobeha.2018.12.002}

\hypertarget{ref-Wolfe2007}{}
Wolfe, J. M. (2007). Guided search 4.0. In \emph{Integrated models of
cognitive systems} (pp. 99--119). Oxford University Press.
doi:\href{https://doi.org/10.1093/acprof:oso/9780195189193.003.0008}{10.1093/acprof:oso/9780195189193.003.0008}

\hypertarget{ref-Yantis2000}{}
Yantis, S. (2000). Goal-directed and stimulus-driven determinants of
attentional control. In S. Monsell \& J. Driver (Eds.), \emph{Control of
cognitive processes: Attention and performance xvii} (pp. 73--103).
Cambridge, MA: MIT Press.

\hypertarget{ref-VanZoest2004}{}
Zoest, W. van, Donk, M., \& Theeuwes, J. (2004). The role of
stimulus-driven and goal-driven control in saccadic visual selection.
\emph{Journal of Experimental Psychology: Human Perception and
Performance}, \emph{30}, 746--759.
doi:\href{https://doi.org/10.1037/0096-1523.30.4.749}{10.1037/0096-1523.30.4.749}

\endgroup

\end{document}

### 2019-04-18 README.Rmd
removing docker stuff
readme changes

@@
 # Please put your title here to include it in the file below. 
-Title <- "Title of your paper goes here"
+Title <- "Overt attentional capture by reward-related stimuli overcomes top-down suppression"
 ```
@@
 
-<!-- Our pre-print is online here:
+Our pre-print is online here:
 
@@
 
-> Authors, (`r format(Sys.Date(), "%Y")`). _Compendium of R code and data for `r Title`_. Accessed `r format(Sys.Date(), "%d %b %Y")`. Online at <https://doi.org/xxx/xxx>  -->
+> Authors, (`r format(Sys.Date(), "%Y")`). _Compendium of R code and data for `r Title`_. Accessed `r format(Sys.Date(), "%d %b %Y")`. Online at <https://doi.org/xxx/xxx>
 
@@
 **Data :** [CC-BY-4.0](http://creativecommons.org/licenses/by/4.0/), Copyright (c) 2019 Daniel Pearson.
-
-### Contributions
-
-We welcome contributions from everyone.
-Before you get started, please see our [contributor guidelines](CONTRIBUTING.md).
-Please note that this project is released with a [Contributor Code of Conduct](CONDUCT.md).
-By participating in this project you agree to abide by its terms.

### 2019-04-18 README.Rmd
readme updates

@@
 
-This repository contains the data and code for our project investigating whether overt attention to reward-related distractors can be suppressed under feature search conditions in the same way as for physically salient distractors (see Gaspelin, Leonard, & Luck, 2017 - Attn Percept Psychophys).
+This repository contains the data and analysis code for our project investigating whether overt attention to reward-related distractors can be suppressed under feature search conditions.
+
+This repository contains data files that have been derived from the raw eye-tracker data.
+The raw eye-gaze files are very large and so are not stored here.
+They can be found at: <https://osf.io/yrdzv/>.
 
@@
 
-> Authors, (YYYY). _`r Title`_. Name of journal/book, Accessed `r format(Sys.Date(), "%d %b %Y")`. Online at <https://doi.org/xxx/xxx>
+> Pearson, D., Watson, P., Cheng, P., Most, S. (2019). _`r Title`_. Name of journal/book, Accessed `r format(Sys.Date(), "%d %b %Y")`. Online at <https://doi.org/xxx/xxx>
 
@@
 
-> Authors, (`r format(Sys.Date(), "%Y")`). _Compendium of R code and data for `r Title`_. Accessed `r format(Sys.Date(), "%d %b %Y")`. Online at <https://doi.org/xxx/xxx>
+> Pearson, D., Watson, P., Cheng, P., & Le Pelley, M. (`r format(Sys.Date(), "%Y")`. Investigating attentional suppression of reward-related distractors. Retrieved from <https://osf.io/yrdzv>
 
@@
 
-Or you can install this compendium as an R package, vmacfeaturesearch, from GitHub with:
-```{r gh-installation, eval = FALSE}
-# install.packages("devtools")
-devtools::install_github("danielpearson90/vmacfeaturesearch")
-```
 ### Licenses

### 2019-04-18 analysis/paper/paper.Rmd
update manuscript

@@
 ---
-title             : "Overt attentional capture by reward-related stimuli overcomes top-down suppression"
+title             : "Overt attentional capture by reward-related stimuli overcomes inhibitory suppression"
 shorttitle        : "Reward overcomes attentional suppression"
@@
 Recently, a hybrid model of attentional selection has been proposed---the *signal suppression hypothesis* [@Gaspelin2018; @Sawaki2010]---which attempts to integrate these two competing accounts.
-According to this model, salient stimuli automatically generate an attentional priority signal (or "attend-to-me" signal) that will go on to capture attention unless it is suppressed by a top-down control process, which builds over repeated experience with the salient stimulus [@Gaspelin2018b].
+According to this model, salient stimuli automatically generate an attentional priority signal (or "attend-to-me" signal) that will go on to capture attention unless it is suppressed by an inhibitory control process, which builds over repeated experience with the salient stimulus [@Gaspelin2018b].
 This account is consistent with stimulus-driven theories, in that it proposes that physically salient stimuli have the potential to involuntarily capture attention; however it is also consistent with goal-directed theories in that it proposes that there is some top-down control of the allocation of attention.
@@
 Thus, participants should be encouraged to search for the specific features that define the target (i.e., the "circleness" of the circle).
-Under these conditions, attention to the salient colour-singleton distractor was suppressed relative to the other non-targets, suggesting that it was treated differently from the other non-targets (inconsistent with goal-directed accounts), yet did not capture gaze (inconsistent with stimulus-driven accounts).
-By contrast, the signal suppression hypothesis can account for these findings by suggesting that the singleton generated an attentional priority signal as a consequence of its physical salience, but this signal could be suppressed by top-down control under conditions that promote a more specific search strategy (i.e., feature search).
+Under these conditions, attention to the salient colour-singleton distractor was suppressed relative to the other non-targets, suggesting that the visual attention system treated the salient singleton differently from the other non-targets (inconsistent with goal-directed accounts), yet did not capture gaze (inconsistent with stimulus-driven accounts).
+By contrast, the signal suppression hypothesis can account for these findings by suggesting that the singleton generated an attentional priority signal as a consequence of its physical salience, but this signal could be suppressed by an inhibitory mechanism under conditions that promoted a more specific search strategy (i.e., feature search).
 Importantly, this suppression effect was observed even for the most rapidly generated eye movements, which was taken as evidence that the suppression effect operates early in processing, before attention is initially allocated.
@@
 This is consistent with the idea of *incentive salience* [@Berridge1998], wherein a reward-related stimulus becomes more salient and attention grabbing to the observer through a change in its perceptual representation.
-This begs the question, if associating a stimulus with reward increases its perceptual priority as though it has become more physically salient, can this priority signal be suppressed by the top-down control process proposed by the signal suppression hypothesis?
+This raises the question, if associating a stimulus with reward increases its perceptual priority as though it has become more physically salient, can this priority signal be suppressed by the inhibitory control process proposed by the signal suppression hypothesis?
 That is, can incentive salience be suppressed in the same way as physical salience?
@@
 Recent evidence suggests that the processes underlying VMAC are closely related to the attentional biases towards drug-related stimuli observed in addiction [@Albertella2017a; @Anderson2013; for review see @Field2008], which can promote relapse in recovering addicts [@Marissen2006; @Waters2012; @Marhe2013].
-Thus it is important to know whether top-down cognitive control processes can be used to overcome the influence of reward on attention when such capture is counterproductive and contrary to our goals.
-We addressed this question by combining Le Pelley et al.'s VMAC procedure with Gaspelin et al.'s (2017) overt attentional suppression procedure to investigate whether reward-related attentional biases can be suppressed by top-down control processes under conditions promoting feature search.
+Thus it is important to know whether cognitive control processes can be used to overcome the influence of reward on attention when such capture is counterproductive and contrary to our goals.
+We addressed this question by combining Le Pelley et al.'s VMAC procedure with Gaspelin et al.'s (2017) overt attentional suppression procedure to investigate whether reward-related attentional biases can be suppressed by inhibitory control processes under conditions promoting feature search.
 
@@
 For the *singleton search* condition, the non-target stimuli were all rendered as the alternative target shape (i.e., if the target was a diamond, all of the non-targets were circles; Figure \@ref(fig:methodFig)B).
-For the *feature search* condition, the non-target stimuli were randomly selected without replacement from a set of two squares and two hexagons, and were never rendered as the alternative target shape (Figure \@ref(fig:methodFig)C).
+For the *feature search* condition, the non-target stimuli were randomly selected without replacement from a set of two squares and two hexagons (such that one of the non-targets was always a shape singleton), and were never rendered as the alternative target shape (Figure \@ref(fig:methodFig)C).
 The target and two of the non-targets were always rendered in grey (CIE $x$,$y$ chromaticity coordinates of .327/.400).
@@
 
-[^2]: Note that the comparison of interest in determining whether a stimulus captured attention, or was otherwise suppressed, is the percentage of first saccades to the singleton vs.
+[^2]: Note that the comparison of interest in determining whether a stimulus captured attention, or was suppressed, is the percentage of first saccades to the singleton vs.
 the average nonsingleton distractor.
@@
 Thus, in line with previous findings [@Gaspelin2016], our data suggest that overt attention to physically salient singletons can be suppressed when participants are encouraged to adopt a specific target template.
-However, singletons that have been associated with high-reward reward capture overt attention, regardless of participants' target template and despite such capture being directly counterproductive to earning reward.
+However, singletons that have been associated with high reward capture overt attention, regardless of participants' target template and despite such capture being directly counterproductive to earning reward.
 
@@
 We calculated mean saccade latency and capture score separately for each trial type and quartile of the individual saccade latency distributions.
-We then analysed the capture scores for the most rapidly generated saccades.
-According to the signal suppression hypothesis, the top-down suppression effect is activated early in processing, prior to the initial allocation of attention [@Gaspelin2018a].
+We then analysed the capture scores for the data from the first quartile of this distribution, i.e., the most rapidly generated saccades.
+According to the signal suppression hypothesis, the attentional suppression effect is activated early in processing, prior to the initial allocation of attention [@Gaspelin2018a].
 Therefore the speed with which a saccade is initiated should have no effect on the extent to which overt attention can be suppressed.
 As illustrated in Figure \@ref(fig:VincentizedPlot), the most rapidly generated saccades were captured by the high-reward singleton (capture scores $>0$) in both the singleton search, `r apa_print(vincentized_singleton_high_q1.ttest)$statistic`, $d_z=$ `r vincentized_singleton_high_q1.es`, and feature search conditions, `r apa_print(vincentized_feature_high_q1.ttest)$statistic`, $d_z=$ `r vincentized_feature_high_q1.es`.
-Similarly, the the most rapidly generated saccades were captured by the low-reward singleton in both the singleton search, `r apa_print(vincentized_singleton_low_q1.ttest)$statistic`, $d_z=$ `r vincentized_singleton_low_q1.es`, and feature search conditions, `r apa_print(vincentized_feature_low_q1.ttest)$statistic`, $d_z=$ `r vincentized_feature_low_q1.es`.
+Similarly, the most rapidly generated saccades were captured by the low-reward singleton in both the singleton search, `r apa_print(vincentized_singleton_low_q1.ttest)$statistic`, $d_z=$ `r vincentized_singleton_low_q1.es`, and feature search conditions, `r apa_print(vincentized_feature_low_q1.ttest)$statistic`, $d_z=$ `r vincentized_feature_low_q1.es`.
 It is notable that we observed capture (rather than suppression) for the fastest saccades for both trial-types in the feature search condition.
@@
 # Discussion
-In this experiment, we investigated the role of top-down control processes in actively suppressing overt attention to physically salient and reward-associated distractor stimuli.
-In line with the signal suppression hypothesis [@Gaspelin2016; @Gaspelin2015], we found that overt attention to physically salient colour singleton distractors can be actively suppressed under conditions that promote top-down guidance of attention.
-Consistent with recent findings [@Gaspelin2018b; @Vatterott2012], this attentional suppression effect gradually emerged over the course of the experiment, as participants gained experience with the physically salient distractor feature.
-Furthermore, we found an effect of reward association on overt attention [i.e., VMAC; @LePelley2015b; @Pearson2015], with participants' gaze more likely to be captured by distractor stimuli that signalled high reward than low reward, even though looking at reward-signalling distractors caused omission of rewards that otherwise would have been delivered.
+In this experiment, we investigated the role of inhibitory control processes in actively suppressing overt attention to physically salient and reward-associated distractor stimuli.
+In line with the signal suppression hypothesis [@Gaspelin2016; @Gaspelin2015], overt attention to physically salient colour singleton distractors was suppressed under conditions that promoted top-down guidance of attention.
+Specifically, under feature search conditions, participants were generally less likely to look at a (low-reward) colour singleton distractor than the average nonsingleton distractor.
+Consistent with recent findings [@Gaspelin2018b; @Vatterott2012], this attentional suppression effect gradually emerged over the course of the experiment, as participants gained experience with the salient-but-irrelevant distractor feature (Figure \@ref(fig:blockPlot)).
+Furthermore, we observed an effect of reward association on overt attention [i.e., VMAC; @LePelley2015b; @Pearson2015], with participants' gaze more likely to be captured by distractor stimuli that signalled high reward than low reward, even though looking at reward-signalling distractors caused omission of rewards that otherwise would have been delivered.
 Similar to the attentional suppression effect, attentional capture by reward-associated distractors also emerged over the course of the experiment, as participants experienced more pairings of stimulus features with reward.
@@
 Nevertheless, the high-reward distractor captured attention, even under conditions that allowed participants to suppress their attention to physically salient distractors that were associated with low reward.
-Our key finding, then, is that reward-related stimuli constitute especially potent attentional priority signals that are relatively immune to suppression by top-down control processes that can act to prevent distraction by physical salience.
+Our key finding, then, is that reward-related stimuli constitute especially potent attentional priority signals that are relatively immune to suppression by inhibitory control processes that can act to prevent distraction by physical salience.
 
@@
 The priority map concept has also been used to explain how selection history influences attentional allocation [@Awh2012; @Failing2018], with the attentional priority signal of reward-related stimulus features increasing with repeated stimulus-reward pairings through a process of associative learning [@Pearson2016; @LePelleya].
-Recent formulations of the signal suppression hypothesis have suggested that the top-down suppression mechanism may operate in a similar way, with the attentional priority of to-be-ignored stimulus features being proactively downweighted with repeated experience [@Gaspelin2018a].
-At first glance, the results of the current study may seem inconsistent with the idea that reward and top-down suppression engage in competition on a common priority map, as the magnitude of the VMAC effect did not differ between search conditions, even though the feature search condition should have encouraged top-down guidance of attention.
-However, there was an overall decrease in the amount of capture by both the high- and low-reward distractor in the feature search condition This raises the possibility that repeated experience of the physically salient stimulus features (i.e., orange and blue colour) allows the attentional priority of those features to be uniformly downweighted by the top-down suppression mechanism.
-In addition, our findings are consistent with the idea that repeated experience of the stimulus feature-reward pairings selectively upweights the attentional priority of the high-reward distractor, such that it overpowers the influence of top-down suppression and thus captures attention.
+Recent formulations of the signal suppression hypothesis have suggested that the attentional suppression mechanism may operate in a similar way, with the attentional priority of to-be-ignored stimulus features being proactively down-weighted with repeated experience [@Gaspelin2018a].
+At first glance, the results of the current study may seem inconsistent with the idea that reward and suppression engage in competition on a common priority map, as the magnitude of the VMAC effect did not differ between search conditions, even though the feature search condition should have encouraged top-down guidance of attention.
+However, there was an _overall_ decrease in the amount of capture by both the high- and low-reward distractor in the feature search condition (supported by a main effect of search condition, e.g., see Figures \@ref(fig:SaccadePlot)B and \@ref(fig:SaccadePlot)D).
+This raises the possibility that repeated experience of the physically salient stimulus features (i.e., orange and blue colour) allows the attentional priority of those features to be uniformly down-weighted by the suppression mechanism.
+In addition, our findings are consistent with the idea that repeated experience of pairings between stimulus features and reward results in selective up-weighting of the attentional priority of the high-reward distractor, such that it overpowers the influence of inhibitory suppression and thus captures attention.
 
-An inconsistency between the results of the current study and that of @Gaspelin2016 comes from the time-course of the attentional capture and suppression effects that were observed.
-According to the signal suppression hypothesis, top-down suppression operates prior to the initial allocation of attention, and so suppression should be observed even for the most rapidly generated saccades.
+An inconsistency between the results of the current study and those of @Gaspelin2016 comes from the time-course of the attentional capture and suppression effects that were observed.
+According to the signal suppression hypothesis, suppression is _proactive_---in that it operates prior to the initial allocation of attention---and so suppression should be observed even for the most rapidly generated saccades.
 Consistent with this idea, @Gaspelin2016 observed an overt attentional suppression effect to physically salient singleton distractors amongst the fastest quartile of saccade latencies.
-In contrast, in the current experiment we observed overt attentional capture in the fastest quartile of saccade latencies, with the suppression effect emerging on trials with slower saccades.
+By contrast, in the current experiment we observed overt attentional capture in the fastest quartile of saccade latencies, with the suppression effect emerging on trials with slower saccades.
 Methodological differences between Gaspelin et al.'s  [-@Gaspelin2016] experiment and the current study may be responsible for this discrepancy.
-For example, the availability of reward on low-reward trials may have influenced capture, either by somewhat increasing the attentional priority of the stimulus feature associated with low-reward reward, or by otherwise influencing participants' motivation to respond quickly.
+For example, the availability of reward on low-reward trials may have influenced capture, either by somewhat increasing the attentional priority of the stimulus feature associated with low reward, or by otherwise influencing participants' motivation to respond quickly.
 Alternatively, the discrepancy in findings may reflect our use of two potential targets (circle and diamond) in the feature search condition, as opposed to the same target on all trials in Gaseplin et al.'s procedure.
 Having two possible targets could reduce the influence of trial-by-trial upweighting of target features [@Maljkovic1994], but may also result in less effective feature search [e.g., @Houtkamp2009; but see @Grubert2015].
+Another possible explanation comes from the use of an intermixed trial structure: as participants randomly experienced trials containing either the high- or low-reward colour throughout the course of the task, it is possible that the proactive down-weighting of the salient-but-irrelevant features could not build up enough to prevent capture for the most rapidly initiated saccades [@Gaspelin2018a].
 How these methodological differences might influence the time-course of overt attentional capture and suppression remains a question for future research.
-Nonetheless, the finding does raise questions about whether the attentional suppression effect that we have observed is truly the result of proactive top-down suppression of salient stimuli, as suggested by the signal suppression hypothesis, or potentially the result of rapid covert disengagement from the salient stimuli [see @Theeuwes2010; @VanZoest2004 for similar arguments].
+Nonetheless, the finding does raise questions about whether the attentional suppression effect that we have observed is truly the result of proactive attentional suppression of salient stimuli, as suggested by the signal suppression hypothesis, or potentially the result of rapid covert disengagement from the salient stimuli [see @Theeuwes2010; @VanZoest2004 for similar arguments].
 
@@
 This is consistent with the idea of incentive salience [@Berridge1998], where the perceptual representation of an otherwise neutral stimulus is modified so as to become more salient and attention grabbing to the observer, as a result of its association with a desired outcome (e.g., drugs, money).
-The current study suggests that incentive salience has a particularly powerful influence on the attentional system, overcoming top-down control mechanisms that can effectively prevent capture by physically salient stimuli.
+The current study suggests that incentive salience has a particularly powerful influence on the attentional system, overcoming inhibitory control mechanisms that can effectively prevent capture by physically salient stimuli.
 This may have implications for the development of treatments for substance use disorders that target these attentional biases.

### 2019-04-18 analysis/paper/paper.tex
update manuscript

@@
 \hypersetup{unicode=true,
-            pdftitle={Overt attentional capture by reward-related stimuli overcomes top-down suppression},
+            pdftitle={Overt attentional capture by reward-related stimuli overcomes inhibitory suppression},
             pdfauthor={Daniel Pearson, Poppy Watson, Phillip Cheng, \& Mike E. Le Pelley},
@@
 
-  \title{Overt attentional capture by reward-related stimuli overcomes top-down
+  \title{Overt attentional capture by reward-related stimuli overcomes inhibitory
 suppression}
@@
 \enquote{attend-to-me} signal) that will go on to capture attention
-unless it is suppressed by a top-down control process, which builds over
-repeated experience with the salient stimulus (Gaspelin \& Luck, 2018a).
-This account is consistent with stimulus-driven theories, in that it
-proposes that physically salient stimuli have the potential to
+unless it is suppressed by an inhibitory control process, which builds
+over repeated experience with the salient stimulus (Gaspelin \& Luck,
+2018a). This account is consistent with stimulus-driven theories, in
+that it proposes that physically salient stimuli have the potential to
 involuntarily capture attention; however it is also consistent with
@@
 attention to the salient colour-singleton distractor was suppressed
-relative to the other non-targets, suggesting that it was treated
-differently from the other non-targets (inconsistent with goal-directed
-accounts), yet did not capture gaze (inconsistent with stimulus-driven
-accounts). By contrast, the signal suppression hypothesis can account
-for these findings by suggesting that the singleton generated an
-attentional priority signal as a consequence of its physical salience,
-but this signal could be suppressed by top-down control under conditions
-that promote a more specific search strategy (i.e., feature search).
-Importantly, this suppression effect was observed even for the most
-rapidly generated eye movements, which was taken as evidence that the
-suppression effect operates early in processing, before attention is
-initially allocated.
+relative to the other non-targets, suggesting that the visual attention
+system treated the salient singleton differently from the other
+non-targets (inconsistent with goal-directed accounts), yet did not
+capture gaze (inconsistent with stimulus-driven accounts). By contrast,
+the signal suppression hypothesis can account for these findings by
+suggesting that the singleton generated an attentional priority signal
+as a consequence of its physical salience, but this signal could be
+suppressed by an inhibitory mechanism under conditions that promoted a
+more specific search strategy (i.e., feature search). Importantly, this
+suppression effect was observed even for the most rapidly generated eye
+movements, which was taken as evidence that the suppression effect
+operates early in processing, before attention is initially allocated.
 
@@
 grabbing to the observer through a change in its perceptual
-representation. This begs the question, if associating a stimulus with
+representation. This raises the question, if associating a stimulus with
 reward increases its perceptual priority as though it has become more
 physically salient, can this priority signal be suppressed by the
-top-down control process proposed by the signal suppression hypothesis?
-That is, can incentive salience be suppressed in the same way as
-physical salience? Aside from the theoretical importance of this
+inhibitory control process proposed by the signal suppression
+hypothesis? That is, can incentive salience be suppressed in the same
+way as physical salience? Aside from the theoretical importance of this
 question, it may also have important clinical implications. Recent
@@
 Franken, 2013; Marissen et al., 2006; A. J. Waters, Marhe, \& Franken,
-2012). Thus it is important to know whether top-down cognitive control
-processes can be used to overcome the influence of reward on attention
-when such capture is counterproductive and contrary to our goals. We
-addressed this question by combining Le Pelley et al.'s VMAC procedure
-with Gaspelin et al.'s (2017) overt attentional suppression procedure to
+2012). Thus it is important to know whether cognitive control processes
+can be used to overcome the influence of reward on attention when such
+capture is counterproductive and contrary to our goals. We addressed
+this question by combining Le Pelley et al.'s VMAC procedure with
+Gaspelin et al.'s (2017) overt attentional suppression procedure to
 investigate whether reward-related attentional biases can be suppressed
-by top-down control processes under conditions promoting feature search.
+by inhibitory control processes under conditions promoting feature
+search.
 
@@
 non-target stimuli were randomly selected without replacement from a set
-of two squares and two hexagons, and were never rendered as the
-alternative target shape (Figure \ref{fig:methodFig}C). The target and
-two of the non-targets were always rendered in grey (CIE \(x\),\(y\)
-chromaticity coordinates of .327/.400). On the majority of trials, one
-of the non-target shapes (the \emph{singleton distractor}) was rendered
-in either orange or blue (CIE \(x\),\(y\) coordinates .492/.445 and
+of two squares and two hexagons (such that one of the non-targets was
+always a shape singleton), and were never rendered as the alternative
+target shape (Figure \ref{fig:methodFig}C). The target and two of the
+non-targets were always rendered in grey (CIE \(x\),\(y\) chromaticity
+coordinates of .327/.400). On the majority of trials, one of the
+non-target shapes (the \emph{singleton distractor}) was rendered in
+either orange or blue (CIE \(x\),\(y\) coordinates .492/.445 and
 .192/.216, respectively). On the remaining trials, all shapes were
@@
   the comparison of interest in determining whether a stimulus captured
-  attention, or was otherwise suppressed, is the percentage of first
-  saccades to the singleton vs.~the average nonsingleton distractor.
-  Thus, while we have included the percentage of first saccades to the
-  target in Figure \ref{fig:SaccadePlot} for the sake of completeness,
-  we have not included these data in our analyses.}, average
-nonsingleton distractor, and singleton distractor) on high- and
-low-reward trials for the singleton search (Figure
-\ref{fig:SaccadePlot}A) and feature search (Figure
-\ref{fig:SaccadePlot}C) conditions; Figures \ref{fig:SaccadePlot}B and
-\ref{fig:SaccadePlot}D show capture scores (difference in percentage of
-first saccades directed towards singleton versus average nonsingleton
-distractor) for the singleton search and feature search conditions,
-respectively. ANOVA analysis of capture scores revealed a significant
-main effect of trial type (high-reward vs low-reward),
-\(F(1, 62) = 45.55\), \(p < .001\), \(\hat{\eta}^2_p = .424\), with the
-singleton capturing attention more often on high-reward trials than
-low-reward trials; once again demonstrating a VMAC effect. A main effect
-of search condition (singleton search vs feature search),
-\(F(1, 62) = 4.89\), \(p = .031\), \(\hat{\eta}^2_p = .073\), indicated
-that both the high-reward and low-reward singleton captured attention
-more often, on average, in the singleton search condition than the
-feature search condition. Importantly, the trial type \(\times\) search
-condition interaction was non-significant, \(F(1, 62) = 0.12\),
-\(p = .735\), \(\hat{\eta}^2_p = .002\), with a corresponding Bayes
-factor of \(\mathrm{BF}_{\textrm{01}} = 3.73\) indicating moderate
-support for the null hypothesis that search condition had no effect on
-the magnitude of the VMAC effect on first saccade direction.
+  attention, or was suppressed, is the percentage of first saccades to
+  the singleton vs.~the average nonsingleton distractor. Thus, while we
+  have included the percentage of first saccades to the target in Figure
+  \ref{fig:SaccadePlot} for the sake of completeness, we have not
+  included these data in our analyses.}, average nonsingleton
+distractor, and singleton distractor) on high- and low-reward trials for
+the singleton search (Figure \ref{fig:SaccadePlot}A) and feature search
+(Figure \ref{fig:SaccadePlot}C) conditions; Figures
+\ref{fig:SaccadePlot}B and \ref{fig:SaccadePlot}D show capture scores
+(difference in percentage of first saccades directed towards singleton
+versus average nonsingleton distractor) for the singleton search and
+feature search conditions, respectively. ANOVA analysis of capture
+scores revealed a significant main effect of trial type (high-reward vs
+low-reward), \(F(1, 62) = 45.55\), \(p < .001\),
+\(\hat{\eta}^2_p = .424\), with the singleton capturing attention more
+often on high-reward trials than low-reward trials; once again
+demonstrating a VMAC effect. A main effect of search condition
+(singleton search vs feature search), \(F(1, 62) = 4.89\), \(p = .031\),
+\(\hat{\eta}^2_p = .073\), indicated that both the high-reward and
+low-reward singleton captured attention more often, on average, in the
+singleton search condition than the feature search condition.
+Importantly, the trial type \(\times\) search condition interaction was
+non-significant, \(F(1, 62) = 0.12\), \(p = .735\),
+\(\hat{\eta}^2_p = .002\), with a corresponding Bayes factor of
+\(\mathrm{BF}_{\textrm{01}} = 3.73\) indicating moderate support for the
+null hypothesis that search condition had no effect on the magnitude of
+the VMAC effect on first saccade direction.
 
@@
 encouraged to adopt a specific target template. However, singletons that
-have been associated with high-reward reward capture overt attention,
+have been associated with high reward capture overt attention,
 regardless of participants' target template and despite such capture
@@
 trial type and quartile of the individual saccade latency distributions.
-We then analysed the capture scores for the most rapidly generated
-saccades. According to the signal suppression hypothesis, the top-down
+We then analysed the capture scores for the data from the first quartile
+of this distribution, i.e., the most rapidly generated saccades.
+According to the signal suppression hypothesis, the attentional
 suppression effect is activated early in processing, prior to the
@@
 2.30, and feature search conditions, \(t(31) = 6.45\), \(p < .001\),
-\(d_z=\) 1.14. Similarly, the the most rapidly generated saccades were
+\(d_z=\) 1.14. Similarly, the most rapidly generated saccades were
 captured by the low-reward singleton in both the singleton search,
@@
 
-In this experiment, we investigated the role of top-down control
+In this experiment, we investigated the role of inhibitory control
 processes in actively suppressing overt attention to physically salient
 and reward-associated distractor stimuli. In line with the signal
-suppression hypothesis (Gaspelin et al., 2015, 2017), we found that
-overt attention to physically salient colour singleton distractors can
-be actively suppressed under conditions that promote top-down guidance
-of attention. Consistent with recent findings (Gaspelin \& Luck, 2018a;
-Vatterott \& Vecera, 2012), this attentional suppression effect
-gradually emerged over the course of the experiment, as participants
-gained experience with the physically salient distractor feature.
-Furthermore, we found an effect of reward association on overt attention
-(i.e., VMAC; M. E. Le Pelley et al., 2015; Pearson et al., 2015), with
-participants' gaze more likely to be captured by distractor stimuli that
-signalled high reward than low reward, even though looking at
-reward-signalling distractors caused omission of rewards that otherwise
-would have been delivered. Similar to the attentional suppression
-effect, attentional capture by reward-associated distractors also
-emerged over the course of the experiment, as participants experienced
-more pairings of stimulus features with reward. Critically, this study
-was the first to demonstrate that---unlike the influence of physical
-salience---the influence of reward association on attention cannot be
-suppressed under conditions that promote top-down guidance of attention.
-Regardless of whether participants were encouraged to search for
-specific target defining features (i.e., feature search mode) or to
-search for the odd-one-out (singleton search mode), stimuli associated
-with high reward captured overt attention. Notably, this attentional
-bias was counterproductive, in that it led to the omission of more high
-rewards than low rewards, and so participants should have been highly
-motivated to suppress their attention to the high-reward distractor if
-possible. Nevertheless, the high-reward distractor captured attention,
-even under conditions that allowed participants to suppress their
-attention to physically salient distractors that were associated with
-low reward. Our key finding, then, is that reward-related stimuli
-constitute especially potent attentional priority signals that are
-relatively immune to suppression by top-down control processes that can
-act to prevent distraction by physical salience.
+suppression hypothesis (Gaspelin et al., 2015, 2017), overt attention to
+physically salient colour singleton distractors was suppressed under
+conditions that promoted top-down guidance of attention. Specifically,
+under feature search conditions, participants were generally less likely
+to look at a (low-reward) colour singleton distractor than the average
+nonsingleton distractor. Consistent with recent findings (Gaspelin \&
+Luck, 2018a; Vatterott \& Vecera, 2012), this attentional suppression
+effect gradually emerged over the course of the experiment, as
+participants gained experience with the salient-but-irrelevant
+distractor feature (Figure \ref{fig:blockPlot}). Furthermore, we
+observed an effect of reward association on overt attention (i.e., VMAC;
+M. E. Le Pelley et al., 2015; Pearson et al., 2015), with participants'
+gaze more likely to be captured by distractor stimuli that signalled
+high reward than low reward, even though looking at reward-signalling
+distractors caused omission of rewards that otherwise would have been
+delivered. Similar to the attentional suppression effect, attentional
+capture by reward-associated distractors also emerged over the course of
+the experiment, as participants experienced more pairings of stimulus
+features with reward. Critically, this study was the first to
+demonstrate that---unlike the influence of physical salience---the
+influence of reward association on attention cannot be suppressed under
+conditions that promote top-down guidance of attention. Regardless of
+whether participants were encouraged to search for specific target
+defining features (i.e., feature search mode) or to search for the
+odd-one-out (singleton search mode), stimuli associated with high reward
+captured overt attention. Notably, this attentional bias was
+counterproductive, in that it led to the omission of more high rewards
+than low rewards, and so participants should have been highly motivated
+to suppress their attention to the high-reward distractor if possible.
+Nevertheless, the high-reward distractor captured attention, even under
+conditions that allowed participants to suppress their attention to
+physically salient distractors that were associated with low reward. Our
+key finding, then, is that reward-related stimuli constitute especially
+potent attentional priority signals that are relatively immune to
+suppression by inhibitory control processes that can act to prevent
+distraction by physical salience.
 
@@
 2016). Recent formulations of the signal suppression hypothesis have
-suggested that the top-down suppression mechanism may operate in a
+suggested that the attentional suppression mechanism may operate in a
 similar way, with the attentional priority of to-be-ignored stimulus
-features being proactively downweighted with repeated experience
+features being proactively down-weighted with repeated experience
 (Gaspelin \& Luck, 2019). At first glance, the results of the current
-study may seem inconsistent with the idea that reward and top-down
-suppression engage in competition on a common priority map, as the
-magnitude of the VMAC effect did not differ between search conditions,
-even though the feature search condition should have encouraged top-down
-guidance of attention. However, there was an overall decrease in the
-amount of capture by both the high- and low-reward distractor in the
-feature search condition This raises the possibility that repeated
-experience of the physically salient stimulus features (i.e., orange and
-blue colour) allows the attentional priority of those features to be
-uniformly downweighted by the top-down suppression mechanism. In
-addition, our findings are consistent with the idea that repeated
-experience of the stimulus feature-reward pairings selectively upweights
-the attentional priority of the high-reward distractor, such that it
-overpowers the influence of top-down suppression and thus captures
-attention.
-
-An inconsistency between the results of the current study and that of
+study may seem inconsistent with the idea that reward and suppression
+engage in competition on a common priority map, as the magnitude of the
+VMAC effect did not differ between search conditions, even though the
+feature search condition should have encouraged top-down guidance of
+attention. However, there was an \emph{overall} decrease in the amount
+of capture by both the high- and low-reward distractor in the feature
+search condition (supported by a main effect of search condition, e.g.,
+see Figures \ref{fig:SaccadePlot}B and \ref{fig:SaccadePlot}D). This
+raises the possibility that repeated experience of the physically
+salient stimulus features (i.e., orange and blue colour) allows the
+attentional priority of those features to be uniformly down-weighted by
+the suppression mechanism. In addition, our findings are consistent with
+the idea that repeated experience of pairings between stimulus features
+and reward results in selective up-weighting of the attentional priority
+of the high-reward distractor, such that it overpowers the influence of
+inhibitory suppression and thus captures attention.
+
+An inconsistency between the results of the current study and those of
 Gaspelin et al. (2017) comes from the time-course of the attentional
 capture and suppression effects that were observed. According to the
-signal suppression hypothesis, top-down suppression operates prior to
-the initial allocation of attention, and so suppression should be
-observed even for the most rapidly generated saccades. Consistent with
-this idea, Gaspelin et al. (2017) observed an overt attentional
-suppression effect to physically salient singleton distractors amongst
-the fastest quartile of saccade latencies. In contrast, in the current
-experiment we observed overt attentional capture in the fastest quartile
-of saccade latencies, with the suppression effect emerging on trials
-with slower saccades. Methodological differences between Gaspelin et
-al.\enquote{s (2017) experiment and the current study may be responsible
-for this discrepancy. For example, the availability of reward on
-low-reward trials may have influenced capture, either by somewhat
-increasing the attentional priority of the stimulus feature associated
-with low-reward reward, or by otherwise influencing participants}
-motivation to respond quickly. Alternatively, the discrepancy in
-findings may reflect our use of two potential targets (circle and
-diamond) in the feature search condition, as opposed to the same target
-on all trials in Gaseplin et al.'s procedure. Having two possible
-targets could reduce the influence of trial-by-trial upweighting of
-target features (Maljkovic \& Nakayama, 1994), but may also result in
-less effective feature search (but see Grubert \& Eimer, 2015; e.g.,
-Houtkamp \& Roelfsema, 2009). How these methodological differences might
-influence the time-course of overt attentional capture and suppression
-remains a question for future research. Nonetheless, the finding does
-raise questions about whether the attentional suppression effect that we
-have observed is truly the result of proactive top-down suppression of
-salient stimuli, as suggested by the signal suppression hypothesis, or
-potentially the result of rapid covert disengagement from the salient
-stimuli (see J. Theeuwes, 2010; Zoest et al., 2004 for similar
-arguments).
+signal suppression hypothesis, suppression is \emph{proactive}---in that
+it operates prior to the initial allocation of attention---and so
+suppression should be observed even for the most rapidly generated
+saccades. Consistent with this idea, Gaspelin et al. (2017) observed an
+overt attentional suppression effect to physically salient singleton
+distractors amongst the fastest quartile of saccade latencies. By
+contrast, in the current experiment we observed overt attentional
+capture in the fastest quartile of saccade latencies, with the
+suppression effect emerging on trials with slower saccades.
+Methodological differences between Gaspelin et al.\enquote{s (2017)
+experiment and the current study may be responsible for this
+discrepancy. For example, the availability of reward on low-reward
+trials may have influenced capture, either by somewhat increasing the
+attentional priority of the stimulus feature associated with low reward,
+or by otherwise influencing participants} motivation to respond quickly.
+Alternatively, the discrepancy in findings may reflect our use of two
+potential targets (circle and diamond) in the feature search condition,
+as opposed to the same target on all trials in Gaseplin et al.'s
+procedure. Having two possible targets could reduce the influence of
+trial-by-trial upweighting of target features (Maljkovic \& Nakayama,
+1994), but may also result in less effective feature search (but see
+Grubert \& Eimer, 2015; e.g., Houtkamp \& Roelfsema, 2009). Another
+possible explanation comes from the use of an intermixed trial
+structure: as participants randomly experienced trials containing either
+the high- or low-reward colour throughout the course of the task, it is
+possible that the proactive down-weighting of the salient-but-irrelevant
+features could not build up enough to prevent capture for the most
+rapidly initiated saccades (Gaspelin \& Luck, 2019). How these
+methodological differences might influence the time-course of overt
+attentional capture and suppression remains a question for future
+research. Nonetheless, the finding does raise questions about whether
+the attentional suppression effect that we have observed is truly the
+result of proactive attentional suppression of salient stimuli, as
+suggested by the signal suppression hypothesis, or potentially the
+result of rapid covert disengagement from the salient stimuli (see J.
+Theeuwes, 2010; Zoest et al., 2004 for similar arguments).
 
@@
 The current study suggests that incentive salience has a particularly
-powerful influence on the attentional system, overcoming top-down
+powerful influence on the attentional system, overcoming inhibitory
 control mechanisms that can effectively prevent capture by physically

### 2019-04-23 analysis/paper/paper.Rmd
fixed paper, added dockerfile for testing

@@
 draft             : no
-
+csl               : "american-psychological-association-6th-edition_no_first_citation.csl"
 header-includes:
@@
 documentclass     : "apa6"
-classoption       : "jou, a4paper, noextraspace"
+classoption       : "man, a4paper, noextraspace, 11pt"
 output            : papaja::apa6_pdf
@@
 library(here)
-load(here::here("analysis", "data", "completed_analysis.rda"))
-# source(here("Analysis Programs", "Figures", "manuscript_figs.r"))
+
+# Source analysis_report.R (the R code from analysis_report.Rmd) to allow this document to have access to  all analyses necessary for manuscript.
+source(here::here("analysis", "analysis_report.R"))
+
 # use this to allow custom decimal places later on
@@
 
-```{r analysis-preferences}
+```{r analysis-preferences, echo=FALSE}
 # Seed for random number generation
@@
 
-```{r methodFig, fig.align='center', fig.cap = '(ref:methodFig)', out.width='100%'}
+```{r methodFig, echo=FALSE, fig.align='center', fig.cap='(ref:methodFig)', fig.pos="!h", out.width='80%'}
 knitr::include_graphics(here("analysis", "figures", "Methods_fig.png"), dpi = 300)
@@
 
-```{r OmissionPlot, fig.align='center', fig.cap = '(ref:omissions)', out.width='100%'}
+```{r OmissionPlot, echo=FALSE, fig.align='center', fig.cap = '(ref:omissions)', out.width='60%', fig.pos = "!h"}
 knitr::include_graphics(here("analysis", "figures", "omission_plot.png"), dpi = 300)
@@
 
-```{r SaccadePlot, fig.align='center', fig.cap = '(ref:saccadeFig)', out.width='100%'}
+```{r SaccadePlot, echo=FALSE, fig.align='center', fig.cap = '(ref:saccadeFig)', out.width='80%', fig.pos = "!h"}
 knitr::include_graphics(here("analysis", "figures", "saccade_plot.png"), dpi = 300)
@@
 
-```{r blockPlot, fig.align='center', fig.cap = '(ref:blockFig)', out.width='100%'}
+```{r blockPlot, echo=FALSE, fig.align='center', fig.cap = '(ref:blockFig)', out.width='60%', fig.pos = "!h"}
 knitr::include_graphics(here("analysis", "figures", "capture_plot_by_block.png"), dpi = 300)
@@
 
-```{r VincentizedPlot, fig.align='center', fig.cap = '(ref:vincentizedFig)', out.width='100%'}
+```{r VincentizedPlot, echo=FALSE, fig.align='center', fig.cap = '(ref:vincentizedFig)', out.width='60%',fig.pos = "!h"}
 knitr::include_graphics(here("analysis", "figures", "vincentized_plot.png"), dpi = 300)
@@
 # References
-```{r create_r-references}
+```{r create_r-references, echo=FALSE}
 r_refs(file = "r-references.bib")

### 2019-04-23 analysis/paper/paper.tex
fixed paper, added dockerfile for testing

@@
-\documentclass[jou, a4paper, noextraspace,floatsintext]{apa6}
+\documentclass[man, a4paper, noextraspace, 11pt,floatsintext]{apa6}
 \usepackage{lmodern}
@@
 attentional control: one that is volitional and goal directed (top-down
-control) and another that is automatic and stimulus driven (S. Yantis,
+control) and another that is automatic and stimulus driven (Yantis,
 2000). However, exactly how these two processes interact has been the
@@
 that attention is initially captured by the most salient stimulus
-presented to an observer, regardless of their current goals (J.
-Theeuwes, 1992, 2010). That is, individuals have no voluntary control
-over the initial allocation of their attention, which is automatically
-drawn to the most salient stimulus in a scene. By contrast,
-\emph{goal-directed} accounts posit that attention is allocated only to
-stimuli that are in some way related to the observer's current goals
-(Folk, Remington, \& Johnston, 1992; Leber \& Egeth, 2006). These
-theories predict that physically salient stimuli will be completely
-ignored by the visual attention system, unless they share some
-feature(s) with the observer's template of expected targets.
+presented to an observer, regardless of their current goals (Theeuwes,
+1992, 2010). That is, individuals have no voluntary control over the
+initial allocation of their attention, which is automatically drawn to
+the most salient stimulus in a scene. By contrast, \emph{goal-directed}
+accounts posit that attention is allocated only to stimuli that are in
+some way related to the observer's current goals (Folk, Remington, \&
+Johnston, 1992; Leber \& Egeth, 2006). These theories predict that
+physically salient stimuli will be completely ignored by the visual
+attention system, unless they share some feature(s) with the observer's
+template of expected targets.
 
@@
 participants perform variants of a commonly used procedure for examining
-attentional capture---the \emph{additional singleton task} (J. Theeuwes,
+attentional capture---the \emph{additional singleton task} (Theeuwes,
 1991, 1992)---while recording eye movements. Eye movements provide a
@@
 from the current study). Under these conditions, both stimulus-driven
-(J. Theeuwes, 1992) and goal-directed (Bacon \& Egeth, 1994) accounts of
+(Theeuwes, 1992) and goal-directed (Bacon \& Egeth, 1994) accounts of
 attentional selection would predict capture, as the template that
@@
 dichotomy (Awh, Belopolsky, \& Theeuwes, 2012; Failing \& Theeuwes,
-2018; M. E. Le Pelley, Mitchell, Beesley, George, \& Wills, 2016). Awh
-et al. (2012) suggested a third category of influences on attentional
+2018; Le Pelley, Mitchell, Beesley, George, \& Wills, 2016). Awh et al.
+(2012) suggested a third category of influences on attentional
 selection, labelled \emph{selection history}. This category describes
@@
 stimulus features and motivationally significant outcomes---such as
-reward (Brian A. Anderson, 2016; Failing \& Theeuwes, 2018; M. E. Le
-Pelley et al., 2016) or punishment (Watson, Pearson, Wiers, \& Le
-Pelley, 2019)---as well as other biases related to the history of
-attentional deployment that cannot be easily explained in terms of
-goal-directed or stimulus-driven control, such as biases for selecting
-stimulus features that have previously acted as targets (e.g., Maljkovic
-\& Nakayama, 1994).
+reward (Anderson, 2016; Failing \& Theeuwes, 2018; Le Pelley et al.,
+2016) or punishment (Watson, Pearson, Wiers, \& Le Pelley, 2019)---as
+well as other biases related to the history of attentional deployment
+that cannot be easily explained in terms of goal-directed or
+stimulus-driven control, such as biases for selecting stimulus features
+that have previously acted as targets (e.g., Maljkovic \& Nakayama,
+1994).
 
@@
 to the attentional biases towards drug-related stimuli observed in
-addiction (Albertella et al., 2017; Brian A Anderson, Faulkner, Rilee,
-Yantis, \& Marvel, 2013; for review see Field \& Cox, 2008), which can
-promote relapse in recovering addicts (Marhe, Waters, Wetering, \&
-Franken, 2013; Marissen et al., 2006; A. J. Waters, Marhe, \& Franken,
-2012). Thus it is important to know whether cognitive control processes
-can be used to overcome the influence of reward on attention when such
-capture is counterproductive and contrary to our goals. We addressed
-this question by combining Le Pelley et al.'s VMAC procedure with
-Gaspelin et al.'s (2017) overt attentional suppression procedure to
-investigate whether reward-related attentional biases can be suppressed
-by inhibitory control processes under conditions promoting feature
-search.
+addiction (Albertella et al., 2017; Anderson, Faulkner, Rilee, Yantis,
+\& Marvel, 2013; for review see Field \& Cox, 2008), which can promote
+relapse in recovering addicts (Marhe, Waters, Wetering, \& Franken,
+2013; Marissen et al., 2006; Waters, Marhe, \& Franken, 2012). Thus it
+is important to know whether cognitive control processes can be used to
+overcome the influence of reward on attention when such capture is
+counterproductive and contrary to our goals. We addressed this question
+by combining Le Pelley et al.'s VMAC procedure with Gaspelin et al.'s
+(2017) overt attentional suppression procedure to investigate whether
+reward-related attentional biases can be suppressed by inhibitory
+control processes under conditions promoting feature search.
 
@@
 Advisory Panel (Psychology). Previous studies of VMAC using gaze
-measures (M. E. Le Pelley et al., 2015; Pearson et al., 2015, 2016) have
+measures (Le Pelley et al., 2015; Pearson et al., 2015, 2016) have
 demonstrated medium to large effect sizes (\(d_z\) = 0.41--1.4, mean =
@@
 preceding 10 ms window. Stimulus presentation was controlled by MATLAB
-using the Psychophysics Toolbox extensions (D. H. Brainard, 1997;
-Kleiner et al., 2007; Pelli, 1997). Experiment scripts, analysis
-scripts, and raw data are available at (\textbf{OSF}).
+using the Psychophysics Toolbox extensions (Brainard, 1997; Kleiner et
+al., 2007; Pelli, 1997). Experiment scripts, analysis scripts, and raw
+data are available at (\textbf{OSF}).
 
@@
 
-\begin{figure}
-
-{\centering \includegraphics[width=1\linewidth]{C:/Users/Daniel/Google Drive/Research/vmacfeaturesearch/analysis/figures/Methods_fig}
+\begin{figure}[!h]
+
+{\centering \includegraphics[width=0.8\linewidth]{C:/Users/Daniel/Google Drive/Research/vmacfeaturesearch/analysis/figures/Methods_fig}
 
@@
 
-In line with previous VMAC protocols (e.g., M. E. Le Pelley et al.,
-2015; Pearson et al., 2016), data from the first two experimental
-trials, and the first two trials after each break were discarded. Hard
-timeouts (2.5\% of all trials) were also discarded. One participant was
-replaced because their mean proportion of valid gaze samples during each
-trial was less than 50\%. One other participant was replaced after
-reporting that they had misunderstood the task instructions. For the
-remaining participants, valid gaze data were registered on an average of
-97.5\% (\(SD=\) 3.7\%) of samples, suggesting high fidelity of gaze
-data.
+In line with previous VMAC protocols (e.g., Le Pelley et al., 2015;
+Pearson et al., 2016), data from the first two experimental trials, and
+the first two trials after each break were discarded. Hard timeouts
+(2.5\% of all trials) were also discarded. One participant was replaced
+because their mean proportion of valid gaze samples during each trial
+was less than 50\%. One other participant was replaced after reporting
+that they had misunderstood the task instructions. For the remaining
+participants, valid gaze data were registered on an average of 97.5\%
+(\(SD=\) 3.7\%) of samples, suggesting high fidelity of gaze data.
 
@@
 
-\begin{figure}
-
-{\centering \includegraphics[width=1\linewidth]{C:/Users/Daniel/Google Drive/Research/vmacfeaturesearch/analysis/figures/omission_plot}
+\begin{figure}[!h]
+
+{\centering \includegraphics[width=0.6\linewidth]{C:/Users/Daniel/Google Drive/Research/vmacfeaturesearch/analysis/figures/omission_plot}
 
@@
 
-\begin{figure}
-
-{\centering \includegraphics[width=1\linewidth]{C:/Users/Daniel/Google Drive/Research/vmacfeaturesearch/analysis/figures/saccade_plot}
+\begin{figure}[!h]
+
+{\centering \includegraphics[width=0.8\linewidth]{C:/Users/Daniel/Google Drive/Research/vmacfeaturesearch/analysis/figures/saccade_plot}
 
@@
 
-\begin{figure}
-
-{\centering \includegraphics[width=1\linewidth]{C:/Users/Daniel/Google Drive/Research/vmacfeaturesearch/analysis/figures/capture_plot_by_block}
+\begin{figure}[!h]
+
+{\centering \includegraphics[width=0.6\linewidth]{C:/Users/Daniel/Google Drive/Research/vmacfeaturesearch/analysis/figures/capture_plot_by_block}
 
@@
 
-\begin{figure}
-
-{\centering \includegraphics[width=1\linewidth]{C:/Users/Daniel/Google Drive/Research/vmacfeaturesearch/analysis/figures/vincentized_plot}
+\begin{figure}[!h]
+
+{\centering \includegraphics[width=0.6\linewidth]{C:/Users/Daniel/Google Drive/Research/vmacfeaturesearch/analysis/figures/vincentized_plot}
 
@@
 observed an effect of reward association on overt attention (i.e., VMAC;
-M. E. Le Pelley et al., 2015; Pearson et al., 2015), with participants'
-gaze more likely to be captured by distractor stimuli that signalled
-high reward than low reward, even though looking at reward-signalling
+Le Pelley et al., 2015; Pearson et al., 2015), with participants' gaze
+more likely to be captured by distractor stimuli that signalled high
+reward than low reward, even though looking at reward-signalling
 distractors caused omission of rewards that otherwise would have been
@@
 spatial location with the highest peak of activation (e.g., Itti \&
-Koch, 2001; J. Theeuwes, 2010; Wolfe, 2007). The priority map concept
-has also been used to explain how selection history influences
-attentional allocation (Awh et al., 2012; Failing \& Theeuwes, 2018),
-with the attentional priority signal of reward-related stimulus features
+Koch, 2001; Theeuwes, 2010; Wolfe, 2007). The priority map concept has
+also been used to explain how selection history influences attentional
+allocation (Awh et al., 2012; Failing \& Theeuwes, 2018), with the
+attentional priority signal of reward-related stimulus features
 increasing with repeated stimulus-reward pairings through a process of
-associative learning (M. E. Le Pelley et al., 2016; Pearson et al.,
-2016). Recent formulations of the signal suppression hypothesis have
-suggested that the attentional suppression mechanism may operate in a
-similar way, with the attentional priority of to-be-ignored stimulus
-features being proactively down-weighted with repeated experience
-(Gaspelin \& Luck, 2019). At first glance, the results of the current
-study may seem inconsistent with the idea that reward and suppression
-engage in competition on a common priority map, as the magnitude of the
-VMAC effect did not differ between search conditions, even though the
-feature search condition should have encouraged top-down guidance of
-attention. However, there was an \emph{overall} decrease in the amount
-of capture by both the high- and low-reward distractor in the feature
-search condition (supported by a main effect of search condition, e.g.,
-see Figures \ref{fig:SaccadePlot}B and \ref{fig:SaccadePlot}D). This
-raises the possibility that repeated experience of the physically
-salient stimulus features (i.e., orange and blue colour) allows the
-attentional priority of those features to be uniformly down-weighted by
-the suppression mechanism. In addition, our findings are consistent with
-the idea that repeated experience of pairings between stimulus features
-and reward results in selective up-weighting of the attentional priority
-of the high-reward distractor, such that it overpowers the influence of
+associative learning (Le Pelley et al., 2016; Pearson et al., 2016).
+Recent formulations of the signal suppression hypothesis have suggested
+that the attentional suppression mechanism may operate in a similar way,
+with the attentional priority of to-be-ignored stimulus features being
+proactively down-weighted with repeated experience (Gaspelin \& Luck,
+2019). At first glance, the results of the current study may seem
+inconsistent with the idea that reward and suppression engage in
+competition on a common priority map, as the magnitude of the VMAC
+effect did not differ between search conditions, even though the feature
+search condition should have encouraged top-down guidance of attention.
+However, there was an \emph{overall} decrease in the amount of capture
+by both the high- and low-reward distractor in the feature search
+condition (supported by a main effect of search condition, e.g., see
+Figures \ref{fig:SaccadePlot}B and \ref{fig:SaccadePlot}D). This raises
+the possibility that repeated experience of the physically salient
+stimulus features (i.e., orange and blue colour) allows the attentional
+priority of those features to be uniformly down-weighted by the
+suppression mechanism. In addition, our findings are consistent with the
+idea that repeated experience of pairings between stimulus features and
+reward results in selective up-weighting of the attentional priority of
+the high-reward distractor, such that it overpowers the influence of
 inhibitory suppression and thus captures attention.
@@
 suggested by the signal suppression hypothesis, or potentially the
-result of rapid covert disengagement from the salient stimuli (see J.
+result of rapid covert disengagement from the salient stimuli (see
 Theeuwes, 2010; Zoest et al., 2004 for similar arguments).
@@
 that these biases may be the result of a common mechanism (Albertella et
-al., 2017; Brian A Anderson et al., 2013). This is consistent with the
-idea of incentive salience (Berridge \& Robinson, 1998), where the
-perceptual representation of an otherwise neutral stimulus is modified
-so as to become more salient and attention grabbing to the observer, as
-a result of its association with a desired outcome (e.g., drugs, money).
-The current study suggests that incentive salience has a particularly
+al., 2017; Anderson et al., 2013). This is consistent with the idea of
+incentive salience (Berridge \& Robinson, 1998), where the perceptual
+representation of an otherwise neutral stimulus is modified so as to
+become more salient and attention grabbing to the observer, as a result
+of its association with a desired outcome (e.g., drugs, money). The
+current study suggests that incentive salience has a particularly
 powerful influence on the attentional system, overcoming inhibitory
@@
 drug use. \emph{Drug and Alcohol Dependence}, \emph{175}, 99--105.
-doi:\href{https://doi.org/10.1016/j.drugalcdep.2017.01.041}{10.1016/j.drugalcdep.2017.01.041}
+\url{https://doi.org/10.1016/j.drugalcdep.2017.01.041}
 
@@
 attentional selection. \emph{Annals of the New York Academy of
-Sciences}, \emph{1369}, 24--39.
-doi:\href{https://doi.org/10.1111/nyas.12957}{10.1111/nyas.12957}
+Sciences}, \emph{1369}, 24--39. \url{https://doi.org/10.1111/nyas.12957}
 
@@
 addiction. \emph{Experimental and Clinical Psychopharmacology},
-\emph{21}, 499--506.
-doi:\href{https://doi.org/10.1037/a0034575}{10.1037/a0034575}
+\emph{21}, 499--506. \url{https://doi.org/10.1037/a0034575}
 
@@
 \emph{Trends in Cognitive Sciences}, \emph{16}, 437--443.
-doi:\href{https://doi.org/10.1016/j.tics.2012.06.010}{10.1016/j.tics.2012.06.010}
+\url{https://doi.org/10.1016/j.tics.2012.06.010}
 
@@
 attentional capture. \emph{Perception \& Psychophysics}, \emph{55},
-485--496.
-doi:\href{https://doi.org/10.3758/BF03205306}{10.3758/BF03205306}
+485--496. \url{https://doi.org/10.3758/BF03205306}
 
@@
 \emph{Brain Research Reviews}, \emph{28}, 309--369.
-doi:\href{https://doi.org/10.1016/S0165-0173(98)00019-8}{10.1016/S0165-0173(98)00019-8}
+\url{https://doi.org/10.1016/S0165-0173(98)00019-8}
 
@@
 Vision}, \emph{10}, 433--436.
-doi:\href{https://doi.org/10.1163/156856897X00357}{10.1163/156856897X00357}
+\url{https://doi.org/10.1163/156856897X00357}
 
@@
 \emph{Vision Research}, \emph{36}, 1827--1837.
-doi:\href{https://doi.org/10.1016/0042-6989(95)00294-4}{10.1016/0042-6989(95)00294-4}
+\url{https://doi.org/10.1016/0042-6989(95)00294-4}
 
@@
 Review}, \emph{25}, 514--538.
-doi:\href{https://doi.org/10.3758/s13423-017-1380-y}{10.3758/s13423-017-1380-y}
+\url{https://doi.org/10.3758/s13423-017-1380-y}
 
@@
 reward. \emph{Journal of Neurophysiology}, \emph{114}, 2316--2327.
-doi:\href{https://doi.org/10.1152/jn.00441.2015}{10.1152/jn.00441.2015}
+\url{https://doi.org/10.1152/jn.00441.2015}
 
@@
 behavioral, and biomedical sciences. \emph{Behavior Research Methods},
-\emph{39}, 175--191.
-doi:\href{https://doi.org/10.3758/BF03193146}{10.3758/BF03193146}
+\emph{39}, 175--191. \url{https://doi.org/10.3758/BF03193146}
 
@@
 \emph{Drug and Alcohol Dependence}, \emph{97}, 1--20.
-doi:\href{https://doi.org/10.1016/j.drugalcdep.2008.03.030}{10.1016/j.drugalcdep.2008.03.030}
+\url{https://doi.org/10.1016/j.drugalcdep.2008.03.030}
 
@@
 Performance}, \emph{18}, 1030--1044.
-doi:\href{https://doi.org/10.1037/0096-1523.18.4.1030}{10.1037/0096-1523.18.4.1030}
+\url{https://doi.org/10.1037/0096-1523.18.4.1030}
 
@@
 Psychology: Human Perception and Performance}, \emph{44}, 626--644.
-doi:\href{https://doi.org/10.1037/xhp0000484}{10.1037/xhp0000484}
+\url{https://doi.org/10.1037/xhp0000484}
 
@@
 distraction by salient stimuli. \emph{Trends in Cognitive Sciences},
-\emph{22}, 79--92.
-doi:\href{https://doi.org/10.1016/j.tics.2017.11.001}{10.1016/j.tics.2017.11.001}
+\emph{22}, 79--92. \url{https://doi.org/10.1016/j.tics.2017.11.001}
 
@@
 Psychology}, \emph{29}, 12--18.
-doi:\href{https://doi.org/10.1016/j.copsyc.2018.10.013}{10.1016/j.copsyc.2018.10.013}
+\url{https://doi.org/10.1016/j.copsyc.2018.10.013}
 
@@
 \emph{Psychological Science}, \emph{26}, 1740--1750.
-doi:\href{https://doi.org/10.1177/0956797615597913}{10.1177/0956797615597913}
+\url{https://doi.org/10.1177/0956797615597913}
 
@@
 \emph{Attention, Perception, \& Psychophysics}, \emph{79}, 45--62.
-doi:\href{https://doi.org/10.3758/s13414-016-1209-1}{10.3758/s13414-016-1209-1}
+\url{https://doi.org/10.3758/s13414-016-1209-1}
 
@@
 Performance}, \emph{41}, 86--101.
-doi:\href{https://doi.org/10.1037/xhp0000019}{10.1037/xhp0000019}
+\url{https://doi.org/10.1037/xhp0000019}
 
@@
 Neuroscience}, \emph{30}, 11096--11103.
-doi:\href{https://doi.org/10.1523/JNEUROSCI.1026-10.2010}{10.1523/JNEUROSCI.1026-10.2010}
+\url{https://doi.org/10.1523/JNEUROSCI.1026-10.2010}
 
@@
 only one item at any one time. \emph{Psychological Research}, \emph{73},
-317--326.
-doi:\href{https://doi.org/10.1007/s00426-008-0157-3}{10.1007/s00426-008-0157-3}
+317--326. \url{https://doi.org/10.1007/s00426-008-0157-3}
 
@@
 overtly ignored. \emph{Nature Neuroscience}, \emph{9}, 1071--1076.
-doi:\href{https://doi.org/10.1038/nn1734}{10.1038/nn1734}
+\url{https://doi.org/10.1038/nn1734}
 
@@
 attention. \emph{Nature Reviews Neuroscience}, \emph{2}, 194--203.
-doi:\href{https://doi.org/10.1038/35058500}{10.1038/35058500}
+\url{https://doi.org/10.1038/35058500}
 
@@
 Niehorster, D. (2007). What's new in Psychtoolbox-3? \emph{Perception},
-\emph{36}, S14.
-doi:\href{https://doi.org/10.1068/v070821}{10.1068/v070821}
+\emph{36}, S14. \url{https://doi.org/10.1068/v070821}
 
@@
 integrative review. \emph{Psychological Bulletin}, \emph{142},
-1111--1140.
-doi:\href{https://doi.org/10.1037/bul0000064}{10.1037/bul0000064}
+1111--1140. \url{https://doi.org/10.1037/bul0000064}
 
@@
 Experimental Psychology: General}, \emph{144}, 158--171.
-doi:\href{https://doi.org/10.1037/xge0000037}{10.1037/xge0000037}
+\url{https://doi.org/10.1037/xge0000037}
 
@@
 Bulletin \& Review}, \emph{13}, 132--138.
-doi:\href{https://doi.org/10.3758/BF03193824}{10.3758/BF03193824}
+\url{https://doi.org/10.3758/BF03193824}
 
@@
 features. \emph{Memory \& Cognition}, \emph{22}, 657--672.
-doi:\href{https://doi.org/10.3758/BF03209251}{10.3758/BF03209251}
+\url{https://doi.org/10.3758/BF03209251}
 
@@
 momentary assessment study. \emph{Journal of Consulting and Clinical
-Psychology}, \emph{81}, 1--12.
-doi:\href{https://doi.org/10.1037/a0030754}{10.1037/a0030754}
+Psychology}, \emph{81}, 1--12. \url{https://doi.org/10.1037/a0030754}
 
@@
 heroin relapse following treatment. \emph{Addiction}, \emph{101},
-1306--1312.
-doi:\href{https://doi.org/10.1111/j.1360-0443.2006.01498.x}{10.1111/j.1360-0443.2006.01498.x}
+1306--1312. \url{https://doi.org/10.1111/j.1360-0443.2006.01498.x}
 
@@
 for Psychology}, \emph{4}, 61--64.
-doi:\href{https://doi.org/10.3758/s13414-012-0291-2}{10.3758/s13414-012-0291-2}
+\url{https://doi.org/10.3758/s13414-012-0291-2}
 
@@
 reward-related stimuli. \emph{Visual Cognition}, \emph{23}, 41--66.
-doi:\href{https://doi.org/10.1080/13506285.2014.994252}{10.1080/13506285.2014.994252}
+\url{https://doi.org/10.1080/13506285.2014.994252}
 
@@
 saccade map. \emph{Attention, Perception, \& Psychophysics}, \emph{78},
-2226--2240.
-doi:\href{https://doi.org/10.3758/s13414-016-1135-2}{10.3758/s13414-016-1135-2}
+2226--2240. \url{https://doi.org/10.3758/s13414-016-1135-2}
 
@@
 Transforming numbers into movies. \emph{Spatial Vision}, \emph{10},
-437--442.
-doi:\href{https://doi.org/10.1163/156856897X00366}{10.1163/156856897X00366}
+437--442. \url{https://doi.org/10.1163/156856897X00366}
 
@@
 of distribution statistics. \emph{Psychological Bulletin}, \emph{86},
-446--461.
-doi:\href{https://doi.org/10.1037/0033-2909.86.3.446}{10.1037/0033-2909.86.3.446}
+446--461. \url{https://doi.org/10.1037/0033-2909.86.3.446}
 
@@
 71--78). New York, NY: ACM Press.
-doi:\href{https://doi.org/10.1145/355017.355028}{10.1145/355017.355028}
+\url{https://doi.org/10.1145/355017.355028}
 
@@
 \emph{Perception \& Psychophysics}, \emph{50}, 184--193.
-doi:\href{https://doi.org/10.3758/BF03212219}{10.3758/BF03212219}
+\url{https://doi.org/10.3758/BF03212219}
 
@@
 \emph{Perception \& Psychophysics}, \emph{51}, 599--606.
-doi:\href{https://doi.org/10.3758/BF03211656}{10.3758/BF03211656}
+\url{https://doi.org/10.3758/BF03211656}
 
@@
 \emph{Acta Psychologica}, \emph{135}, 77--99.
-doi:\href{https://doi.org/10.1016/j.actpsy.2010.02.006}{10.1016/j.actpsy.2010.02.006}
+\url{https://doi.org/10.1016/j.actpsy.2010.02.006}
 
@@
 \& Review}, \emph{19}, 871--878.
-doi:\href{https://doi.org/10.3758/s13423-012-0280-4}{10.3758/s13423-012-0280-4}
+\url{https://doi.org/10.3758/s13423-012-0280-4}
 
@@
 cocaine. \emph{Psychopharmacology}, \emph{219}, 909--921.
-doi:\href{https://doi.org/10.1007/s00213-011-2424-z}{10.1007/s00213-011-2424-z}
+\url{https://doi.org/10.1007/s00213-011-2424-z}
 
@@
 Sciences}, \emph{26}, 107--113.
-doi:\href{https://doi.org/10.1016/j.cobeha.2018.12.002}{10.1016/j.cobeha.2018.12.002}
+\url{https://doi.org/10.1016/j.cobeha.2018.12.002}
 
@@
 cognitive systems} (pp. 99--119). Oxford University Press.
-doi:\href{https://doi.org/10.1093/acprof:oso/9780195189193.003.0008}{10.1093/acprof:oso/9780195189193.003.0008}
+\url{https://doi.org/10.1093/acprof:oso/9780195189193.003.0008}
 
@@
 Performance}, \emph{30}, 746--759.
-doi:\href{https://doi.org/10.1037/0096-1523.30.4.749}{10.1037/0096-1523.30.4.749}
+\url{https://doi.org/10.1037/0096-1523.30.4.749}
 

### 2019-04-23 analysis/analysis_report.R

@@ -1,13 +1,13 @@
----
-title: "Analysis Report"
-author: "Daniel Pearson"
-date: "18 April 2019"
-output: html_document
-editor_options: 
-  chunk_output_type: console
----
-
-```{r setup, include=FALSE, echo=FALSE}
+#' ---
+#' title: "Analysis Report"
+#' author: "Daniel Pearson"
+#' date: "18 April 2019"
+#' output: html_document
+#' editor_options: 
+#'   chunk_output_type: console
+#' ---
+#' 
+## ----setup, include=FALSE, echo=FALSE------------------------------------
 knitr::opts_chunk$set(echo = TRUE)
 options(knitr.duplicate.label = 'allow')
 library(tidyverse)
@@ -56,19 +56,19 @@ my_theme <- theme_ipsum_rc(grid = F, axis_title_just = "c", axis_title_size = 14
         legend.text = element_text(size = 14),
         legend.title = element_text(size = 14))
 
-```
 
-# Omission Trial Analysis
-
-```{r Load Behavioural Data, include=FALSE}
+#' 
+#' # Omission Trial Analysis
+#' 
+## ----Load Behavioural Data, include=FALSE--------------------------------
 files <- dir(path = here::here("analysis", "data", "raw_data", "BehavData"), pattern = "*.mat")
 
 filedata <- here::here("analysis", "data", "raw_data", "BehavData", files) %>%
   map(readMat) %>%
   map("DATA")
-```
 
-```{r Tidy Behavioural Data, include = FALSE}
+#' 
+## ----Tidy Behavioural Data, include = FALSE------------------------------
 #This is some messy code that lets us tidy the exptTrialInfo data from the nested .mat struct files
 
 subNums <- filedata %>%
@@ -129,10 +129,10 @@ exptdata <- exptdata %>%
 exptdata <- exptdata %>% 
   mutate(gender = tolower(gender)) %>% 
   mutate(dType = factor(distractType, levels = c(1,2,3), labels = c("High", "Low", "Absent")))
-```
 
-We first removed participants who had poor gaze data (mean proportion of valid gaze samples during the fixation or trial period < .5).
-```{r Remove participants with poor gaze data}
+#' 
+#' We first removed participants who had poor gaze data (mean proportion of valid gaze samples during the fixation or trial period < .5).
+## ----Remove participants with poor gaze data-----------------------------
 propCutoff <- .5
 allTracks <- exptdata %>%
   group_by(sub) %>%
[…]

### 2019-04-23 analysis/paper/analysis_report.R

@@ -1,15 +1,5 @@
----
-title: "Analysis Report"
-author: "Daniel Pearson"
-date: "18 April 2019"
-output: html_document
-editor_options: 
-  chunk_output_type: console
----
-
-```{r setup, include=FALSE, echo=FALSE}
+## ----setup, include=FALSE, echo=FALSE------------------------------------
 knitr::opts_chunk$set(echo = TRUE)
-options(knitr.duplicate.label = 'allow')
 library(tidyverse)
 library(R.matlab)
 library(afex)
@@ -56,19 +46,15 @@ my_theme <- theme_ipsum_rc(grid = F, axis_title_just = "c", axis_title_size = 14
         legend.text = element_text(size = 14),
         legend.title = element_text(size = 14))
 
-```
 
-# Omission Trial Analysis
-
-```{r Load Behavioural Data, include=FALSE}
+## ----Load Behavioural Data, include=FALSE--------------------------------
 files <- dir(path = here::here("analysis", "data", "raw_data", "BehavData"), pattern = "*.mat")
 
 filedata <- here::here("analysis", "data", "raw_data", "BehavData", files) %>%
   map(readMat) %>%
   map("DATA")
-```
 
-```{r Tidy Behavioural Data, include = FALSE}
+## ----Tidy Behavioural Data, include = FALSE------------------------------
 #This is some messy code that lets us tidy the exptTrialInfo data from the nested .mat struct files
 
 subNums <- filedata %>%
@@ -129,10 +115,8 @@ exptdata <- exptdata %>%
 exptdata <- exptdata %>% 
   mutate(gender = tolower(gender)) %>% 
   mutate(dType = factor(distractType, levels = c(1,2,3), labels = c("High", "Low", "Absent")))
-```
 
-We first removed participants who had poor gaze data (mean proportion of valid gaze samples during the fixation or trial period < .5).
-```{r Remove participants with poor gaze data}
+## ----Remove participants with poor gaze data-----------------------------
 propCutoff <- .5
 allTracks <- exptdata %>%
   group_by(sub) %>%
@@ -150,11 +134,8 @@ allTracks_summ <- allTracks %>%
 
 exptdata <- exptdata %>%
  filter(!sub %in% poortracks$sub)
-```
 
-`r length(poortracks)` participants were removed due to having a poor quality eye gaze data.
-
-```{r Remove participants for any other reasons}
[…]

### 2019-04-24 analysis/paper/paper.Rmd
testing travis

@@
 keywords          : "attentional capture, reward, suppression, cognitive control"
-wordcount         : "6656"
+wordcount         : "6787"
 
@@
 classoption       : "man, a4paper, noextraspace, 11pt"
-output            : papaja::apa6_pdf
+output            : papaja::apa6_docx
 nocite: |
@@
 Stimulus presentation was controlled by MATLAB using the Psychophysics Toolbox extensions [@Brainard1997; @Kleiner2007; @Pelli1997].
-Experiment scripts, analysis scripts, and raw data are available at (**OSF**).
 
@@
 In cases where a conclusion is drawn on the basis of a null effect, we report the Bayes factor that corresponds to a Bayesian *t*-test using the default Cauchy prior, conducted using the BayesFactor package [@R-BayesFactor].
+Experiment scripts, raw data, and a reproducible research compendium of analysis scripts [@marwick2018] are available at https://osf.io/yrdzv/.
 

### 2019-04-24 analysis/paper/paper.tex
testing travis

@@
 
-\usepackage{amsthm}
-\newtheorem{theorem}{Theorem}[section]
-\newtheorem{lemma}{Lemma}[section]
-\theoremstyle{definition}
-\newtheorem{definition}{Definition}[section]
-\newtheorem{corollary}{Corollary}[section]
-\newtheorem{proposition}{Proposition}[section]
-\theoremstyle{definition}
-\newtheorem{example}{Example}[section]
-\theoremstyle{definition}
-\newtheorem{exercise}{Exercise}[section]
-\theoremstyle{remark}
-\newtheorem*{remark}{Remark}
-\newtheorem*{solution}{Solution}
 \begin{document}
@@
 using the Psychophysics Toolbox extensions (Brainard, 1997; Kleiner et
-al., 2007; Pelli, 1997). Experiment scripts, analysis scripts, and raw
-data are available at (\textbf{OSF}).
+al., 2007; Pelli, 1997).
 
@@
 
-{\centering \includegraphics[width=0.8\linewidth]{C:/Users/Daniel/Google Drive/Research/vmacfeaturesearch/analysis/figures/Methods_fig}
+{\centering \includegraphics[width=0.8\linewidth]{E:/Users/Daniel/Google Drive/Research/vmacfeaturesearch/analysis/figures/Methods_fig}
 
@@
 \emph{t}-test using the default Cauchy prior, conducted using the
-BayesFactor package (Morey \& Rouder, 2018).
+BayesFactor package (Morey \& Rouder, 2018). Experiment scripts, raw
+data, and a reproducible research compendium of analysis scripts
+(Marwick, Boettiger, \& Mullen, 2018) are available at
+\url{https://osf.io/yrdzv/}.
 
@@
 
-{\centering \includegraphics[width=0.6\linewidth]{C:/Users/Daniel/Google Drive/Research/vmacfeaturesearch/analysis/figures/omission_plot}
+{\centering \includegraphics[width=0.6\linewidth]{E:/Users/Daniel/Google Drive/Research/vmacfeaturesearch/analysis/figures/omission_plot}
 
@@
 
-{\centering \includegraphics[width=0.8\linewidth]{C:/Users/Daniel/Google Drive/Research/vmacfeaturesearch/analysis/figures/saccade_plot}
+{\centering \includegraphics[width=0.8\linewidth]{E:/Users/Daniel/Google Drive/Research/vmacfeaturesearch/analysis/figures/saccade_plot}
 
@@
 
-{\centering \includegraphics[width=0.6\linewidth]{C:/Users/Daniel/Google Drive/Research/vmacfeaturesearch/analysis/figures/capture_plot_by_block}
+{\centering \includegraphics[width=0.6\linewidth]{E:/Users/Daniel/Google Drive/Research/vmacfeaturesearch/analysis/figures/capture_plot_by_block}
 
@@
 
-{\centering \includegraphics[width=0.6\linewidth]{C:/Users/Daniel/Google Drive/Research/vmacfeaturesearch/analysis/figures/vincentized_plot}
+{\centering \includegraphics[width=0.6\linewidth]{E:/Users/Daniel/Google Drive/Research/vmacfeaturesearch/analysis/figures/vincentized_plot}
 
@@
 
+\hypertarget{ref-marwick2018}{}
+Marwick, B., Boettiger, C., \& Mullen, L. (2018). Packaging data
+analytical work reproducibly using R (and friends), e3192v2.
+\url{https://doi.org/10.7287/peerj.preprints.3192v2}
+
 \hypertarget{ref-Morey2008}{}

### 2019-04-24 README.Rmd
small readme update
updated readme

@@
 # Please put your title here to include it in the file below. 
-Title <- "Overt attentional capture by reward-related stimuli overcomes top-down suppression"
+Title <- "Overt attentional capture by reward-related stimuli overcomes inhibitory suppression"
 ```
@@
 # vmacfeaturesearch
+
+[![Travis-CI Build Status](https://travis-ci.org/danielpearson90/vmacfeaturesearch.svg?branch=master)](https://travis-ci.org/danielpearson90/vmacfeaturesearch)
 

### 2019-04-24 analysis/analysis_report.rmd
testing circleci
working locally

@@
 author: "Daniel Pearson"
-date: "11 April 2019"
+date: "18 April 2019"
 output: html_document
@@
 knitr::opts_chunk$set(echo = TRUE)
+options(knitr.duplicate.label = 'allow')
 library(tidyverse)
@@
 
-st_options(bootstrap.css     = FALSE,       # Already part of the theme so no need for it
-           plain.ascii       = FALSE,       # One of the essential settings
-           style             = "rmarkdown", # Idem.
-           dfSummary.silent  = TRUE,        # Suppresses messages about temporary files
-           footnote          = NA,          # Keeping the results minimalistic
-           subtitle.emphasis = FALSE)       # For the vignette theme, this gives
+#st_options(bootstrap.css     = FALSE,       # Already part of the theme so no need for it
+#           plain.ascii       = FALSE,       # One of the essential settings
+#           style             = "rmarkdown", # Idem.
+#           dfSummary.silent  = TRUE,        # Suppresses messages about temporary files
+#           footnote          = NA,          # Keeping the results minimalistic
+#           subtitle.emphasis = FALSE)       # For the vignette theme, this gives
                                             # much better results. Your mileage may vary.
 
-st_css()
+# st_css()
 
@@
 ```
+
+```{r, echo=FALSE, message=FALSE, results='hide', purl=FALSE}
+input  = knitr::current_input()  # filename of input document
+output = paste(tools::file_path_sans_ext(input), 'R', sep = '.')
+knitr::purl(input,output,documentation=2,quiet=T)
+```

### 2019-04-24 analysis/paper/paper.Rmd
working locally

@@
     affiliation   : "1"
-  - name          : "Phillip Cheng"
+  - name          : "Phillip (Xin) Cheng"
     affiliation   : "2"
@@
   - id            : "2"
-    institution   : "Department of Psychology, Macquarie University"
+    institution   : "Department of Cognitive Science, Macquarie University"
 
@@
 classoption       : "man, a4paper, noextraspace, 11pt"
-output            : papaja::apa6_docx
+output            : papaja::apa6_pdf
 nocite: |
@@
 In cases where a conclusion is drawn on the basis of a null effect, we report the Bayes factor that corresponds to a Bayesian *t*-test using the default Cauchy prior, conducted using the BayesFactor package [@R-BayesFactor].
+Bayes
+factors are interpreted in line with the guidelines suggested by @Jeffreys1961.
 Experiment scripts, raw data, and a reproducible research compendium of analysis scripts [@marwick2018] are available at https://osf.io/yrdzv/.

### 2019-04-24 analysis/paper/paper.tex
working locally

@@
             pdftitle={Overt attentional capture by reward-related stimuli overcomes inhibitory suppression},
-            pdfauthor={Daniel Pearson, Poppy Watson, Phillip Cheng, \& Mike E. Le Pelley},
+            pdfauthor={Daniel Pearson, Poppy Watson, Phillip (Xin) Cheng, \& Mike E. Le Pelley},
             pdfkeywords={attentional capture, reward, suppression, cognitive control},
@@
     \author{Daniel Pearson\textsuperscript{1}, Poppy Watson\textsuperscript{1},
-Phillip Cheng\textsuperscript{2}, \& Mike E. Le
+Phillip (Xin) Cheng\textsuperscript{2}, \& Mike E. Le
 Pelley\textsuperscript{1}}
@@
 \vspace{0.5cm}
-\textsuperscript{1} School of Psychology, UNSW Sydney\\\textsuperscript{2} Department of Psychology, Macquarie University}
-\keywords{attentional capture, reward, suppression, cognitive control\newline\indent Word count: 6656}
+\textsuperscript{1} School of Psychology, UNSW Sydney\\\textsuperscript{2} Department of Cognitive Science, Macquarie University}
+\keywords{attentional capture, reward, suppression, cognitive control\newline\indent Word count: 6787}
 \usepackage{csquotes}
@@
 \emph{t}-test using the default Cauchy prior, conducted using the
-BayesFactor package (Morey \& Rouder, 2018). Experiment scripts, raw
-data, and a reproducible research compendium of analysis scripts
-(Marwick, Boettiger, \& Mullen, 2018) are available at
+BayesFactor package (Morey \& Rouder, 2018). Bayes factors are
+interpreted in line with the guidelines suggested by Jeffreys (1961).
+Experiment scripts, raw data, and a reproducible research compendium of
+analysis scripts (Marwick, Boettiger, \& Mullen, 2018) are available at
 \url{https://osf.io/yrdzv/}.
@@
 
+\hypertarget{ref-Jeffreys1961}{}
+Jeffreys, H. (1961). \emph{Theory of probability} (3rd ed.). Oxford, UK:
+Oxford University Press.
+
 \hypertarget{ref-Kleiner2007}{}

### 2019-04-26 README.Rmd
updated with github pat
updated Readme and minor paper changes

@@
 
-> Pearson, D., Watson, P., Cheng, P., Most, S. (2019). _`r Title`_. Name of journal/book, Accessed `r format(Sys.Date(), "%d %b %Y")`. Online at <https://doi.org/xxx/xxx>
+> Pearson, D., Watson, P., Cheng, P., & Le Pelley, M. (2019). _`r Title`_. Name of journal/book, Accessed `r format(Sys.Date(), "%d %b %Y")`. Online at <https://doi.org/xxx/xxx>
 
@@
 
-> Pearson, D., Watson, P., Cheng, P., & Le Pelley, M. (`r format(Sys.Date(), "%Y")`. Investigating attentional suppression of reward-related distractors. Retrieved from <https://osf.io/yrdzv>
+> Pearson, D., Watson, P., Cheng, P., & Le Pelley, M. (`r format(Sys.Date(), "%Y")`). Investigating attentional suppression of reward-related distractors. Retrieved from <https://osf.io/yrdzv>
 
@@
 You can download the compendium as a zip from from this URL: <https://github.com/danielpearson90/vmacfeaturesearch/archive/master.zip>
+
+Once you have downloaded and extracted the compendium, you can open [the project](vmacfeaturesearch.Rproj) with RStudio, and knit [analysis_report.Rmd](analysis/analysis_report.Rmd) to produce a report containing all statistical analyses contained in our preprint.
+You can also knit [paper.Rmd](analysis/paper/paper.Rmd) to produce a reproducible copy of the preprint.
+
+This compendium is still a work in progress, with Docker integration planned for the future.
 

### 2019-04-26 analysis/paper/paper.Rmd
updated Readme and minor paper changes

@@
 For example, when driving towards an intersection, we can selectively attend to a stop sign on a busy street.
-Sometimes, however, we may find that stimuli that are irrelevant to our current task may nevertheless capture our attention in a seemingly automatic and involuntary way (e.g., a flashing alert, or colourful billboard).
+Sometimes, however, we may find that stimuli that are irrelevant to our current task nevertheless capture our attention in a seemingly automatic and involuntary way (e.g., a flashing alert, or colourful billboard).
 Consistent with this framework, an influential view of attentional selection has drawn a distinction between two forms of attentional control: one that is volitional and goal directed (top-down control) and another that is automatic and stimulus driven [@Yantis2000].
@@
 This account is consistent with stimulus-driven theories, in that it proposes that physically salient stimuli have the potential to involuntarily capture attention; however it is also consistent with goal-directed theories in that it proposes that there is some top-down control of the allocation of attention.
-Evidence supporting the signal suppression hypothesis has largely come from the event-related potential (ERP) literature [for review, see @Gaspelin2018a], however recent studies have demonstrated behavioural evidence of suppression in the context of overt attention [i.e., eye-movements: see @Gaspelin2016; @Gaspelin2018b; @Ipata2006] and covert attention [i.e., shifts of attention that are not accompanied by eye-movements: see @Gaspelin2015].
+Evidence supporting the signal suppression hypothesis has largely come from the event-related potential (ERP) literature [for review, see @Gaspelin2018a], however recent studies have demonstrated behavioural evidence of suppression in the context of overt attention [i.e., eye-movements: see @Gaspelin2018b; @Gaspelin2016; @Ipata2006] and covert attention [i.e., shifts of attention that are not accompanied by eye-movements: see @Gaspelin2015].
 
@@
 factors are interpreted in line with the guidelines suggested by @Jeffreys1961.
-Experiment scripts, raw data, and a reproducible research compendium of analysis scripts [@marwick2018] are available at https://osf.io/yrdzv/.
+Experiment scripts, raw data, and a reproducible research compendium of analysis scripts [@R-rrtools] are available at https://osf.io/yrdzv/.
 

### 2019-04-26 analysis/paper/paper.tex
updated Readme and minor paper changes

--- 2019-04-23 analysis/paper/paper.tex
@@
 Sometimes, however, we may find that stimuli that are irrelevant to our
-current task may nevertheless capture our attention in a seemingly
-automatic and involuntary way (e.g., a flashing alert, or colourful
-billboard). Consistent with this framework, an influential view of
-attentional selection has drawn a distinction between two forms of
-attentional control: one that is volitional and goal directed (top-down
-control) and another that is automatic and stimulus driven (Yantis,
-2000). However, exactly how these two processes interact has been the
-subject of extensive debate.
+current task nevertheless capture our attention in a seemingly automatic
+and involuntary way (e.g., a flashing alert, or colourful billboard).
+Consistent with this framework, an influential view of attentional
+selection has drawn a distinction between two forms of attentional
+control: one that is volitional and goal directed (top-down control) and
+another that is automatic and stimulus driven (Yantis, 2000). However,
+exactly how these two processes interact has been the subject of
+extensive debate.
 
@@
 recent studies have demonstrated behavioural evidence of suppression in
-the context of overt attention (Gaspelin \& Luck, 2018a; i.e.,
-eye-movements: see Gaspelin, Leonard, \& Luck, 2017; Ipata, Gee,
-Gottlieb, Bisley, \& Goldberg, 2006) and covert attention (i.e., shifts
-of attention that are not accompanied by eye-movements: see Gaspelin,
+the context of overt attention (i.e., eye-movements: see Gaspelin \&
+Luck, 2018a; Gaspelin, Leonard, \& Luck, 2017; Ipata, Gee, Gottlieb,
+Bisley, \& Goldberg, 2006) and covert attention (i.e., shifts of
+attention that are not accompanied by eye-movements: see Gaspelin,
 Leonard, \& Luck, 2015).
@@
 \emph{t}-test using the default Cauchy prior, conducted using the
-BayesFactor package (Morey \& Rouder, 2018).
+BayesFactor package (Morey \& Rouder, 2018). Bayes factors are
+interpreted in line with the guidelines suggested by Jeffreys (1961).
+Experiment scripts, raw data, and a reproducible research compendium of
+analysis scripts (Marwick, 2019) are available at
+\url{https://osf.io/yrdzv/}.
 
@@
 
+\hypertarget{ref-R-rrtools}{}
+Marwick, B. (2019). \emph{Rrtools: Creates a reproducible research
+compendium}. Retrieved from \url{https://github.com/benmarwick/rrtools}
+
 \hypertarget{ref-Morey2008}{}

### 2019-04-26 README.Rmd
more readme fixes

@@
 
-Once you have downloaded and extracted the compendium, you can open [the project](vmacfeaturesearch.Rproj) with RStudio, and knit [analysis_report.Rmd](analysis/analysis_report.Rmd) to produce a report containing all statistical analyses contained in our preprint.
+Once you have downloaded and extracted the compendium, you can open [the project](vmacfeaturesearch.Rproj) with RStudio, and knit [analysis_report.rmd](analysis/analysis_report.rmd) to produce a report containing all statistical analyses contained in our preprint.
 You can also knit [paper.Rmd](analysis/paper/paper.Rmd) to produce a reproducible copy of the preprint.

### 2019-04-26 analysis/paper/paper.Rmd
references fixed

@@
 For the *feature search* condition, the non-target stimuli were randomly selected without replacement from a set of two squares and two hexagons (such that one of the non-targets was always a shape singleton), and were never rendered as the alternative target shape (Figure \@ref(fig:methodFig)C).
-The target and two of the non-targets were always rendered in grey (CIE $x$,$y$ chromaticity coordinates of .327/.400).
-On the majority of trials, one of the non-target shapes (the *singleton distractor*) was rendered in either orange or blue (CIE $x$,$y$ coordinates .492/.445 and .192/.216, respectively).
+The target and two of the non-targets were always rendered in grey (CIE $x$, $y$ chromaticity coordinates of .327/.400).
+On the majority of trials, one of the non-target shapes (the *singleton distractor*) was rendered in either orange or blue (CIE $x$, $y$ coordinates .492/.445 and .192/.216, respectively).
 On the remaining trials, all shapes were rendered in grey such that there was no singleton distractor.

### 2019-04-26 analysis/paper/paper.tex
references fixed

@@
 Theeuwes, 2015; Pearson et al., 2016), a pattern similar to that
-observed in capture by physical salience (e.g., Zoest, Donk, \&
+observed in capture by physical salience (e.g., van Zoest, Donk, \&
 Theeuwes, 2004). Similarly, electrophysiological studies have shown that
@@
 target shape (Figure \ref{fig:methodFig}C). The target and two of the
-non-targets were always rendered in grey (CIE \(x\),\(y\) chromaticity
+non-targets were always rendered in grey (CIE \(x\), \(y\) chromaticity
 coordinates of .327/.400). On the majority of trials, one of the
 non-target shapes (the \emph{singleton distractor}) was rendered in
-either orange or blue (CIE \(x\),\(y\) coordinates .492/.445 and
+either orange or blue (CIE \(x\), \(y\) coordinates .492/.445 and
 .192/.216, respectively). On the remaining trials, all shapes were
@@
 result of rapid covert disengagement from the salient stimuli (see
-Theeuwes, 2010; Zoest et al., 2004 for similar arguments).
+Theeuwes, 2010; van Zoest et al., 2004 for similar arguments).
 
@@
 
+\hypertarget{ref-VanZoest2004}{}
+van Zoest, W., Donk, M., \& Theeuwes, J. (2004). The role of
+stimulus-driven and goal-driven control in saccadic visual selection.
+\emph{Journal of Experimental Psychology: Human Perception and
+Performance}, \emph{30}, 746--759.
+\url{https://doi.org/10.1037/0096-1523.30.4.749}
+
 \hypertarget{ref-Vatterott2012}{}
@@
 
-\hypertarget{ref-VanZoest2004}{}
-Zoest, W. van, Donk, M., \& Theeuwes, J. (2004). The role of
-stimulus-driven and goal-driven control in saccadic visual selection.
-\emph{Journal of Experimental Psychology: Human Perception and
-Performance}, \emph{30}, 746--759.
-\url{https://doi.org/10.1037/0096-1523.30.4.749}
-
 \endgroup

### 2019-04-26 analysis/analysis_report (1).R
deleted duplicate files

@@ -1,986 +1,0 @@
-#' ---
-#' title: "Analysis Report"
-#' author: "Daniel Pearson"
-#' date: "18 April 2019"
-#' output: html_document
-#' editor_options: 
-#'   chunk_output_type: console
-#' ---
-#' 
-## ----setup, include=FALSE, echo=FALSE------------------------------------
-knitr::opts_chunk$set(echo = TRUE)
-options(knitr.duplicate.label = 'allow')
-library(tidyverse)
-library(R.matlab)
-library(afex)
-library(emmeans)
-library(here)
-library(patchwork)
-library(cowplot)
-library(BayesFactor)
-library(hrbrthemes)
-library(ggsignif)
-library(summarytools)
-
-st_options(bootstrap.css     = FALSE,       # Already part of the theme so no need for it
-           plain.ascii       = FALSE,       # One of the essential settings
-           style             = "rmarkdown", # Idem.
-           dfSummary.silent  = TRUE,        # Suppresses messages about temporary files
-           footnote          = NA,          # Keeping the results minimalistic
-           subtitle.emphasis = FALSE)       # For the vignette theme, this gives
-                                            # much better results. Your mileage may vary.
-
-st_css()
-
-library(knitr)
-opts_chunk$set(comment=NA, prompt=FALSE, cache=FALSE, echo=TRUE, results='asis')
-
-source(here::here("R", "dz_calculator.r"))
-source(here::here("R", "vmac_pal.R"))
-source(here::here("R", "summarySEwithin2.r"))
-
-vmacCols <- vmac_pal()
-my_theme <- theme_ipsum_rc(grid = F, axis_title_just = "c", axis_title_size = 14, axis_text_size = 12, strip_text_size = 14, plot_title_size = 14, subtitle_size = 14, ticks = T) +
-  theme(legend.position = "none", 
-        plot.margin = margin(.5,1,.5,1,"cm"),
-        axis.line = element_line(colour = "black", size = .5),
-        axis.ticks.x = element_blank(),
-        axis.ticks.y = element_line(colour = "black", size = .5),
-        #aspect.ratio = 1.1,
-        plot.tag = element_text(size = 20, family = font_rc),
-        axis.title = element_text(margin = margin(12,1,1,1, unit = "cm")),
-        axis.text.x = element_text(margin = margin(t = 4, unit = 'pt'), colour = 'black'),
[…]

### 2019-04-26 analysis/paper/analysis_report (1).R

@@ -1,909 +1,0 @@
-## ----setup, include=FALSE, echo=FALSE------------------------------------
-knitr::opts_chunk$set(echo = TRUE)
-library(tidyverse)
-library(R.matlab)
-library(afex)
-library(emmeans)
-library(here)
-library(patchwork)
-library(cowplot)
-library(BayesFactor)
-library(hrbrthemes)
-library(ggsignif)
-library(summarytools)
-
-st_options(bootstrap.css     = FALSE,       # Already part of the theme so no need for it
-           plain.ascii       = FALSE,       # One of the essential settings
-           style             = "rmarkdown", # Idem.
-           dfSummary.silent  = TRUE,        # Suppresses messages about temporary files
-           footnote          = NA,          # Keeping the results minimalistic
-           subtitle.emphasis = FALSE)       # For the vignette theme, this gives
-                                            # much better results. Your mileage may vary.
-
-st_css()
-
-library(knitr)
-opts_chunk$set(comment=NA, prompt=FALSE, cache=FALSE, echo=TRUE, results='asis')
-
-source(here::here("R", "dz_calculator.r"))
-source(here::here("R", "vmac_pal.R"))
-source(here::here("R", "summarySEwithin2.r"))
-
-vmacCols <- vmac_pal()
-my_theme <- theme_ipsum_rc(grid = F, axis_title_just = "c", axis_title_size = 14, axis_text_size = 12, strip_text_size = 14, plot_title_size = 14, subtitle_size = 14, ticks = T) +
-  theme(legend.position = "none", 
-        plot.margin = margin(.5,1,.5,1,"cm"),
-        axis.line = element_line(colour = "black", size = .5),
-        axis.ticks.x = element_blank(),
-        axis.ticks.y = element_line(colour = "black", size = .5),
-        #aspect.ratio = 1.1,
-        plot.tag = element_text(size = 20, family = font_rc),
-        axis.title = element_text(margin = margin(12,1,1,1, unit = "cm")),
-        axis.text.x = element_text(margin = margin(t = 4, unit = 'pt'), colour = 'black'),
-        axis.text.y = element_text(margin = margin(r = 4, unit = 'pt'), colour = 'black'),
-        axis.title.x = element_text(margin = margin(t = 8, unit = 'pt')),
-        axis.title.y = element_text(margin = margin(r = 8, unit = 'pt')),
[…]

### 2019-04-29 analysis/paper/paper.Rmd
fixed typos in paper and readme

@@
 By contrast, if participants were *less* likely to make a saccade to the singleton distractor than one of the nonsingleton non-targets, this would suggest that attention to the singleton distractor had been suppressed.
-In @Gaspelin2016\'s Experiment 1, participants were encouraged to adopt a strategy of searching for the "odd-one-out" in the display [i.e, *singleton-search mode*; @Bacon1994], by having the target be randomly either a circle amongst diamonds or a diamond amongst circles on each trial (see Figure \@ref(fig:methodFig)A for an example from the current study).
+In @Gaspelin2016\'s Experiment 1, participants were encouraged to adopt a strategy of searching for the "odd-one-out" in the display [i.e., *singleton-search mode*; @Bacon1994], by having the target be randomly either a circle amongst diamonds or a diamond amongst circles on each trial (see Figure \@ref(fig:methodFig)A for an example from the current study).
 Under these conditions, both stimulus-driven [@Theeuwes1992] and goal-directed [@Bacon1994] accounts of attentional selection would predict capture, as the template that participants use to locate the target (i.e., any singleton) is broad enough to include the singleton distractor.
@@
 The identity of the non-target shapes varied by search condition.
-For the *singleton search* condition, the non-target stimuli were all rendered as the alternative target shape (i.e., if the target was a diamond, all of the non-targets were circles; Figure \@ref(fig:methodFig)B).
-For the *feature search* condition, the non-target stimuli were randomly selected without replacement from a set of two squares and two hexagons (such that one of the non-targets was always a shape singleton), and were never rendered as the alternative target shape (Figure \@ref(fig:methodFig)C).
+For the *singleton search* condition, the non-target stimuli were all rendered as the alternative target shape (i.e., if the target was a diamond, all of the non-targets were circles; Figure \@ref(fig:methodFig)A).
+For the *feature search* condition, the non-target stimuli were randomly selected without replacement from a set of two squares and two hexagons (such that one of the non-targets was always a shape singleton), and were never rendered as the alternative target shape (Figure \@ref(fig:methodFig)B).
 The target and two of the non-targets were always rendered in grey (CIE $x$, $y$ chromaticity coordinates of .327/.400).
@@
 For half of the participants in each condition, orange was the high-reward colour and blue was the low-reward colour; these colour-reward relationships were reversed for the remaining participants.
-There were three types of trial: (1) *high-reward trials*, in which the singleton distractor was rendered in the high-reward colour and 500 points were available for a rapid respnse (see below); (2) *low-reward trials*, in which the singleton distractor was rendered in the low-reward colour and 10 points were available; and (3) *distractor-absent trials*, in which all non-targets were rendered in grey and 10 points were available.
+There were three types of trial: (1) *high-reward trials*, in which the singleton distractor was rendered in the high-reward colour and 500 points were available for a rapid response (see below); (2) *low-reward trials*, in which the singleton distractor was rendered in the low-reward colour and 10 points were available; and (3) *distractor-absent trials*, in which all non-targets were rendered in grey and 10 points were available.
 The experiment comprised 8 blocks of 60 trials each, for a total of 480 experimental trials.
@@
 In order to quantify support for the null hypothesis that the influence of reward on attentional capture did not vary depending on participants' target template, we conducted a Bayesian *t*-test to compare the magnitude of the VMAC effect across the two search conditions.
-This revealed a Bayes Factor of `r apa_print(vmac_condition_bayes)$statistic`, indicating moderate support for the null hypothesis of no difference in the size of the VMAC effect under singleton search and fearure search conditions.
+This revealed a Bayes Factor of `r apa_print(vmac_condition_bayes)$statistic`, indicating moderate support for the null hypothesis of no difference in the size of the VMAC effect under singleton search and feature search conditions.
 
@@
 By contrast, in the current experiment we observed overt attentional capture in the fastest quartile of saccade latencies, with the suppression effect emerging on trials with slower saccades.
-Methodological differences between Gaspelin et al.'s  [-@Gaspelin2016] experiment and the current study may be responsible for this discrepancy.
-For example, the availability of reward on low-reward trials may have influenced capture, either by somewhat increasing the attentional priority of the stimulus feature associated with low reward, or by otherwise influencing participants' motivation to respond quickly.
-Alternatively, the discrepancy in findings may reflect our use of two potential targets (circle and diamond) in the feature search condition, as opposed to the same target on all trials in Gaseplin et al.'s procedure.
+Methodological differences between Gaspelin et al.\'s  [-@Gaspelin2016] experiment and the current study may be responsible for this discrepancy.
+For example, the availability of reward on low-reward trials may have influenced capture, either by somewhat increasing the attentional priority of the stimulus feature associated with low reward, or by otherwise influencing participants\' motivation to respond quickly.
+Alternatively, the discrepancy in findings may reflect our use of two potential targets (circle and diamond) in the feature search condition, as opposed to the same target on all trials in Gaspelin et al.'s procedure.
 Having two possible targets could reduce the influence of trial-by-trial upweighting of target features [@Maljkovic1994], but may also result in less effective feature search [e.g., @Houtkamp2009; but see @Grubert2015].
@@
 (A) Participants in the singleton search condition experienced search displays where the target was a unique shape (either a circle amongst diamonds or diamond amongst circles).
-(B) Participants in the feature search condition experienced search displays where the target was either a circle or diamond shape presented amongst a set of heterogenous shapes.
+(B) Participants in the feature search condition experienced search displays where the target was either a circle or diamond shape presented amongst a set of heterogeneous shapes.
 On most trials, one of the non-target shapes was rendered in either orange or blue so as to be a colour singleton distractor, leaving two other nonsingleton non-targets in the display.

### 2019-04-29 analysis/paper/paper.tex
fixed typos in paper and readme

@@
 Experiment 1, participants were encouraged to adopt a strategy of
-searching for the \enquote{odd-one-out} in the display (i.e,
+searching for the \enquote{odd-one-out} in the display (i.e.,
 \emph{singleton-search mode}; Bacon \& Egeth, 1994), by having the
@@
 diamond, all of the non-targets were circles; Figure
-\ref{fig:methodFig}B). For the \emph{feature search} condition, the
+\ref{fig:methodFig}A). For the \emph{feature search} condition, the
 non-target stimuli were randomly selected without replacement from a set
@@
 always a shape singleton), and were never rendered as the alternative
-target shape (Figure \ref{fig:methodFig}C). The target and two of the
+target shape (Figure \ref{fig:methodFig}B). The target and two of the
 non-targets were always rendered in grey (CIE \(x\), \(y\) chromaticity
@@
 experienced search displays where the target was either a circle or
-diamond shape presented amongst a set of heterogenous shapes. On most
+diamond shape presented amongst a set of heterogeneous shapes. On most
 trials, one of the non-target shapes was rendered in either orange or
@@
 rendered in the high-reward colour and 500 points were available for a
-rapid respnse (see below); (2) \emph{low-reward trials}, in which the
+rapid response (see below); (2) \emph{low-reward trials}, in which the
 singleton distractor was rendered in the low-reward colour and 10 points
@@
 moderate support for the null hypothesis of no difference in the size of
-the VMAC effect under singleton search and fearure search conditions.
+the VMAC effect under singleton search and feature search conditions.
 
@@
 suppression effect emerging on trials with slower saccades.
-Methodological differences between Gaspelin et al.\enquote{s (2017)
-experiment and the current study may be responsible for this
-discrepancy. For example, the availability of reward on low-reward
-trials may have influenced capture, either by somewhat increasing the
-attentional priority of the stimulus feature associated with low reward,
-or by otherwise influencing participants} motivation to respond quickly.
+Methodological differences between Gaspelin et al.'s (2017) experiment
+and the current study may be responsible for this discrepancy. For
+example, the availability of reward on low-reward trials may have
+influenced capture, either by somewhat increasing the attentional
+priority of the stimulus feature associated with low reward, or by
+otherwise influencing participants' motivation to respond quickly.
 Alternatively, the discrepancy in findings may reflect our use of two
 potential targets (circle and diamond) in the feature search condition,
-as opposed to the same target on all trials in Gaseplin et al.'s
+as opposed to the same target on all trials in Gaspelin et al.'s
 procedure. Having two possible targets could reduce the influence of

### 2019-05-14 README.Rmd
fixed typos in paper and readme
binder integration 2

@@
 
-[![Travis-CI Build Status](https://travis-ci.org/danielpearson90/vmacfeaturesearch.svg?branch=master)](https://travis-ci.org/danielpearson90/vmacfeaturesearch)
+[![Travis-CI Build Status](https://travis-ci.org/danielpearson90/vmacfeaturesearch.svg?branch=master)](https://travis-ci.org/danielpearson90/vmacfeaturesearch) [![Binder](https://mybinder.org/badge_logo.svg)](https://mybinder.org/v2/gh/danielpearson90/vmacfeaturesearch/master/?urlpath=rstudio)
 
@@
 
-> Pearson, D., Watson, P., Cheng, P., & Le Pelley, M. (2019). _`r Title`_. Name of journal/book, Accessed `r format(Sys.Date(), "%d %b %Y")`. Online at <https://doi.org/xxx/xxx>
+> Pearson, D., Watson, P., Cheng, P., & Le Pelley, M. (2019). _`r Title`_. PsyArXiv, Accessed `r format(Sys.Date(), "%d %b %Y")`. Online at <https://doi.org/10.31234/osf.io/db9hg>
 

### 2019-05-14 README.Rmd
binder working

@@
 
-This repository contains data files that have been derived from the raw eye-tracker data.
-The raw eye-gaze files are very large and so are not stored here.
-They can be found at: <https://osf.io/yrdzv/>.
-
 Our pre-print is online here:
@@
 
-### How to download or install
+### Contents
+- [:file_folder: analysis](/analysis): Contains analysis report in R Markdown format, as well as R script format.
+- [:file_folder: analysis/paper](/analysis/paper): R markdown source document for the manuscript.
+- [:file_folder: analysis/data](/analysis/data): Data files that have been dericed from the raw eye-tracker data.
+The raw eye-gaze files are very large and so are not stored here.
+They can be found at: <https://osf.io/yrdzv/>.
+- [:file_folder: analysis/figures](/analysis/figures): Figures generated in the analysis.
 
-You can download the compendium as a zip from from this URL: <https://github.com/danielpearson90/vmacfeaturesearch/archive/master.zip>
+### Reproducibility
+This repository is organized as a reproducible research compendium. 
+Click the ![Binder](https://mybinder.org/badge_logo.svg) button above to explore in an interactive RStudio session (this takes approximate 15-20 mins to build).
+Binder uses [rocker-project.org](https://rocker-project.org) Docker images to ensure a consistent and reproducible computational environment.
+These Docker images can also be used locally.
 
-Once you have downloaded and extracted the compendium, you can open [the project](vmacfeaturesearch.Rproj) with RStudio, and knit [analysis_report.rmd](analysis/analysis_report.rmd) to produce a report containing all statistical analyses contained in our preprint.
-You can also knit [paper.Rmd](analysis/paper/paper.Rmd) to produce a reproducible copy of the preprint.
+To explore the code locally, clone or download this repository into RStudio or your perferred environment and install the compendium by running `devtools::install(dep=TRUE)`.
 
-This compendium is still a work in progress, with Docker integration planned for the future.
+This compendium is checked by Travis-CI continuous integration.  Click the ![Build Status](https://travis-ci.org/cboettig/noise-phenomena.svg?branch=master) button above for details.
 

### 2019-10-28 analysis/analysis_report.rmd
revised submission

@@
 
+afex_options(emmeans_model = "multivariate")
+
 #st_options(bootstrap.css     = FALSE,       # Already part of the theme so no need for it
@@
 source(here::here("R", "dz_calculator.r"))
+source(here::here("R", "ds_calculator.r"))
 source(here::here("R", "vmac_pal.R"))
 source(here::here("R", "summarySEwithin2.r"))
+source(here::here("R", "remove_lz.R"))
 
@@
 
+awaredata <- filedata %>%
+  map(27)  %>% 
+  modify(as.data.frame)
+
+index_removed_awaredata <- which(sapply(awaredata, nrow) < 4)
+
+awaredata <- awaredata[-index_removed_awaredata]
+
+awaredata <- Map(cbind, awaredata, sub = subNums[-index_removed_awaredata]) %>% 
+  bind_rows()
+
+colnames(awaredata)[1:5] <- c("question_type", "trial_counter", "colour", "clicked_button", "confidence_rating")
+
+awaredata$question_type <- factor(awaredata$question_type, labels = c("to_target", "to_distractor"))
+awaredata$colour <- factor(awaredata$colour, labels = c("high", "low"))
+
 counterbals <- filedata %>%
@@
   mutate(dType = factor(distractType, levels = c(1,2,3), labels = c("High", "Low", "Absent")))
+```
+
+```{r Prepare data for repetition priming analysis}
+exptdata <- exptdata %>%
+  mutate(singleton_present = case_when(distractType == 1 | distractType == 2 ~ 1,
+                                       TRUE ~ 0)) %>% 
+  mutate(singleton_repetition = case_when(singleton_present == lag(singleton_present) & distractType != 3 ~ 1,
+                                          TRUE ~ 0))
+
 ```
@@
 
-save_plot(here::here("analysis", "figures", "omission_plot.png"), omissionPlot_ms, ncol = 1, nrow = 2, type = "cairo", base_aspect_ratio = 1.1, dpi = 300)
+# save_plot(here::here("analysis", "figures", "omission_plot.png"), omissionPlot_ms, ncol = 1, nrow = 2, type = "cairo", base_aspect_ratio = 1.1, dpi = 300)
 
@@
 feature_physicalsalience_omissions.es
+
+```
+
+Exploratory analyses following reviews:
+```{r}
+absent_singleton_vs_feature.ttest <- t.test(feature_absent_omissions, singleton_absent_omissions, var.equal = T)
+absent_singleton_vs_feature.ttest
+absent_singleton_vs_feature.es <- ds_calculator(feature_absent_omissions, singleton_absent_omissions)
+absent_singleton_vs_feature.es
+
+low_singleton_vs_feature.ttest <- t.test(singleton_low_omissions,feature_low_omissions, var.equal = T)
+low_singleton_vs_feature.ttest
+low_singleton_vs_feature.es <- ds_calculator(singleton_low_omissions, feature_low_omissions)
 ```
@@
 
-saccadePlot_ms_row1 <- saccadePlot_singleton + captureBarPlot_singleton + plot_spacer() + plot_layout(nrow = 1, widths = c(2,1,.1))
+saccadePlot_ms_row1 <- saccadePlot_singleton + captureBarPlot_singleton + plot_spacer() + plot_layout(nrow = 1, widths = c(2.2,1,.1))
 
@@
 
-save_plot(here("analysis", "figures", "saccade_plot.png"), saccadePlot_ms, ncol = 2, nrow = 2, type = "cairo", base_aspect_ratio = .9, dpi = 300)
+ # save_plot(here("analysis", "figures", "saccade_plot.png"), saccadePlot_ms, ncol = 2.2, nrow = 2, type = "cairo", base_aspect_ratio = .9, dpi = 300)
 
@@
 Singleton_low.ttest
+
+Singleton_low.ttestBF_onesided <- captureData_means_byparticipant %>%
+  ungroup() %>%
+  filter(condition == "Singleton Search") %>%
+  filter(dType == "Low") %>%
+  select(Capture) %>%
+  pull() %>%
+  ttestBF(nullInterval = c(0,Inf))
+
+Singleton_low.ttestBF_directional <- Singleton_low.ttestBF_onesided[1]/Singleton_low.ttestBF_onesided[2]
+
+Singleton_low.ttestBF_onesided_2 <- captureData_means_byparticipant %>%
+  ungroup() %>%
+  filter(condition == "Singleton Search") %>%
+  filter(dType == "Low") %>%
+  select(Capture) %>%
+  pull() %>%
+  ttestBF(nullInterval = c(0,-Inf))
+
+1/Singleton_low.ttestBF_onesided_2
 
@@
 
-save_plot(here("analysis", "figures","capture_plot_by_block.png"), capturePlot_byblock_vert, ncol = 1, nrow = 2, type = "cairo", base_aspect_ratio = 1.1, dpi = 300)
+# save_plot(here("analysis", "figures","capture_plot_by_block.png"), capturePlot_byblock_vert, ncol = 1, nrow = 2, type = "cairo", base_aspect_ratio = 1.1, dpi = 300)
 
@@
 
-save_plot(here("analysis","figures","vincentized_plot.png"), vincentizedPlot_ms, ncol = 1, nrow = 2, type = "cairo", base_aspect_ratio = 1.1, dpi = 300)
+# save_plot(here("analysis","figures","vincentized_plot.png"), vincentizedPlot_ms, ncol = 1.2, nrow = 2, type = "cairo", base_aspect_ratio = 1.1, dpi = 300)
 
@@
 
+## Repetition priming effects
+
+```{r Repetition Priming Plots}
+
+saccadeData_means_bysingletonrepetition <- 
+  saccadedata %>%
+  mutate(sub = as.factor(sub)) %>%
+  filter(dType != "Absent") %>% 
+  group_by(sub, condition, singleton_repetition, dType) %>%
+  summarise(saccade_to_target = mean(saccade_to_target, na.rm = T),
+            saccade_to_singleton = mean(saccade_to_singleton, na.rm = T),
+            saccade_to_nonsingleton = mean(saccade_to_nonsingleton, na.rm = T)/mean(num_nonsingletons, na.rm = T),
+            num_nonsingletons = mean(num_nonsingletons, na.rm = T),
+            capture = saccade_to_singleton - saccade_to_nonsingleton,
+            n = n())
+
+# capture_singleton_repetition.ANOVA <- aov_car(capture ~ singleton_repetition*condition*dType + Error(sub/singleton_repetition*dType), data = saccadeData_means_bysingletonrepetition, anova_table = list(es="pes"))
+
+#knitr::kable(nice(capture_singleton_repetition.ANOVA))
+
+capturemeans_bysingletonrepetition <- summarySEwithin2(data = saccadeData_means_bysingletonrepetition, measurevar = "capture", betweenvars = "condition", withinvars = c("singleton_repetition"), idvar = "sub", na.rm = T) %>%
+  select(-ends_with("Normed"))
+
+capturemeans_bysingletonrepetition_individual <- saccadeData_means_bysingletonrepetition %>% 
+  ungroup() %>% 
+  group_by(sub, condition, singleton_repetition) %>% 
+  select(capture) %>% 
+  summarize(m_capture = mean(capture))
+
+capturemeans_bysingletonrepetition_individual$singleton_repetition <- factor(capturemeans_bysingletonrepetition_individual$singleton_repetition)
+
+average_singleton_repetition <- saccadeData_means_bysingletonrepetition %>% 
+  ungroup() %>% 
+  group_by(singleton_repetition) %>% 
+  summarise(mean_n = mean(n))
+
+singleton_repetition_singleton_search_plot <- ggplot(data = filter(capturemeans_bysingletonrepetition, condition == "Singleton Search"), aes(x = singleton_repetition, y = capture, group = 1)) +
+  geom_path() +
+  geom_path(data = filter(capturemeans_bysingletonrepetition_individual, condition == "Singleton Search"), aes(group = sub, x = singleton_repetition, y = m_capture), alpha = .1) + 
+  geom_errorbar(aes(ymax = capture + se, ymin = capture - se), width = .1) +
+  geom_point(size = 3) + 
+  geom_hline(yintercept = 0, linetype = "dashed") +
+  geom_signif(comparisons = list(c(1,2)), annotations = "***", y_position = .3, colour = "black", tip_length = 0) +
+  labs(y = "Capture Score", x= "", tag = "A", title = "Singleton Search") +
+  #lims(y = c(-.2, .3)) +
+  scale_color_manual(values = vmacCols) +
+  scale_x_discrete(labels = c("No-repeat", "Repeat")) +
+  scale_y_continuous(labels = scales::percent_format(accuracy = 1), limits = c(-.2,.45), breaks = seq(-.2, .45, .1), expand = c(0,0)) +
+  my_theme +
+  theme(strip.text = element_text(face = "bold"))
+
+singleton_repetition_feature_search_plot <- ggplot(data = filter(capturemeans_bysingletonrepetition, condition == "Feature Search"), aes(x = singleton_repetition, y = capture, group = 1)) +
+  geom_path() +
+  geom_path(data = filter(capturemeans_bysingletonrepetition_individual, condition == "Feature Search"), aes(group = sub, x = singleton_repetition, y = m_capture), alpha = .1) + 
+  geom_errorbar(aes(ymax = capture + se, ymin = capture - se), width = .1) +
+  geom_point(size = 3) + 
+  geom_hline(yintercept = 0, linetype = "dashed") +
+  # geom_signif(comparisons = list(c(1,2)), annotations = "***", y_position = .3, colour = "black", tip_length = 0) +
+  labs(y = "Capture Score", x= "", tag = "B", title = "Feature Search") +
+  #lims(y = c(-.2, .3)) +
+  scale_color_manual(values = vmacCols) +
+  scale_x_discrete(labels = c("No-repeat", "Repeat")) +
+  scale_y_continuous(labels = scales::percent_format(accuracy = 1), limits = c(-.2,.45), breaks = seq(-.2, .45, .1), expand = c(0,0)) +
+  my_theme +
+  theme(strip.text = element_text(face = "bold"))
+
+singleton_repetition_plot_horz <- plot_grid(singleton_repetition_singleton_search_plot, singleton_repetition_feature_search_plot, align = 'vh')
+# singleton_repetition_plot_horz <- ggdraw(add_sub(singleton_repetition_plot_horz, "Singleton Repetition", fontfamily = font_rc, vpadding=grid::unit(0,"lines"), y = 6, x = 0.55, vjust = 4.5))
+
+# plot_grid(singleton_repetition_plot_horz, title, ncol = 1, rel_heights = c(1,.1))
+
+# save_plot(here::here("analysis", "figures", "singleton_repetition_priming.png"), singleton_repetition_plot_horz, type = "cairo", ncol = 1.3, nrow = 1)
+
+```
+
+```{r Repetition Priming Statistics} 
+capture_singleton_repetition.ANOVA <- aov_car(capture ~ singleton_repetition*condition*dType + Error(sub/singleton_repetition*dType), data = saccadeData_means_bysingletonrepetition, anova_table = list(es="pes"))
+
+knitr::kable(nice(capture_singleton_repetition.ANOVA))
+
+saccadeData_means_bysingletonrepetition_no_dtype <- 
+  saccadedata %>%
+  mutate(sub = as.factor(sub)) %>%
+  filter(dType != "Absent") %>% 
+  group_by(sub, condition, singleton_repetition) %>%
+  summarise(saccade_to_target = mean(saccade_to_target, na.rm = T),
+            saccade_to_singleton = mean(saccade_to_singleton, na.rm = T),
+            saccade_to_nonsingleton = mean(saccade_to_nonsingleton, na.rm = T)/mean(num_nonsingletons, na.rm = T),
+            num_nonsingletons = mean(num_nonsingletons, na.rm = T),
+            capture = saccade_to_singleton - saccade_to_nonsingleton,
+            n = n())
+
+capture_singleton_repetition_no_dtype.ANOVA <- aov_car(capture ~ singleton_repetition*condition + Error(sub/singleton_repetition), data = saccadeData_means_bysingletonrepetition_no_dtype, anova_table = list(es="pes"))
+
+singleton_search_no_repeat <- saccadeData_means_bysingletonrepetition_no_dtype %>% 
+  filter(condition == "Singleton Search", singleton_repetition == 0) %>% 
+  pull(capture)
+
+singleton_search_repeat <- saccadeData_means_bysingletonrepetition_no_dtype %>% 
+  filter(condition == "Singleton Search", singleton_repetition == 1) %>% 
+  pull(capture)
+
+singleton_search_singleton_repetition.ttest <- saccadeData_means_bysingletonrepetition_no_dtype %>% 
+  filter(condition == "Singleton Search") %>% 
+  t.test(formula = capture ~ singleton_repetition, data = ., paired = T)
+
+singleton_search_singleton_repetition.es <- dz_calculator(singleton_search_repeat, singleton_search_no_repeat)
+
+feature_search_no_repeat <- saccadeData_means_bysingletonrepetition_no_dtype %>% 
+  filter(condition == "Feature Search", singleton_repetition == 0) %>% 
+  pull(capture)
+
+feature_search_repeat <- saccadeData_means_bysingletonrepetition_no_dtype %>% 
+  filter(condition == "Feature Search", singleton_repetition == 1) %>% 
+  pull(capture)
+
+feature_search_singleton_repetition.ttest <- t.test(x = feature_search_repeat, y = feature_search_no_repeat, paired = T)
+
+feature_search_singleton_repetition.es <- dz_calculator(feature_search_repeat, feature_search_no_repeat)
+
+feature_search_singleton_repetition.BF <- ttestBF(x = feature_search_repeat, y = feature_search_no_repeat, paired = T)
+
+```
+
+Summarising these findings: there is an effect of singleton repetition (where capture is reduced following a trial in which a singleton of any identity was presented) for singleton-search mode, but not feature search mode.
+
+```{r Contingency belief score data prep}
+awaredata <- awaredata %>%
+  mutate(accuracy = case_when(colour == "high" & clicked_button == 3 & question_type == "to_target" ~ 1,
+                              colour == "low" & clicked_button == 2 & question_type == "to_target" ~ 1,
+                              question_type == "to_distractor" & clicked_button == 1 ~ 1,
+                              TRUE ~ 0)) %>%
+  mutate(belief_score = case_when(accuracy == 1 ~ confidence_rating,
+                                  TRUE ~ -confidence_rating))
+
+captureData_means_byparticipant$sub_num <- as.numeric(as.character(captureData_means_byparticipant$sub))
+
+awareness_scores <- right_join(awaredata, captureData_means_byparticipant, by = c("sub" = "sub_num")) %>%
+  filter(question_type == "to_distractor")
+
+awareness_scores_totarget <- right_join(awaredata, captureData_means_byparticipant, by = c("sub" = "sub_num")) %>%
+  filter(question_type == "to_target")
+
+```
+
+```{r Reward contingency belief data}
+high_reward_awareness.cor <- awareness_scores_totarget %>% 
+  filter(dType == "High", colour == "high") %>% 
+  cor.test(~ Capture + belief_score, data = .)
+
+high_reward_contingency_plot <- awareness_scores_totarget %>%
+  filter(dType == "High", colour == "high") %>%
+  ggplot(aes(x = belief_score, y = Capture)) +
+         geom_point(aes(shape = condition), alpha = .5, size = 3) +
+  geom_smooth(method = "lm", se = FALSE, colour = "black", size = .5) +
+  scale_y_continuous(labels = scales::percent_format(accuracy=1), limits = c(-.25, .75)) +
+  scale_shape_manual(values = c(20,4))+
+  labs(x = "Reward contingency belief score", subtitle = "High reward") +
+  annotate(x = -5, y = .70, label=paste0("r(62) = ", remove_lz(high_reward_awareness.cor$estimate, 3)), geom = "text", size = 5, family = font_rc, hjust = 0) +
+  my_theme +
+  guides(shape = guide_legend(title = "Condition", override.aes = list(alpha = 1))) +
+  theme(axis.ticks.x = element_line(),
+        legend.position = "bottom")
+
+contingency_legend <- get_legend(high_reward_contingency_plot)
+
+high_reward_contingency_plot <- high_reward_contingency_plot +
+  theme(legend.position = "none")
+
+low_reward_awareness.cor <- awareness_scores_totarget %>% 
+  filter(dType == "Low", colour == "low") %>% 
+  cor.test(~ Capture + belief_score, data = .)
+
+low_reward_contingency_plot <- awareness_scores_totarget %>%
+  filter(dType == "Low", colour == "low") %>%
+  ggplot(aes(x = belief_score, y = Capture)) +
+         geom_point(aes(shape = condition), alpha = .5, size = 3) +
+  geom_smooth(method = "lm", se = FALSE, colour = "black", size = .5) +
+  scale_y_continuous(labels = scales::percent_format(accuracy=1), limits = c(-.25, .75)) +
+  scale_shape_manual(values = c(20,4))+
+  labs(x = "Reward contingency belief score", subtitle = "Low reward") +
+  annotate(x = -5, y = .70, label=paste0("r(62) = ", remove_lz(low_reward_awareness.cor$estimate, 3)), geom = "text", size = 5, family = font_rc, hjust = 0) +
+  my_theme +
+  theme(axis.ticks.x = element_line())
+
+reward_contingency_plots <- plot_grid(high_reward_contingency_plot, low_reward_contingency_plot)
+
+reward_contingency_plots_legend <- plot_grid(reward_contingency_plots, contingency_legend, rel_heights = c(1,.1), nrow = 2)
+
+# save_plot(here::here("analysis", "figures", "reward_contingency_plot.png"), reward_contingency_plots_legend, ncol = 1.4, nrow = 1.1, type = "cairo")
+
+# Count people who reported correct colour--reward relationships for each distractor type:
+reward_awareness <- awareness_scores_totarget %>%
+    group_by(dType,colour) %>%
+    count(accuracy) %>%
+  mutate(accuracy = case_when(accuracy == 0 ~ "correct",
+                              TRUE ~ "incorrect")) %>% 
+    pivot_wider(names_from = accuracy, values_from = n) %>% 
+  mutate(total = correct + incorrect) %>% 
+  filter(dType == "High") %>% 
+  ungroup() %>% 
+  select(-dType)
+
+```
+
+```{r Omission contingency belief data}
+
+# Test for significant correlation b/w awareness test for omission contingency with high-val colour and capture by high-val colour
+
+high_omission_awareness.cor <- awareness_scores %>%
+  filter(question_type == "to_distractor", dType == "High", colour == "high") %>%
+  cor.test(~ Capture + belief_score, data = .)
+
+high_omission_contingency_plot <- awareness_scores %>%
+  filter(dType == "High", colour == "high") %>%
+  ggplot(aes(x = belief_score, y = Capture)) +
+         geom_point(aes(shape = condition), alpha = .5, size = 3) +
+  geom_smooth(method = "lm", se = FALSE, colour = "black", size = .5) +
+  scale_y_continuous(labels = scales::percent_format(accuracy=1), limits = c(-.25, .75)) +
+  scale_shape_manual(values = c(20,4))+
+  labs(x = "Omission contingency belief score", subtitle = "High reward") +
+  annotate(x = -5, y = .70, label=paste0("r(62) = ", remove_lz(high_omission_awareness.cor$estimate, 3), "***"), geom = "text", size = 5, family = font_rc, hjust = 0) +
+  my_theme +
+  theme(axis.ticks.x = element_line())
+
+# Test for significant correlation b/w awareness test for omission contingency with low-val colour and capture by low-val colour
+
+low_omission_awareness.cor <- awareness_scores %>%
+  filter(question_type == "to_distractor", dType == "Low", colour == "low") %>%
+  cor.test(~ Capture + belief_score, data = .)
+
+low_omission_contingency_plot <- awareness_scores %>%
+  filter(dType == "Low", colour == "low") %>%
+  ggplot(aes(x = belief_score, y = Capture)) +
+         geom_point(aes(shape = condition), alpha = .5, size = 3) +
+  geom_smooth(method = "lm", se = FALSE, linetype = "solid", colour = "black", size = .5) +
+  scale_y_continuous(labels = scales::percent_format(accuracy=1), limits = c(-.25, .75)) +
+  scale_shape_manual(values = c(20,4))+
+  labs(x = "Omission contingency belief score", subtitle = "Low reward") +
+  annotate(x = -5, y = .70, label=paste0("r(62) = ", remove_lz(low_omission_awareness.cor$estimate, 3)), geom = "text", size = 5, family = font_rc, hjust = 0) +
+  # facet_grid(~dType) +
+  my_theme +
+  theme(axis.ticks.x = element_line())
+
+omission_contingency_plots <- plot_grid(high_omission_contingency_plot, low_omission_contingency_plot)
+
+omission_contingency_plots_legend <- plot_grid(omission_contingency_plots, contingency_legend, rel_heights = c(1,.1), nrow = 2)
+
+# save_plot(here::here("analysis", "figures", "omission_contingency_plot.png"), omission_contingency_plots_legend, ncol = 1.4, nrow = 1.1, type = "cairo")
+
+omission_awareness <- awareness_scores %>%
+    group_by(dType,colour) %>%
+    count(accuracy) %>%
+  mutate(accuracy = case_when(accuracy == 0 ~ "correct",
+                              TRUE ~ "incorrect")) %>% 
+    pivot_wider(names_from = accuracy, values_from = n) %>% 
+  mutate(total = correct + incorrect) %>% 
+  filter(dType == "High") %>% 
+  ungroup() %>% 
+  select(-dType)
+
+```
+
 ```{r, echo=FALSE, message=FALSE, results='hide', purl=FALSE}

### 2019-10-28 analysis/paper/paper.Rmd
revised submission

@@
   - name          : "Daniel Pearson"
-    affiliation   : "1"
+    affiliation   : "1,2"
     corresponding : yes    # Define only one corresponding author
-    address       : "School of Psychology, University of New South Wales, UNSW Sydney NSW 2052, Australia"
-    email         : "d.pearson@unsw.edu.au"
+    address       : "Institute of Cognitive Neuroscience, University College London, Gower Street, London WC1E 6BT, UK"
+    email         : "daniel.pearson@ucl.ac.uk"
   - name          : "Poppy Watson"
-    affiliation   : "1"
+    affiliation   : "2"
   - name          : "Phillip (Xin) Cheng"
+    affiliation   : "3"
+  - name          : "Mike E. Le Pelley"
     affiliation   : "2"
-  - name          : "Mike E. Le Pelley"
-    affiliation   : "1"
 
@@
   - id            : "1"
+    institution   : "Institute of Cognitive Neuroscience, University College London"
+  - id            : "2"
     institution   : "School of Psychology, UNSW Sydney"
-  - id            : "2"
+  - id            : "3"
     institution   : "Department of Cognitive Science, Macquarie University"
@@
 However, recent findings have suggested that attention to salient-but-irrelevant stimuli can be suppressed when observers use a specific target template to guide their search (i.e., feature search).
-Increasingly, evidence suggests that attentional selection is influenced by factors other than the physical salience of a stimulus and the observer’s goals.
+A separate line of research has indicated that attentional selection is influenced by factors other than the physical salience of a stimulus and the observer’s goals.
 For instance, pairing a stimulus with reward has been shown to increase the extent to which it captures attention and gaze (as though it has become more physically salient), even when such capture has negative consequences for the observer.
-We investigated whether capture by reward can be suppressed in the same way as capture by physical salience using eye-tracking with a rewarded visual search task.
+Here we used eye-tracking with a rewarded visual search task to investigate whether capture by reward can be suppressed in the same way as capture by physical salience.
 When participants were encouraged to use feature search, attention to a distractor paired with relatively small reward was suppressed.
-By contrast, attention was captured by a distractor paired with large reward, even when such capture resulted in the loss of large reward.
-These findings suggest that reward-related stimuli are given special priority to the visual attention system and have implications for our understanding of real-world biases to reward-related stimuli, such as those seen in addiction.
+However, under the same conditions attention was captured by a distractor paired with large reward, even when such capture resulted in reward omission.
+These findings suggest that reward-related stimuli are given special priority within the visual attention system over and above physically-salient stimuli, and have implications for our understanding of real-world biases to reward-related stimuli, such as those seen in addiction.
 
 keywords          : "attentional capture, reward, suppression, cognitive control"
-wordcount         : "6787"
+wordcount         : "8515"
 
@@
 By contrast, if participants were *less* likely to make a saccade to the singleton distractor than one of the nonsingleton non-targets, this would suggest that attention to the singleton distractor had been suppressed.
-In @Gaspelin2016\'s Experiment 1, participants were encouraged to adopt a strategy of searching for the "odd-one-out" in the display [i.e., *singleton-search mode*; @Bacon1994], by having the target be randomly either a circle amongst diamonds or a diamond amongst circles on each trial (see Figure \@ref(fig:methodFig)A for an example from the current study).
+In Gaspelin et al.'s Experiment 1, participants were encouraged to adopt a strategy of searching for the "odd-one-out" in the display [i.e., *singleton-search mode*; @Bacon1994], by having the target be randomly either a circle amongst diamonds or a diamond amongst circles on each trial (see Figure \@ref(fig:methodFig)A for an example from the current study).
 Under these conditions, both stimulus-driven [@Theeuwes1992] and goal-directed [@Bacon1994] accounts of attentional selection would predict capture, as the template that participants use to locate the target (i.e., any singleton) is broad enough to include the singleton distractor.
@@
 In Experiment 2, participants were instead encouraged to adopt a more specific target template [i.e., *feature-search mode*; @Bacon1994], by consistently mapping the target identity to one shape (e.g., search for a circle on every trial), and having a heterogeneous set of shapes act as the non-targets (see Figure \@ref(fig:methodFig)B).
-This manipulation makes searching for any singleton a highly inefficient strategy, as there are multiple singleton nontargets in the display (e.g., a circle, a square, a triangle, and a red shape).
+This manipulation makes searching for any singleton a highly inefficient strategy, as there are multiple singleton non-targets in the display (e.g., a circle, a square, a triangle, and a red shape).
 Thus, participants should be encouraged to search for the specific features that define the target (i.e., the "circleness" of the circle).
@@
 ## The role of selection history in guiding attention
-Up to this point we have discussed the set of influences on attentional control as a dichotomy: goal-directed versus stimulus-driven.
+Up to this point we have discussed the set of influences on attentional control as either goal-directed or stimulus-driven.
 However, a growing literature has questioned this framework, pointing to demonstrations of attentional selection biases that fall outside this dichotomy [@Awh2012; @LePelleya; @Failing2018].
@@
 [-@LePelley2015b; see also @Pearson2015].
-In a variant of the additional singleton task, participants were more likely to make a saccade towards a colour-singleton distractor signalling the availability of high reward (e.g., 10$\text{\textcent{}}$) than a singleton distractor signalling low reward (1$\text{\textcent{}}$), even though looking at the reward-signalling singletons was counterproductive, as it resulted in the omission of the reward that would otherwise have been delivered.
+In a variant of the additional singleton task, participants were more likely to make a saccade towards a colour-singleton distractor signalling the availability of high reward (e.g., 10¢) than a singleton distractor signalling low reward (1¢), even though looking at the reward-signalling singletons was counterproductive, as it resulted in the omission of the reward that would otherwise have been delivered.
 That is, participants were more likely to have their attention and gaze captured by a distractor signalling high reward, even though this led to the omission of more high rewards.
@@
 For example, eye-tracking studies have demonstrated that VMAC is largest for the most rapidly generated saccades, and diminishes with increasing saccade latency [@Pearson2016; @Failing2015], a pattern similar to that observed in capture by physical salience [e.g., @VanZoest2004].
-Similarly, electrophysiological studies have shown that reward affects ERP components thought to index low-level perceptual activity [@Hickey2010].
-This is consistent with the idea of *incentive salience* [@Berridge1998], wherein a reward-related stimulus becomes more salient and attention grabbing to the observer through a change in its perceptual representation.
+Similarly, neuroimaging and electrophysiological studies have shown that the influence of reward arises early on in visual processing, with reward effects observed as early as low-level visual cortex [e.g., @MacLean2015; @Serences2008; @Serences2010].
+Considered together, these findings suggest that the attentional priority of a reward-related stimulus is increased (at least in part) through the augmentation of its stimulus-driven perceptual activity, akin to increasing its *incentive salience* [@Berridge1998].
 This raises the question, if associating a stimulus with reward increases its perceptual priority as though it has become more physically salient, can this priority signal be suppressed by the inhibitory control process proposed by the signal suppression hypothesis?
 That is, can incentive salience be suppressed in the same way as physical salience?
+This question formed the focus of the current study.
 Aside from the theoretical importance of this question, it may also have important clinical implications.
-Recent evidence suggests that the processes underlying VMAC are closely related to the attentional biases towards drug-related stimuli observed in addiction [@Albertella2017a; @Anderson2013; for review see @Field2008], which can promote relapse in recovering addicts [@Marissen2006; @Waters2012; @Marhe2013].
+Recent evidence suggests that the processes underlying VMAC are closely related to the attentional biases towards drug-related stimuli observed in addiction [@Albertella2017a; @Albertella2019; @Albertella2019a; @Anderson2013; for review see @Field2008], which can promote relapse in recovering addicts [@Marissen2006; @Waters2012; @Marhe2013].
 Thus it is important to know whether cognitive control processes can be used to overcome the influence of reward on attention when such capture is counterproductive and contrary to our goals.
@@
 All stimuli were presented on a black background.
-The fixation display consisted of a white cross (0.5$^\circ$ visual angle), presented in the centre of the screen and surrounded by a white circle (diameter 3.0$^\circ$).
-The search display consisted of four filled shapes (size 1.6$^\circ$ $\times$ 1.6$^\circ$) presented above, below, left and right of screen centre (eccentricity 4.5$^\circ$).
+The fixation display consisted of a white cross ($0.5^\circ$ visual angle), presented in the centre of the screen and surrounded by a white circle (diameter $3.0^\circ$).
+The search display consisted of four filled shapes (size $1.6^\circ \times 1.6^\circ$) presented above, below, left and right of screen centre (eccentricity $4.5^\circ$).
 One of the shapes was designated as the target, and the other three shapes were designated non-targets.
@@
 The feedback display showed the points earned on the current trial.
-If the response time (RT) exceeded the soft-timeout threshold (see below), the message "Too slow" appeared below the reward feedback.
+If the response time (RT) exceeded 1000 ms, the message "Too slow" appeared below the reward feedback.
 
@@
 On high-reward and low-reward trials, the location of the singleton distractor was randomly selected from the three remaining locations.
-A small, circular region of interest (ROI) with diameter 1.7$^\circ$ visual angle was defined around the centre of the target, with a larger ROI (diameter 2.6$^\circ$) defined around the singleton distractor.
+A small, circular region of interest (ROI) with diameter $1.7^\circ$ visual angle was defined around the centre of the target, with a larger ROI (diameter $2.6^\circ$) defined around the singleton distractor.
 A response was registered when the participant had accumulated 100 ms of gaze dwell time within the target ROI.
@@
 Any gaze falling within the ROI around this (non-salient) stimulus triggered a reward omission in the same way as on trials with a singleton distractor.
-Responses with RTs that were slower than the soft-timeout threshold (1000 ms) were also not rewarded.
+Responses with RTs that were slower than 1000 ms were also not rewarded.
 
@@
 Those in the singleton search condition were instructed to move their eyes to the "unique shape" on each trial, whereas those in the feature search condition were instructed to move their eyes to the "circle or diamond".
-Participants were also informed about the relationships between distractor colour and reward availability (e.g., that if an orange shape was present in the display they could 500 points, and if a blue shape was present they could win 10 points); they were not informed that looking at the reward-associated distractor would cancel the reward for the current trial.
-The instructions stated that they would earn 0 points if their RT was slower than the soft-timeout threshold, and that their reward also depended on how accurately they moved their eyes to the target.
+Participants were also informed about the relationships between distractor colour and reward availability (e.g., that if an orange shape was present in the display they could win 500 points, and if a blue shape was present they could win 10 points); they were not informed that looking at the reward-associated distractor would cancel the reward for the current trial [previous research suggests that whether or not participants are explicitly informed of this has no influence on the magnitude of the VMAC effect that is observed: @Pearson2015].
+The instructions stated that participants would earn 0 points if their RT was slower than 1000 ms, and that their reward also depended on how accurately they moved their eyes to the target.
 Participants were told that they could earn between 7 and 15 AUD for good performance, but no specific information about the conversion rate from points to AUD was provided.
@@
 
+Consistent with previous VMAC protocols [@LePelley2015b; @Pearson2015; @Pearson2016], participants completed a brief questionnaire after finishing the visual search task, to assess their knowledge of the colour--reward contingencies, and of the omission contingency (i.e., that looking at the coloured distractor caused omission of reward).
+Participants were presented with an orange and blue circle, in random order, and for each were asked to indicate whether they would earn 0 points, 10 points, or 500 points when the display contained a circle of that colour and they (1) moved their eyes quickly and accurately to the target, or (2) looked at the coloured shape before looking at the diamond.
+As this study was primarily concerned with the role of non-volitional attentional control processes in attentional suppression of reward-related stimuli [cf.
+@Gaspelin2018a], we did not have an explicit hypothesis to motivate our analysis of these questionnaire data.
+However, in the interest of completeness we present an exploratory analysis of these data in supplemental materials.
+
 ## Data analysis
-In line with previous VMAC protocols [e.g., @LePelley2015b; @Pearson2016], data from the first two experimental trials, and the first two trials after each break were discarded.
+In line with previous protocols [e.g., @LePelley2015b; @Pearson2016], data from the first two experimental trials, and the first two trials after each break were discarded.
 Hard timeouts (`r op(hardtimeouts$perc[hardtimeouts$timeout == 1], 1)`\% of all trials) were also discarded.
@@
 Saccades were detected in the raw gaze data (sampled at 300 Hz) using a velocity-threshold identification algorithm [@Salvucci2000].
-Saccade latency was measured as the duration from onset of the search display to the point at which eye-movement velocity exceeded 40$^\circ$/s.
-Following previous protocols [@Pearson2016], we excluded trials with anticipatory saccades (saccade latency <80 ms; `r op(totalSaccadeTrialsDiscarded$prop_anticipatory,1)`\% of all trials), trials in which no gaze was recorded within 100 pixels (5.1$^\circ$) of the fixation point within the first 80 ms (`r op(totalSaccadeTrialsDiscarded$prop_outside_fix, 1)`\% of trials), and trials in which there was insufficient gaze data to detect a saccade (`r op(totalSaccadeTrialsDiscarded$prop_bad_data, 1)`\% of trials).
+Saccade latency was measured as the duration from onset of the search display to the point at which eye-movement velocity exceeded $40^\circ$/s.
+Following previous protocols [@Pearson2016], we excluded trials with anticipatory saccades (saccade latency <80 ms; `r op(totalSaccadeTrialsDiscarded$prop_anticipatory,1)`\% of all trials), trials in which no gaze was recorded within 100 pixels ($5.1^\circ$) of the fixation point within the first 80 ms (`r op(totalSaccadeTrialsDiscarded$prop_outside_fix, 1)`\% of trials), and trials in which there was insufficient gaze data to detect a saccade (`r op(totalSaccadeTrialsDiscarded$prop_bad_data, 1)`\% of trials).
 To classify the direction of the first saccade on each trial, the angular deviation between the endpoint of the saccade and each stimulus location was calculated.
-The saccade was defined as going in the direction of a stimulus if the angular deviation was less than $30^\circ$ to the left or right of that stimulus.
+The saccade was defined as going in the direction of a stimulus if the angular deviation was less than $30^\circ$ clockwise or anticlockwise from the centre of that stimulus.
 
-There were two primary dependent measures: (1) the percentage of reward omissions---that is, trials on which participants looked at the singleton distractor (or nonsingleton distractor randomly assigned to act as the "singleton distractor" location: see Design) and hence reward was cancelled---for high-reward, low-reward, and distractor-absent trials, and (2) the percentage of first saccades directed towards the singleton distractor versus the average nonsingleton distractor (that is, the mean across the two nonsingleton distractors present in each search display; see Figure \@ref(fig:methodFig)), on high-reward and low-reward trials.
+There were two primary dependent measures: (1) the percentage of reward omissions---that is, trials on which participants looked at the singleton distractor (or nonsingleton non-target randomly assigned to act as the "singleton distractor" location; see Design) and hence reward was cancelled---for high-reward, low-reward, and distractor-absent trials, and (2) the percentage of first saccades directed towards the singleton distractor versus the average nonsingleton distractor---that is, the mean across the two nonsingleton non-targets present in each search display; see Figure \@ref(fig:methodFig)---on high-reward and low-reward trials.
 
 For the analysis of reward omissions, we were particularly interested in two contrasts.
-First, the comparison between the high-reward and low-reward trials allowed us to examine the effect of reward on attention, since both displays contained a physically salient colour-singleton distractor, with the only difference being the magnitude of reward that the distractor signalled.
-Second, the comparison between the low-reward and distractor-absent trials allowed us to examine the effect of physical salience on attention, since these different trial types differed in whether the display contained a colour-singleton distractor, but had the same reward magnitude available (10 points).
+First, the comparison between the high-reward and low-reward trials allowed us to examine the effect of reward on attention, since both displays contained a physically salient colour-singleton distractor that provided information about the reward available on that trial, with the only difference being the *magnitude* of reward that the distractor signalled.
+Second, the comparison between the low-reward and distractor-absent trials allowed us to examine the effect of physical salience on attention, since these trial types differed in whether the display contained a colour-singleton distractor, but had the same reward magnitude available (10 points).
 These contrasts were compared for the singleton search and feature search conditions using 2 $\times$ 2 mixed ANOVAs.
 
-For the analysis of saccade direction, we were primarily interested in the difference between the percentage of trials on which first saccades were directed towards the singleton distractor and the mean of both nonsingleton distractors across high- and low-reward trials.
+For the analysis of saccade direction, we were primarily interested in the difference between the percentage of trials on which first saccades were directed towards the singleton distractor and the mean of both nonsingleton non-targets across high- and low-reward trials.
 These data were converted into a *capture score* by subtracting the percentage of trials where the first saccade was directed towards the average nonsingleton from the percentage of trials where the first saccade was directed towards the singleton.
@@
 In cases where a conclusion is drawn on the basis of a null effect, we report the Bayes factor that corresponds to a Bayesian *t*-test using the default Cauchy prior, conducted using the BayesFactor package [@R-BayesFactor].
-Bayes
-factors are interpreted in line with the guidelines suggested by @Jeffreys1961.
-Experiment scripts, raw data, and a reproducible research compendium of analysis scripts [@R-rrtools] are available at https://osf.io/yrdzv/.
+Bayes factors are interpreted in line with the guidelines suggested by @Jeffreys1961.
+Experiment scripts (including verbatim task instructions), raw data, and a reproducible research compendium of analysis scripts [@R-rrtools] are available at https://osf.io/yrdzv/.
 
@@
 Critically, this main effect was qualified by a significant trial type $\times$ search condition interaction, `r apa_print.afex_aov(omissions_salience.ANOVA, mse = F, es = "pes")$full_result$condition_dType`, indicating that the effect of physical salience on overt attentional capture differed across search conditions.
-Paired-samples *t*-tests revealed that participants in the singleton search condition triggered significantly more reward omissions on trials that contained a colour-singleton distractor than those that did not, `r apa_print(singleton_physicalsalience_omissions.ttest)$statistic`, $d_z=$ `r singleton_physicalsalience_omissions.es`, suggesting that overt attention was captured by the physically salient singleton.
-In contrast, participants in the feature search condition triggered fewer reward omissions on trials containing a colour-singleton distractor than trials with no coloured singleton, `r apa_print(feature_physicalsalience_omissions.ttest)$statistic`, $d_z=$ `r feature_physicalsalience_omissions.es`, suggesting that overt attention to the singleton distractor was suppressed under conditions promoting feature search, consistent with previous findings [@Gaspelin2016].
+Paired-samples *t*-tests revealed that participants in the singleton search condition triggered significantly more reward omissions on trials that contained a colour-singleton distractor than on trials without a singleton distractor, `r apa_print(singleton_physicalsalience_omissions.ttest)$statistic`, $d_z=$ `r singleton_physicalsalience_omissions.es`, suggesting that overt attention was captured by the physically salient singleton.
+By contrast, participants in the feature search condition triggered fewer reward omissions on trials containing a colour-singleton distractor than trials with no coloured singleton, `r apa_print(feature_physicalsalience_omissions.ttest)$statistic`, $d_z=$ `r feature_physicalsalience_omissions.es`, suggesting that overt attention to the singleton distractor was suppressed under conditions promoting feature search, consistent with previous findings [@Gaspelin2016].
+
+Orthogonal contrasts used independent *t*-tests to compare the rate of reward omissions between search conditions across each trial type.
+On low-reward trials, there was no significant difference between the singleton search and feature search groups in the rate of reward omissions, `r apa_print(low_singleton_vs_feature.ttest)$statistic`, $d_s=$ `r low_singleton_vs_feature.es`.
+However, on distractor-absent trials participants in the feature search condition triggered significantly more reward omissions (i.e., they were more likely to look at the non-target that had been randomly selected to act as the 'distractor' location) than those in the singleton search condition, `r apa_print(absent_singleton_vs_feature.ttest)$statistic`, $d_s=$ `r absent_singleton_vs_feature.es`.
+
+These analyses suggest that the critical trial type $\times$ search condition interaction was primarily driven by a difference in performance on distractor-absent trials, presumably because it was harder to differentiate the target from non-targets in the feature search condition [@Theeuwes2004], meaning participants were more likely to erroneously fixate non-targets on distractor-absent trials.
+The more important finding for current purposes is that participants in the feature search group were significantly *less* likely to look at a physically salient distractor (when one was present in the search display), than a random non-target (when there was no salient distractor in the display), which suggests that feature search allows participants to exert some control over the extent to which their gaze is directed to physically salient distractors---consistent with previous evidence [@Gaspelin2016; @Gaspelin2019a; @Gaspelin2018b].
 
@@
 ## First Saccade Direction
-Figure \@ref(fig:SaccadePlot) shows the percentage of first saccades directed towards each stimulus type (i.e., the target[^2], average nonsingleton distractor, and singleton distractor) on high- and low-reward trials for the singleton search (Figure \@ref(fig:SaccadePlot)A) and feature search (Figure \@ref(fig:SaccadePlot)C) conditions; Figures \@ref(fig:SaccadePlot)B and \@ref(fig:SaccadePlot)D show capture scores (difference in percentage of first saccades directed towards singleton versus average nonsingleton distractor) for the singleton search and feature search conditions, respectively.
+The analyses of reward omissions in the previous section measure how likely participants were to look at the singleton across trial types in absolute terms (did they look at the singleton or not?).
+Our subsequent analyses focused on the direction of participants’ first saccade on each trial, which measures how likely participants were to look at the singleton on a particular trial type *relative to other shapes in the display*.
+Figure \@ref(fig:SaccadePlot) shows the percentage of first saccades directed towards each stimulus type (i.e., the target[^2], average nonsingleton non-target, and singleton distractor) on high- and low-reward trials for the singleton search (Figure \@ref(fig:SaccadePlot)A) and feature search (Figure \@ref(fig:SaccadePlot)C) conditions; Figures \@ref(fig:SaccadePlot)B and \@ref(fig:SaccadePlot)D show capture scores (difference in percentage of first saccades directed towards singleton versus average nonsingleton non-target) for the singleton search and feature search conditions, respectively.
 ANOVA analysis of capture scores revealed a significant main effect of trial type (high-reward vs low-reward), `r apa_print.afex_aov(capture.ANOVA, mse = F, es = "pes")$full_result$dType`, with the singleton capturing attention more often on high-reward trials than low-reward trials; once again demonstrating a VMAC effect.
 A main effect of search condition (singleton search vs feature search), `r apa_print.afex_aov(capture.ANOVA, mse = F, es = "pes")$full_result$condition`, indicated that both the high-reward and low-reward singleton captured attention more often, on average, in the singleton search condition than the feature search condition.
-Importantly, the trial type $\times$ search condition interaction was non-significant, `r apa_print.afex_aov(capture.ANOVA, mse = F, es = "pes")$full_result$condition_dType`, with a corresponding Bayes factor of `r apa_print(capture_bayes)$statistic` indicating moderate support for the null hypothesis that search condition had no effect on the magnitude of the VMAC effect on first saccade direction.
+Importantly, the trial type $\times$ search condition interaction was non-significant, `r apa_print.afex_aov(capture.ANOVA, mse = F, es = "pes")$full_result$condition_dType`, with a corresponding Bayes factor of `r apa_print(capture_bayes)$statistic` indicating moderate support for the null hypothesis that search condition had no effect on the magnitude of the VMAC effect.
 
 [^2]: Note that the comparison of interest in determining whether a stimulus captured attention, or was suppressed, is the percentage of first saccades to the singleton vs.
-the average nonsingleton distractor.
-Thus, while we have included the percentage of first saccades to the target in Figure \@ref(fig:SaccadePlot) for the sake of completeness, we have not included these data in our analyses.
+the average nonsingleton non-target Thus, while we have included the percentage of first saccades to the target in Figure \@ref(fig:SaccadePlot) for the sake of completeness, we have not included these data in our analyses.
 
-Next we tested whether overt attention to each distractor type was captured or suppressed in each search condition.
-Planned one-sample *t*-tests showed that capture scores were significantly greater than zero (indicating that overt attention was captured by the high-reward singleton) under conditions promoting singleton search, `r apa_print(Singleton_high.ttest)$statistic`, $d_z=$ `r Singleton_high.es`, as well as feature search, `r apa_print(Feature_high.ttest)$statistic`, $d_z=$ `r Feature_high.es`.
-For the low-reward distractor, there was a non-significant numerical trend towards capture in the singleton search condition, `r apa_print(Singleton_low.ttest)$statistic`, $d_z=$ `r Singleton_low.es`.
-In contrast, for the feature search condition, capture score was significantly below zero, `r apa_print(Feature_low.ttest)$statistic`, $d_z=$ `r Feature_low.es`, indicating that overt attention to the low-reward singleton was suppressed.
-Thus, in line with previous findings [@Gaspelin2016], our data suggest that overt attention to physically salient singletons can be suppressed when participants are encouraged to adopt a specific target template.
-However, singletons that have been associated with high reward capture overt attention, regardless of participants' target template and despite such capture being directly counterproductive to earning reward.
+Next we tested whether overt attention to the physically salient (low-reward) distractor was captured (capture score > 0) or suppressed (capture score < 0) in each search condition.
+A planned one-sample *t*-test indicated that participants in the feature search condition demonstrated capture scores that were significantly below zero, `r apa_print(Feature_low.ttest)$statistic`, $d_z=$ `r Feature_low.es`, suggesting that participants were able to suppress their overt attention to the physically salient distractor, consistent with the predictions of the signal suppression hypothesis (see Introduction) and with previous findings [@Gaspelin2016; @Gaspelin2019a; @Gaspelin2018b].
+By contrast, in the singleton search condition, the mean capture score on low-reward trials was numerically but not significantly greater than zero, `r apa_print(Singleton_low.ttest)$statistic`, $d_z=$ `r Singleton_low.es`.
+Bayesian analysis revealed that the data were anectodally in favour of the null hypothesis (capture score = 0) over the alternative hypothesis of capture by the low-reward distractor (capture score > 0), `r apa_print(Singleton_low.ttestBF_onesided[1])$statistic`, and moderate support for the null hypothesis relative to the alternative hypothesis of suppression (capture score < 0), `r apa_print(Singleton_low.ttestBF_onesided_2[1])$statistic`.
+There was also moderate evidence in favour of capture versus suppression, `r apa_print(Singleton_low.ttestBF_directional)$statistic`.
+In sum then, data from the singleton search condition are somewhat equivocal in determining whether or not the low-reward distractor captured attention.
+However, these data are inconsistent with the hypothesis that attention to the low-reward distractor was suppressed under these conditions.
+In contrast to low-reward trials, capture scores on high-reward trials were significantly greater than zero (indicating that overt attention was captured by the high-reward singleton) for both the singleton search condition, `r apa_print(Singleton_high.ttest)$statistic`, $d_z=$ `r Singleton_high.es`, and the feature search condition, `r apa_print(Feature_high.ttest)$statistic`, $d_z=$ `r Feature_high.es`.
 
-```{r blockPlot, echo=FALSE, fig.align='center', fig.cap = '(ref:blockFig)', out.width='60%', fig.pos = "!h"}
+Taken together, the data relating to first saccade direction suggest that overt attention to physically salient singletons can be suppressed below the baseline level of attention to non-salient non-targets only when participants are encouraged to adopt a specific target template (i.e., under feature search conditions), which is consistent with previous findings [e.g., @Gaspelin2016].
+The critical novel finding of the current study is that, by contrast, singletons that have been associated with relatively high reward capture overt attention, regardless of the target template that participants are encouraged to adopt, and despite such capture being directly counterproductive to earning reward.
+
+```{r blockPlot, echo=FALSE, fig.align='center', fig.cap = '(ref:blockPlot)', out.width='60%', fig.pos = "!h"}
 knitr::include_graphics(here("analysis", "figures", "capture_plot_by_block.png"), dpi = 300)
@@
 In order to investigate this in the current study, we divided the experiment into four epochs (96 trials/epoch) and calculated capture scores (as described earlier) for each trial type (see Figure \@ref(fig:blockPlot)).
-These data were analysed using an ANOVA with factors of search condition (singleton search, feature search), trial type (high, low), and epoch (1--4).
+These data were analysed using an ANOVA with factors of search condition (singleton search, feature search), trial type (high reward, low reward), and epoch (1--4).
 This once again revealed a main effect of search condition, `r apa_print.afex_aov(capture_byblock.ANOVA, mse = F, es = "pes")$full_result$condition`, and trial type, `r apa_print.afex_aov(capture_byblock.ANOVA, mse = F, es = "pes")$full_result$dType`.
@@
 There were no other significant main or interaction effects (all *p*'s $>.25$).
-Follow-up contrasts revealed a significant negative linear trend for low-reward trials, $t(369)=$ `r printnum(capture_byblock.polys$t.ratio[[4]])`, $p$ `r printp(capture_byblock.polys$p.value[[4]])`, with capture by the low-reward distractor decreasing as the experiment progressed and experience with the physically salient feature increased (notably, in the feature search condition scores become increasingly negative, indicating increasing \emph{suppression} of the low-reward distractor).
-In contrast, for high-reward trials there was a significant positive linear trend, $t(369)=$ `r printnum(capture_byblock.polys$t.ratio[[1]])`, $p=$ `r printp(capture_byblock.polys$p.value[[1]])`, with capture by the high-reward distractor increasing as the experiment progressed and experience with the reward associated feature increased.
+Follow-up contrasts revealed a significant negative linear trend for low-reward trials, $t(62)=$ `r printnum(capture_byblock.polys$t.ratio[[4]])`, $p$ `r printp(capture_byblock.polys$p.value[[4]])`, with capture by the low-reward distractor decreasing as the experiment progressed and experience with the physically salient feature increased (notably, in the feature search condition scores became increasingly negative, indicating increasing *suppression* of the low-reward distractor).
+In contrast, for high-reward trials there was a significant positive linear trend, $t(62)=$ `r printnum(capture_byblock.polys$t.ratio[[1]])`, $p=$ `r printp(capture_byblock.polys$p.value[[1]])`, with capture by the high-reward distractor increasing as the experiment progressed and experience with the reward associated feature increased.
 
@@
 ## Attentional capture/suppression effects for the fastest quartile of saccadic latencies
-To investigate the time course of the overt attentional capture and suppression effects, we analysed capture scores (proportion of first saccades towards the singleton distractor minus the average nonsingleton distractor) on high-reward and low-reward trials as a function of saccade latency using the Vincentizing procedure [@Ratcliff1979].
+To investigate the time course of the overt attentional capture and suppression effects, we analysed capture scores (proportion of first saccades towards the singleton distractor minus the average nonsingleton non-target) on high-reward and low-reward trials as a function of saccade latency using the Vincentizing procedure [@Ratcliff1979].
 We calculated mean saccade latency and capture score separately for each trial type and quartile of the individual saccade latency distributions.
@@
 
+```{r PrimingPlot, echo=FALSE, fig.align='center', fig.cap = '(ref:PrimingPlot)', out.width='80%',fig.pos = "!h"}
+knitr::include_graphics(here("analysis", "figures", "singleton_repetition_priming.png"), dpi = 300)
+
+```
+
+## Repetition priming
+Attentional suppression has also been shown to be influenced by trial-by-trial repetition priming, such that attentional capture by a salient singleton on a trial ($N$) will be reduced when the preceding trial ($N-1$) also contained a salient singleton [@Won2019].
+An exploratory analysis was conducted to investigate whether such repetition priming was influencing overt attention in the current task.
+First, we tested whether repeated experience of a salient singleton (regardless of its specific colour identity) reduced capture.
+Capture scores were entered into a 2 (trial type: high, low) $\times$ 2 (singleton repetition: repeat, no-repeat) $\times$ 2 (search condition) ANOVA.
+This revealed that trial type did not significantly interact with any other factor (all $p > .53$).
+The data were therefore collapsed across reward level (Figure \@ref(fig:PrimingPlot)) and analysed with a 2 (singleton repetition) $\times$ 2 (search condition) ANOVA, which revealed a main effect of search condition, `r apa_print.afex_aov(capture_singleton_repetition_no_dtype.ANOVA, mse = F, es = "pes")$full_result$condition`, and a main effect of singleton repetition, `r apa_print.afex_aov(capture_singleton_repetition_no_dtype.ANOVA, mse = F, es = "pes")$full_result$singleton_repetition`.
+These main effects were mediated by a singleton repetition $\times$ search condition interaction, `r apa_print.afex_aov(capture_singleton_repetition_no_dtype.ANOVA, mse = F, es = "pes")$full_result$condition_singleton_repetition`.
+Follow-up *t*-tests indicated that participants in the singleton search condition demonstrated a significant singleton repetition priming effect, `r apa_print(singleton_search_singleton_repetition.ttest)$statistic`, $d_z=$ `r singleton_search_singleton_repetition.es`, such that a salient singleton distractor was less likely to capture overt attention when the previous trial had also contained a singleton distractor (irrespective of its colour).
+However, there was moderate evidence to suggest that participants in the feature search condition did not demonstrate a repetition priming effect, with capture equivalent regardless of whether the previous trial contained a singleton `r apa_print(feature_search_singleton_repetition.ttest)$statistic`, $d_z=$ `r feature_search_singleton_repetition.es`, `r apa_print(feature_search_singleton_repetition.BF)$statistic`.
+
 # Discussion
@@
 In line with the signal suppression hypothesis [@Gaspelin2016; @Gaspelin2015], overt attention to physically salient colour singleton distractors was suppressed under conditions that promoted top-down guidance of attention.
-Specifically, under feature search conditions, participants were generally less likely to look at a (low-reward) colour singleton distractor than the average nonsingleton distractor.
-Consistent with recent findings [@Gaspelin2018b; @Vatterott2012], this attentional suppression effect gradually emerged over the course of the experiment, as participants gained experience with the salient-but-irrelevant distractor feature (Figure \@ref(fig:blockPlot)).
+Specifically, under feature search conditions, participants were generally less likely to look at a (low-reward) colour singleton distractor than the average nonsingleton non-target.
+Consistent with recent findings [@Gaspelin2018b; @Vatterott2012], this attentional suppression effect emerged gradually over the course of the experiment, as participants gained experience with the salient-but-irrelevant distractor feature (Figure \@ref(fig:blockPlot)).
 Furthermore, we observed an effect of reward association on overt attention [i.e., VMAC; @LePelley2015b; @Pearson2015], with participants' gaze more likely to be captured by distractor stimuli that signalled high reward than low reward, even though looking at reward-signalling distractors caused omission of rewards that otherwise would have been delivered.
@@
 Nevertheless, the high-reward distractor captured attention, even under conditions that allowed participants to suppress their attention to physically salient distractors that were associated with low reward.
-Our key finding, then, is that reward-related stimuli constitute especially potent attentional priority signals that are relatively immune to suppression by inhibitory control processes that can act to prevent distraction by physical salience.
+Our key finding, then, is that reward-related stimuli constitute especially potent attentional priority signals that are not only immune to volitional attentional control [e.g., @Pearson2015], but are also relatively immune to suppression by non-volitional inhibitory control processes that can act to prevent distraction by physical salience.
+This finding contrasts with the view that reward influences attentional selection (solely) by increasing the perceptual salience of reward-associated stimuli [e.g., @MacLean2015; @Serences2008; @Serences2010].
+Our findings suggest instead that the visual system gives special priority to reward-associated stimuli, potentially by enhancing associated neural activity via multiple pathways [cf.
+@Anderson2019a].
+Moreover, these findings suggest limits on the inhibitory mechanism proposed by the signal-suppression hypothesis.
+It is not the case that feature search allows individuals to suppress their attention to *all* salient stimuli---stimuli that have been imbued with *incentive salience* through their association with reward are seemingly beyond the capacity of attentional control.
+
+## Do reward and suppression compete on a common priority map?
 
@@
 The priority map concept has also been used to explain how selection history influences attentional allocation [@Awh2012; @Failing2018], with the attentional priority signal of reward-related stimulus features increasing with repeated stimulus-reward pairings through a process of associative learning [@Pearson2016; @LePelleya].
-Recent formulations of the signal suppression hypothesis have suggested that the attentional suppression mechanism may operate in a similar way, with the attentional priority of to-be-ignored stimulus features being proactively down-weighted with repeated experience [@Gaspelin2018a].
+Recent formulations of the signal suppression hypothesis have suggested that the attentional suppression mechanism may operate in a similar way, with the attentional priority of to-be-ignored stimulus features being proactively down-weighted with repeated experience [@Gaspelin2018a; see also @Won2019].
 At first glance, the results of the current study may seem inconsistent with the idea that reward and suppression engage in competition on a common priority map, as the magnitude of the VMAC effect did not differ between search conditions, even though the feature search condition should have encouraged top-down guidance of attention.
 However, there was an _overall_ decrease in the amount of capture by both the high- and low-reward distractor in the feature search condition (supported by a main effect of search condition, e.g., see Figures \@ref(fig:SaccadePlot)B and \@ref(fig:SaccadePlot)D).
-This raises the possibility that repeated experience of the physically salient stimulus features (i.e., orange and blue colour) allows the attentional priority of those features to be uniformly down-weighted by the suppression mechanism.
-In addition, our findings are consistent with the idea that repeated experience of pairings between stimulus features and reward results in selective up-weighting of the attentional priority of the high-reward distractor, such that it overpowers the influence of inhibitory suppression and thus captures attention.
+Moreover, repeated experience of the salient distractor resulted in decreased capture across both the singleton and feature search conditions (Figure \@ref(fig:blockPlot)).
+This raises the possibility that repeated experience of the physically salient stimulus features (i.e., orange and blue colour) allows the attentional priority of those features to be uniformly down-weighted by the suppression mechanism, regardless of search strategy.
+At the same time, repeated experience of pairings between stimulus features and reward results in selective up-weighting of the attentional priority of the high-reward distractor, such that it overpowers the influence of inhibitory suppression and thus captures attention across both search conditions.
 
+## Reactive vs. proactive suppression
 An inconsistency between the results of the current study and those of @Gaspelin2016 comes from the time-course of the attentional capture and suppression effects that were observed.
@@
 By contrast, in the current experiment we observed overt attentional capture in the fastest quartile of saccade latencies, with the suppression effect emerging on trials with slower saccades.
-Methodological differences between Gaspelin et al.\'s  [-@Gaspelin2016] experiment and the current study may be responsible for this discrepancy.
+Methodological differences between Gaspelin et al.'s  [-@Gaspelin2016] experiment and the current study may be responsible for this discrepancy.
 For example, the availability of reward on low-reward trials may have influenced capture, either by somewhat increasing the attentional priority of the stimulus feature associated with low reward, or by otherwise influencing participants\' motivation to respond quickly.
+Similarly, the distractors in the current task differ from those used by Gaspelin et al.
+in terms of the information value that they provide---the colour of the singleton presented on each trial informs participants about the magnitude of reward available, which may increase its attentional priority [e.g., @Foley2014; @Gottlieb2014].
 Alternatively, the discrepancy in findings may reflect our use of two potential targets (circle and diamond) in the feature search condition, as opposed to the same target on all trials in Gaspelin et al.'s procedure.
 Having two possible targets could reduce the influence of trial-by-trial upweighting of target features [@Maljkovic1994], but may also result in less effective feature search [e.g., @Houtkamp2009; but see @Grubert2015].
-Another possible explanation comes from the use of an intermixed trial structure: as participants randomly experienced trials containing either the high- or low-reward colour throughout the course of the task, it is possible that the proactive down-weighting of the salient-but-irrelevant features could not build up enough to prevent capture for the most rapidly initiated saccades [@Gaspelin2018a].
 How these methodological differences might influence the time-course of overt attentional capture and suppression remains a question for future research.
-Nonetheless, the finding does raise questions about whether the attentional suppression effect that we have observed is truly the result of proactive attentional suppression of salient stimuli, as suggested by the signal suppression hypothesis, or potentially the result of rapid covert disengagement from the salient stimuli [see @Theeuwes2010; @VanZoest2004 for similar arguments].
+Nonetheless, the finding does raise questions about whether the attentional suppression effect that we have observed is truly the result of a proactive attentional suppression mechanism, as suggested by the signal suppression hypothesis, or potentially the result of rapid covert disengagement from the salient stimuli [e.g., @Born2011; @Fukuda2011; @Geng2010; @McPeek2006; @Theeuwes2010; @VanZoest2004; for a review, see @Geng2014].
 
+## What role does feature search play in attentional suppression?
+As discussed in the preceding sections, there were certain notable similarities in the pattern of attention across both the singleton search and feature search conditions.
+For instance, in both conditions the degree of capture by the low-reward distractor decreased over the course of the experiment [as participants gained more experience with the to-be-ignored distractor feature: @Gaspelin2018b; @Vatterott2012], and as saccade latency increased [as participants had more time to enact top-down attentional control processes: @Pearson2016; @VanZoest2004].
+The key difference between the two conditions was that participants in the feature search condition were (in the aggregate) able to reduce attention to the physically salient distractor below the baseline level of attention paid to nonsalient non-targets.
+One interpretation of these findings is that feature search has a *quantitative*, rather than *qualitative*, influence on attentional suppression.
+On this account, the same processes responsible for reducing capture are at play across both search modes, but the overall rate of capture is reduced under feature search.
+However, we did find a difference between the two search modes in an exploratory analysis of repetition priming---while participants in the singleton search condition demonstrated a singleton repetition priming effect [consistent with @Won2019], those in the feature search condition did not.
+This suggests that there may be a qualitative difference between the two search modes: singleton search allows for trial-by-trial suppression of a physically salient distractor on the basis of its dissimilarity from the other stimuli in the display [i.e., *second-order salience*: @Won2019], whereas feature search relies on the suppression of a template of the specific feature value(s) that define the salient distractor (i.e.
+*first-order features*), which gradually builds up over repeated experience of the to-be-ignored stimulus [@Gaspelin2018b].
+
+While attentional suppression below baseline has typically been observed when participants are encouraged to use feature search mode, and not when they are encouraged to use singleton search mode [e.g., @Gaspelin2015; @Gaspelin2016], the role that feature search plays in allowing these below-baseline suppression effects to emerge has not been clearly defined.
+Previous research has suggested several potential mechanisms for reduced capture under feature search conditions, such as a mismatch between the distractor and the participant's attentional set [@Bacon1994], a narrower focus of attention when searching heterogeneous displays [@Theeuwes2004; @Theeuwes2010], and reduced attentional capacity under increased perceptual load [@Forster2008].
+However, none of these accounts necessarily predicts suppression of attention to salient distractors below the baseline level of attention given to non-salient distractors.
+Future research should therefore aim to more clearly delineate the role that feature search plays in allowing these below-baseline attentional suppression effects to emerge.
+
+## Conclusion
+In conclusion, the current study suggests that reward-associated stimuli have a particularly powerful influence on the attentional system, overcoming inhibitory control mechanisms that can effectively prevent capture by physically salient stimuli.
 As mentioned previously, attentional capture by stimuli associated with monetary rewards can be mapped on to the attentional biases to drug-related stimuli seen in addiction.
@@
 This is consistent with the idea of incentive salience [@Berridge1998], where the perceptual representation of an otherwise neutral stimulus is modified so as to become more salient and attention grabbing to the observer, as a result of its association with a desired outcome (e.g., drugs, money).
-The current study suggests that incentive salience has a particularly powerful influence on the attentional system, overcoming inhibitory control mechanisms that can effectively prevent capture by physically salient stimuli.
-This may have implications for the development of treatments for substance use disorders that target these attentional biases.
+Understanding the conditions under which these attentional biases can and cannot be overcome may therefore have implications for the development of treatments for substance use disorders that target these attentional biases.
 
@@
 Individual participant performance is shown by faint grey lines.
-Error bars in all figures represent within-subjects SEM [@Cousineau2005] with Morey [-@Morey2008] correction.
-*** $p<.005$, * $p<.05$.
+Error bars in all figures represent within-subjects SEM [@Morey2008].
+*** $p<.001$, * $p<.05$.
 
@@
 
-(ref:blockFig) Capture scores across five 96-trial epochs of the experiment for participants in the (A) singleton search condition and (B) feature search condition.
+(ref:blockPlot) Capture scores across five 96-trial epochs of the experiment for participants in the (A) singleton search condition and (B) feature search condition.
 Positive capture scores indicate that the singleton distractor captured attention, whereas negative capture scores indicate that attention to the singleton distractor was suppressed.
@@
 *** $p<.001$, ** $p<.01$.
+
+(ref:PrimingPlot) Repetition priming data for participants in the (A) Singleton Search condition and (B) Feature Search condition.
+Individual participant performance is shown by faint grey lines.
+Error bars represent within-subjects SEM.
+*** $p<.001$.
 

### 2019-10-28 analysis/paper/supplemental_materials.Rmd
revised submission

---
title             : "Supplementary Materials to accompany \"Overt attentional capture by reward-related stimuli overcomes inhibitory suppression\""
shorttitle        : "Supplementary Materials"

author: 
  - name          : "Daniel Pearson"
    affiliation   : "1,2"
    corresponding : yes    # Define only one corresponding author
    address       : "Institute of Cognitive Neuroscience, University College London, Gower Street, London WC1E 6BT, UK"
    email         : "daniel.pearson@ucl.ac.uk"
  - name          : "Poppy Watson"
    affiliation   : "2"
  - name          : "Phillip (Xin) Cheng"
    affiliation   : "3"
  - name          : "Mike E. Le Pelley"
    affiliation   : "2"

affiliation:
  - id            : "1"
    institution   : "Institute of Cognitive Neuroscience, University College London"
  - id            : "2"
    institution   : "School of Psychology, UNSW Sydney"
  - id            : "3"
    institution   : "Department of Cognitive Science, Macquarie University"

authornote:

abstract:

bibliography      : ["r-references.bib", "mendeley.bib"]

floatsintext      : yes
figurelist        : no
tablelist         : no
footnotelist      : no
linenumbers       : no
mask              : no
draft             : no
csl               : "american-psychological-association-6th-edition_no_first_citation.csl"
header-includes:
  - \raggedbottom

documentclass     : "apa6"
classoption       : "man, a4paper, noextraspace, 11pt"
output            : papaja::apa6_docx
nocite: |

---

```{r setup, include = FALSE}
library("papaja")
library(here)

# Source analysis_report.R (the R code from analysis_report.Rmd) to allow this document to have access to  all analyses necessary for manuscript.
source(here::here("analysis", "analysis_report.R"))

# use this to allow custom decimal places later on
op = function(x, d=2) sprintf(paste0("%1.",d,"f"), x) 
```

```{r analysis-preferences, echo=FALSE}
# Seed for random number generation
set.seed(42)
knitr::opts_chunk$set(cache.extra = knitr::rand_seed)
```

# Analysis of questionnaire data
After completing the visual search task, participants completed a brief questionnaire which assessed their knowledge of the colour--reward contingencies---i.e., which colour would be followed by high reward, and which colour would be followed by low reward; these relationships were explicitly instructed of at the start of the experiment---and of the omission contingency---i.e., that looking at either distractor would result in the omission of the reward that would otherwise be delivered; this was not explicitly instructed at the start of the experiment. For each distractor colour, participants were asked to indicate which reward value they would receive if they "quickly and accurately moving their eyes to the target" or "looked at the distractor before looking at the target" (out of the options: 0 points, 10 points, or 500 points). After making their choice, participants were asked to rate their confidence in their decision, from 1 ("Not at all confident") to 5 ("Very confident").

These data were converted into a *contingency belief score* by multiplying their confidence rating by $+1$ if they selected the correct point value, or $-1$ if they selected either of the incorrect point values. For example, if a participant responded that they would receive 500 points for quickly and accurately moving their eyes to the target when a high-reward distractor was present in the display with a confidence of 4, their reward contingency belief score for this colour would be 4. If they responded that they would receive 10 points for looking at the high-reward distractor before looking at the target with a confidence of 3, their omission contingency belief score for this colour would be $-3$.

```{r rewardContingencyPlot, echo=FALSE, fig.align='center', fig.cap = '(ref:rewardContingencyFig)', out.width='60%',fig.pos = "!h"}
knitr::include_graphics(here("analysis", "figures", "reward_contingency_plot.png"), dpi = 300)

```

Figure \@ref(fig:rewardContingencyPlot) shows scatterplots of reward contingency belief scores against capture scores (calculated as described in the main text) on high- and low-reward trials. As expected, the vast majority of participants reported the correct point values that were associated with the high- (`r reward_awareness[reward_awareness$colour=="high",]$correct`/`r reward_awareness[reward_awareness$colour=="high",]$total`) and low-reward distractors (`r reward_awareness[reward_awareness$colour=="low",]$correct`/`r reward_awareness[reward_awareness$colour=="low",]$total`). Consistent with previous findings [@Pearson2015; see also @LePelleya], there was no significant relationship between participant's awareness of the colour--reward relationships and capture---high-reward: $r =$ `r remove_lz(high_reward_awareness.cor$estimate,3)`, `r apa_print.htest(high_reward_awareness.cor)$statistic`; low-reward: $r =$ `r remove_lz(low_reward_awareness.cor$estimate,3)`, `r apa_print.htest(low_reward_awareness.cor)$statistic`.

```{r omissionContingencyPlot, echo=FALSE, fig.align='center', fig.cap = '(ref:omissionContingencyFig)', out.width='60%',fig.pos = "!h"}
knitr::include_graphics(here("analysis", "figures", "omission_contingency_plot.png"), dpi = 300)

```

Figure \@ref(fig:omissionContingencyPlot) shows scatterplots of omission contingency belief scores against capture scores on high- and low-reward trials. The majority of participants did not accurately report the omission contingency for the high (`r omission_awareness[omission_awareness$colour=="high",]$correct`/`r omission_awareness[omission_awareness$colour=="high",]$total`) and low-reward distractors (`r omission_awareness[omission_awareness$colour=="low",]$correct`/`r omission_awareness[omission_awareness$colour=="low",]$total`). There was a significant positive correlation between participant's omission contingency belief score for the high-reward distractor and the degree to which their overt attention was captured by the high-reward distractor, $r =$ `r remove_lz(high_omission_awareness.cor$estimate,3)`, `r apa_print.htest(high_omission_awareness.cor)$statistic`, such that participants who confidently believed that looking at the high-reward distractor would trigger reward omission were more likely to have their gaze captured by the high-reward distractor. There was no significant correlation between omission contingency belief scores and capture for the low-reward distractor, $r =$ `r remove_lz(low_omission_awareness.cor$estimate,3)`, `r apa_print.htest(low_omission_awareness.cor)$statistic`.

Consistent with previous research [@Pearson2015], these findings suggests that explicit awareness of the omission contingency does not allow participants to reduce the extent to which their gaze is captured by reward-associated distractors. Rather, it seems to suggest that explicit awareness of the omission contingencies counterproductively *increases* the extent to which gaze is captured by the high-reward distractor. This could be explained by an "attentional white bear" effect [@Cunningham2016; @Moher2012], where participants' attention is paradoxically drawn to items that have known non-target features. In other words, once participants learn that looking at the high-reward distractor will cause them to lose out on a high-value reward, they intentionally try to avoid looking at the high-reward distractor, which counterproductively causes them to look at the high-reward distractor more often. However, an alternative explanation is that the direction of causality is reversed---those who have had their gaze captured by the high-reward distractor more often have had more opportunity to learn about the omission contingency, and thus can report it more confidently at the end of the experiment. As the current findings are correlational in nature, we are unable to tease apart these two accounts. However, it is notable that previous research using an experimental manipulation of awareness of the omission contingency in the VMAC task found evidence to suggest that there was no difference in the size of the VMAC effect between those who were made aware of the omission contingency and those who were not made aware of the omission contingency [@Pearson2015].

(ref:rewardContingencyFig) Scatterplot of capture scores (calculated as explained in main text) against reward contingency belief scores for high-reward (left panel) and low-reward (right panel) distractors.

(ref:omissionContingencyFig) Scatterplot of capture scores against omission contingency belief scores for high-reward (left panel) and low-reward (right panel) distractors. *** $p <.001$.

\newpage
# References

### 2019-10-28 analysis/analysis_report.R

@@ -22,22 +22,26 @@ library(hrbrthemes)
 library(ggsignif)
 library(summarytools)
 
-st_options(bootstrap.css     = FALSE,       # Already part of the theme so no need for it
-           plain.ascii       = FALSE,       # One of the essential settings
-           style             = "rmarkdown", # Idem.
-           dfSummary.silent  = TRUE,        # Suppresses messages about temporary files
-           footnote          = NA,          # Keeping the results minimalistic
-           subtitle.emphasis = FALSE)       # For the vignette theme, this gives
+afex_options(emmeans_model = "multivariate")
+
+#st_options(bootstrap.css     = FALSE,       # Already part of the theme so no need for it
+#           plain.ascii       = FALSE,       # One of the essential settings
+#           style             = "rmarkdown", # Idem.
+#           dfSummary.silent  = TRUE,        # Suppresses messages about temporary files
+#           footnote          = NA,          # Keeping the results minimalistic
+#           subtitle.emphasis = FALSE)       # For the vignette theme, this gives
                                             # much better results. Your mileage may vary.
 
-st_css()
+# st_css()
 
 library(knitr)
 opts_chunk$set(comment=NA, prompt=FALSE, cache=FALSE, echo=TRUE, results='asis')
 
 source(here::here("R", "dz_calculator.r"))
+source(here::here("R", "ds_calculator.r"))
 source(here::here("R", "vmac_pal.R"))
 source(here::here("R", "summarySEwithin2.r"))
+source(here::here("R", "remove_lz.R"))
 
 vmacCols <- vmac_pal()
 my_theme <- theme_ipsum_rc(grid = F, axis_title_just = "c", axis_title_size = 14, axis_text_size = 12, strip_text_size = 14, plot_title_size = 14, subtitle_size = 14, ticks = T) +
@@ -80,7 +84,23 @@ exptdata <- filedata %>%
   map(24) %>%
   map(2) %>%
   modify(as.data.frame)
-  
+
+awaredata <- filedata %>%
+  map(27)  %>% 
+  modify(as.data.frame)
+
+index_removed_awaredata <- which(sapply(awaredata, nrow) < 4)
+
+awaredata <- awaredata[-index_removed_awaredata]
[…]

### 2020-01-31 analysis/analysis_report.rmd
simplify for Binder

@@
 library(here)
-library(patchwork)
-library(cowplot)
 library(BayesFactor)
-library(hrbrthemes)
-library(ggsignif)
-library(summarytools)
 
 afex_options(emmeans_model = "multivariate")
-
-#st_options(bootstrap.css     = FALSE,       # Already part of the theme so no need for it
-#           plain.ascii       = FALSE,       # One of the essential settings
-#           style             = "rmarkdown", # Idem.
-#           dfSummary.silent  = TRUE,        # Suppresses messages about temporary files
-#           footnote          = NA,          # Keeping the results minimalistic
-#           subtitle.emphasis = FALSE)       # For the vignette theme, this gives
-                                            # much better results. Your mileage may vary.
-
-# st_css()
 
@@
 
-vmacCols <- vmac_pal()
-my_theme <- theme_ipsum_rc(grid = F, axis_title_just = "c", axis_title_size = 14, axis_text_size = 12, strip_text_size = 14, plot_title_size = 14, subtitle_size = 14, ticks = T) +
-  theme(legend.position = "none", 
-        plot.margin = margin(.5,1,.5,1,"cm"),
-        axis.line = element_line(colour = "black", size = .5),
-        axis.ticks.x = element_blank(),
-        axis.ticks.y = element_line(colour = "black", size = .5),
-        #aspect.ratio = 1.1,
-        plot.tag = element_text(size = 20, family = font_rc),
-        axis.title = element_text(margin = margin(12,1,1,1, unit = "cm")),
-        axis.text.x = element_text(margin = margin(t = 4, unit = 'pt'), colour = 'black'),
-        axis.text.y = element_text(margin = margin(r = 4, unit = 'pt'), colour = 'black'),
-        axis.title.x = element_text(margin = margin(t = 8, unit = 'pt')),
-        axis.title.y = element_text(margin = margin(r = 8, unit = 'pt')),
-        legend.text = element_text(size = 14),
-        legend.title = element_text(size = 14))
+# These packages are required for producing the figures. Commenting out to try and simplify the project for Binder
+#library(patchwork)
+#library(cowplot)
+#
+#library(hrbrthemes)
+#library(ggsignif)
+#library(summarytools)
+
+#vmacCols <- vmac_pal()
+#my_theme <- theme_ipsum_rc(grid = F, axis_title_just = "c", axis_title_size = 14, axis_text_size = 12, strip_text_size = 14, plot_title_size = 14, subtitle_size = 14, ticks = T) +
+#  theme(legend.position = "none", 
+        # plot.margin = margin(.5,1,.5,1,"cm"),
+        # axis.line = element_line(colour = "black", size = .5),
+        # axis.ticks.x = element_blank(),
+        # axis.ticks.y = element_line(colour = "black", size = .5),
+        # #aspect.ratio = 1.1,
+        # plot.tag = element_text(size = 20, family = font_rc),
+        # axis.title = element_text(margin = margin(12,1,1,1, unit = "cm")),
+        # axis.text.x = element_text(margin = margin(t = 4, unit = 'pt'), colour = 'black'),
+        # axis.text.y = element_text(margin = margin(r = 4, unit = 'pt'), colour = 'black'),
+        # axis.title.x = element_text(margin = margin(t = 8, unit = 'pt')),
+        # axis.title.y = element_text(margin = margin(r = 8, unit = 'pt')),
+        # legend.text = element_text(size = 14),
+        # legend.title = element_text(size = 14))
 
@@
 
-This is the data set that we are left with:
-
-```{r Glimpse exptdata after exclusions}
-print(dfSummary(exptdata, style = "grid", graph.magnif = 0.75, tmp.img.dir = "/tmp"),  max.tbl.height = 300, method = "render")
-```
-
-Key for each of the variables in the table:
+<!-- This is the data set that we are left with: -->
+
+<!-- ```{r Glimpse exptdata after exclusions} -->
+<!-- print(dfSummary(exptdata, style = "grid", graph.magnif = 0.75, tmp.img.dir = "/tmp"),  max.tbl.height = 300, method = "render") -->
+<!-- ``` -->
+
+Key for each of the variables in the df:
 
@@
 
-Draw a graph of omission trials for each condition:
-
-```{r Omission Trial Graph, fig.height=10, fig.width=5.5, message=FALSE, warning=FALSE, echo=FALSE}
-omissionPlot_singleton <- exptdata %>%
-  filter(condition == "Singleton Search") %>%
-  group_by(sub, dType) %>%
-  summarise(m = mean(omissionTrial)) %>%
-  ggplot(aes(x = dType, y = m, fill = dType, shape = dType)) +
-  geom_errorbar(data = filter(exptdata_means_bycondition, condition == "Singleton Search"), aes(x = dType, y = m, ymin = m-se, ymax = m+se), colour = "black", width = .15) +
-  geom_line(aes(group = sub), colour = "black", alpha = .1, linetype = "solid", size = .5) +
-  geom_line(data = filter(exptdata_means_bycondition, condition == "Singleton Search"), aes(x = dType, y = m, group = 1), colour = "black") + 
-  geom_point(data = filter(exptdata_means_bycondition, condition == "Singleton Search"), aes(x = dType, y = m), colour = "black", size = 3) +
-  geom_signif(comparisons = list(c("High", "Low"), c("Low", "Absent")), annotations = c("***","*"), y_position = c(.61,.57), colour = "black", tip_length = 0) +
-  scale_y_continuous(labels = scales::percent_format(accuracy = 1), expand = c(0,0), limits = c(0,.8)) +
-  scale_x_discrete(labels = c("High\nreward", "Low\nreward", "Distractor\nabsent")) +
-  scale_fill_manual(values = vmacCols) +
-  scale_colour_manual(values = vmacCols) +
-  scale_shape_manual(name = "Trial Type", guide = guide_legend(), values = c(21,22,23)) +
-  labs(y = "% Reward Omissions", x = "Trial Type", tag = "A", title = "Singleton Search") +
-  my_theme
-
-omissionPlot_feature <- 
-  exptdata %>%
-  filter(condition == "Feature Search") %>%
-  group_by(sub, dType) %>%
-  summarise(m = mean(omissionTrial)) %>%
-  ggplot(aes(x = dType, y = m, fill = dType, shape = dType)) +
-  geom_line(aes(group = sub), colour = "black", alpha = .1, linetype = "solid", size = .5) +
-  geom_errorbar(data = filter(exptdata_means_bycondition, condition == "Feature Search"), aes(x = dType, y = m, ymin = m-se, ymax = m+se), colour = "black", width = .15) +
-  geom_line(data = filter(exptdata_means_bycondition, condition == "Feature Search"), aes(x = dType, y = m, group = 1), colour = "black") + 
-  geom_point(data = filter(exptdata_means_bycondition, condition == "Feature Search"), aes(x = dType, y = m), colour = "black", size = 3) +
-  geom_signif(comparisons = list(c("High", "Low"), c("Low", "Absent")), annotations = c("***","***"), y_position = c(.61,.57), colour = "black", tip_length = 0) +
-  scale_y_continuous(labels = scales::percent_format(accuracy = 1), expand = c(0,0), limits = c(0,.8)) +
-  scale_x_discrete(labels = c("High\nreward", "Low\nreward", "Distractor\nabsent")) +
-  scale_fill_manual(values = vmacCols) +
-  scale_shape_manual(name = "Distractor Type", guide = guide_legend(), values = c(21,22,23)) +
-  labs(y = "% Reward Omissions", x = "Trial Type", tag = "B", title = "Feature Search") +
-  my_theme
-
-omissionPlot_ms <- omissionPlot_singleton / omissionPlot_feature
-
-# save_plot(here::here("analysis", "figures", "omission_plot.png"), omissionPlot_ms, ncol = 1, nrow = 2, type = "cairo", base_aspect_ratio = 1.1, dpi = 300)
-
-omissionPlot_ms
-
-```
+<!-- Draw a graph of omission trials for each condition: -->
+
+<!-- ```{r Omission Trial Graph, fig.height=10, fig.width=5.5, message=FALSE, warning=FALSE, echo=FALSE} -->
+<!-- omissionPlot_singleton <- exptdata %>% -->
+<!--   filter(condition == "Singleton Search") %>% -->
+<!--   group_by(sub, dType) %>% -->
+<!--   summarise(m = mean(omissionTrial)) %>% -->
+<!--   ggplot(aes(x = dType, y = m, fill = dType, shape = dType)) + -->
+<!--   geom_errorbar(data = filter(exptdata_means_bycondition, condition == "Singleton Search"), aes(x = dType, y = m, ymin = m-se, ymax = m+se), colour = "black", width = .15) + -->
+<!--   geom_line(aes(group = sub), colour = "black", alpha = .1, linetype = "solid", size = .5) + -->
+<!--   geom_line(data = filter(exptdata_means_bycondition, condition == "Singleton Search"), aes(x = dType, y = m, group = 1), colour = "black") +  -->
+<!--   geom_point(data = filter(exptdata_means_bycondition, condition == "Singleton Search"), aes(x = dType, y = m), colour = "black", size = 3) + -->
+<!--   geom_signif(comparisons = list(c("High", "Low"), c("Low", "Absent")), annotations = c("***","*"), y_position = c(.61,.57), colour = "black", tip_length = 0) + -->
+<!--   scale_y_continuous(labels = scales::percent_format(accuracy = 1), expand = c(0,0), limits = c(0,.8)) + -->
+<!--   scale_x_discrete(labels = c("High\nreward", "Low\nreward", "Distractor\nabsent")) + -->
+<!--   scale_fill_manual(values = vmacCols) + -->
+<!--   scale_colour_manual(values = vmacCols) + -->
+<!--   scale_shape_manual(name = "Trial Type", guide = guide_legend(), values = c(21,22,23)) + -->
+<!--   labs(y = "% Reward Omissions", x = "Trial Type", tag = "A", title = "Singleton Search") + -->
+<!--   my_theme -->
+
+<!-- omissionPlot_feature <-  -->
+<!--   exptdata %>% -->
+<!--   filter(condition == "Feature Search") %>% -->
+<!--   group_by(sub, dType) %>% -->
+<!--   summarise(m = mean(omissionTrial)) %>% -->
+<!--   ggplot(aes(x = dType, y = m, fill = dType, shape = dType)) + -->
+<!--   geom_line(aes(group = sub), colour = "black", alpha = .1, linetype = "solid", size = .5) + -->
+<!--   geom_errorbar(data = filter(exptdata_means_bycondition, condition == "Feature Search"), aes(x = dType, y = m, ymin = m-se, ymax = m+se), colour = "black", width = .15) + -->
+<!--   geom_line(data = filter(exptdata_means_bycondition, condition == "Feature Search"), aes(x = dType, y = m, group = 1), colour = "black") +  -->
+<!--   geom_point(data = filter(exptdata_means_bycondition, condition == "Feature Search"), aes(x = dType, y = m), colour = "black", size = 3) + -->
+<!--   geom_signif(comparisons = list(c("High", "Low"), c("Low", "Absent")), annotations = c("***","***"), y_position = c(.61,.57), colour = "black", tip_length = 0) + -->
+<!--   scale_y_continuous(labels = scales::percent_format(accuracy = 1), expand = c(0,0), limits = c(0,.8)) + -->
+<!--   scale_x_discrete(labels = c("High\nreward", "Low\nreward", "Distractor\nabsent")) + -->
+<!--   scale_fill_manual(values = vmacCols) + -->
+<!--   scale_shape_manual(name = "Distractor Type", guide = guide_legend(), values = c(21,22,23)) + -->
+<!--   labs(y = "% Reward Omissions", x = "Trial Type", tag = "B", title = "Feature Search") + -->
+<!--   my_theme -->
+
+<!-- omissionPlot_ms <- omissionPlot_singleton / omissionPlot_feature -->
+
+<!-- # save_plot(here::here("analysis", "figures", "omission_plot.png"), omissionPlot_ms, ncol = 1, nrow = 2, type = "cairo", base_aspect_ratio = 1.1, dpi = 300) -->
+
+<!-- omissionPlot_ms -->
+
+<!-- ``` -->
 
@@
 
-```{r Glimpse saccadedata}
-print(dfSummary(saccadedata, style = "grid", graph.magnif = 0.75, tmp.img.dir = "/tmp"),  max.tbl.height = 300, method = "render")
-```
+<!-- ```{r Glimpse saccadedata} -->
+<!-- print(dfSummary(saccadedata, style = "grid", graph.magnif = 0.75, tmp.img.dir = "/tmp"),  max.tbl.height = 300, method = "render") -->
+<!-- ``` -->
 
@@
 
-Graph of the first saccade data and capture scores:
-
-```{r First Saccade Direction - Plot, echo=FALSE, fig.height=10, fig.width=10, message=FALSE, warning=FALSE}
-saccadePlot_singleton <- saccadeData_means_bycondition %>%
-  filter(condition == "Singleton Search", dType != "Absent") %>%
-  ggplot(aes(group = dType, y = proportionSaccades, fill = dType, x = stimType, shape = dType, colour = dType)) +
-  geom_line(aes(linetype = dType, colour = dType), na.rm = T, size = .5, position = position_dodge(width = .6)) +
-  geom_point(aes(group = dType, y = proportionSaccades, x = stimType), na.rm = T, size = 1.5, alpha = .3, stroke = F, data = filter(saccadePlotDataParticipants, condition == "Singleton Search", dType != "Absent"), position = position_jitterdodge(dodge.width = .6, jitter.width = .2)) +
-  geom_errorbar(aes(ymin = proportionSaccades-se, ymax = proportionSaccades+se), na.rm = T, linetype = "solid", position = position_dodge(width = .6, preserve = "total"), show.legend = FALSE, colour = "black", width = .3) +
-  geom_point(na.rm = T, size = 3, position = position_dodge(width = .6), colour = "black") +
-  scale_y_continuous(labels = scales::percent_format(accuracy = 1), expand = c(0,0), limits = c(0,.8)) +
-  scale_linetype_manual(name = "Trial Type", values = c("solid", "longdash", "dotdash"), guide = guide_legend(), labels = c("High-reward", "Low-reward")) +
-  scale_fill_manual(name = "Trial Type", values = vmacCols, labels = c("High-reward", "Low-reward")) +
-  scale_colour_manual(name = "Trial Type", values = vmacCols, labels = c("High-reward", "Low-reward")) +
-  scale_shape_manual(name = "Trial Type", guide = guide_legend(), values = c(21,22,23), labels = c("High-reward", "Low-reward")) +
-  ylab("% First Saccades") + xlab("Stimulus Type") + labs(tag = "A", title = "Singleton Search") +
-  my_theme
-
-saccadePlot_feature <- saccadeData_means_bycondition %>%
-  filter(condition == "Feature Search", dType != "Absent") %>%
-  ggplot(aes(group = dType, y = proportionSaccades, fill = dType, x = stimType, shape = dType, colour = dType)) +
-  geom_line(aes(linetype = dType, colour = dType), na.rm = T, size = .5, position = position_dodge(width = .6)) +
-  geom_point(aes(group = dType, y = proportionSaccades, x = stimType), na.rm = T, size = 1.5, alpha = .3, stroke = F, data = filter(saccadePlotDataParticipants, condition == "Feature Search", dType != "Absent"), position = position_jitterdodge(dodge.width = .6, jitter.width = .2)) +
-  geom_errorbar(aes(ymin = proportionSaccades-se, ymax = proportionSaccades+se), na.rm = T, linetype = "solid", position = position_dodge(width = .6, preserve = "total"), show.legend = FALSE, colour = "black", width = .3) +
-  geom_point(na.rm = T, size = 3, position = position_dodge(width = .6), colour = "black") +
-  scale_y_continuous(labels = scales::percent_format(accuracy = 1), expand = c(0,0), limits = c(0,.8)) +
-  scale_linetype_manual(name = "Distractor Type", values = c("solid", "longdash", "dotdash"), guide = guide_legend()) +
-  scale_fill_manual(name = "Distractor Type", values = vmacCols) +
-  scale_colour_manual(name = "Distractor Type", values = vmacCols) +
-  scale_shape_manual(name = "Distractor Type", guide = guide_legend(), values = c(21,22,23)) +
-  ylab("% First Saccades") + xlab("Stimulus Type") + labs(tag = "C", title = "Feature Search") +
-  my_theme
-
-legend_saccade <- get_legend(saccadePlot_singleton + theme(legend.position = "bottom",
-                                                           legend.title = element_text(size = 14),
-                                                           legend.text = element_text(size = 14),
-                                                           legend.key.width = unit(24, 'pt')))
-
-## Capture Bar Plots
-captureBarPlot_singleton <- captureMeans %>%
-  filter(condition == "Singleton Search") %>%
-  mutate(annotation = c("***", " ")) %>%
-  ggplot(aes(x = dType, y = Capture, fill = dType)) +
-  annotate(geom = "text", label = "Capture", x = 2.85, y = .15, angle = 90, vjust = 1, hjust = .5, family = font_rc) +
-  annotate(geom = "text", label = "Suppression", x = 2.85, y = -.15, angle = 90, vjust = 1, hjust = .5, family = font_rc) +
-  annotate(geom = "segment", x = 2.65, xend = 2.65, y = -.03, yend = -.27, arrow = arrow(type = 'closed', length = unit(6, 'pt'))) +
-  annotate(geom = "segment", x = 2.65, xend = 2.65, y = .03, yend = .27, arrow = arrow(type = 'closed', length = unit(6, 'pt'))) +
-  geom_col(position = position_dodge(.9), size = .3) +
-  geom_hline(yintercept = 0, color = "black", size = .5) +
-  geom_errorbar(aes(ymax = Capture + se, ymin = Capture - se), position = position_dodge(.9), width = .1) +
-  geom_text(aes(label = annotation), nudge_y = .05) +
-  scale_y_continuous(labels = scales::percent_format(accuracy = 1), expand = c(0,0), limits = c(-.3001, .3001)) +
-  scale_x_discrete(labels = c("High\nreward", "Low\nreward")) +
-  coord_cartesian(xlim = c(1,2),
-                  clip = 'off') +
-  scale_fill_manual(name = "Distractor Type", values = vmacCols, guide = guide_legend()) +
-  ylab("Capture Score") + xlab("Trial Type") + labs(tag = "B") +
-  my_theme
-
-captureBarPlot_feature <- 
-  captureMeans %>%
-  filter(condition == "Feature Search") %>%
-  mutate(annotation = c("***", "*")) %>%
-  ggplot(aes(x = dType, y = Capture, fill = dType)) +
-  annotate(geom = "text", label = "Capture", x = 2.85, y = .15, angle = 90, vjust = 1, hjust = .5, family = font_rc) +
-  annotate(geom = "text", label = "Suppression", x = 2.85, y = -.15, angle = 90, vjust = 1, hjust = .5, family = font_rc) +
-  annotate(geom = "segment", x = 2.65, xend = 2.65, y = -.03, yend = -.27, arrow = arrow(type = 'closed', length = unit(6, 'pt'))) +
-  annotate(geom = "segment", x = 2.65, xend = 2.65, y = .03, yend = .27, arrow = arrow(type = 'closed', length = unit(6, 'pt'))) +
-  geom_col(position = position_dodge(.9), size = .3) + 
-  geom_hline(yintercept = 0, size = .5) +
-  geom_errorbar(aes(ymax = Capture + se, ymin = Capture - se), position = position_dodge(.9), width = .1) +
-  geom_text(aes(label = annotation), nudge_y = c(.05, .07)) +
-  scale_y_continuous(labels = scales::percent_format(accuracy = 1), expand = c(0,0), limits = c(-.3001, .3001)) +
-  scale_x_discrete(labels = c("High\nreward", "Low\nreward")) +
-  coord_cartesian(xlim = c(1,2),
-                  clip = 'off') +
-  scale_fill_manual(name = "Distractor Type", values = vmacCols, guide = guide_legend()) +
-  ylab("Capture Score") + xlab("Trial Type") + labs(tag = "D") +
-  my_theme
-
-saccadePlot_ms_row1 <- saccadePlot_singleton + captureBarPlot_singleton + plot_spacer() + plot_layout(nrow = 1, widths = c(2.2,1,.1))
-
-saccadePlot_ms_row2 <- saccadePlot_feature + captureBarPlot_feature + plot_spacer() + plot_layout(nrow = 1, widths = c(2,1,.1))
-
-saccadePlot_ms <- saccadePlot_ms_row1 / legend_saccade / saccadePlot_ms_row2 + plot_layout(heights = c(1,.1,1))
-
- # save_plot(here("analysis", "figures", "saccade_plot.png"), saccadePlot_ms, ncol = 2.2, nrow = 2, type = "cairo", base_aspect_ratio = .9, dpi = 300)
-
-saccadePlot_ms
-```
+<!-- Graph of the first saccade data and capture scores: -->
+
+<!-- ```{r First Saccade Direction - Plot, echo=FALSE, fig.height=10, fig.width=10, message=FALSE, warning=FALSE} -->
+<!-- saccadePlot_singleton <- saccadeData_means_bycondition %>% -->
+<!--   filter(condition == "Singleton Search", dType != "Absent") %>% -->
+<!--   ggplot(aes(group = dType, y = proportionSaccades, fill = dType, x = stimType, shape = dType, colour = dType)) + -->
+<!--   geom_line(aes(linetype = dType, colour = dType), na.rm = T, size = .5, position = position_dodge(width = .6)) + -->
+<!--   geom_point(aes(group = dType, y = proportionSaccades, x = stimType), na.rm = T, size = 1.5, alpha = .3, stroke = F, data = filter(saccadePlotDataParticipants, condition == "Singleton Search", dType != "Absent"), position = position_jitterdodge(dodge.width = .6, jitter.width = .2)) + -->
+<!--   geom_errorbar(aes(ymin = proportionSaccades-se, ymax = proportionSaccades+se), na.rm = T, linetype = "solid", position = position_dodge(width = .6, preserve = "total"), show.legend = FALSE, colour = "black", width = .3) + -->
+<!--   geom_point(na.rm = T, size = 3, position = position_dodge(width = .6), colour = "black") + -->
+<!--   scale_y_continuous(labels = scales::percent_format(accuracy = 1), expand = c(0,0), limits = c(0,.8)) + -->
+<!--   scale_linetype_manual(name = "Trial Type", values = c("solid", "longdash", "dotdash"), guide = guide_legend(), labels = c("High-reward", "Low-reward")) + -->
+<!--   scale_fill_manual(name = "Trial Type", values = vmacCols, labels = c("High-reward", "Low-reward")) + -->
+<!--   scale_colour_manual(name = "Trial Type", values = vmacCols, labels = c("High-reward", "Low-reward")) + -->
+<!--   scale_shape_manual(name = "Trial Type", guide = guide_legend(), values = c(21,22,23), labels = c("High-reward", "Low-reward")) + -->
+<!--   ylab("% First Saccades") + xlab("Stimulus Type") + labs(tag = "A", title = "Singleton Search") + -->
+<!--   my_theme -->
+
+<!-- saccadePlot_feature <- saccadeData_means_bycondition %>% -->
+<!--   filter(condition == "Feature Search", dType != "Absent") %>% -->
+<!--   ggplot(aes(group = dType, y = proportionSaccades, fill = dType, x = stimType, shape = dType, colour = dType)) + -->
+<!--   geom_line(aes(linetype = dType, colour = dType), na.rm = T, size = .5, position = position_dodge(width = .6)) + -->
+<!--   geom_point(aes(group = dType, y = proportionSaccades, x = stimType), na.rm = T, size = 1.5, alpha = .3, stroke = F, data = filter(saccadePlotDataParticipants, condition == "Feature Search", dType != "Absent"), position = position_jitterdodge(dodge.width = .6, jitter.width = .2)) + -->
+<!--   geom_errorbar(aes(ymin = proportionSaccades-se, ymax = proportionSaccades+se), na.rm = T, linetype = "solid", position = position_dodge(width = .6, preserve = "total"), show.legend = FALSE, colour = "black", width = .3) + -->
+<!--   geom_point(na.rm = T, size = 3, position = position_dodge(width = .6), colour = "black") + -->
+<!--   scale_y_continuous(labels = scales::percent_format(accuracy = 1), expand = c(0,0), limits = c(0,.8)) + -->
+<!--   scale_linetype_manual(name = "Distractor Type", values = c("solid", "longdash", "dotdash"), guide = guide_legend()) + -->
+<!--   scale_fill_manual(name = "Distractor Type", values = vmacCols) + -->
+<!--   scale_colour_manual(name = "Distractor Type", values = vmacCols) + -->
+<!--   scale_shape_manual(name = "Distractor Type", guide = guide_legend(), values = c(21,22,23)) + -->
+<!--   ylab("% First Saccades") + xlab("Stimulus Type") + labs(tag = "C", title = "Feature Search") + -->
+<!--   my_theme -->
+
+<!-- legend_saccade <- get_legend(saccadePlot_singleton + theme(legend.position = "bottom", -->
+<!--                                                            legend.title = element_text(size = 14), -->
+<!--                                                            legend.text = element_text(size = 14), -->
+<!--                                                            legend.key.width = unit(24, 'pt'))) -->
+
+<!-- ## Capture Bar Plots -->
+<!-- captureBarPlot_singleton <- captureMeans %>% -->
+<!--   filter(condition == "Singleton Search") %>% -->
+<!--   mutate(annotation = c("***", " ")) %>% -->
+<!--   ggplot(aes(x = dType, y = Capture, fill = dType)) + -->
+<!--   annotate(geom = "text", label = "Capture", x = 2.85, y = .15, angle = 90, vjust = 1, hjust = .5, family = font_rc) + -->
+<!--   annotate(geom = "text", label = "Suppression", x = 2.85, y = -.15, angle = 90, vjust = 1, hjust = .5, family = font_rc) + -->
+<!--   annotate(geom = "segment", x = 2.65, xend = 2.65, y = -.03, yend = -.27, arrow = arrow(type = 'closed', length = unit(6, 'pt'))) + -->
+<!--   annotate(geom = "segment", x = 2.65, xend = 2.65, y = .03, yend = .27, arrow = arrow(type = 'closed', length = unit(6, 'pt'))) + -->
+<!--   geom_col(position = position_dodge(.9), size = .3) + -->
+<!--   geom_hline(yintercept = 0, color = "black", size = .5) + -->
+<!--   geom_errorbar(aes(ymax = Capture + se, ymin = Capture - se), position = position_dodge(.9), width = .1) + -->
+<!--   geom_text(aes(label = annotation), nudge_y = .05) + -->
+<!--   scale_y_continuous(labels = scales::percent_format(accuracy = 1), expand = c(0,0), limits = c(-.3001, .3001)) + -->
+<!--   scale_x_discrete(labels = c("High\nreward", "Low\nreward")) + -->
+<!--   coord_cartesian(xlim = c(1,2), -->
+<!--                   clip = 'off') + -->
+<!--   scale_fill_manual(name = "Distractor Type", values = vmacCols, guide = guide_legend()) + -->
+<!--   ylab("Capture Score") + xlab("Trial Type") + labs(tag = "B") + -->
+<!--   my_theme  -->
+
+<!-- captureBarPlot_feature <-  -->
+<!--   captureMeans %>% -->
+<!--   filter(condition == "Feature Search") %>% -->
+<!--   mutate(annotation = c("***", "*")) %>% -->
+<!--   ggplot(aes(x = dType, y = Capture, fill = dType)) + -->
+<!--   annotate(geom = "text", label = "Capture", x = 2.85, y = .15, angle = 90, vjust = 1, hjust = .5, family = font_rc) + -->
+<!--   annotate(geom = "text", label = "Suppression", x = 2.85, y = -.15, angle = 90, vjust = 1, hjust = .5, family = font_rc) + -->
+<!--   annotate(geom = "segment", x = 2.65, xend = 2.65, y = -.03, yend = -.27, arrow = arrow(type = 'closed', length = unit(6, 'pt'))) + -->
+<!--   annotate(geom = "segment", x = 2.65, xend = 2.65, y = .03, yend = .27, arrow = arrow(type = 'closed', length = unit(6, 'pt'))) + -->
+<!--   geom_col(position = position_dodge(.9), size = .3) +  -->
+<!--   geom_hline(yintercept = 0, size = .5) + -->
+<!--   geom_errorbar(aes(ymax = Capture + se, ymin = Capture - se), position = position_dodge(.9), width = .1) + -->
+<!--   geom_text(aes(label = annotation), nudge_y = c(.05, .07)) + -->
+<!--   scale_y_continuous(labels = scales::percent_format(accuracy = 1), expand = c(0,0), limits = c(-.3001, .3001)) + -->
+<!--   scale_x_discrete(labels = c("High\nreward", "Low\nreward")) + -->
+<!--   coord_cartesian(xlim = c(1,2), -->
+<!--                   clip = 'off') + -->
+<!--   scale_fill_manual(name = "Distractor Type", values = vmacCols, guide = guide_legend()) + -->
+<!--   ylab("Capture Score") + xlab("Trial Type") + labs(tag = "D") + -->
+<!--   my_theme -->
+
+<!-- saccadePlot_ms_row1 <- saccadePlot_singleton + captureBarPlot_singleton + plot_spacer() + plot_layout(nrow = 1, widths = c(2.2,1,.1)) -->
+
+<!-- saccadePlot_ms_row2 <- saccadePlot_feature + captureBarPlot_feature + plot_spacer() + plot_layout(nrow = 1, widths = c(2,1,.1)) -->
+
+<!-- saccadePlot_ms <- saccadePlot_ms_row1 / legend_saccade / saccadePlot_ms_row2 + plot_layout(heights = c(1,.1,1)) -->
+
+<!--  # save_plot(here("analysis", "figures", "saccade_plot.png"), saccadePlot_ms, ncol = 2.2, nrow = 2, type = "cairo", base_aspect_ratio = .9, dpi = 300) -->
+
+<!-- saccadePlot_ms -->
+<!-- ``` -->
 
@@
 
-```{r Block Analysis Graph, echo=FALSE, fig.height=10, fig.width=5, message=FALSE, warning=FALSE}
-capturePlot_byblock_singleton <- 
-  capturemeans_byblock %>%
-  filter(condition == "Singleton Search") %>%
-  ggplot(aes(x = newblock, y = capture, group = dType, shape = dType, colour = dType)) +
-  #geom_rect(fill = "#D3D3D3", xmin = -Inf, xmax = Inf, ymin = -Inf, ymax = 0, alpha = .3, inherit.aes = F) +
-  geom_hline(yintercept = 0, colour = "black", size = .5, linetype = "dotted") +
-  annotate(geom = "text", label = "Capture", x = 4.7, y = .15, angle = 90, vjust = 1, hjust = .5, family = font_rc) +
-  annotate(geom = "text", label = "Suppression", x = 4.7, y = -.15, angle = 90, vjust = 1, hjust = .5, family = font_rc) +
-  annotate(geom = "segment", x = 4.5, xend = 4.5, y = -.03, yend = -.27, arrow = arrow(type = 'closed', length = unit(6, 'pt'))) +
-  annotate(geom = "segment", x = 4.5, xend = 4.5, y = .03, yend = .27, arrow = arrow(type = 'closed', length = unit(6, 'pt'))) +
-  geom_line(aes(linetype = dType), size = .5) +
-  geom_errorbar(aes(ymin = capture - se, ymax = capture + se), width = .1, colour = "black") +
-  geom_point(aes(shape = dType, fill = dType), size = 3, colour = "black") +
-  scale_shape_manual(name = "Distractor Type", guide = guide_legend(), values = c(21,22)) +
-  scale_fill_manual(name = "Distractor Type", values = vmacCols, guide = guide_legend()) +
-  scale_colour_manual(name = "Distractor Type", values = vmacCols, guide = guide_legend()) +
-  scale_y_continuous(expand = c(0,0), limits = c(-.3,.301), breaks = seq(-.3, .3, .1), labels = scales::percent_format(accuracy = 1)) +
-  scale_x_discrete() +
-  coord_cartesian(xlim = c(1,4),
-                  clip = 'off') +
-  scale_linetype_manual(name = "Distractor Type", values = c("solid", "longdash"), guide = guide_legend()) +
-  ylab("Capture Score") + xlab("Epoch (96 trials)") + labs(tag = "A", title = 'Singleton Search') +
-  my_theme
-
-capturePlot_byblock_feature <- 
-  capturemeans_byblock %>%
-  filter(condition == "Feature Search") %>%
-  ggplot(aes(x = newblock, y = capture, group = dType, shape = dType, colour = dType)) +
-  geom_hline(yintercept = 0, colour = "black", size = .5, linetype = "dotted") +
-  annotate(geom = "text", label = "Capture", x = 4.7, y = .15, angle = 90, vjust = 1, hjust = .5, family = font_rc) +
-  annotate(geom = "text", label = "Suppression", x = 4.7, y = -.15, angle = 90, vjust = 1, hjust = .5, family = font_rc) +
-  annotate(geom = "segment", x = 4.5, xend = 4.5, y = -.03, yend = -.27, arrow = arrow(type = 'closed', length = unit(6, 'pt'))) +
-  annotate(geom = "segment", x = 4.5, xend = 4.5, y = .03, yend = .27, arrow = arrow(type = 'closed', length = unit(6, 'pt'))) +
-  geom_line(aes(linetype = dType), size = .5) +
-  geom_errorbar(aes(ymin = capture - se, ymax = capture + se), width = .1, colour = "black") +
-  geom_point(aes(shape = dType, fill = dType), size = 3, colour = "black") +
-  scale_shape_manual(name = "Distractor Type", guide = guide_legend(), values = c(21,22)) +
-  scale_fill_manual(name = "Distractor Type", values = vmacCols, guide = guide_legend()) +
-  scale_colour_manual(name = "Distractor Type", values = vmacCols, guide = guide_legend()) +
-  scale_y_continuous(expand = c(0,0), limits = c(-.3,.301), breaks = seq(-.3, .3, .1), labels = scales::percent_format(accuracy = 1)) +
-  scale_x_discrete() +
-  coord_cartesian(xlim = c(1,4),
-                  clip = 'off') +
-  scale_linetype_manual(name = "Distractor Type", values = c("solid", "longdash"), guide = guide_legend()) +
-  ylab("Capture Score") + xlab("Epoch (96 trials)") + labs(tag = "B", title = 'Feature Search') +
-  my_theme
-
-capturePlot_byblock_vert <- (capturePlot_byblock_singleton + plot_spacer() + plot_layout(widths = c(1,.1))) / legend_saccade / (capturePlot_byblock_feature + plot_spacer() + plot_layout(widths = c(1,.1))) + plot_layout(heights = c(1,.1,1))
-
-capturePlot_byblock_vert
-
-# save_plot(here("analysis", "figures","capture_plot_by_block.png"), capturePlot_byblock_vert, ncol = 1, nrow = 2, type = "cairo", base_aspect_ratio = 1.1, dpi = 300)
-
-```
+<!-- ```{r Block Analysis Graph, echo=FALSE, fig.height=10, fig.width=5, message=FALSE, warning=FALSE} -->
+<!-- capturePlot_byblock_singleton <-  -->
+<!--   capturemeans_byblock %>% -->
+<!--   filter(condition == "Singleton Search") %>% -->
+<!--   ggplot(aes(x = newblock, y = capture, group = dType, shape = dType, colour = dType)) + -->
+<!--   #geom_rect(fill = "#D3D3D3", xmin = -Inf, xmax = Inf, ymin = -Inf, ymax = 0, alpha = .3, inherit.aes = F) + -->
+<!--   geom_hline(yintercept = 0, colour = "black", size = .5, linetype = "dotted") + -->
+<!--   annotate(geom = "text", label = "Capture", x = 4.7, y = .15, angle = 90, vjust = 1, hjust = .5, family = font_rc) + -->
+<!--   annotate(geom = "text", label = "Suppression", x = 4.7, y = -.15, angle = 90, vjust = 1, hjust = .5, family = font_rc) + -->
+<!--   annotate(geom = "segment", x = 4.5, xend = 4.5, y = -.03, yend = -.27, arrow = arrow(type = 'closed', length = unit(6, 'pt'))) + -->
+<!--   annotate(geom = "segment", x = 4.5, xend = 4.5, y = .03, yend = .27, arrow = arrow(type = 'closed', length = unit(6, 'pt'))) + -->
+<!--   geom_line(aes(linetype = dType), size = .5) + -->
+<!--   geom_errorbar(aes(ymin = capture - se, ymax = capture + se), width = .1, colour = "black") + -->
+<!--   geom_point(aes(shape = dType, fill = dType), size = 3, colour = "black") + -->
+<!--   scale_shape_manual(name = "Distractor Type", guide = guide_legend(), values = c(21,22)) + -->
+<!--   scale_fill_manual(name = "Distractor Type", values = vmacCols, guide = guide_legend()) + -->
+<!--   scale_colour_manual(name = "Distractor Type", values = vmacCols, guide = guide_legend()) + -->
+<!--   scale_y_continuous(expand = c(0,0), limits = c(-.3,.301), breaks = seq(-.3, .3, .1), labels = scales::percent_format(accuracy = 1)) + -->
+<!--   scale_x_discrete() + -->
+<!--   coord_cartesian(xlim = c(1,4), -->
+<!--                   clip = 'off') + -->
+<!--   scale_linetype_manual(name = "Distractor Type", values = c("solid", "longdash"), guide = guide_legend()) + -->
+<!--   ylab("Capture Score") + xlab("Epoch (96 trials)") + labs(tag = "A", title = 'Singleton Search') + -->
+<!--   my_theme -->
+
+<!-- capturePlot_byblock_feature <-  -->
+<!--   capturemeans_byblock %>% -->
+<!--   filter(condition == "Feature Search") %>% -->
+<!--   ggplot(aes(x = newblock, y = capture, group = dType, shape = dType, colour = dType)) + -->
+<!--   geom_hline(yintercept = 0, colour = "black", size = .5, linetype = "dotted") + -->
+<!--   annotate(geom = "text", label = "Capture", x = 4.7, y = .15, angle = 90, vjust = 1, hjust = .5, family = font_rc) + -->
+<!--   annotate(geom = "text", label = "Suppression", x = 4.7, y = -.15, angle = 90, vjust = 1, hjust = .5, family = font_rc) + -->
+<!--   annotate(geom = "segment", x = 4.5, xend = 4.5, y = -.03, yend = -.27, arrow = arrow(type = 'closed', length = unit(6, 'pt'))) + -->
+<!--   annotate(geom = "segment", x = 4.5, xend = 4.5, y = .03, yend = .27, arrow = arrow(type = 'closed', length = unit(6, 'pt'))) + -->
+<!--   geom_line(aes(linetype = dType), size = .5) + -->
+<!--   geom_errorbar(aes(ymin = capture - se, ymax = capture + se), width = .1, colour = "black") + -->
+<!--   geom_point(aes(shape = dType, fill = dType), size = 3, colour = "black") + -->
+<!--   scale_shape_manual(name = "Distractor Type", guide = guide_legend(), values = c(21,22)) + -->
+<!--   scale_fill_manual(name = "Distractor Type", values = vmacCols, guide = guide_legend()) + -->
+<!--   scale_colour_manual(name = "Distractor Type", values = vmacCols, guide = guide_legend()) + -->
+<!--   scale_y_continuous(expand = c(0,0), limits = c(-.3,.301), breaks = seq(-.3, .3, .1), labels = scales::percent_format(accuracy = 1)) + -->
+<!--   scale_x_discrete() + -->
+<!--   coord_cartesian(xlim = c(1,4), -->
+<!--                   clip = 'off') + -->
+<!--   scale_linetype_manual(name = "Distractor Type", values = c("solid", "longdash"), guide = guide_legend()) + -->
+<!--   ylab("Capture Score") + xlab("Epoch (96 trials)") + labs(tag = "B", title = 'Feature Search') + -->
+<!--   my_theme -->
+
+<!-- capturePlot_byblock_vert <- (capturePlot_byblock_singleton + plot_spacer() + plot_layout(widths = c(1,.1))) / legend_saccade / (capturePlot_byblock_feature + plot_spacer() + plot_layout(widths = c(1,.1))) + plot_layout(heights = c(1,.1,1)) -->
+
+<!-- capturePlot_byblock_vert -->
+
+<!-- # save_plot(here("analysis", "figures","capture_plot_by_block.png"), capturePlot_byblock_vert, ncol = 1, nrow = 2, type = "cairo", base_aspect_ratio = 1.1, dpi = 300) -->
+
+<!-- ``` -->
 
@@
 
-```{r Vincentized Analysis - Graph, echo=FALSE, warning=FALSE, fig.height=10, fig.width=5, message=FALSE}
-
-vincentized_annotations <- c("***"," "," "," ","**"," "," "," ","***"," "," "," ","***"," "," ","")
-
-vincentizedPlot_singleton <- saccade_direction_quartiles_means_bycondition %>%
-  mutate(annotations = vincentized_annotations) %>%
-  filter(condition == "Singleton Search") %>%
-  ggplot(aes(x = mean_latency, y = capture, fill = dType, linetype = dType, colour = dType)) +
-  annotate(geom = "text", label = "Capture", x = 370, y = .3, angle = 90, vjust = 1, hjust = .5, family = font_rc) +
-  annotate(geom = "text", label = "Suppression", x = 370, y = -.2, angle = 90, vjust = 1, hjust = .5, family = font_rc) +
-  annotate(geom = "segment", x = 365, xend = 365, y = -.03, yend = -.37, arrow = arrow(type = 'closed', length = unit(6, 'pt'))) +
-  annotate(geom = "segment", x = 365, xend = 365, y = .03, yend = .57, arrow = arrow(type = 'closed', length = unit(6, 'pt'))) +
-  geom_linerange(aes(ymin = capture-se.prop, ymax = capture + se.prop), colour = "black", linetype = "solid", size = .5) +
-  geom_errorbarh(aes(xmin = mean_latency-se.latency, xmax = mean_latency+se.latency, height = 0), linetype = "solid", size = .5, colour = "black") +
-  geom_line(size = .5) +
-  geom_point(aes(shape = dType, fill = dType), size = 3, colour = "black") +
-  geom_hline(yintercept = 0, colour = "black", size = .5, linetype = "dotted") +
-  geom_text(aes(label = annotations), nudge_y = .07, colour = "black") +
-  scale_fill_manual(name = "Trial Type", values = vmacCols, guide = guide_legend(), labels = c("High-reward", "Low-reward")) +
-  scale_colour_manual(name = "Trial Type", values = vmacCols, guide = guide_legend(), labels = c("High-reward", "Low-reward")) +
-  scale_y_continuous(labels = scales::percent_format(accuracy = 1), expand = c(0,0), limits = c(-.4,.621)) +
-  scale_x_continuous(expand = c(0,0), limits = c(165, 380), breaks = seq(125,375,50)) +
-  scale_shape_manual(name = "Trial Type", guide = guide_legend(), values = c(21,22), labels = c("High-reward", "Low-reward")) +
-  scale_linetype_manual(name = "Trial Type", values = c("solid", "longdash"), guide = guide_legend(), labels = c("High-reward", "Low-reward")) +
-  coord_cartesian(xlim = c(165,360),
-                  clip = 'off') +
-  ylab("Capture Score") + xlab("Saccade latency (ms)") + labs(tag = "A", title = 'Singleton Search') +
-  my_theme + theme(axis.ticks.x = element_line(colour = "black", size = .5))
-
-vincentizedPlot_feature <- 
-  saccade_direction_quartiles_means_bycondition %>%
-  mutate(annotations = vincentized_annotations) %>%
-  filter(condition == "Feature Search") %>%
-  mutate(nudge_y = c(rep(.07, 7), -.07), nudge_x = c(0,0,0,-5,0,0,0,5)) %>%
-  ggplot(aes(x = mean_latency, y = capture, fill = dType, linetype = dType, colour = dType)) +
-  annotate(geom = "text", label = "Capture", x = 370, y = .3, angle = 90, vjust = 1, hjust = .5, family = font_rc) +
-  annotate(geom = "text", label = "Suppression", x = 370, y = -.2, angle = 90, vjust = 1, hjust = .5, family = font_rc) +
-  annotate(geom = "segment", x = 365, xend = 365, y = -.03, yend = -.37, arrow = arrow(type = 'closed', length = unit(6, 'pt'))) +
-  annotate(geom = "segment", x = 365, xend = 365, y = .03, yend = .57, arrow = arrow(type = 'closed', length = unit(6, 'pt'))) +
-  geom_linerange(aes(ymin = capture-se.prop, ymax = capture + se.prop), colour = "black", linetype = "solid", size = .5) +
-  geom_errorbarh(aes(xmin = mean_latency-se.latency, xmax = mean_latency+se.latency, height = 0), linetype = "solid", size = .5, colour = "black") +
-  geom_line(size = .5) +
-  geom_point(aes(shape = dType, fill = dType), size = 3, colour = "black") +
-  geom_hline(yintercept = 0, colour = "black", size = .5, linetype = "dotted") +
-  geom_text(aes(label = annotations, y = capture + nudge_y, x = mean_latency), colour = "black") +
-  scale_fill_manual(name = "Trial Type", values = vmacCols, guide = guide_legend()) +
-  scale_colour_manual(name = "Trial Type", values = vmacCols, guide = guide_legend()) +
-  scale_y_continuous(labels = scales::percent_format(accuracy = 1), expand = c(0,0), limits = c(-.4,.621)) +
-  scale_x_continuous(expand = c(0,0), limits = c(165, 380), breaks = seq(125,375,50)) +
-  scale_linetype_manual(name = "Trial Type", values = c("solid", "longdash"), guide = guide_legend()) +
-  scale_shape_manual(name = "Trial Type", guide = guide_legend(), values = c(21,22)) +
-  coord_cartesian(xlim = c(165,360),
-                  clip = 'off') +
-  ylab("Capture Score") + xlab("Saccade latency (ms)") + labs(tag = "B", title = 'Feature Search') +
-  my_theme + theme(axis.ticks.x = element_line(colour = "black", size = .5))
-
-legend_vincentizedPlot <- get_legend(vincentizedPlot_singleton + theme(legend.position = "bottom",
-                                                                       legend.title = element_text(size = 12),
-                                                                       legend.text = element_text(size = 12),
-                                                                       legend.key.width = unit(24, 'pt')))
-
-vincentizedPlot_ms <- vincentizedPlot_singleton + plot_spacer() + legend_saccade + plot_spacer() + vincentizedPlot_feature + plot_spacer() + plot_layout(nrow = 3, ncol = 2, heights = c(1,.2,1), widths = c(1,.05))
-
-# save_plot(here("analysis","figures","vincentized_plot.png"), vincentizedPlot_ms, ncol = 1.2, nrow = 2, type = "cairo", base_aspect_ratio = 1.1, dpi = 300)
-
-vincentizedPlot_ms
-```
+<!-- ```{r Vincentized Analysis - Graph, echo=FALSE, warning=FALSE, fig.height=10, fig.width=5, message=FALSE} -->
+
+<!-- vincentized_annotations <- c("***"," "," "," ","**"," "," "," ","***"," "," "," ","***"," "," ","") -->
+
+<!-- vincentizedPlot_singleton <- saccade_direction_quartiles_means_bycondition %>% -->
+<!--   mutate(annotations = vincentized_annotations) %>% -->
+<!--   filter(condition == "Singleton Search") %>% -->
+<!--   ggplot(aes(x = mean_latency, y = capture, fill = dType, linetype = dType, colour = dType)) + -->
+<!--   annotate(geom = "text", label = "Capture", x = 370, y = .3, angle = 90, vjust = 1, hjust = .5, family = font_rc) + -->
+<!--   annotate(geom = "text", label = "Suppression", x = 370, y = -.2, angle = 90, vjust = 1, hjust = .5, family = font_rc) + -->
+<!--   annotate(geom = "segment", x = 365, xend = 365, y = -.03, yend = -.37, arrow = arrow(type = 'closed', length = unit(6, 'pt'))) + -->
+<!--   annotate(geom = "segment", x = 365, xend = 365, y = .03, yend = .57, arrow = arrow(type = 'closed', length = unit(6, 'pt'))) + -->
+<!--   geom_linerange(aes(ymin = capture-se.prop, ymax = capture + se.prop), colour = "black", linetype = "solid", size = .5) + -->
+<!--   geom_errorbarh(aes(xmin = mean_latency-se.latency, xmax = mean_latency+se.latency, height = 0), linetype = "solid", size = .5, colour = "black") + -->
+<!--   geom_line(size = .5) + -->
+<!--   geom_point(aes(shape = dType, fill = dType), size = 3, colour = "black") + -->
+<!--   geom_hline(yintercept = 0, colour = "black", size = .5, linetype = "dotted") + -->
+<!--   geom_text(aes(label = annotations), nudge_y = .07, colour = "black") + -->
+<!--   scale_fill_manual(name = "Trial Type", values = vmacCols, guide = guide_legend(), labels = c("High-reward", "Low-reward")) + -->
+<!--   scale_colour_manual(name = "Trial Type", values = vmacCols, guide = guide_legend(), labels = c("High-reward", "Low-reward")) + -->
+<!--   scale_y_continuous(labels = scales::percent_format(accuracy = 1), expand = c(0,0), limits = c(-.4,.621)) + -->
+<!--   scale_x_continuous(expand = c(0,0), limits = c(165, 380), breaks = seq(125,375,50)) + -->
+<!--   scale_shape_manual(name = "Trial Type", guide = guide_legend(), values = c(21,22), labels = c("High-reward", "Low-reward")) + -->
+<!--   scale_linetype_manual(name = "Trial Type", values = c("solid", "longdash"), guide = guide_legend(), labels = c("High-reward", "Low-reward")) + -->
+<!--   coord_cartesian(xlim = c(165,360), -->
+<!--                   clip = 'off') + -->
+<!--   ylab("Capture Score") + xlab("Saccade latency (ms)") + labs(tag = "A", title = 'Singleton Search') + -->
+<!--   my_theme + theme(axis.ticks.x = element_line(colour = "black", size = .5)) -->
+
+<!-- vincentizedPlot_feature <-  -->
+<!--   saccade_direction_quartiles_means_bycondition %>% -->
+<!--   mutate(annotations = vincentized_annotations) %>% -->
+<!--   filter(condition == "Feature Search") %>% -->
+<!--   mutate(nudge_y = c(rep(.07, 7), -.07), nudge_x = c(0,0,0,-5,0,0,0,5)) %>% -->
+<!--   ggplot(aes(x = mean_latency, y = capture, fill = dType, linetype = dType, colour = dType)) + -->
+<!--   annotate(geom = "text", label = "Capture", x = 370, y = .3, angle = 90, vjust = 1, hjust = .5, family = font_rc) + -->
+<!--   annotate(geom = "text", label = "Suppression", x = 370, y = -.2, angle = 90, vjust = 1, hjust = .5, family = font_rc) + -->
+<!--   annotate(geom = "segment", x = 365, xend = 365, y = -.03, yend = -.37, arrow = arrow(type = 'closed', length = unit(6, 'pt'))) + -->
+<!--   annotate(geom = "segment", x = 365, xend = 365, y = .03, yend = .57, arrow = arrow(type = 'closed', length = unit(6, 'pt'))) + -->
+<!--   geom_linerange(aes(ymin = capture-se.prop, ymax = capture + se.prop), colour = "black", linetype = "solid", size = .5) + -->
+<!--   geom_errorbarh(aes(xmin = mean_latency-se.latency, xmax = mean_latency+se.latency, height = 0), linetype = "solid", size = .5, colour = "black") + -->
+<!--   geom_line(size = .5) + -->
+<!--   geom_point(aes(shape = dType, fill = dType), size = 3, colour = "black") + -->
+<!--   geom_hline(yintercept = 0, colour = "black", size = .5, linetype = "dotted") + -->
+<!--   geom_text(aes(label = annotations, y = capture + nudge_y, x = mean_latency), colour = "black") + -->
+<!--   scale_fill_manual(name = "Trial Type", values = vmacCols, guide = guide_legend()) + -->
+<!--   scale_colour_manual(name = "Trial Type", values = vmacCols, guide = guide_legend()) + -->
+<!--   scale_y_continuous(labels = scales::percent_format(accuracy = 1), expand = c(0,0), limits = c(-.4,.621)) + -->
+<!--   scale_x_continuous(expand = c(0,0), limits = c(165, 380), breaks = seq(125,375,50)) + -->
+<!--   scale_linetype_manual(name = "Trial Type", values = c("solid", "longdash"), guide = guide_legend()) + -->
+<!--   scale_shape_manual(name = "Trial Type", guide = guide_legend(), values = c(21,22)) + -->
+<!--   coord_cartesian(xlim = c(165,360), -->
+<!--                   clip = 'off') + -->
+<!--   ylab("Capture Score") + xlab("Saccade latency (ms)") + labs(tag = "B", title = 'Feature Search') + -->
+<!--   my_theme + theme(axis.ticks.x = element_line(colour = "black", size = .5)) -->
+
+<!-- legend_vincentizedPlot <- get_legend(vincentizedPlot_singleton + theme(legend.position = "bottom", -->
+<!--                                                                        legend.title = element_text(size = 12), -->
+<!--                                                                        legend.text = element_text(size = 12), -->
+<!--                                                                        legend.key.width = unit(24, 'pt'))) -->
+
+<!-- vincentizedPlot_ms <- vincentizedPlot_singleton + plot_spacer() + legend_saccade + plot_spacer() + vincentizedPlot_feature + plot_spacer() + plot_layout(nrow = 3, ncol = 2, heights = c(1,.2,1), widths = c(1,.05)) -->
+
+<!-- # save_plot(here("analysis","figures","vincentized_plot.png"), vincentizedPlot_ms, ncol = 1.2, nrow = 2, type = "cairo", base_aspect_ratio = 1.1, dpi = 300) -->
+
+<!-- vincentizedPlot_ms -->
+<!-- ``` -->
 
@@
 
-```{r Repetition Priming Plots}
-
+<!-- ```{r Repetition Priming Plots} -->
+```{r}
 saccadeData_means_bysingletonrepetition <-
@@
             n = n())
-
-# capture_singleton_repetition.ANOVA <- aov_car(capture ~ singleton_repetition*condition*dType + Error(sub/singleton_repetition*dType), data = saccadeData_means_bysingletonrepetition, anova_table = list(es="pes"))
-
-#knitr::kable(nice(capture_singleton_repetition.ANOVA))
-
-capturemeans_bysingletonrepetition <- summarySEwithin2(data = saccadeData_means_bysingletonrepetition, measurevar = "capture", betweenvars = "condition", withinvars = c("singleton_repetition"), idvar = "sub", na.rm = T) %>%
-  select(-ends_with("Normed"))
-
-capturemeans_bysingletonrepetition_individual <- saccadeData_means_bysingletonrepetition %>% 
-  ungroup() %>% 
-  group_by(sub, condition, singleton_repetition) %>% 
-  select(capture) %>% 
-  summarize(m_capture = mean(capture))
-
-capturemeans_bysingletonrepetition_individual$singleton_repetition <- factor(capturemeans_bysingletonrepetition_individual$singleton_repetition)
-
-average_singleton_repetition <- saccadeData_means_bysingletonrepetition %>% 
-  ungroup() %>% 
-  group_by(singleton_repetition) %>% 
-  summarise(mean_n = mean(n))
-
-singleton_repetition_singleton_search_plot <- ggplot(data = filter(capturemeans_bysingletonrepetition, condition == "Singleton Search"), aes(x = singleton_repetition, y = capture, group = 1)) +
-  geom_path() +
-  geom_path(data = filter(capturemeans_bysingletonrepetition_individual, condition == "Singleton Search"), aes(group = sub, x = singleton_repetition, y = m_capture), alpha = .1) + 
-  geom_errorbar(aes(ymax = capture + se, ymin = capture - se), width = .1) +
-  geom_point(size = 3) + 
-  geom_hline(yintercept = 0, linetype = "dashed") +
-  geom_signif(comparisons = list(c(1,2)), annotations = "***", y_position = .3, colour = "black", tip_length = 0) +
-  labs(y = "Capture Score", x= "", tag = "A", title = "Singleton Search") +
-  #lims(y = c(-.2, .3)) +
-  scale_color_manual(values = vmacCols) +
-  scale_x_discrete(labels = c("No-repeat", "Repeat")) +
-  scale_y_continuous(labels = scales::percent_format(accuracy = 1), limits = c(-.2,.45), breaks = seq(-.2, .45, .1), expand = c(0,0)) +
-  my_theme +
-  theme(strip.text = element_text(face = "bold"))
-
-singleton_repetition_feature_search_plot <- ggplot(data = filter(capturemeans_bysingletonrepetition, condition == "Feature Search"), aes(x = singleton_repetition, y = capture, group = 1)) +
-  geom_path() +
-  geom_path(data = filter(capturemeans_bysingletonrepetition_individual, condition == "Feature Search"), aes(group = sub, x = singleton_repetition, y = m_capture), alpha = .1) + 
-  geom_errorbar(aes(ymax = capture + se, ymin = capture - se), width = .1) +
-  geom_point(size = 3) + 
-  geom_hline(yintercept = 0, linetype = "dashed") +
-  # geom_signif(comparisons = list(c(1,2)), annotations = "***", y_position = .3, colour = "black", tip_length = 0) +
-  labs(y = "Capture Score", x= "", tag = "B", title = "Feature Search") +
-  #lims(y = c(-.2, .3)) +
-  scale_color_manual(values = vmacCols) +
-  scale_x_discrete(labels = c("No-repeat", "Repeat")) +
-  scale_y_continuous(labels = scales::percent_format(accuracy = 1), limits = c(-.2,.45), breaks = seq(-.2, .45, .1), expand = c(0,0)) +
-  my_theme +
-  theme(strip.text = element_text(face = "bold"))
-
-singleton_repetition_plot_horz <- plot_grid(singleton_repetition_singleton_search_plot, singleton_repetition_feature_search_plot, align = 'vh')
-# singleton_repetition_plot_horz <- ggdraw(add_sub(singleton_repetition_plot_horz, "Singleton Repetition", fontfamily = font_rc, vpadding=grid::unit(0,"lines"), y = 6, x = 0.55, vjust = 4.5))
-
-# plot_grid(singleton_repetition_plot_horz, title, ncol = 1, rel_heights = c(1,.1))
-
-# save_plot(here::here("analysis", "figures", "singleton_repetition_priming.png"), singleton_repetition_plot_horz, type = "cairo", ncol = 1.3, nrow = 1)
-
-```
+```
+
+<!-- # capture_singleton_repetition.ANOVA <- aov_car(capture ~ singleton_repetition*condition*dType + Error(sub/singleton_repetition*dType), data = saccadeData_means_bysingletonrepetition, anova_table = list(es="pes")) -->
+
+<!-- #knitr::kable(nice(capture_singleton_repetition.ANOVA)) -->
+
+<!-- capturemeans_bysingletonrepetition <- summarySEwithin2(data = saccadeData_means_bysingletonrepetition, measurevar = "capture", betweenvars = "condition", withinvars = c("singleton_repetition"), idvar = "sub", na.rm = T) %>% -->
+<!--   select(-ends_with("Normed")) -->
+
+<!-- capturemeans_bysingletonrepetition_individual <- saccadeData_means_bysingletonrepetition %>%  -->
+<!--   ungroup() %>%  -->
+<!--   group_by(sub, condition, singleton_repetition) %>%  -->
+<!--   select(capture) %>%  -->
+<!--   summarize(m_capture = mean(capture)) -->
+
+<!-- capturemeans_bysingletonrepetition_individual$singleton_repetition <- factor(capturemeans_bysingletonrepetition_individual$singleton_repetition) -->
+
+<!-- average_singleton_repetition <- saccadeData_means_bysingletonrepetition %>%  -->
+<!--   ungroup() %>%  -->
+<!--   group_by(singleton_repetition) %>%  -->
+<!--   summarise(mean_n = mean(n)) -->
+
+<!-- singleton_repetition_singleton_search_plot <- ggplot(data = filter(capturemeans_bysingletonrepetition, condition == "Singleton Search"), aes(x = singleton_repetition, y = capture, group = 1)) + -->
+<!--   geom_path() + -->
+<!--   geom_path(data = filter(capturemeans_bysingletonrepetition_individual, condition == "Singleton Search"), aes(group = sub, x = singleton_repetition, y = m_capture), alpha = .1) +  -->
+<!--   geom_errorbar(aes(ymax = capture + se, ymin = capture - se), width = .1) + -->
+<!--   geom_point(size = 3) +  -->
+<!--   geom_hline(yintercept = 0, linetype = "dashed") + -->
+<!--   geom_signif(comparisons = list(c(1,2)), annotations = "***", y_position = .3, colour = "black", tip_length = 0) + -->
+<!--   labs(y = "Capture Score", x= "", tag = "A", title = "Singleton Search") + -->
+<!--   #lims(y = c(-.2, .3)) + -->
+<!--   scale_color_manual(values = vmacCols) + -->
+<!--   scale_x_discrete(labels = c("No-repeat", "Repeat")) + -->
+<!--   scale_y_continuous(labels = scales::percent_format(accuracy = 1), limits = c(-.2,.45), breaks = seq(-.2, .45, .1), expand = c(0,0)) + -->
+<!--   my_theme + -->
+<!--   theme(strip.text = element_text(face = "bold")) -->
+
+<!-- singleton_repetition_feature_search_plot <- ggplot(data = filter(capturemeans_bysingletonrepetition, condition == "Feature Search"), aes(x = singleton_repetition, y = capture, group = 1)) + -->
+<!--   geom_path() + -->
+<!--   geom_path(data = filter(capturemeans_bysingletonrepetition_individual, condition == "Feature Search"), aes(group = sub, x = singleton_repetition, y = m_capture), alpha = .1) +  -->
+<!--   geom_errorbar(aes(ymax = capture + se, ymin = capture - se), width = .1) + -->
+<!--   geom_point(size = 3) +  -->
+<!--   geom_hline(yintercept = 0, linetype = "dashed") + -->
+<!--   # geom_signif(comparisons = list(c(1,2)), annotations = "***", y_position = .3, colour = "black", tip_length = 0) + -->
+<!--   labs(y = "Capture Score", x= "", tag = "B", title = "Feature Search") + -->
+<!--   #lims(y = c(-.2, .3)) + -->
+<!--   scale_color_manual(values = vmacCols) + -->
+<!--   scale_x_discrete(labels = c("No-repeat", "Repeat")) + -->
+<!--   scale_y_continuous(labels = scales::percent_format(accuracy = 1), limits = c(-.2,.45), breaks = seq(-.2, .45, .1), expand = c(0,0)) + -->
+<!--   my_theme + -->
+<!--   theme(strip.text = element_text(face = "bold")) -->
+
+<!-- singleton_repetition_plot_horz <- plot_grid(singleton_repetition_singleton_search_plot, singleton_repetition_feature_search_plot, align = 'vh') -->
+<!-- # singleton_repetition_plot_horz <- ggdraw(add_sub(singleton_repetition_plot_horz, "Singleton Repetition", fontfamily = font_rc, vpadding=grid::unit(0,"lines"), y = 6, x = 0.55, vjust = 4.5)) -->
+
+<!-- # plot_grid(singleton_repetition_plot_horz, title, ncol = 1, rel_heights = c(1,.1)) -->
+
+<!-- # save_plot(here::here("analysis", "figures", "singleton_repetition_priming.png"), singleton_repetition_plot_horz, type = "cairo", ncol = 1.3, nrow = 1) -->
+
+<!-- ``` -->
 
@@
 
-high_reward_contingency_plot <- awareness_scores_totarget %>%
-  filter(dType == "High", colour == "high") %>%
-  ggplot(aes(x = belief_score, y = Capture)) +
-         geom_point(aes(shape = condition), alpha = .5, size = 3) +
-  geom_smooth(method = "lm", se = FALSE, colour = "black", size = .5) +
-  scale_y_continuous(labels = scales::percent_format(accuracy=1), limits = c(-.25, .75)) +
-  scale_shape_manual(values = c(20,4))+
-  labs(x = "Reward contingency belief score", subtitle = "High reward") +
-  annotate(x = -5, y = .70, label=paste0("r(62) = ", remove_lz(high_reward_awareness.cor$estimate, 3)), geom = "text", size = 5, family = font_rc, hjust = 0) +
-  my_theme +
-  guides(shape = guide_legend(title = "Condition", override.aes = list(alpha = 1))) +
-  theme(axis.ticks.x = element_line(),
-        legend.position = "bottom")
-
-contingency_legend <- get_legend(high_reward_contingency_plot)
-
-high_reward_contingency_plot <- high_reward_contingency_plot +
-  theme(legend.position = "none")
-
-low_reward_awareness.cor <- awareness_scores_totarget %>% 
-  filter(dType == "Low", colour == "low") %>% 
-  cor.test(~ Capture + belief_score, data = .)
-
-low_reward_contingency_plot <- awareness_scores_totarget %>%
-  filter(dType == "Low", colour == "low") %>%
-  ggplot(aes(x = belief_score, y = Capture)) +
-         geom_point(aes(shape = condition), alpha = .5, size = 3) +
-  geom_smooth(method = "lm", se = FALSE, colour = "black", size = .5) +
-  scale_y_continuous(labels = scales::percent_format(accuracy=1), limits = c(-.25, .75)) +
-  scale_shape_manual(values = c(20,4))+
-  labs(x = "Reward contingency belief score", subtitle = "Low reward") +
-  annotate(x = -5, y = .70, label=paste0("r(62) = ", remove_lz(low_reward_awareness.cor$estimate, 3)), geom = "text", size = 5, family = font_rc, hjust = 0) +
-  my_theme +
-  theme(axis.ticks.x = element_line())
-
-reward_contingency_plots <- plot_grid(high_reward_contingency_plot, low_reward_contingency_plot)
-
-reward_contingency_plots_legend <- plot_grid(reward_contingency_plots, contingency_legend, rel_heights = c(1,.1), nrow = 2)
+# high_reward_contingency_plot <- awareness_scores_totarget %>%
+#   filter(dType == "High", colour == "high") %>%
+#   ggplot(aes(x = belief_score, y = Capture)) +
+#          geom_point(aes(shape = condition), alpha = .5, size = 3) +
+#   geom_smooth(method = "lm", se = FALSE, colour = "black", size = .5) +
+#   scale_y_continuous(labels = scales::percent_format(accuracy=1), limits = c(-.25, .75)) +
+#   scale_shape_manual(values = c(20,4))+
+#   labs(x = "Reward contingency belief score", subtitle = "High reward") +
+#   annotate(x = -5, y = .70, label=paste0("r(62) = ", remove_lz(high_reward_awareness.cor$estimate, 3)), geom = "text", size = 5, family = font_rc, hjust = 0) +
+#   my_theme +
+#   guides(shape = guide_legend(title = "Condition", override.aes = list(alpha = 1))) +
+#   theme(axis.ticks.x = element_line(),
+#         legend.position = "bottom")
+# 
+# contingency_legend <- get_legend(high_reward_contingency_plot)
+# 
+# high_reward_contingency_plot <- high_reward_contingency_plot +
+#   theme(legend.position = "none")
+# 
+# low_reward_awareness.cor <- awareness_scores_totarget %>% 
+#   filter(dType == "Low", colour == "low") %>% 
+#   cor.test(~ Capture + belief_score, data = .)
+# 
+# low_reward_contingency_plot <- awareness_scores_totarget %>%
+#   filter(dType == "Low", colour == "low") %>%
+#   ggplot(aes(x = belief_score, y = Capture)) +
+#          geom_point(aes(shape = condition), alpha = .5, size = 3) +
+#   geom_smooth(method = "lm", se = FALSE, colour = "black", size = .5) +
+#   scale_y_continuous(labels = scales::percent_format(accuracy=1), limits = c(-.25, .75)) +
+#   scale_shape_manual(values = c(20,4))+
+#   labs(x = "Reward contingency belief score", subtitle = "Low reward") +
+#   annotate(x = -5, y = .70, label=paste0("r(62) = ", remove_lz(low_reward_awareness.cor$estimate, 3)), geom = "text", size = 5, family = font_rc, hjust = 0) +
+#   my_theme +
+#   theme(axis.ticks.x = element_line())
+# 
+# reward_contingency_plots <- plot_grid(high_reward_contingency_plot, low_reward_contingency_plot)
+# 
+# reward_contingency_plots_legend <- plot_grid(reward_contingency_plots, contingency_legend, rel_heights = c(1,.1), nrow = 2)
 
@@
 
-high_omission_contingency_plot <- awareness_scores %>%
-  filter(dType == "High", colour == "high") %>%
-  ggplot(aes(x = belief_score, y = Capture)) +
-         geom_point(aes(shape = condition), alpha = .5, size = 3) +
-  geom_smooth(method = "lm", se = FALSE, colour = "black", size = .5) +
-  scale_y_continuous(labels = scales::percent_format(accuracy=1), limits = c(-.25, .75)) +
-  scale_shape_manual(values = c(20,4))+
-  labs(x = "Omission contingency belief score", subtitle = "High reward") +
-  annotate(x = -5, y = .70, label=paste0("r(62) = ", remove_lz(high_omission_awareness.cor$estimate, 3), "***"), geom = "text", size = 5, family = font_rc, hjust = 0) +
-  my_theme +
-  theme(axis.ticks.x = element_line())
+# high_omission_contingency_plot <- awareness_scores %>%
+#   filter(dType == "High", colour == "high") %>%
+#   ggplot(aes(x = belief_score, y = Capture)) +
+#          geom_point(aes(shape = condition), alpha = .5, size = 3) +
+#   geom_smooth(method = "lm", se = FALSE, colour = "black", size = .5) +
+#   scale_y_continuous(labels = scales::percent_format(accuracy=1), limits = c(-.25, .75)) +
+#   scale_shape_manual(values = c(20,4))+
+#   labs(x = "Omission contingency belief score", subtitle = "High reward") +
+#   annotate(x = -5, y = .70, label=paste0("r(62) = ", remove_lz(high_omission_awareness.cor$estimate, 3), "***"), geom = "text", size = 5, family = font_rc, hjust = 0) +
+#   my_theme +
+#   theme(axis.ticks.x = element_line())
 
@@
 
-low_omission_contingency_plot <- awareness_scores %>%
-  filter(dType == "Low", colour == "low") %>%
-  ggplot(aes(x = belief_score, y = Capture)) +
-         geom_point(aes(shape = condition), alpha = .5, size = 3) +
-  geom_smooth(method = "lm", se = FALSE, linetype = "solid", colour = "black", size = .5) +
-  scale_y_continuous(labels = scales::percent_format(accuracy=1), limits = c(-.25, .75)) +
-  scale_shape_manual(values = c(20,4))+
-  labs(x = "Omission contingency belief score", subtitle = "Low reward") +
-  annotate(x = -5, y = .70, label=paste0("r(62) = ", remove_lz(low_omission_awareness.cor$estimate, 3)), geom = "text", size = 5, family = font_rc, hjust = 0) +
-  # facet_grid(~dType) +
-  my_theme +
-  theme(axis.ticks.x = element_line())
-
-omission_contingency_plots <- plot_grid(high_omission_contingency_plot, low_omission_contingency_plot)
-
-omission_contingency_plots_legend <- plot_grid(omission_contingency_plots, contingency_legend, rel_heights = c(1,.1), nrow = 2)
+# low_omission_contingency_plot <- awareness_scores %>%
+#   filter(dType == "Low", colour == "low") %>%
+#   ggplot(aes(x = belief_score, y = Capture)) +
+#          geom_point(aes(shape = condition), alpha = .5, size = 3) +
+#   geom_smooth(method = "lm", se = FALSE, linetype = "solid", colour = "black", size = .5) +
+#   scale_y_continuous(labels = scales::percent_format(accuracy=1), limits = c(-.25, .75)) +
+#   scale_shape_manual(values = c(20,4))+
+#   labs(x = "Omission contingency belief score", subtitle = "Low reward") +
+#   annotate(x = -5, y = .70, label=paste0("r(62) = ", remove_lz(low_omission_awareness.cor$estimate, 3)), geom = "text", size = 5, family = font_rc, hjust = 0) +
+#   # facet_grid(~dType) +
+#   my_theme +
+#   theme(axis.ticks.x = element_line())
+# 
+# omission_contingency_plots <- plot_grid(high_omission_contingency_plot, low_omission_contingency_plot)
+# 
+# omission_contingency_plots_legend <- plot_grid(omission_contingency_plots, contingency_legend, rel_heights = c(1,.1), nrow = 2)
 

### 2020-01-31 analysis/analysis_report.R

@@ -7,7 +7,7 @@
 #'   chunk_output_type: console
 #' ---
 #' 
-## ----setup, include=FALSE, echo=FALSE------------------------------------
+## ----setup, include=FALSE, echo=FALSE-----------------------------------------
 knitr::opts_chunk$set(echo = TRUE)
 options(knitr.duplicate.label = 'allow')
 library(tidyverse)
@@ -15,24 +15,9 @@ library(R.matlab)
 library(afex)
 library(emmeans)
 library(here)
-library(patchwork)
-library(cowplot)
 library(BayesFactor)
-library(hrbrthemes)
-library(ggsignif)
-library(summarytools)
 
 afex_options(emmeans_model = "multivariate")
-
-#st_options(bootstrap.css     = FALSE,       # Already part of the theme so no need for it
-#           plain.ascii       = FALSE,       # One of the essential settings
-#           style             = "rmarkdown", # Idem.
-#           dfSummary.silent  = TRUE,        # Suppresses messages about temporary files
-#           footnote          = NA,          # Keeping the results minimalistic
-#           subtitle.emphasis = FALSE)       # For the vignette theme, this gives
-                                            # much better results. Your mileage may vary.
-
-# st_css()
 
 library(knitr)
 opts_chunk$set(comment=NA, prompt=FALSE, cache=FALSE, echo=TRUE, results='asis')
@@ -43,28 +28,36 @@ source(here::here("R", "vmac_pal.R"))
 source(here::here("R", "summarySEwithin2.r"))
 source(here::here("R", "remove_lz.R"))
 
-vmacCols <- vmac_pal()
-my_theme <- theme_ipsum_rc(grid = F, axis_title_just = "c", axis_title_size = 14, axis_text_size = 12, strip_text_size = 14, plot_title_size = 14, subtitle_size = 14, ticks = T) +
-  theme(legend.position = "none", 
-        plot.margin = margin(.5,1,.5,1,"cm"),
-        axis.line = element_line(colour = "black", size = .5),
-        axis.ticks.x = element_blank(),
-        axis.ticks.y = element_line(colour = "black", size = .5),
-        #aspect.ratio = 1.1,
-        plot.tag = element_text(size = 20, family = font_rc),
-        axis.title = element_text(margin = margin(12,1,1,1, unit = "cm")),
-        axis.text.x = element_text(margin = margin(t = 4, unit = 'pt'), colour = 'black'),
[…]

### 2020-01-31 README.Rmd
trying to fix binder

@@
 
-[![Travis-CI Build Status](https://travis-ci.org/danielpearson90/vmacfeaturesearch.svg?branch=master)](https://travis-ci.org/danielpearson90/vmacfeaturesearch) [![Binder](https://mybinder.org/badge_logo.svg)](https://mybinder.org/v2/gh/danielpearson90/vmacfeaturesearch/master/?urlpath=rstudio)
+<!-- badges: start -->
+[![Travis-CI Build Status](https://travis-ci.org/danielpearson90/vmacfeaturesearch.svg?branch=master)](https://travis-ci.org/danielpearson90/vmacfeaturesearch) 
+[![Launch Rstudio Binder](http://mybinder.org/badge_logo.svg)](https://mybinder.org/v2/gh/danielpearson90/vmacfeaturesearch/master?urlpath=rstudio)
+<!-- badges: end -->
 

### 2020-01-31 .binder/install.R
attempt #2

@@ -1,0 +1,19 @@
+install.packages('crayon')
+install.packages('afex')
+install.packages('BayesFactor')
+install.packages('cowplot')
+install.packages('emmeans')
+install.packages('here')
+install.packages('knitr')
+install.packages('R.matlab')
+install.packages('scales')
+install.packages('tidyverse')
+install.packages('afex')
+install.packages('BayesFactor')
+install.packages('devtools')
+install.packages('rmarkdown')
+install.packages('tools')
+install.packages('bookdown')
+install.packages('crayon')
+install.packages('data.table')
+devtools::install_github('crsh/papaja')
